### 2019-07-16 Main/Begeman_iceshelf_les_project.tex
Update 2019-07-16

\documentclass[letterpaper,10pt]{report}

\usepackage{ifxetex,ifluatex} % provides way to check if document is being processed with xetex or luatex

\usepackage[colorlinks = true,
unicode=true,
linkcolor = Black,
urlcolor  = Black,
citecolor = Black,
anchorcolor = blue]{hyperref}

\usepackage[english]{babel} % language support

% --- page layout ---

\usepackage{lastpage} % allows user to refer to last page with label LastPage
\usepackage{titlesec} % options for title, headers, contents

%header
\usepackage{fancyhdr} % customize headers and footers
\pagestyle{fancy}
\fancyhf{}
\rhead{Carolyn Begeman, PALM development, Page \thepage \thinspace \thinspace of \pageref{LastPage}}
\lhead{}
\renewcommand{\headrulewidth}{0pt}

% page dimensions
\usepackage{geometry}
\geometry{letterpaper, top=0.75in, left=1in, total={6.5in,9.5in}, headheight=12pt, headsep=.1in} % topmargin=-23pt,

\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother

% set paragraph settings
\IfFileExists{parskip.sty}{%
	\usepackage{parskip}
}{% else
	\setlength{\parindent}{0pt}
	\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\setcounter{secnumdepth}{3} % set maximum depth of subsections

%\usepackage{caption}
%\captionsetup[table]{skip=8pt]}

% --- font-related packages ---

\usepackage{mathptmx} % make Times default font, with math font
\usepackage{lmodern} % load Latin Modern family of fonts
\usepackage{amssymb,amsmath} % define AMS symbol fonts
\usepackage[usenames,dvipsnames]{color} % color model

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

% use microtype if available
\IfFileExists{microtype.sty}{%
	\usepackage[]{microtype}
	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\hypersetup{
	pdfborder={0 0 0},
	breaklinks=true}
%\urlstyle{same}  % don't use monospace font for urls
%\usepackage[utf8]{inputenc} % specify input encoding, \DeclareUnicodeCharacter

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\else % if luatex or xelatex
\ifxetex
\usepackage{mathspec}
\else
\usepackage{fontspec}
\fi
\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi

% set fontsize for section and subsection
\newcommand{\secfnt}{\fontsize{12}{14}}
\titlespacing\section{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
\newcommand{\ssecfnt}{\fontsize{12}{14}}
\titlespacing\subsection{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
\renewcommand{\baselinestretch}{1}

% settings for text that designates code
\definecolor{light-gray}{gray}{0.95} 
\newcommand{\code}[1]{\texttt{#1}} %{\colorbox{light-gray}

% --- lists ---
\usepackage{enumitem,amssymb}
\newlist{todolist}{itemize}{2}
\setlist[todolist]{label=$\square$}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
	\hspace{-2.5pt}}
\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}

% --- graphics ---

\usepackage{graphicx,grffile}

% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

%\graphicspath{ {} }

%\date{} %replace date with text \date{text}

\begin{document}%\thispagestyle{empty}
\tableofcontents{}
\chapter{Motivation}

% from CK application
Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.  Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.  These critical processes are not captured by even the most advanced Earth System Models (ESMs), such as the DOE’s Energy Exascale Earth System Model (E3SM), of which LANL is a major developer. Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas. Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete. A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.

% from postdoc proposal
The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet. The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice. In turn, the Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base; accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL. One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution. Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL. This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting. A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.

% plan
I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES). Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity. During the first year of the project, I will simulate the IOBL using the MIT General Circulation Model (MITgcm) in a LES ocean configuration. An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface. I will vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates when the modeled IOBL has equilibrated.  During the second year of the project, I will implement the resulting parameterization in the Model for Prediction Across Scales Ocean (MPAS-O), the ocean component of DOE’s new Energy Exascale Earth System Model (E3SM). Using MPAS-O in idealized configurations, I will investigate the parameterization’s impact on sub-ice-shelf ocean circulation and the distribution of ice-shelf melting as compared with previous parameterizations. I will focus on the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse. Resources for this work include MPAS-O, developed at LANL, and existing allocations at a number of DOE HPC facilities (including LANL).

The proposed work, characterizing turbulence in the presence of a buoyancy flux and sloping boundary, addresses a fundamental problem in fluid dynamics. The work also has direct societal relevance because ice-ocean interactions are believed to be a major control on future sea level rise. This new parameterization for ice-shelf melting will support an ongoing effort at LANL and other national labs to accurately couple ice sheet and ocean models and will be exportable from MPAS-O to other models. Thus, in addition to significantly improving simulations of ocean circulation, Antarctic ice loss, and sea level rise in E3SM, it could provide similar advances to other Earth system modeling efforts.

%\chapter{Relevant literature}
%Put something here

\chapter{The PALM model}
    \section{Table of variables}

    \textbf{Acronyms}:
    SGS = sub-grid-scale
    TKE = turbulent kinetic energy

    \begin{tabular}{c|c}
       $e$      & SGS TKE \\
       $\theta$ & potential temperature \\
       $S$      & practical salinity
    \end{tabular}
	\section{Model overview}

	The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany). It has been applied to the simulation of atmospheric and ocean boundary layers. However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer. For this application, the key model development was the implementation of dynamic melting fluxes.

	Prognostic equations:
	Momentum conservation
	\begin{equation} \label{eq:uprog}
	\frac{\partial u_i}{\partial t} = -\frac{\partial u_i u_j}{\partial x_i}-\varepsilon_{ijk} f_j u_k + \varepsilon_{i3j} f_3 u_{g,j} - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} + g \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} - \frac{\partial}{\partial x_j}(\bar{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
	\end{equation}

	Mass conservation for incompressible flows
	\begin{equation} \label{eq:volconserv}
	\frac{\partial u_j}{\partial x_j} = 0
	\end{equation}

	Heat and salt conservation
	\begin{equation} \label{eq:ptprog}
	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i \theta''} - F_T)
	\end{equation}

	\begin{equation} \label{eq:saprog}
	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i Sa''} + F_S)
	\end{equation}

	Turbulence closure by the gradient mean approximation
	\begin{equation} \label{eq:momdiff}
	\bar{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
	\end{equation}

	\begin{equation} \label{eq:ptdiff}
	\bar{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
	\end{equation}

	Prognostic equation for SGS TKE
	\begin{equation} \label{eq:eprog}
	\frac{\partial e}{\partial t} = -u_j \frac{\partial e}{\partial x_j} - (\bar{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g}{\rho_0}\bar{u''_3 \rho''}
	\end{equation}

	modified perturbation pressure:
	\begin{equation} \label{eq:pi}
	\pi^* = p^* + \frac{2}{3}\rho_0 e
	\end{equation}
	where $p^*$ is the perturbation pressure and the turbulent kinetic energy $e$ is

	\begin{equation} \label{eq:e}
	e = \frac{1}{2}\bar{u''_i u''_i}
	\end{equation}

	\begin{equation} \label{eq:sadiff}
	\bar{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
	\end{equation}

	Eddy diffusivity of momentum
	\begin{equation} \label{eq:Km}
	K_m = c_m l \sqrt{e}
	\end{equation}

	Eddy diffusivity of heat and salt
	\begin{equation} \label{eq:Kh}
	K_h = (1+\frac{2l}{\Delta})K_m
	\end{equation}
    where
	\begin{equation} \label{eq:gridl}
	\Delta = \sqrt[3]{\Delta x \Delta y \Delta z}
	\end{equation}

	%The model enforces incompressibility with 
	%\begin{equation} \label{eq:pdiv}
	%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
	%\end{equation}

	\subsection{Sloping surface}
	We represent a sloping ice base by rotating the gravity vector while keeping the domain a rectangular prism. The ice base always slopes in the x-dimension of our domain. The sloping surface modifies buoyancy terms in the model and imposes a surface pressure gradient. The surface pressure gradient was accurate in PALM v0, but the buoyancy terms were based only on temperature rather than density. We define buoyancy based on the in-situ density, $g cos(\alpha) \rho/\rho_0$.

	Sloping surface requires cyclic boundary conditions. There are two possible approaches in the sloping surface case:
	(a) Slope offset: Choose initial conditions in which isopycnals follow isobars. When water is cycled across boundaries, apply a temperature offset determined by the slope and the initial temperature gradient. Apply a salinity offset as well (not implemented in PALM v0).
	(b) No offset: Choose initial conditions in which isopycnals are parallel to the surface. Do not apply any temperature or salinity offset to water cycled across boundaries.

	\textbf{Development}:
	PALM vslope: Analogous to slope offset in temperature field, define slope offset for salinity field.
	\begin{itemize}
		\item To do list
		\begin{todolist}
			\item Add \code{sa\_slope\_offest} to \code{advec\_s\_bc}
			\item Option to turn slope offset off, would make \code{slope\_offset}=0 in \code{init\_slope}
			\item Option to set initial temperature and salinity gradients parallel to ice base. Wouldn't need to recompute \code{pt\_init} or \code{sa\_init} in \code{init\_slope} (Same as last item?).
		\end{todolist}
	\end{itemize}

	\section{Monin-Obukhov Similarity Theory for the surface layer}
    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.

    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic). We denote this depth $z_m$.

    The friction velocity is defined following "law of the wall"
    \begin{equation}
        u_* = \kappa u_m / log(z_m/z_0)
    \end{equation}

    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
    \begin{equation}
        \zeta = \frac{f z}{\eta_* u_*}
    \end{equation}

    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
    \begin{equation}
        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
    \end{equation}
    where $L_O$ is the Monin-Obukhov length
    \begin{equation}
        L_O = \rho \frac{u_*^3}{\kappa F_{B}}
    \end{equation}

    The momentum flux, expressed in imaginary notation where real values are aligned with the x-axis and imaginary values are aligned with the y-axis:
    \begin{equation}
        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
    \end{equation}
    \begin{equation}
        u'w' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
    \end{equation}
    \begin{equation}
        v'w' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
    \end{equation}

    \section{Melt rate solution method}
	% gamma_X
	% Depends on positive melt rate and that the effect of stratification is to reduce fluxes rather than enhance fluxes as a result of buoyancy from sloping surface

	Asay-Davis Eq. 24-26
	\begin{equation}
	\rho_{sw} \gamma_T (T_b-T) = \rho_{fw} m(\frac{-L_i}{c_p})
	\end{equation}
	\begin{equation}
	\rho_{sw} \gamma_S (S_b-S) = \rho_{fw} m S_b
	\end{equation}
	\begin{equation}
	T_b = T_b^{n-1}+c_2 S_b - c_2 S_b^{n-1}
	\end{equation}

	\begin{equation}
	(\gamma_T c_2) S_b^2 + (\gamma_T(T_b^{n-1}-c_2 S_b^{n-1}-T)-\gamma_S \frac{-L_i}{c_p})S_b + \gamma_S\frac{-L_i}{c_p}S=0
	\end{equation}

	%Asay-Davis Eq. 29-30
	%\begin{equation}
	%	F_T = -c_p(\rho_{sw} \gamma_T + \rho_{fw} m)(T_b-T)
	%\end{equation}
	%$F_T > 0, m > 0, T_b-T > 0$

	%\begin{equation}
	%	F_S = -(\rho_{sw} \gamma_S + \rho_{fw} m)(S_b-S)
	%\end{equation}
	%$F_S > 0, m > 0, S_b-S < 0$

	%Substituing the melt rate equation, these equations can also be expressed as
	%\begin{equation}
	%F_T = -\rho_{sw} c_p(\gamma_T - \gamma_S \frac{S_b-S}{S_b})(T_b-T)
	%\end{equation}
	%\begin{equation}
	%F_S = -\rho_{sw} (\gamma_S - \gamma_S \frac{S_b-S}{S_b})(S_b-S)
	%\end{equation}

	\begin{equation}
	F_B = g(\beta F_S - \alpha F_T)
	\end{equation}

	%$F_T,F_S$ stored in \code{surf\_def\_h}.

	General Implementation strategy
	\begin{enumerate}
		\item Initialization: 
		a. shf, sasws are assigned (to 0), 
		b. Friction velocity is initialized (to 0?). 
		c. Define buoyancy flux from shf and sasws 
			(need to have alpha and beta at the surface)
		\item Calculate exchange velocities $\gamma_T,\gamma_S$ as described in the previous section based on shf, sasws, us at previous timestep
		\item Use 3 equations to solve for $S_b, T_b$
		\item Iterate if $S_b$ is significantly different from prior $S_b$ used to define $dT_f/dS$.
		\item Calculate heat, salt fluxes from 3 equations
		\item Iterate 2-5 if buoyancy flux is significantly different than initial buoyancy flux
		% consider calculating momentum fluxes
	\end{enumerate}

	Implementation choices to explore:
	What is the best choice for $T, S$?

	parameter choices
	$L_O$ minimum = vertical grid dimension/20
	$L_O$ maximum = vertical domain dimension * 20
	$\gamma_fr$ exchange velocity for freezing case
	$z_m$ distance from the interface for boundary layer conditions
	$c_d$ roughness coefficient
	domain size
	domain resolution

	%can argue that $L_O$ minimum and $\gamma_fr$ don't matter if for the cases we run so little of the domain is freezing that it doesn't modify mean fluxes of momentum, heat and salt

	\textbf{initial and boundary conditions}
	Cyclic horizontal boundary conditions
	Velocity:
	zero at the ice-ocean interface
	Bottom boundary: u,v consistent with horizontal pressure gradients. w=0

	Pressure:
	horizontal pressure gradients
	surface pressure (indicative of domain depth)

	Temperature:
	far-field temperature relaxed at the bottom third of the domain

	Salinity:
	far-field salinity relaxed at the bottom third of the domain
	Initial

\end{document}

### 2019-08-13 Main/Begeman_iceshelf_les_project.tex
2019-08-123

@@
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
+\providecommand{\tightitemize}{%
 	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
@@
 
-% --- lists ---
+% --- itemizes ---
 \usepackage{enumitem,amssymb}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
+\newitemize{todoitemize}{itemize}{2}
+\setitemize[todoitemize]{label=$\square$}
 \usepackage{pifont}
@@
 \usepackage{graphicx,grffile}
+\usepackage{makecell}
 
@@
 	\begin{equation} \label{eq:uprog}
-	\frac{\partial u_i}{\partial t} = -\frac{\partial u_i u_j}{\partial x_i}-\varepsilon_{ijk} f_j u_k + \varepsilon_{i3j} f_3 u_{g,j} - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} + g \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} - \frac{\partial}{\partial x_j}(\bar{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
+	\frac{\partial u_i}{\partial t} = 
+	-\frac{\partial u_i u_j}{\partial x_i}
+	-\varepsilon_{ijk} f_j u_k 
+	+ \varepsilon_{i3j} f_3 u_{g,j} 
+	- \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} 
+	+ g_3 \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} 
+	+ g_1 \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} 
+	- \frac{\partial}{\partial x_j}(\overline{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
 	\end{equation}
+
+	where \\
+	$g = g [sin \alpha,0,cos \alpha]$\\
+	$f = 2 \Omega [sin \phi sin \alpha,cos \phi,sin \phi cos \alpha]$
 
@@
 	\begin{equation} \label{eq:ptprog}
-	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i \theta''} - F_T)
+	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\overline{u''_i \theta''} - F_T)
 	\end{equation}
@@
 	\begin{equation} \label{eq:saprog}
-	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i Sa''} + F_S)
+	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\overline{u''_i Sa''} + F_S)
 	\end{equation}
@@
 	\begin{equation} \label{eq:momdiff}
-	\bar{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
+	\overline{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
 	\end{equation}
@@
 	\begin{equation} \label{eq:ptdiff}
-	\bar{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
+	\overline{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
 	\end{equation}
+
+%	Prognostic equation for Resolved TKE
+%	\begin{equation} \label{eq:eprog}
+%	\frac{\partial e}{\partial t} = 
+%	-u_j \frac{\partial e}{\partial x_j} 
+%	- (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
+%	\end{equation}
 
@@
 	\begin{equation} \label{eq:eprog}
-	\frac{\partial e}{\partial t} = -u_j \frac{\partial e}{\partial x_j} - (\bar{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g}{\rho_0}\bar{u''_3 \rho''}
+	\frac{\partial e}{\partial t} = 
+	-u_j \frac{\partial e}{\partial x_j} 
+	- (\overline{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u''_i \rho''}
 	\end{equation}
@@
 	\begin{equation} \label{eq:e}
-	e = \frac{1}{2}\bar{u''_i u''_i}
+	e = \frac{1}{2}\overline{u''_i u''_i}
 	\end{equation}
@@
 	\begin{equation} \label{eq:sadiff}
-	\bar{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
+	\overline{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
 	\end{equation}
@@
 	%\end{equation}
-
+	\newpage
 	\subsection{Sloping surface}
@@
 	\begin{itemize}
-		\item To do list
-		\begin{todolist}
+		\item To do itemize
+		\begin{todoitemize}
 			\item Add \code{sa\_slope\_offest} to \code{advec\_s\_bc}
@@
 			\item Option to set initial temperature and salinity gradients parallel to ice base. Wouldn't need to recompute \code{pt\_init} or \code{sa\_init} in \code{init\_slope} (Same as last item?).
-		\end{todolist}
+		\end{todoitemize}
 	\end{itemize}
-
+	\newpage		
 	\section{Monin-Obukhov Similarity Theory for the surface layer}
@@
 
-    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic).
+    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unreaitemizeic).
 We denote this depth $z_m$.
@@
     \end{equation}
+    \newpage
+    \section{Nondimensionalization}
+
+    \begin{equation}
+        Z = \frac{z}{h}
+    \end{equation}
+    Define domain size in terms of $Z$
+
+    \begin{equation}
+        h_{\nu} = u_*/\nu
+    \end{equation}
+
+    \begin{equation}
+        h_{BL} = u_* \eta_*/f
+    \end{equation}
+
+    \begin{equation}
+        U = \frac{u}{u_*}
+    \end{equation}
+
+    \begin{equation}
+        U = \frac{u}{u_g}
+    \end{equation}
+
+    \begin{equation}
+        u_* = (\frac{1}{\rho}\int_0^h \frac{\partial \overline{p}}{\partial x} dz)^{1/2} 
+    \end{equation}
+
+    \begin{equation}
+        u_g = - \frac{dp/dy}{\rho f}
+    \end{equation}
+
+    \begin{equation}
+        \Theta = \frac{\theta - \theta_\infty}{Q_\theta/u_*}
+    \end{equation}
+    $(\theta - \theta_\infty)$ and $Q_\theta$ are derived from output. $Q_x$ is the scalar flux at the interface
+
+    \begin{equation}
+        Q_x = \kappa_x \frac{\partial X}{\partial z}
+    \end{equation}
+
+    \newpage
 
@@
 
-	Implementation choices to explore:
-	What is the best choice for $T, S$?
-
-	parameter choices
-	$L_O$ minimum = vertical grid dimension/20
-	$L_O$ maximum = vertical domain dimension * 20
-	$\gamma_fr$ exchange velocity for freezing case
-	$z_m$ distance from the interface for boundary layer conditions
-	$c_d$ roughness coefficient
-	domain size
-	domain resolution
+	\begin{table}[htbp]%{\textwidth}
+	\caption{$\Delta z = $vertical grid dimension, $\gamma_{fr} = $exchange velocity for freezing case, $z_m = $distance from the interface for boundary layer conditions, $\Delta z_m = $averaging width for boundary layer conditions}
+	\label{table:most_prm}
+    \centering
+    \begin{tabular}{|l|l|l|}
+	\hline
+	Parameter & Optimal value & Sensitivity test outcome\\
+	\hline
+	$L_O$ minimum & $\Delta z/20$ & \makecell[l]{X\% of the domain reaches $L_O$ minimum \\ for X temperature case} \\ \hline
+	$L_O$ maximum & $20\Delta z$ & \makecell[l]{X\% of the domain reaches $L_O$ maximum \\ for X temperature case}\\ \hline
+    $\gamma_{fr}$ & $(5.7e-3) u_*$ & \makecell[l]{X\% of the domain is freezing \\ for X temperature case}\\ \hline
+    $z_m$ & max(z(min $d\theta/dz$),z(min $dS/dz$)) & not tested\\ \hline %up to 2 x boundary layer depth
+    $\Delta z_m$ & $0 - 5$ & not tested\\ \hline
+    $\Delta x_m = \Delta y_m$ & $\Delta z_m, L_x$ & not tested\\ \hline
+	$c_d$ & $(1e-3) - (5e-3)$ & not tested\\ \hline
+    \end{tabular}
+	\end{table}
 
 	%can argue that $L_O$ minimum and $\gamma_fr$ don't matter if for the cases we run so little of the domain is freezing that it doesn't modify mean fluxes of momentum, heat and salt
+	\newpage
+	\section{Initial and boundary conditions}
 
-	\textbf{initial and boundary conditions}
-	Cyclic horizontal boundary conditions
 	Velocity:
-	zero at the ice-ocean interface
-	Bottom boundary: u,v consistent with horizontal pressure gradients. w=0
+	\begin{itemize}
+	\item Cyclic horizontal boundary conditions
+	\item \textbf{u} = 0 at the ice-ocean interface
+	\item Bottom boundary: u,v consistent with horizontal pressure gradients. w=0
+	\end{itemize}
 
 	Pressure:
-	horizontal pressure gradients
-	surface pressure (indicative of domain depth)
+	\begin{itemize}
+	\item Prescribed horizontal pressure gradients
+	\item Hydrostatic initial pressure based on prescribed surface pressure and initial density profile.
+	\end{itemize}
 
 	Temperature:
-	far-field temperature relaxed at the bottom third of the domain
+	\begin{itemize}
+	    \item Cyclic horizontal boundary conditions
+	    \item far-field temperature relaxed at the bottom third of the domain
+	    \item interface temperature determined by melt rate parameterization, set to the freezing point
+	\end{itemize}
 
 	Salinity:
-	far-field salinity relaxed at the bottom third of the domain
-	Initial
+    \begin{itemize}
+	    \item Cyclic horizontal boundary conditions
+	    \item far-field salinity relaxed at the bottom third of the domain
+	    \item interface salinity determined by melt rate parameterization
+	\end{itemize}
+
+	\newpage
+
+	\section{Parameter space to explore}
 

### 2019-08-13 Main/Begeman_iceshelf_les_project.tex
diagnostics

@@
 
+diagnostics:
+
+anisotropy measures
+
+velocity anisotropy tensor (symmetric, traceless, no elements in isotropic flow):
+\begin{equation}
+	b_{i,j} = \frac{<u_i'u_j'>}{<u_k'u_k'>} - \frac{\delta_ij}{3}
+\end{equation}
+can be expressed similarly for the scalar gradient field (if you have the fluctuations along x,y,z axes)
+and the vorticity field where $\omega = \grad x u$
+
+\begin{equation}
+b_{11} = \frac{<u_1'u_1'>}{<u_2'u_2'>} 
++ \frac{<u_1'u_1'>}{<u_3'u_3'>} 
+\end{equation}
+\begin{equation}
+	b_{12} = \frac{<u_1'u_2'>}{<u_1'u_1'>} 
+	              + \frac{<u_1'u_2'>}{<u_2'u_2'>} 
+	              + \frac{<u_1'u_2'>}{<u_3'u_3'>}
+\end{equation}
+\begin{equation}
+b_{22} =  \frac{<u_1'u_1'>}{<u_2'u_2'>} 
++ \frac{<u_1'u_1'>}{<u_3'u_3'>}
+\end{equation}
+\begin{equation}
+b_{23} = \frac{<u_2'u_3'>}{<u_1'u_1'>} 
++ \frac{<u_2'u_3'>}{<u_2'u_2'>} 
++ \frac{<u_2'u_3'>}{<u_3'u_3'>}
+\end{equation}
+\begin{equation}
+b_{13} = \frac{<u_1'u_3'>}{<u_1'u_1'>} 
++ \frac{<u_1'u_3'>}{<u_2'u_2'>} 
++ \frac{<u_1'u_3'>}{<u_3'u_3'>}
+\end{equation}
+\begin{equation}
+b_{33} = \frac{<u_3'u_3'>}{<u_1'u_1'>} 
++ \frac{<u_3'u_3'>}{<u_2'u_2'>} 
+\end{equation}
+where angle brackets are a volume average
+
+code up the anisotropy tensor:
+b11 = u*2/v*2 + u*2/w*2
+b22 = v*2/u*2 + v*2/w*2
+b33 = w*2/u*2 + w*2/v*2
+b12 = u*v*/u*2 + u*v*/v*2 + u*v*/w*2
+b13 = u*w*/u*2 + u*w*/v*2 + u*w*/w*2
+b22 = v*w*/u*2 + v*w*/v*2 + v*w*/w*2
+
+look at the evolution of these through time
+and look at the depth distribution
+
 \end{document}

### 2020-08-25 A01_ice_surface_fluxes.tex
Updates to main and supplements

Momentum flux

    Components of surface stress $\tau_i$
    \begin{equation*}
    \tau_i = \rho \overline{u_i''w''}
    \end{equation*}
    for i = 1,2.

    Friction velocity $u_*$
    \begin{equation*}
    u_*^2=|\tau_0|^{1/2}
    \end{equation*}
    % \begin{equation*}
    % u_*^2=(\overline{u''w''}^2 + \overline{v''w''}^2)^{1/2}
    % \end{equation*}

    Turbulence closure
    \begin{equation*}
    \overline{u_i''w''} = k_m \frac{\partial u_i}{\partial z}
    \end{equation*}

    There is empirical support for a linear increase in eddy diffusivity from the wall
    \begin{equation*}
    u_* = \frac{k z}{\Psi_m(\zeta) } \frac{\partial u}{\partial z}
    \end{equation*}
    where $\zeta = z/L_O$

    We integrate using this relationship (or $\Psi = 1$ to get $u_*$
    \begin{equation*}
    \Psi_m(\zeta) = 1 + \beta_m \zeta
    \end{equation*}
    where $\beta_m = 4.8$ (Wyngaard 2010; Zhou et al. 2017)

    We integrate using this relationship to get $u_i''w''$
    \begin{equation*}
    \beta_m = (\frac{1}{R_c} + \frac{f L_O}{u_* \chi_N})(1-\eta_*)
    \end{equation*}
    (McPhee 1981)

    % Integrating for $u(z)$ (this is never needed because all we need is stress
    % \begin{equation*}
    % u = \frac{u_*}{k} ln(frac{z}{z_0} + \frac{\beta_m}{k}\zeta + C_m
    %\end{equation*}
    % \begin{equation*}
    % u = \frac{u_*}{k} ln(frac{z}{z_0} = c_d(z)^{\frac{-1}{2}}u_*
    % \end{equation*}
    % The friction velocity is defined following "law of the wall"
    % \begin{equation}
    %     u_* = \kappa u_m / log(z_m/z_0)
    % \end{equation}

    \begin{equation*}
    \overline{u_i''w''}(z_1) = u_* (\phi_i(\textbf{u(z_1)}))
    \end{equation*}

    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.

    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic). We denote this depth $z_m$.

    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
    \begin{equation}
        \zeta = \frac{z}{\eta_* u_*/f}
    \end{equation}

    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
    \begin{equation}
        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
    \end{equation}
    where $L_O$ is the Monin-Obukhov length
    \begin{equation}
        L_O = \rho \frac{u_*^3}{\kappa F_B}
    \end{equation}

    \begin{equation}
	F_B = g(\beta w'S' - \alpha w'\theta')
	\end{equation}

    \begin{equation}
        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
    \end{equation}
    \begin{equation}
        \phi_1 = (u_1* RE(\tau) + u_2* IM(\tau))
    \end{equation}
    \begin{equation}
        \phi_2 = (u_2* RE(\tau) + u_1* IM(\tau))
    \end{equation}

    \begin{equation}
        u''w'' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
    \end{equation}
    \begin{equation}
        v''w'' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
    \end{equation}

### 2020-08-25 A03_slope_impl_details.tex
Updates to main and supplements

--- 2019-07-16 Main/Begeman_iceshelf_les_project.tex
@@
-\documentclass[letterpaper,10pt]{report}
-
-\usepackage{ifxetex,ifluatex} % provides way to check if document is being processed with xetex or luatex
-
-\usepackage[colorlinks = true,
-unicode=true,
-linkcolor = Black,
-urlcolor  = Black,
-citecolor = Black,
-anchorcolor = blue]{hyperref}
-
-\usepackage[english]{babel} % language support
-
-% --- page layout ---
-
-\usepackage{lastpage} % allows user to refer to last page with label LastPage
-\usepackage{titlesec} % options for title, headers, contents
-
-%header
-\usepackage{fancyhdr} % customize headers and footers
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Carolyn Begeman, PALM development, Page \thepage \thinspace \thinspace of \pageref{LastPage}}
-\lhead{}
-\renewcommand{\headrulewidth}{0pt}
-
-% page dimensions
-\usepackage{geometry}
-\geometry{letterpaper, top=0.75in, left=1in, total={6.5in,9.5in}, headheight=12pt, headsep=.1in} % topmargin=-23pt,
-
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-
-% set paragraph settings
-\IfFileExists{parskip.sty}{%
-	\usepackage{parskip}
-}{% else
-	\setlength{\parindent}{0pt}
-	\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-\setcounter{secnumdepth}{3} % set maximum depth of subsections
-
-%\usepackage{caption}
-%\captionsetup[table]{skip=8pt]}
-
-% --- font-related packages ---
-
-\usepackage{mathptmx} % make Times default font, with math font
-\usepackage{lmodern} % load Latin Modern family of fonts
-\usepackage{amssymb,amsmath} % define AMS symbol fonts
-\usepackage[usenames,dvipsnames]{color} % color model
-
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-	\usepackage[]{microtype}
-	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\hypersetup{
-	pdfborder={0 0 0},
-	breaklinks=true}
-%\urlstyle{same}  % don't use monospace font for urls
-%\usepackage[utf8]{inputenc} % specify input encoding, \DeclareUnicodeCharacter
-
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-\ifxetex
-\usepackage{mathspec}
-\else
-\usepackage{fontspec}
-\fi
-\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-
-% set fontsize for section and subsection
-\newcommand{\secfnt}{\fontsize{12}{14}}
-\titlespacing\section{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newcommand{\ssecfnt}{\fontsize{12}{14}}
-\titlespacing\subsection{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
-\renewcommand{\baselinestretch}{1}
-
-% settings for text that designates code
-\definecolor{light-gray}{gray}{0.95} 
-\newcommand{\code}[1]{\texttt{#1}} %{\colorbox{light-gray}
-
-% --- lists ---
-\usepackage{enumitem,amssymb}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
-\usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}%
-\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
-	\hspace{-2.5pt}}
-\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}
-
-% --- graphics ---
-
-\usepackage{graphicx,grffile}
-
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-%\graphicspath{ {} }
-
-%\date{} %replace date with text \date{text}
-
-\begin{document}%\thispagestyle{empty}
-\tableofcontents{}
-\chapter{Motivation}
-
-% from CK application
-Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
-Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.
-These critical processes are not captured by even the most advanced Earth System Models (ESMs), such as the DOE’s Energy Exascale Earth System Model (E3SM), of which LANL is a major developer.
-Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
-Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete.
-A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.
-
-% from postdoc proposal
-The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet.
-The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice.
-In turn, the Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base; accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
-One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution.
-Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL.
-This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting.
-A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.
-
-% plan
-I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
-Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
-During the first year of the project, I will simulate the IOBL using the MIT General Circulation Model (MITgcm) in a LES ocean configuration.
-An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface.
-I will vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates when the modeled IOBL has equilibrated.
-During the second year of the project, I will implement the resulting parameterization in the Model for Prediction Across Scales Ocean (MPAS-O), the ocean component of DOE’s new Energy Exascale Earth System Model (E3SM).
-Using MPAS-O in idealized configurations, I will investigate the parameterization’s impact on sub-ice-shelf ocean circulation and the distribution of ice-shelf melting as compared with previous parameterizations.
-I will focus on the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
-Resources for this work include MPAS-O, developed at LANL, and existing allocations at a number of DOE HPC facilities (including LANL).
-
-The proposed work, characterizing turbulence in the presence of a buoyancy flux and sloping boundary, addresses a fundamental problem in fluid dynamics.
-The work also has direct societal relevance because ice-ocean interactions are believed to be a major control on future sea level rise.
-This new parameterization for ice-shelf melting will support an ongoing effort at LANL and other national labs to accurately couple ice sheet and ocean models and will be exportable from MPAS-O to other models.
-Thus, in addition to significantly improving simulations of ocean circulation, Antarctic ice loss, and sea level rise in E3SM, it could provide similar advances to other Earth system modeling efforts.
-
-%\chapter{Relevant literature}
-%Put something here
-
-\chapter{The PALM model}
-    \section{Table of variables}
-
-    \textbf{Acronyms}:
-    SGS = sub-grid-scale
-    TKE = turbulent kinetic energy
-
-    \begin{tabular}{c|c}
-       $e$      & SGS TKE \\
-       $\theta$ & potential temperature \\
-       $S$      & practical salinity
-    \end{tabular}
-	\section{Model overview}
-
-	The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany).
-It has been applied to the simulation of atmospheric and ocean boundary layers.
-However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
-For this application, the key model development was the implementation of dynamic melting fluxes.
-
-	Prognostic equations:
-	Momentum conservation
-	\begin{equation} \label{eq:uprog}
-	\frac{\partial u_i}{\partial t} = -\frac{\partial u_i u_j}{\partial x_i}-\varepsilon_{ijk} f_j u_k + \varepsilon_{i3j} f_3 u_{g,j} - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} + g \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} - \frac{\partial}{\partial x_j}(\bar{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
-	\end{equation}
-
-	Mass conservation for incompressible flows
-	\begin{equation} \label{eq:volconserv}
-	\frac{\partial u_j}{\partial x_j} = 0
-	\end{equation}
-
-	Heat and salt conservation
-	\begin{equation} \label{eq:ptprog}
-	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i \theta''} - F_T)
-	\end{equation}
-
-	\begin{equation} \label{eq:saprog}
-	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i Sa''} + F_S)
-	\end{equation}
-
-	Turbulence closure by the gradient mean approximation
-	\begin{equation} \label{eq:momdiff}
-	\bar{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
-	\end{equation}
-
-	\begin{equation} \label{eq:ptdiff}
-	\bar{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
-	\end{equation}
-
-	Prognostic equation for SGS TKE
-	\begin{equation} \label{eq:eprog}
-	\frac{\partial e}{\partial t} = -u_j \frac{\partial e}{\partial x_j} - (\bar{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g}{\rho_0}\bar{u''_3 \rho''}
-	\end{equation}
-
-	modified perturbation pressure:
-	\begin{equation} \label{eq:pi}
-	\pi^* = p^* + \frac{2}{3}\rho_0 e
-	\end{equation}
-	where $p^*$ is the perturbation pressure and the turbulent kinetic energy $e$ is
-
-	\begin{equation} \label{eq:e}
-	e = \frac{1}{2}\bar{u''_i u''_i}
-	\end{equation}
-
-	\begin{equation} \label{eq:sadiff}
-	\bar{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
-	\end{equation}
-
-	Eddy diffusivity of momentum
-	\begin{equation} \label{eq:Km}
-	K_m = c_m l \sqrt{e}
-	\end{equation}
-
-	Eddy diffusivity of heat and salt
-	\begin{equation} \label{eq:Kh}
-	K_h = (1+\frac{2l}{\Delta})K_m
-	\end{equation}
-    where
-	\begin{equation} \label{eq:gridl}
-	\Delta = \sqrt[3]{\Delta x \Delta y \Delta z}
-	\end{equation}
-
-	%The model enforces incompressibility with 
-	%\begin{equation} \label{eq:pdiv}
-	%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
-	%\end{equation}
-
-	\subsection{Sloping surface}
-	We represent a sloping ice base by rotating the gravity vector while keeping the domain a rectangular prism.
-The ice base always slopes in the x-dimension of our domain.
-The sloping surface modifies buoyancy terms in the model and imposes a surface pressure gradient.
-The surface pressure gradient was accurate in PALM v0, but the buoyancy terms were based only on temperature rather than density.
-We define buoyancy based on the in-situ density, $g cos(\alpha) \rho/\rho_0$.
-
+% appendix 
+% considerations for cyclic boundary conditions
 Sloping surface requires cyclic boundary conditions. There are two possible approaches in the sloping surface case:
@@
 (b) No offset: Choose initial conditions in which isopycnals are parallel to the surface. Do not apply any temperature or salinity offset to water cycled across boundaries.
-
-	\textbf{Development}:
-	PALM vslope: Analogous to slope offset in temperature field, define slope offset for salinity field.
-	\begin{itemize}
-		\item To do list
-		\begin{todolist}
-			\item Add \code{sa\_slope\_offest} to \code{advec\_s\_bc}
-			\item Option to turn slope offset off, would make \code{slope\_offset}=0 in \code{init\_slope}
-			\item Option to set initial temperature and salinity gradients parallel to ice base. Wouldn't need to recompute \code{pt\_init} or \code{sa\_init} in \code{init\_slope} (Same as last item?).
-		\end{todolist}
-	\end{itemize}
-
-	\section{Monin-Obukhov Similarity Theory for the surface layer}
-    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.
-
-    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic).
-We denote this depth $z_m$.
-
-    The friction velocity is defined following "law of the wall"
-    \begin{equation}
-        u_* = \kappa u_m / log(z_m/z_0)
-    \end{equation}
-
-    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
-    \begin{equation}
-        \zeta = \frac{f z}{\eta_* u_*}
-    \end{equation}
-
-    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
-    \begin{equation}
-        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
-    \end{equation}
-    where $L_O$ is the Monin-Obukhov length
-    \begin{equation}
-        L_O = \rho \frac{u_*^3}{\kappa F_{B}}
-    \end{equation}
-
-    The momentum flux, expressed in imaginary notation where real values are aligned with the x-axis and imaginary values are aligned with the y-axis:
-    \begin{equation}
-        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
-    \end{equation}
-    \begin{equation}
-        u'w' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
-    \end{equation}
-    \begin{equation}
-        v'w' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
-    \end{equation}
-
-    \section{Melt rate solution method}
-	% gamma_X
-	% Depends on positive melt rate and that the effect of stratification is to reduce fluxes rather than enhance fluxes as a result of buoyancy from sloping surface
-
-	Asay-Davis Eq. 24-26
-	\begin{equation}
-	\rho_{sw} \gamma_T (T_b-T) = \rho_{fw} m(\frac{-L_i}{c_p})
-	\end{equation}
-	\begin{equation}
-	\rho_{sw} \gamma_S (S_b-S) = \rho_{fw} m S_b
-	\end{equation}
-	\begin{equation}
-	T_b = T_b^{n-1}+c_2 S_b - c_2 S_b^{n-1}
-	\end{equation}
-
-	\begin{equation}
-	(\gamma_T c_2) S_b^2 + (\gamma_T(T_b^{n-1}-c_2 S_b^{n-1}-T)-\gamma_S \frac{-L_i}{c_p})S_b + \gamma_S\frac{-L_i}{c_p}S=0
-	\end{equation}
-
-	%Asay-Davis Eq. 29-30
-	%\begin{equation}
-	%	F_T = -c_p(\rho_{sw} \gamma_T + \rho_{fw} m)(T_b-T)
-	%\end{equation}
-	%$F_T > 0, m > 0, T_b-T > 0$
-
-	%\begin{equation}
-	%	F_S = -(\rho_{sw} \gamma_S + \rho_{fw} m)(S_b-S)
-	%\end{equation}
-	%$F_S > 0, m > 0, S_b-S < 0$
-
-	%Substituing the melt rate equation, these equations can also be expressed as
-	%\begin{equation}
-	%F_T = -\rho_{sw} c_p(\gamma_T - \gamma_S \frac{S_b-S}{S_b})(T_b-T)
-	%\end{equation}
-	%\begin{equation}
-	%F_S = -\rho_{sw} (\gamma_S - \gamma_S \frac{S_b-S}{S_b})(S_b-S)
-	%\end{equation}
-
-	\begin{equation}
-	F_B = g(\beta F_S - \alpha F_T)
-	\end{equation}
-
-	%$F_T,F_S$ stored in \code{surf\_def\_h}.
-
-	General Implementation strategy
-	\begin{enumerate}
-		\item Initialization: 
-		a. shf, sasws are assigned (to 0), 
-		b. Friction velocity is initialized (to 0?). 
-		c. Define buoyancy flux from shf and sasws 
-			(need to have alpha and beta at the surface)
-		\item Calculate exchange velocities $\gamma_T,\gamma_S$ as described in the previous section based on shf, sasws, us at previous timestep
-		\item Use 3 equations to solve for $S_b, T_b$
-		\item Iterate if $S_b$ is significantly different from prior $S_b$ used to define $dT_f/dS$.
-		\item Calculate heat, salt fluxes from 3 equations
-		\item Iterate 2-5 if buoyancy flux is significantly different than initial buoyancy flux
-		% consider calculating momentum fluxes
-	\end{enumerate}
-
-	Implementation choices to explore:
-	What is the best choice for $T, S$?
-
-	parameter choices
-	$L_O$ minimum = vertical grid dimension/20
-	$L_O$ maximum = vertical domain dimension * 20
-	$\gamma_fr$ exchange velocity for freezing case
-	$z_m$ distance from the interface for boundary layer conditions
-	$c_d$ roughness coefficient
-	domain size
-	domain resolution
-
-	%can argue that $L_O$ minimum and $\gamma_fr$ don't matter if for the cases we run so little of the domain is freezing that it doesn't modify mean fluxes of momentum, heat and salt
-
-	\textbf{initial and boundary conditions}
-	Cyclic horizontal boundary conditions
-	Velocity:
-	zero at the ice-ocean interface
-	Bottom boundary: u,v consistent with horizontal pressure gradients. w=0
-
-	Pressure:
-	horizontal pressure gradients
-	surface pressure (indicative of domain depth)
-
-	Temperature:
-	far-field temperature relaxed at the bottom third of the domain
-
-	Salinity:
-	far-field salinity relaxed at the bottom third of the domain
-	Initial
-
-\end{document}

### 2020-08-25 A04_buoyancy_considerations.tex
Updates to main and supplements

    \subsection{Possible issues in "buoyancy" forcing}

    Velocity tendency / Momentum balance
	\begin{equation} \label{eq:uprog}
	\frac{\partial u_i}{\partial t} = 
	- \frac{\partial u_i u_j}{\partial x_i}
	- \varepsilon_{ijk} f_j u_k 
	+ \varepsilon_{i3j} f_3 u_{g,j}
	+ g_i \frac{\rho - \rho_0}{\rho_0}
	- \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i}
	- \frac{\partial}{\partial x_j}(\overline{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
	- \frac{\tau}{\rho}
	\end{equation}

	\subsubsection{Large-scale pressure gradient from sloping ice shelf}
	The "buoyancy" term in Equation \ref{eq:uprog} arises from both the large-scale pressure gradient in hydrostatic equilibrium in the rotated domain and the local  should appear as a separate term in the momentum equation:
	\begin{equation}
	    \frac{du_i}{dt}(ice) = -\frac{1}{\rho_0}\frac{dp}{dx_i} + \frac{\rho}{\rho_0}g_i
	\end{equation}
	Neglecting horizontal changes in density, the pressure gradient in hydrostatic equilibrium can be expressed as
	\begin{equation}
	    \frac{dp}{dx_i}(x_i) = \rho_w g_i% + \frac{d\rho_w}{dx_i} g_i x_i \cdot \frac{\textbf{g}}{\|\textbf{g}\|}
	\end{equation}
	where $\rho_w$ is the ambient density associated with far-field conditions.
	%where the term due to the change in density is a function of the distance along the axis ($x_i$) projected onto the gravity vector

	Horizontal changes in density can be neglected. The change in pressure along the ice shelf base in hydrostatic equilibrium for a 1 km domain is
	\begin{equation}
	    \Delta P = \rho_w g \sin \alpha L_x = 1e3 * 1e1 * 1e-3 * 1e3 = 1e4 [Pa]
	\end{equation}
	The resulting change in density is about $5e-3$ $kg/m^3$ ($d\rho/dP =$ $5e-7 kg/m^3/Pa$).
	%\begin{equation}
	%\frac{dp}{dx}(x) = \rho_w g\sin\alpha + \frac{d\rho_w}{dx} g\sin^2\alpha x
	%    = \rho_w g\sin\alpha (1 + \frac{d\rho_w}{dp}g\sin^2\alpha x)
	%\end{equation}
	%Assuming the change in density with distance along the x-axis is due only to the non-density-dependent change in density, the resulting change in 
	%\begin{equation}
	%    \frac{dp}{dx}(x) = \rho_w g\sin\alpha (1 + \frac{d\rho_w}{dp}g\sin^2\alpha x)
	%\end{equation}
	%\begin{equation}
	%    \frac{d\rho_w}{dp}g\sin^2\alpha x = 	5e-7 * 1e1 * 1e-3 * 1e3 \ll 1
	%\end{equation}
	%\begin{equation}
	%    \frac{du_i}{dt}(ice) = -\frac{\rho_w}{\rho_0}g_i + \frac{\rho}{\rho_0}g_i = 
	%    \frac{\rho-\rho_w}{\rho_0}g_i
	%\end{equation}

	\subsubsection{Density differences resulting from rotated domain}
	Currently, density is computed as a function of the hydrostatic pressure, $P_0 + $ the piecewise integral $\int \rho_0(z) g dz$ where the $z$-axis is perpendicular to the ice base. \textit{Make sure that the rotated z is used}

	Perturbation pressure term is not included in velocity tendency initially. It is computed after the fact as the divergence of the velocity field, then subtracted from the velocity field to ensure that the divergence is (nearly) zero. \textbf{The divergence equation, below, also assumes that density gradients only matter along the z-axis.} Details of the pressure solver \href{https://palm.muk.uni-hannover.de/trac/wiki/doc/tec/pres}{here}.
    \begin{equation}
         D = \nabla \cdot \rho u = \rho_0\frac{du}{dx} + \rho_0\frac{dv}{dy} + \frac{d\rho u}{dz}
    \end{equation}
    \begin{equation}\label{eq:utend_D}
        \frac{du_i}{dt}(D) = -\frac{dD}{dx_i}  
    \end{equation}
    Note: It doesn't seem that D divided by $\rho$ before Equation \ref{eq:utend_D} is applied.

	The perturbation pressure is defined as
	\begin{equation}
	    \pi_* = p_∗ + 2 \rho_0 e
	\end{equation}
	but this quantity is not computed for the ``poisfft'' method.

### 2020-08-25 A07_3eqn_impl_details.tex
Updates to main and supplements

--- 2019-07-16 Main/Begeman_iceshelf_les_project.tex
@@
-\documentclass[letterpaper,10pt]{report}
-
-\usepackage{ifxetex,ifluatex} % provides way to check if document is being processed with xetex or luatex
-
-\usepackage[colorlinks = true,
-unicode=true,
-linkcolor = Black,
-urlcolor  = Black,
-citecolor = Black,
-anchorcolor = blue]{hyperref}
-
-\usepackage[english]{babel} % language support
-
-% --- page layout ---
-
-\usepackage{lastpage} % allows user to refer to last page with label LastPage
-\usepackage{titlesec} % options for title, headers, contents
-
-%header
-\usepackage{fancyhdr} % customize headers and footers
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Carolyn Begeman, PALM development, Page \thepage \thinspace \thinspace of \pageref{LastPage}}
-\lhead{}
-\renewcommand{\headrulewidth}{0pt}
-
-% page dimensions
-\usepackage{geometry}
-\geometry{letterpaper, top=0.75in, left=1in, total={6.5in,9.5in}, headheight=12pt, headsep=.1in} % topmargin=-23pt,
-
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-
-% set paragraph settings
-\IfFileExists{parskip.sty}{%
-	\usepackage{parskip}
-}{% else
-	\setlength{\parindent}{0pt}
-	\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-\setcounter{secnumdepth}{3} % set maximum depth of subsections
-
-%\usepackage{caption}
-%\captionsetup[table]{skip=8pt]}
-
-% --- font-related packages ---
-
-\usepackage{mathptmx} % make Times default font, with math font
-\usepackage{lmodern} % load Latin Modern family of fonts
-\usepackage{amssymb,amsmath} % define AMS symbol fonts
-\usepackage[usenames,dvipsnames]{color} % color model
-
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-	\usepackage[]{microtype}
-	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\hypersetup{
-	pdfborder={0 0 0},
-	breaklinks=true}
-%\urlstyle{same}  % don't use monospace font for urls
-%\usepackage[utf8]{inputenc} % specify input encoding, \DeclareUnicodeCharacter
-
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-\ifxetex
-\usepackage{mathspec}
-\else
-\usepackage{fontspec}
-\fi
-\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-
-% set fontsize for section and subsection
-\newcommand{\secfnt}{\fontsize{12}{14}}
-\titlespacing\section{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newcommand{\ssecfnt}{\fontsize{12}{14}}
-\titlespacing\subsection{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
-\renewcommand{\baselinestretch}{1}
-
-% settings for text that designates code
-\definecolor{light-gray}{gray}{0.95} 
-\newcommand{\code}[1]{\texttt{#1}} %{\colorbox{light-gray}
-
-% --- lists ---
-\usepackage{enumitem,amssymb}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
-\usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}%
-\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
-	\hspace{-2.5pt}}
-\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}
-
-% --- graphics ---
-
-\usepackage{graphicx,grffile}
-
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-%\graphicspath{ {} }
-
-%\date{} %replace date with text \date{text}
-
-\begin{document}%\thispagestyle{empty}
-\tableofcontents{}
-\chapter{Motivation}
-
-% from CK application
-Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
-Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.
-These critical processes are not captured by even the most advanced Earth System Models (ESMs), such as the DOE’s Energy Exascale Earth System Model (E3SM), of which LANL is a major developer.
-Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
-Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete.
-A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.
-
-% from postdoc proposal
-The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet.
-The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice.
-In turn, the Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base; accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
-One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution.
-Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL.
-This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting.
-A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.
-
-% plan
-I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
-Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
-During the first year of the project, I will simulate the IOBL using the MIT General Circulation Model (MITgcm) in a LES ocean configuration.
-An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface.
-I will vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates when the modeled IOBL has equilibrated.
-During the second year of the project, I will implement the resulting parameterization in the Model for Prediction Across Scales Ocean (MPAS-O), the ocean component of DOE’s new Energy Exascale Earth System Model (E3SM).
-Using MPAS-O in idealized configurations, I will investigate the parameterization’s impact on sub-ice-shelf ocean circulation and the distribution of ice-shelf melting as compared with previous parameterizations.
-I will focus on the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
-Resources for this work include MPAS-O, developed at LANL, and existing allocations at a number of DOE HPC facilities (including LANL).
-
-The proposed work, characterizing turbulence in the presence of a buoyancy flux and sloping boundary, addresses a fundamental problem in fluid dynamics.
-The work also has direct societal relevance because ice-ocean interactions are believed to be a major control on future sea level rise.
-This new parameterization for ice-shelf melting will support an ongoing effort at LANL and other national labs to accurately couple ice sheet and ocean models and will be exportable from MPAS-O to other models.
-Thus, in addition to significantly improving simulations of ocean circulation, Antarctic ice loss, and sea level rise in E3SM, it could provide similar advances to other Earth system modeling efforts.
-
-%\chapter{Relevant literature}
-%Put something here
-
-\chapter{The PALM model}
-    \section{Table of variables}
-
-    \textbf{Acronyms}:
-    SGS = sub-grid-scale
-    TKE = turbulent kinetic energy
-
-    \begin{tabular}{c|c}
-       $e$      & SGS TKE \\
-       $\theta$ & potential temperature \\
-       $S$      & practical salinity
-    \end{tabular}
-	\section{Model overview}
-
-	The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany).
-It has been applied to the simulation of atmospheric and ocean boundary layers.
-However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
-For this application, the key model development was the implementation of dynamic melting fluxes.
-
-	Prognostic equations:
-	Momentum conservation
-	\begin{equation} \label{eq:uprog}
-	\frac{\partial u_i}{\partial t} = -\frac{\partial u_i u_j}{\partial x_i}-\varepsilon_{ijk} f_j u_k + \varepsilon_{i3j} f_3 u_{g,j} - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} + g \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} - \frac{\partial}{\partial x_j}(\bar{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
-	\end{equation}
-
-	Mass conservation for incompressible flows
-	\begin{equation} \label{eq:volconserv}
-	\frac{\partial u_j}{\partial x_j} = 0
-	\end{equation}
-
-	Heat and salt conservation
-	\begin{equation} \label{eq:ptprog}
-	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i \theta''} - F_T)
-	\end{equation}
-
-	\begin{equation} \label{eq:saprog}
-	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i Sa''} + F_S)
-	\end{equation}
-
-	Turbulence closure by the gradient mean approximation
-	\begin{equation} \label{eq:momdiff}
-	\bar{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
-	\end{equation}
-
-	\begin{equation} \label{eq:ptdiff}
-	\bar{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
-	\end{equation}
-
-	Prognostic equation for SGS TKE
-	\begin{equation} \label{eq:eprog}
-	\frac{\partial e}{\partial t} = -u_j \frac{\partial e}{\partial x_j} - (\bar{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g}{\rho_0}\bar{u''_3 \rho''}
-	\end{equation}
-
-	modified perturbation pressure:
-	\begin{equation} \label{eq:pi}
-	\pi^* = p^* + \frac{2}{3}\rho_0 e
-	\end{equation}
-	where $p^*$ is the perturbation pressure and the turbulent kinetic energy $e$ is
-
-	\begin{equation} \label{eq:e}
-	e = \frac{1}{2}\bar{u''_i u''_i}
-	\end{equation}
-
-	\begin{equation} \label{eq:sadiff}
-	\bar{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
-	\end{equation}
-
-	Eddy diffusivity of momentum
-	\begin{equation} \label{eq:Km}
-	K_m = c_m l \sqrt{e}
-	\end{equation}
-
-	Eddy diffusivity of heat and salt
-	\begin{equation} \label{eq:Kh}
-	K_h = (1+\frac{2l}{\Delta})K_m
-	\end{equation}
-    where
-	\begin{equation} \label{eq:gridl}
-	\Delta = \sqrt[3]{\Delta x \Delta y \Delta z}
-	\end{equation}
-
-	%The model enforces incompressibility with 
-	%\begin{equation} \label{eq:pdiv}
-	%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
-	%\end{equation}
-
-	\subsection{Sloping surface}
-	We represent a sloping ice base by rotating the gravity vector while keeping the domain a rectangular prism.
-The ice base always slopes in the x-dimension of our domain.
-The sloping surface modifies buoyancy terms in the model and imposes a surface pressure gradient.
-The surface pressure gradient was accurate in PALM v0, but the buoyancy terms were based only on temperature rather than density.
-We define buoyancy based on the in-situ density, $g cos(\alpha) \rho/\rho_0$.
-
-	Sloping surface requires cyclic boundary conditions. There are two possible approaches in the sloping surface case:
-	(a) Slope offset: Choose initial conditions in which isopycnals follow isobars.
-When water is cycled across boundaries, apply a temperature offset determined by the slope and the initial temperature gradient.
-Apply a salinity offset as well (not implemented in PALM v0).
-	(b) No offset: Choose initial conditions in which isopycnals are parallel to the surface. Do not apply any temperature or salinity offset to water cycled across boundaries.
-
-	\textbf{Development}:
-	PALM vslope: Analogous to slope offset in temperature field, define slope offset for salinity field.
-	\begin{itemize}
-		\item To do list
-		\begin{todolist}
-			\item Add \code{sa\_slope\_offest} to \code{advec\_s\_bc}
-			\item Option to turn slope offset off, would make \code{slope\_offset}=0 in \code{init\_slope}
-			\item Option to set initial temperature and salinity gradients parallel to ice base. Wouldn't need to recompute \code{pt\_init} or \code{sa\_init} in \code{init\_slope} (Same as last item?).
-		\end{todolist}
-	\end{itemize}
-
-	\section{Monin-Obukhov Similarity Theory for the surface layer}
-    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.
-
-    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic).
-We denote this depth $z_m$.
-
-    The friction velocity is defined following "law of the wall"
-    \begin{equation}
-        u_* = \kappa u_m / log(z_m/z_0)
-    \end{equation}
-
-    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
-    \begin{equation}
-        \zeta = \frac{f z}{\eta_* u_*}
-    \end{equation}
-
-    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
-    \begin{equation}
-        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
-    \end{equation}
-    where $L_O$ is the Monin-Obukhov length
-    \begin{equation}
-        L_O = \rho \frac{u_*^3}{\kappa F_{B}}
-    \end{equation}
-
-    The momentum flux, expressed in imaginary notation where real values are aligned with the x-axis and imaginary values are aligned with the y-axis:
-    \begin{equation}
-        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
-    \end{equation}
-    \begin{equation}
-        u'w' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
-    \end{equation}
-    \begin{equation}
-        v'w' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
-    \end{equation}
-
-    \section{Melt rate solution method}
-	% gamma_X
-	% Depends on positive melt rate and that the effect of stratification is to reduce fluxes rather than enhance fluxes as a result of buoyancy from sloping surface
-
-	Asay-Davis Eq. 24-26
-	\begin{equation}
-	\rho_{sw} \gamma_T (T_b-T) = \rho_{fw} m(\frac{-L_i}{c_p})
-	\end{equation}
-	\begin{equation}
-	\rho_{sw} \gamma_S (S_b-S) = \rho_{fw} m S_b
-	\end{equation}
-	\begin{equation}
-	T_b = T_b^{n-1}+c_2 S_b - c_2 S_b^{n-1}
-	\end{equation}
-
+    % quadratic
     \begin{equation}
@@
 	\end{equation}
+
+	% gamma_X
+	% Depends on positive melt rate and that the effect of stratification is to reduce fluxes rather than enhance fluxes as a result of buoyancy from sloping surface
 
@@
 
-	\begin{equation}
-	F_B = g(\beta F_S - \alpha F_T)
-	\end{equation}
-
-	%$F_T,F_S$ stored in \code{surf\_def\_h}.
-
 	General Implementation strategy
@@
 		\item Calculate heat, salt fluxes from 3 equations
-		\item Iterate 2-5 if buoyancy flux is significantly different than initial buoyancy flux
+		\item Iterate 2-5 until the change in $S_b$ from the last iteration is less than a tolerance of XX
 		% consider calculating momentum fluxes
 	\end{enumerate}
-
-	Implementation choices to explore:
-	What is the best choice for $T, S$?
-
-	parameter choices
-	$L_O$ minimum = vertical grid dimension/20
-	$L_O$ maximum = vertical domain dimension * 20
-	$\gamma_fr$ exchange velocity for freezing case
-	$z_m$ distance from the interface for boundary layer conditions
-	$c_d$ roughness coefficient
-	domain size
-	domain resolution
-
-	%can argue that $L_O$ minimum and $\gamma_fr$ don't matter if for the cases we run so little of the domain is freezing that it doesn't modify mean fluxes of momentum, heat and salt
-
-	\textbf{initial and boundary conditions}
-	Cyclic horizontal boundary conditions
-	Velocity:
-	zero at the ice-ocean interface
-	Bottom boundary: u,v consistent with horizontal pressure gradients. w=0
-
-	Pressure:
-	horizontal pressure gradients
-	surface pressure (indicative of domain depth)
-
-	Temperature:
-	far-field temperature relaxed at the bottom third of the domain
-
-	Salinity:
-	far-field salinity relaxed at the bottom third of the domain
-	Initial
-
-\end{document}

### 2020-08-25 custom_header.tex
Updates to main and supplements

--- 2019-07-16 Main/Begeman_iceshelf_les_project.tex
@@
 
-% --- lists ---
+% --- itemizes ---
 \usepackage{enumitem,amssymb}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
+%\newitemize{todoitemize}{itemize}{2}
+%\setitemize[todoitemize]{label=$\square$}
 \usepackage{pifont}
@@
 %\date{} %replace date with text \date{text}
-
-\begin{document}%\thispagestyle{empty}
-\tableofcontents{}
-\chapter{Motivation}
-
-% from CK application
-Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
-Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.
-These critical processes are not captured by even the most advanced Earth System Models (ESMs), such as the DOE’s Energy Exascale Earth System Model (E3SM), of which LANL is a major developer.
-Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
-Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete.
-A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.
-
-% from postdoc proposal
-The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet.
-The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice.
-In turn, the Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base; accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
-One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution.
-Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL.
-This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting.
-A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.
-
-% plan
-I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
-Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
-During the first year of the project, I will simulate the IOBL using the MIT General Circulation Model (MITgcm) in a LES ocean configuration.
-An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface.
-I will vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates when the modeled IOBL has equilibrated.
-During the second year of the project, I will implement the resulting parameterization in the Model for Prediction Across Scales Ocean (MPAS-O), the ocean component of DOE’s new Energy Exascale Earth System Model (E3SM).
-Using MPAS-O in idealized configurations, I will investigate the parameterization’s impact on sub-ice-shelf ocean circulation and the distribution of ice-shelf melting as compared with previous parameterizations.
-I will focus on the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
-Resources for this work include MPAS-O, developed at LANL, and existing allocations at a number of DOE HPC facilities (including LANL).
-
-The proposed work, characterizing turbulence in the presence of a buoyancy flux and sloping boundary, addresses a fundamental problem in fluid dynamics.
-The work also has direct societal relevance because ice-ocean interactions are believed to be a major control on future sea level rise.
-This new parameterization for ice-shelf melting will support an ongoing effort at LANL and other national labs to accurately couple ice sheet and ocean models and will be exportable from MPAS-O to other models.
-Thus, in addition to significantly improving simulations of ocean circulation, Antarctic ice loss, and sea level rise in E3SM, it could provide similar advances to other Earth system modeling efforts.
-
-%\chapter{Relevant literature}
-%Put something here
-
-\chapter{The PALM model}
-    \section{Table of variables}
-
-    \textbf{Acronyms}:
-    SGS = sub-grid-scale
-    TKE = turbulent kinetic energy
-
-    \begin{tabular}{c|c}
-       $e$      & SGS TKE \\
-       $\theta$ & potential temperature \\
-       $S$      & practical salinity
-    \end{tabular}
-	\section{Model overview}
-
-	The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany).
-It has been applied to the simulation of atmospheric and ocean boundary layers.
-However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
-For this application, the key model development was the implementation of dynamic melting fluxes.
-
-	Prognostic equations:
-	Momentum conservation
-	\begin{equation} \label{eq:uprog}
-	\frac{\partial u_i}{\partial t} = -\frac{\partial u_i u_j}{\partial x_i}-\varepsilon_{ijk} f_j u_k + \varepsilon_{i3j} f_3 u_{g,j} - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} + g \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} - \frac{\partial}{\partial x_j}(\bar{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
-	\end{equation}
-
-	Mass conservation for incompressible flows
-	\begin{equation} \label{eq:volconserv}
-	\frac{\partial u_j}{\partial x_j} = 0
-	\end{equation}
-
-	Heat and salt conservation
-	\begin{equation} \label{eq:ptprog}
-	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i \theta''} - F_T)
-	\end{equation}
-
-	\begin{equation} \label{eq:saprog}
-	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i Sa''} + F_S)
-	\end{equation}
-
-	Turbulence closure by the gradient mean approximation
-	\begin{equation} \label{eq:momdiff}
-	\bar{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
-	\end{equation}
-
-	\begin{equation} \label{eq:ptdiff}
-	\bar{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
-	\end{equation}
-
-	Prognostic equation for SGS TKE
-	\begin{equation} \label{eq:eprog}
-	\frac{\partial e}{\partial t} = -u_j \frac{\partial e}{\partial x_j} - (\bar{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g}{\rho_0}\bar{u''_3 \rho''}
-	\end{equation}
-
-	modified perturbation pressure:
-	\begin{equation} \label{eq:pi}
-	\pi^* = p^* + \frac{2}{3}\rho_0 e
-	\end{equation}
-	where $p^*$ is the perturbation pressure and the turbulent kinetic energy $e$ is
-
-	\begin{equation} \label{eq:e}
-	e = \frac{1}{2}\bar{u''_i u''_i}
-	\end{equation}
-
-	\begin{equation} \label{eq:sadiff}
-	\bar{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
-	\end{equation}
-
-	Eddy diffusivity of momentum
-	\begin{equation} \label{eq:Km}
-	K_m = c_m l \sqrt{e}
-	\end{equation}
-
-	Eddy diffusivity of heat and salt
-	\begin{equation} \label{eq:Kh}
-	K_h = (1+\frac{2l}{\Delta})K_m
-	\end{equation}
-    where
-	\begin{equation} \label{eq:gridl}
-	\Delta = \sqrt[3]{\Delta x \Delta y \Delta z}
-	\end{equation}
-
-	%The model enforces incompressibility with 
-	%\begin{equation} \label{eq:pdiv}
-	%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
-	%\end{equation}
-
-	\subsection{Sloping surface}
-	We represent a sloping ice base by rotating the gravity vector while keeping the domain a rectangular prism.
-The ice base always slopes in the x-dimension of our domain.
-The sloping surface modifies buoyancy terms in the model and imposes a surface pressure gradient.
-The surface pressure gradient was accurate in PALM v0, but the buoyancy terms were based only on temperature rather than density.
-We define buoyancy based on the in-situ density, $g cos(\alpha) \rho/\rho_0$.
-
-	Sloping surface requires cyclic boundary conditions. There are two possible approaches in the sloping surface case:
-	(a) Slope offset: Choose initial conditions in which isopycnals follow isobars.
-When water is cycled across boundaries, apply a temperature offset determined by the slope and the initial temperature gradient.
-Apply a salinity offset as well (not implemented in PALM v0).
-	(b) No offset: Choose initial conditions in which isopycnals are parallel to the surface. Do not apply any temperature or salinity offset to water cycled across boundaries.
-
-	\textbf{Development}:
-	PALM vslope: Analogous to slope offset in temperature field, define slope offset for salinity field.
-	\begin{itemize}
-		\item To do list
-		\begin{todolist}
-			\item Add \code{sa\_slope\_offest} to \code{advec\_s\_bc}
-			\item Option to turn slope offset off, would make \code{slope\_offset}=0 in \code{init\_slope}
-			\item Option to set initial temperature and salinity gradients parallel to ice base. Wouldn't need to recompute \code{pt\_init} or \code{sa\_init} in \code{init\_slope} (Same as last item?).
-		\end{todolist}
-	\end{itemize}
-
-	\section{Monin-Obukhov Similarity Theory for the surface layer}
-    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.
-
-    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic).
-We denote this depth $z_m$.
-
-    The friction velocity is defined following "law of the wall"
-    \begin{equation}
-        u_* = \kappa u_m / log(z_m/z_0)
-    \end{equation}
-
-    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
-    \begin{equation}
-        \zeta = \frac{f z}{\eta_* u_*}
-    \end{equation}
-
-    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
-    \begin{equation}
-        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
-    \end{equation}
-    where $L_O$ is the Monin-Obukhov length
-    \begin{equation}
-        L_O = \rho \frac{u_*^3}{\kappa F_{B}}
-    \end{equation}
-
-    The momentum flux, expressed in imaginary notation where real values are aligned with the x-axis and imaginary values are aligned with the y-axis:
-    \begin{equation}
-        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
-    \end{equation}
-    \begin{equation}
-        u'w' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
-    \end{equation}
-    \begin{equation}
-        v'w' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
-    \end{equation}
-
-    \section{Melt rate solution method}
-	% gamma_X
-	% Depends on positive melt rate and that the effect of stratification is to reduce fluxes rather than enhance fluxes as a result of buoyancy from sloping surface
-
-	Asay-Davis Eq. 24-26
-	\begin{equation}
-	\rho_{sw} \gamma_T (T_b-T) = \rho_{fw} m(\frac{-L_i}{c_p})
-	\end{equation}
-	\begin{equation}
-	\rho_{sw} \gamma_S (S_b-S) = \rho_{fw} m S_b
-	\end{equation}
-	\begin{equation}
-	T_b = T_b^{n-1}+c_2 S_b - c_2 S_b^{n-1}
-	\end{equation}
-
-	\begin{equation}
-	(\gamma_T c_2) S_b^2 + (\gamma_T(T_b^{n-1}-c_2 S_b^{n-1}-T)-\gamma_S \frac{-L_i}{c_p})S_b + \gamma_S\frac{-L_i}{c_p}S=0
-	\end{equation}
-
-	%Asay-Davis Eq. 29-30
-	%\begin{equation}
-	%	F_T = -c_p(\rho_{sw} \gamma_T + \rho_{fw} m)(T_b-T)
-	%\end{equation}
-	%$F_T > 0, m > 0, T_b-T > 0$
-
-	%\begin{equation}
-	%	F_S = -(\rho_{sw} \gamma_S + \rho_{fw} m)(S_b-S)
-	%\end{equation}
-	%$F_S > 0, m > 0, S_b-S < 0$
-
-	%Substituing the melt rate equation, these equations can also be expressed as
-	%\begin{equation}
-	%F_T = -\rho_{sw} c_p(\gamma_T - \gamma_S \frac{S_b-S}{S_b})(T_b-T)
-	%\end{equation}
-	%\begin{equation}
-	%F_S = -\rho_{sw} (\gamma_S - \gamma_S \frac{S_b-S}{S_b})(S_b-S)
-	%\end{equation}
-
-	\begin{equation}
-	F_B = g(\beta F_S - \alpha F_T)
-	\end{equation}
-
-	%$F_T,F_S$ stored in \code{surf\_def\_h}.
-
-	General Implementation strategy
-	\begin{enumerate}
-		\item Initialization: 
-		a. shf, sasws are assigned (to 0), 
-		b. Friction velocity is initialized (to 0?). 
-		c. Define buoyancy flux from shf and sasws 
-			(need to have alpha and beta at the surface)
-		\item Calculate exchange velocities $\gamma_T,\gamma_S$ as described in the previous section based on shf, sasws, us at previous timestep
-		\item Use 3 equations to solve for $S_b, T_b$
-		\item Iterate if $S_b$ is significantly different from prior $S_b$ used to define $dT_f/dS$.
-		\item Calculate heat, salt fluxes from 3 equations
-		\item Iterate 2-5 if buoyancy flux is significantly different than initial buoyancy flux
-		% consider calculating momentum fluxes
-	\end{enumerate}
-
-	Implementation choices to explore:
-	What is the best choice for $T, S$?
-
-	parameter choices
-	$L_O$ minimum = vertical grid dimension/20
-	$L_O$ maximum = vertical domain dimension * 20
-	$\gamma_fr$ exchange velocity for freezing case
-	$z_m$ distance from the interface for boundary layer conditions
-	$c_d$ roughness coefficient
-	domain size
-	domain resolution
-
-	%can argue that $L_O$ minimum and $\gamma_fr$ don't matter if for the cases we run so little of the domain is freezing that it doesn't modify mean fluxes of momentum, heat and salt
-
-	\textbf{initial and boundary conditions}
-	Cyclic horizontal boundary conditions
-	Velocity:
-	zero at the ice-ocean interface
-	Bottom boundary: u,v consistent with horizontal pressure gradients. w=0
-
-	Pressure:
-	horizontal pressure gradients
-	surface pressure (indicative of domain depth)
-
-	Temperature:
-	far-field temperature relaxed at the bottom third of the domain
-
-	Salinity:
-	far-field salinity relaxed at the bottom third of the domain
-	Initial
-
-\end{document}

### 2020-08-25 main.tex
Updates to main and supplements

--- 2019-07-16 Main/Begeman_iceshelf_les_project.tex
@@
-\documentclass[letterpaper,10pt]{report}
+\documentclass[draft]{styles/agujournal2019}
+\usepackage{url} 
+\usepackage{lineno}
+\linenumbers
+\draftfalse
+\journalname{JGR: Oceans}
 
-\usepackage{ifxetex,ifluatex} % provides way to check if document is being processed with xetex or luatex
+\begin{document}
+\input{agu_begindoc.tex}
 
-\usepackage[colorlinks = true,
-unicode=true,
-linkcolor = Black,
-urlcolor  = Black,
-citecolor = Black,
-anchorcolor = blue]{hyperref}
+\section{Introduction}
 
-\usepackage[english]{babel} % language support
-
-% --- page layout ---
-
-\usepackage{lastpage} % allows user to refer to last page with label LastPage
-\usepackage{titlesec} % options for title, headers, contents
-
-%header
-\usepackage{fancyhdr} % customize headers and footers
-\pagestyle{fancy}
-\fancyhf{}
-\rhead{Carolyn Begeman, PALM development, Page \thepage \thinspace \thinspace of \pageref{LastPage}}
-\lhead{}
-\renewcommand{\headrulewidth}{0pt}
-
-% page dimensions
-\usepackage{geometry}
-\geometry{letterpaper, top=0.75in, left=1in, total={6.5in,9.5in}, headheight=12pt, headsep=.1in} % topmargin=-23pt,
-
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-
-% set paragraph settings
-\IfFileExists{parskip.sty}{%
-	\usepackage{parskip}
-}{% else
-	\setlength{\parindent}{0pt}
-	\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-\setcounter{secnumdepth}{3} % set maximum depth of subsections
-
-%\usepackage{caption}
-%\captionsetup[table]{skip=8pt]}
-
-% --- font-related packages ---
-
-\usepackage{mathptmx} % make Times default font, with math font
-\usepackage{lmodern} % load Latin Modern family of fonts
-\usepackage{amssymb,amsmath} % define AMS symbol fonts
-\usepackage[usenames,dvipsnames]{color} % color model
-
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-	\usepackage[]{microtype}
-	\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\hypersetup{
-	pdfborder={0 0 0},
-	breaklinks=true}
-%\urlstyle{same}  % don't use monospace font for urls
-%\usepackage[utf8]{inputenc} % specify input encoding, \DeclareUnicodeCharacter
-
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-\ifxetex
-\usepackage{mathspec}
-\else
-\usepackage{fontspec}
-\fi
-\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-
-% set fontsize for section and subsection
-\newcommand{\secfnt}{\fontsize{12}{14}}
-\titlespacing\section{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
-\newcommand{\ssecfnt}{\fontsize{12}{14}}
-\titlespacing\subsection{0pt}{0pt plus 2pt minus 2pt}{0pt plus 2pt minus 2pt}
-\renewcommand{\baselinestretch}{1}
-
-% settings for text that designates code
-\definecolor{light-gray}{gray}{0.95} 
-\newcommand{\code}[1]{\texttt{#1}} %{\colorbox{light-gray}
-
-% --- lists ---
-\usepackage{enumitem,amssymb}
-\newlist{todolist}{itemize}{2}
-\setlist[todolist]{label=$\square$}
-\usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}%
-\newcommand{\done}{\rlap{$\square$}{\raisebox{2pt}{\large\hspace{1pt}\cmark}}%
-	\hspace{-2.5pt}}
-\newcommand{\wontfix}{\rlap{$\square$}{\large\hspace{1pt}\xmark}}
-
-% --- graphics ---
-
-\usepackage{graphicx,grffile}
-
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
-%\graphicspath{ {} }
-
-%\date{} %replace date with text \date{text}
-
-\begin{document}%\thispagestyle{empty}
-\tableofcontents{}
-\chapter{Motivation}
-
-% from CK application
+\paragraph{}% from CK application
 Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
@@
 
-% plan
 I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
@@
 
-%\chapter{Relevant literature}
-%Put something here
+\section{Methods}
 
-\chapter{The PALM model}
-    \section{Table of variables}
-
-    \textbf{Acronyms}:
-    SGS = sub-grid-scale
-    TKE = turbulent kinetic energy
-
-    \begin{tabular}{c|c}
-       $e$      & SGS TKE \\
-       $\theta$ & potential temperature \\
-       $S$      & practical salinity
-    \end{tabular}
-	\section{Model overview}
-
+	%\paragraph{The PALM model}
     The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany).
@@
 	\begin{equation} \label{eq:uprog}
-	\frac{\partial u_i}{\partial t} = -\frac{\partial u_i u_j}{\partial x_i}-\varepsilon_{ijk} f_j u_k + \varepsilon_{i3j} f_3 u_{g,j} - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} + g \frac{\rho - \langle \rho \rangle}{\langle \rho \rangle}\delta_{i3} - \frac{\partial}{\partial x_j}(\bar{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
+	\frac{\partial u_i}{\partial t} = 
+	-\frac{\partial u_i u_j}{\partial x_i}
+	-\varepsilon_{ijk} f_j u_k 
+	+ \varepsilon_{i3j} f_3 u_{g,j} 
+    + g_i \frac{\rho - \rho_a}{\rho_0}
+	- \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i}
+	- \frac{\partial}{\partial x_j}(\overline{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
+	- \frac{\tau_i}{\rho}
 	\end{equation}
 
-	Mass conservation for incompressible flows
-	\begin{equation} \label{eq:volconserv}
-	\frac{\partial u_j}{\partial x_j} = 0
+	The terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum fluxes.
+
+	\paragraph{Sloping surface}
+	We represent a sloping ice base by rotating the gravity and Coriolis vectors while keeping the domain a rectangular prism. The ice base always slopes in the x-dimension of our domain. 
+	%In PALM v0 the buoyancy terms were based only on temperature rather than density. 
+	Thus, 
+	\begin{equation} \label{eq:g}
+    	\textbf{g} = g [sin \alpha,0,cos \alpha]
+    \end{equation}
+	\begin{equation} \label{eq:f}
+        \textbf{f} = 2 \Omega [sin \phi sin \alpha,cos \phi,sin \phi cos \alpha]
 	\end{equation}
 
-	Heat and salt conservation
-	\begin{equation} \label{eq:ptprog}
-	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i \theta''} - F_T)
+	The buoyancy term combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density.
+The along-slope pressure gradient is set by the ambient density of the water column $\rho_a$.
+This ambient density is determined using the far-field temperature and salinity values and the initial vertical hydrostatic pressure profile in the middle of the domain.
+Thus, we assume that the evolution of density in the boundary layer does not significantly affect ice-shelf slope.
+We also assume that
+	\begin{equation}
+	    \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
+	    \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
 	\end{equation}
+	In other words, we assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes.
+These density differences are verified to be within XX $kg/m^3$ for these simulations.
+This simplification has the advantage of avoiding pressure discontinuities across periodic boundary conditions.
 
-	\begin{equation} \label{eq:saprog}
-	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\bar{u''_i Sa''} + F_S)
-	\end{equation}
+	\paragraph{Surface drag}
+	The last term in Equation \ref{eq:uprog} represents the loss of momentum due to drag between the ice surface and the flow, where $\tau$ is the shear stress.
+We discuss the parameterization of $\tau$ in XX.
 
-	Turbulence closure by the gradient mean approximation
-	\begin{equation} \label{eq:momdiff}
-	\bar{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
-	\end{equation}
-
-	\begin{equation} \label{eq:ptdiff}
-	\bar{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
-	\end{equation}
-
-	Prognostic equation for SGS TKE
-	\begin{equation} \label{eq:eprog}
-	\frac{\partial e}{\partial t} = -u_j \frac{\partial e}{\partial x_j} - (\bar{u''_i u''_j})\frac{\partial u_i}{\partial x_j} + \frac{g}{\rho_0}\bar{u''_3 \rho''}
-	\end{equation}
-
-	modified perturbation pressure:
-	\begin{equation} \label{eq:pi}
-	\pi^* = p^* + \frac{2}{3}\rho_0 e
-	\end{equation}
-	where $p^*$ is the perturbation pressure and the turbulent kinetic energy $e$ is
-
-	\begin{equation} \label{eq:e}
-	e = \frac{1}{2}\bar{u''_i u''_i}
-	\end{equation}
-
-	\begin{equation} \label{eq:sadiff}
-	\bar{u''_i Sa''} = -K_h \frac{\partial Sa}{\partial x_i}
-	\end{equation}
-
-	Eddy diffusivity of momentum
-	\begin{equation} \label{eq:Km}
-	K_m = c_m l \sqrt{e}
-	\end{equation}
-
-	Eddy diffusivity of heat and salt
-	\begin{equation} \label{eq:Kh}
-	K_h = (1+\frac{2l}{\Delta})K_m
-	\end{equation}
-    where
-	\begin{equation} \label{eq:gridl}
-	\Delta = \sqrt[3]{\Delta x \Delta y \Delta z}
-	\end{equation}
-
+	%Mass conservation for incompressible flows
+	%\begin{equation} \label{eq:volconserv}
+	%\frac{\partial u_j}{\partial x_j} = 0
+	%\end{equation}
 	%The model enforces incompressibility with 
@@
 
-	\subsection{Sloping surface}
-	We represent a sloping ice base by rotating the gravity vector while keeping the domain a rectangular prism.
-The ice base always slopes in the x-dimension of our domain.
-The sloping surface modifies buoyancy terms in the model and imposes a surface pressure gradient.
-The surface pressure gradient was accurate in PALM v0, but the buoyancy terms were based only on temperature rather than density.
-We define buoyancy based on the in-situ density, $g cos(\alpha) \rho/\rho_0$.
-
-	Sloping surface requires cyclic boundary conditions. There are two possible approaches in the sloping surface case:
-	(a) Slope offset: Choose initial conditions in which isopycnals follow isobars.
-When water is cycled across boundaries, apply a temperature offset determined by the slope and the initial temperature gradient.
-Apply a salinity offset as well (not implemented in PALM v0).
-	(b) No offset: Choose initial conditions in which isopycnals are parallel to the surface. Do not apply any temperature or salinity offset to water cycled across boundaries.
-
-	\textbf{Development}:
-	PALM vslope: Analogous to slope offset in temperature field, define slope offset for salinity field.
-	\begin{itemize}
-		\item To do list
-		\begin{todolist}
-			\item Add \code{sa\_slope\_offest} to \code{advec\_s\_bc}
-			\item Option to turn slope offset off, would make \code{slope\_offset}=0 in \code{init\_slope}
-			\item Option to set initial temperature and salinity gradients parallel to ice base. Wouldn't need to recompute \code{pt\_init} or \code{sa\_init} in \code{init\_slope} (Same as last item?).
-		\end{todolist}
-	\end{itemize}
-
-	\section{Monin-Obukhov Similarity Theory for the surface layer}
-    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.
-
-    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic).
-We denote this depth $z_m$.
-
-    The friction velocity is defined following "law of the wall"
-    \begin{equation}
-        u_* = \kappa u_m / log(z_m/z_0)
+	Heat and salt conservation
+	\begin{equation} \label{eq:ptprog}
+	\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\overline{u'_i \theta'}) % - F_T
 	\end{equation}
 
-    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
-    \begin{equation}
-        \zeta = \frac{f z}{\eta_* u_*}
+	\begin{equation} \label{eq:saprog}
+	\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\overline{u'_i S'})
 	\end{equation}
 
-    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
-    \begin{equation}
-        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
-    \end{equation}
-    where $L_O$ is the Monin-Obukhov length
-    \begin{equation}
-        L_O = \rho \frac{u_*^3}{\kappa F_{B}}
+	Dynamic ice melting influences these equations through a modification to the SGS vertical fluxes of heat and salt at the top of the model domain, discussed XX.
+
+	%Turbulence closure by the gradient mean approximation
+	%\begin{equation} \label{eq:momdiff}
+	%\overline{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
+    %\end{equation}
+
+	%\begin{equation} \label{eq:ptdiff}
+	%\overline{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
+	%\end{equation}
+
+	%\begin{equation} \label{eq:e}
+	%e = \frac{1}{2}\overline{u'_i u'_i}
+	%\end{equation}
+
+    Prognostic equation for Resolved TKE
+	\begin{equation} \label{eq:eprog}
+	\frac{\partial e^*}{\partial t} = 
+	-u_j \frac{\partial e^*}{\partial x_j} 
+	- (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
 	\end{equation}
 
-    The momentum flux, expressed in imaginary notation where real values are aligned with the x-axis and imaginary values are aligned with the y-axis:
-    \begin{equation}
-        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
-    \end{equation}
-    \begin{equation}
-        u'w' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
-    \end{equation}
-    \begin{equation}
-        v'w' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
-    \end{equation}
+	The turbulence closure scheme is XX. We refer the readers to XX for the details.
 
-    \section{Melt rate solution method}
-	% gamma_X
-	% Depends on positive melt rate and that the effect of stratification is to reduce fluxes rather than enhance fluxes as a result of buoyancy from sloping surface
+	Large-scale horizontal pressure gradients are used to drive mean flow and mean shear.
 
-	Asay-Davis Eq. 24-26
-	\begin{equation}
-	\rho_{sw} \gamma_T (T_b-T) = \rho_{fw} m(\frac{-L_i}{c_p})
-	\end{equation}
-	\begin{equation}
-	\rho_{sw} \gamma_S (S_b-S) = \rho_{fw} m S_b
-	\end{equation}
-	\begin{equation}
-	T_b = T_b^{n-1}+c_2 S_b - c_2 S_b^{n-1}
-	\end{equation}
+	%\paragraph{Initial and boundary conditions}
+	Boundary conditions for velocity, temperature and salinity are cyclic at the side boundaries, dirichlet at the bottom boundary, and von Neumann at the top boundary. 
+	The bottom third of the domain is a sponge layer within which velocity, temperature, and salinity are relaxed toward their values at the bottom of the domain.
+The temperature and salinity at the bottom of the domain are chosen to represent typical sub-ice-shelf water masses.
+XX.
+The sponge layer results in no vertical fluxes of heat, salt, or momentum across the bottom boundary.
 
-	\begin{equation}
-	(\gamma_T c_2) S_b^2 + (\gamma_T(T_b^{n-1}-c_2 S_b^{n-1}-T)-\gamma_S \frac{-L_i}{c_p})S_b + \gamma_S\frac{-L_i}{c_p}S=0
-	\end{equation}
+\section{Figures and Tables}
 
-	%Asay-Davis Eq. 29-30
-	%\begin{equation}
-	%	F_T = -c_p(\rho_{sw} \gamma_T + \rho_{fw} m)(T_b-T)
-	%\end{equation}
-	%$F_T > 0, m > 0, T_b-T > 0$
+\subsection{Figures}
 
-	%\begin{equation}
-	%	F_S = -(\rho_{sw} \gamma_S + \rho_{fw} m)(S_b-S)
-	%\end{equation}
-	%$F_S > 0, m > 0, S_b-S < 0$
+\subsection{Tables}
+\input{table1.tex}
 
-	%Substituing the melt rate equation, these equations can also be expressed as
-	%\begin{equation}
-	%F_T = -\rho_{sw} c_p(\gamma_T - \gamma_S \frac{S_b-S}{S_b})(T_b-T)
-	%\end{equation}
-	%\begin{equation}
-	%F_S = -\rho_{sw} (\gamma_S - \gamma_S \frac{S_b-S}{S_b})(S_b-S)
-	%\end{equation}
+\section{Acknowledgements}
 
-	\begin{equation}
-	F_B = g(\beta F_S - \alpha F_T)
-	\end{equation}
-
-	%$F_T,F_S$ stored in \code{surf\_def\_h}.
-
-	General Implementation strategy
-	\begin{enumerate}
-		\item Initialization: 
-		a. shf, sasws are assigned (to 0), 
-		b. Friction velocity is initialized (to 0?). 
-		c. Define buoyancy flux from shf and sasws 
-			(need to have alpha and beta at the surface)
-		\item Calculate exchange velocities $\gamma_T,\gamma_S$ as described in the previous section based on shf, sasws, us at previous timestep
-		\item Use 3 equations to solve for $S_b, T_b$
-		\item Iterate if $S_b$ is significantly different from prior $S_b$ used to define $dT_f/dS$.
-		\item Calculate heat, salt fluxes from 3 equations
-		\item Iterate 2-5 if buoyancy flux is significantly different than initial buoyancy flux
-		% consider calculating momentum fluxes
-	\end{enumerate}
-
-	Implementation choices to explore:
-	What is the best choice for $T, S$?
-
-	parameter choices
-	$L_O$ minimum = vertical grid dimension/20
-	$L_O$ maximum = vertical domain dimension * 20
-	$\gamma_fr$ exchange velocity for freezing case
-	$z_m$ distance from the interface for boundary layer conditions
-	$c_d$ roughness coefficient
-	domain size
-	domain resolution
-
-	%can argue that $L_O$ minimum and $\gamma_fr$ don't matter if for the cases we run so little of the domain is freezing that it doesn't modify mean fluxes of momentum, heat and salt
-
-	\textbf{initial and boundary conditions}
-	Cyclic horizontal boundary conditions
-	Velocity:
-	zero at the ice-ocean interface
-	Bottom boundary: u,v consistent with horizontal pressure gradients. w=0
-
-	Pressure:
-	horizontal pressure gradients
-	surface pressure (indicative of domain depth)
-
-	Temperature:
-	far-field temperature relaxed at the bottom third of the domain
-
-	Salinity:
-	far-field salinity relaxed at the bottom third of the domain
-	Initial
+This research used resources provided by the Los Alamos National Laboratory Institutional Computing Program, which is supported by the U.S.
+Department of Energy National Nuclear Security Administration under Contract No.
+89233218CNA000001.
 

### 2020-08-25 styles/amspaper.tex
Updates to main and supplements

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% amspaper.tex --  LaTeX-based template for submissions to American 
% Meteorological Society journals
%
% Template developed by Amy Hendrickson, 2013, TeXnology Inc., 
% amyh@texnology.com, http://www.texnology.com
% following earlier work by Brian Papa, American Meteorological Society
%
% Email questions to latex@ametsoc.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PREAMBLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Start with one of the following:
% DOUBLE-SPACED VERSION FOR SUBMISSION TO THE AMS
\documentclass{ametsoc}

% TWO-COLUMN JOURNAL PAGE LAYOUT---FOR AUTHOR USE ONLY
% \documentclass[twocol]{ametsoc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% To be entered only if twocol option is used

\journal{jamc}

%  Please choose a journal abbreviation to use above from the following list:
% 
%   jamc     (Journal of Applied Meteorology and Climatology)
%   jtech     (Journal of Atmospheric and Oceanic Technology)
%   jhm      (Journal of Hydrometeorology)
%   jpo     (Journal of Physical Oceanography)
%   jas      (Journal of Atmospheric Sciences)	
%   jcli      (Journal of Climate)
%   mwr      (Monthly Weather Review)
%   wcas      (Weather, Climate, and Society)
%   waf       (Weather and Forecasting)
%   bams (Bulletin of the American Meteorological Society)
%   ei    (Earth Interactions)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Citations should be of the form ``author year''  not ``author, year''
\bibpunct{(}{)}{;}{a}{}{,}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% To be entered by author:

%% May use \\ to break lines in title:

\title{Title here}

%%% Enter authors' names, as you see in this example:
%%% Use \correspondingauthor{} and \thanks{Current Affiliation:...}
%%% immediately following the appropriate author.
%%%
%%% Note that the \correspondingauthor{} command is NECESSARY.
%%% The \thanks{} commands are OPTIONAL.

    \authors{Author One\correspondingauthor{Author One, 
     American Meteorological Society, 
     45 Beacon St., Boston, MA 02108.}
 and Author Two\thanks{Current affiliation: American Meteorological Society, 
     45 Beacon St., Boston, MA 02108.}}

     \affiliation{American Meteorological Society, 
     Boston, Massachusetts}

\email{latex@ametsoc.org}

    \extraauthor{Extra Author}
    \extraaffil{Affiliation, City, State/Province, Country}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%
% Enter your Abstract here

\abstract{Enter the text of your abstract here.  This is a sample American
Meteorological Society (AMS) \LaTeX\ template.  This document provides
authors with instructions on the use of the AMS \LaTeX\ template.  Authors
should refer to the file amspaper.tex to review the actual \LaTeX\ code used
to create this document. The template.tex
file should be modified by authors for their own manuscript.}

\begin{document}

%% Necessary!
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\section{Introduction}

This document will provide authors with the basic American Meteorological
Society (AMS) formatting guidelines. This document was created using \LaTeX\
and demonstrates how to use the \LaTeX\ template when submitting a manuscript
to the AMS.  The following sections will outline the guidelines and
formatting for text, math, figures, and tables while using \LaTeX\/ for a
submission to the AMS. An attempt to compile amspaper.tex should be made
before using the template. The files have been tested on Windows, Linux, and
Mac OS using \TeX\ Live 2011 (available online at
\url{http://www.tug.org/texlive/}). Feedback and questions should be sent to
latex@ametsoc.org. Additional information is available on the AMS \LaTeX\ Submission Info
web page (\url{http://www2.ametsoc.org/ams/index.cfm/publications/authors/journal-and-bams-authors/author-resources/latex-author-info/}).

Authors should use the empty template.tex to begin their
paper. A valuable source of \LaTeX\ information is the {TeX
Frequently Asked Questions} page (available online at \url{faq.tug.org}).

\section{Formatting text and sections}
The text should be divided into sections, each with a separate heading and
consecutive numbering. Note, however, that single secondary, tertiary, and
quaternary sections remain unnumbered. Each section heading should be placed
on a separate line using the appropriate \LaTeX\ commands.

\subsection*{Secondary headings} 
Secondary headings labeled with letters are formatted using the
$\backslash$subsection$*${\tt\string{\string}} for a single
subsection within a section or
 or $\backslash$subsection{\tt\string{\string}} 
for multiple
subsections within one section.

\subsubsection*{Tertiary headings} 
Tertiary headings are formatted using the
$\backslash$subsubsection$*${\tt\string{\string}} for single a subsubsection
within a subsection or
$\backslash$subsubsection{\tt\string{\string}} 
for multiple subsubsections
within a subsection.

\paragraph*{Quaternary headings} 
Quaternary headings are formatted using the
$\backslash$paragraph$*${\tt\string{\string}} for a single paragraph within
a subsubsection or
$\backslash$paragraph{\tt\string{\string}} 
for multiple paragraphs
within a subsection.

\section{Citations}
Citations to standard references in text should consist of the name of the
author and the year of publication, for example, \citet{Becker+Schmitz2003} or
\citep{Becker+Schmitz2003} using the appropriate $\backslash$citet\ or
$\backslash$citep commands, respectively. A variety of citation formats can
be used with the natbib package; however, the AMS prefers that authors use only the $\backslash$citet\ and
$\backslash$citep commands. References should be entered in the references.bib file. For a thorough
discussion of how to enter references into the references.bib database file
following AMS style, please refer to the \textbf{AMS\_Refs.pdf} document
included in this package.

\section{Formatting math}
The following sections will outline the basic formatting rules for
mathematical symbols and units.  In addition, a review of the amspaper.tex
file will show how this is done with the use of \LaTeX\ commands.  The AMS
template provides the American Mathematical Society math, font, symbol, and
boldface packages for use in math mode.

\subsection{Mathematical symbols}
Symbols must be of the same font style both in text discussion and in
displayed equations or terms (and figures should be prepared to match).
Scalar single-character symbols are set italic, Greek, or script. Examples
are $u$, $L$ [note that $\upsilon$ (Greek upsilon) is used instead of
\textit{v} (italic ``vee'') to avoid confusion with $\nu$ (Greek nu) often
used for viscosity; this is handled automatically when in \LaTeX\ math mode],
$w$, $x$, $y$, $z$, $f$, $g$, $r$, indices such as $i$ or $j$, and constants
such as $C_D$, $k$, or $K$. Multiple-character scalar variables,
abbreviations, nondimensional numbers, and acronyms for variables are set
regular nonitalic: $\mathrm{LWC}$, $\mathrm{Re}$, $\mathrm{Ro}$,
$\mathrm{BT}$, $\mathrm{abs}$, $\mathrm{obs}$, $\mathrm{max}$,
$\mathrm{min}$, $\mathrm{Re}$/$\mathrm{Im}$ (real/imaginary), etc. For
vectors, use boldface nonitalic Times Roman as in $\mathbf{V}$, $\mathbf{v}$,
or $\mathbf{x}$, and $\mathbf{i}$, $\mathbf{j}$, and $\mathbf{k}$ unit
vectors. Do not use the \LaTeX\ $\backslash$vec command to denote vectors.
For matrix notation, use nonitalic boldface Arial (or sans serif) font as in
$\pmb{\mathsf{A}}$, $\pmb{\mathsf{B}}$, or $\pmb{\mathsf{M}}$. Note that you will need to use the 
$\backslash$pmb command for boldface sans serif; the $\backslash$bm command will not work. All mathematical
operator abbreviations/acronyms are set lowercase regular Roman font, except
$O$ (on the order of): $\sin$, $\cos$, $\tan$, $\tanh$, $\mathrm{cov}$, $\Pr$
(for probability; note same as Prandtl number), $\mathrm{const}$ (for
constant), $\mathrm{c.c.}$ (complex conjugate).

\subsection{Units}
Units are always set on a single line with a space separating the
denominator, which is set with a superscript $-1$, $-2$, and so on, rather
than using a slash for ``per.'' Examples are g kg$^{-1}$, m$^2$ s$^{-1}$, W
m$^{-2}$, g m$^{-3}$, and m s$^{-1}$ (note that ms$^{-1}$ is the unit for
``per millisecond'').

\subsection{Equations}
Brief equations or terms set inline in text must be set as a single-line
expression because page proofs are not double spaced, for example,
$\rho^{-1}p/x$ or $(1/{\rho})p/x$ or $(a-b)/(c+d)$; that is, use a
superscript $-1$ for the denominator. In case of a more complicated term or
equation, it should be set as an unnumbered display equation, such as
\begin{displaymath} x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  \end{displaymath}

Otherwise, numbered display equations can be entered using the appropriate
equation command, such as \begin{equation}
x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  \end{equation}

Lists of equations are punctuated as written English, and commas, semicolons,
and periods are placed where appropriate. Conjunctions such as ``and,''
``while,'' ``when,'' or ``for'' are also typically placed before the final
element in a mathematical phrase, as befits the intended mathematical
meaning.

\section{Figures and tables}
The AMS prefers that all figures and tables are placed {\bf at the end of the document} prior to submission. 
A list of tables and a list of figures will appear near the end of the PDF
file, before the actual tables and figures. These lists are necessary for submission.

For appendix figures and tables, special commands are needed to manually 
change the numbering to ensure that each appendix figure or table is numbered 
as part of the respective appendix and not as a continuation of the main paper. Use the command
$\backslash$appendcaption\{\} instead of the usual $\backslash$caption\{\} to adjust the 
numbering; for example, for Table A1, you would use the command \verb+\appendcaption{A1}+.

Note that the normal $\backslash$ref\{\} command cannot be used to cite 
appendix figures and tables as the numbering will be incorrect. Callouts for appendix figures 
and tables in the text will need to be written out as plain text, for example, Fig. A1 and Table A1.

\subsection{Figures}
The insertion of a sample figure (Fig. \ref{f1})  
and caption is given below (in the .tex document) and at the end of the document. Standard figure sizes are 19 (one column), 
27, 33, and 39 (two columns) picas.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURES---PLACE AT END OF DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{figure}[h]
% \centerline{\includegraphics[width=19pc]{figure01.pdf}}
%  \caption{Enter the caption for your figure here.  Repeat as
%  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
%\end{figure}
%

\subsection{Tables}
Each table must be numbered, provided with a caption, and mentioned
specifically in the text. 
See below (in the .tex document) and at the end of the document for the formatting of a sample table (Table
\ref{t1}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLES---PLACE AT END OF DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[h]
%\caption{This is a sample table caption and table layout.  
%Table from Lorenz (1963).}\label{t1}
%\begin{center}
%\begin{tabular}{ccccrrcrc}
%\topline
%$N$ & $X$ & $Y$ & $Z$\\
%\midline
% 0000 & 0000 & 0010 & 0000 \\
% 0005 & 0004 & 0012 & 0000 \\
% 0010 & 0009 & 0020 & 0000 \\
% 0015 & 0016 & 0036 & 0002 \\
% 0020 & 0030 & 0066 & 0007 \\
% 0025 & 0054 & 0115 & 0024 \\
%\botline
%\end{tabular}
%\end{center}
%\end{table}
%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
Keep acknowledgments (note correct spelling: no ``e'' between the ``g'' and
``m'') as brief as possible. In general, acknowledge only direct help in
writing or research. Financial support (e.g., grant numbers) for the work
done, for an author, or for the laboratory where the work was performed is
best acknowledged here rather than as footnotes to the title or to an
author's name. Contribution numbers (if the work has been published by the
author's institution or organization) should be included as footnotes on the title page,
not in the acknowledgments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% APPENDIXES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% If only one appendix, use
%%\appendix%

%% If more than one appendix, use \appendix[<letter>], e.g.,
 \appendix[A]

\appendixtitle{Title of Appendix}

\subsection{Appendix section}

The AMS template allows authors to format an unlimited number of
appendixes. To format a single appendix, use the $\backslash$appendix
command with no additional argument. Otherwise, add the appropriate
one-letter argument to the $\backslash$appendix command (e.g.
$\backslash$appendix[A], $\backslash$appendix[B],
$\backslash$appendix[C], etc.) corresponding to the appropriate
appendix.

The title of the appendix can be formatted using the
$\backslash$appendixtitle{\tt\string{\string}} 
 command. The $\backslash$subsection, $\backslash$subsubection,
and $\backslash$paragraph commands are used to create sections within
the appendix. (Note that the appendix title takes the place of $\backslash$section 
in the appendix, so the first section should begin with $\backslash$subsection
instead of $\backslash$section.)
 Equations are automatically numbered appropriately for 
each appendix. Here is an example of the first equation in appendix
A, automatically labeled (\ref{eq:1}): 
\begin{equation} \label{eq:1}
x=\frac{2b\pm\sqrt{b^{2}-4ac}}{2c}.  
\end{equation}

For appendix figures and tables, special commands are needed to manually 
change the numbering to ensure that each appendix figure or table is numbered 
as part of the appendix and not as a continuation of the main paper. Use the command
$\backslash$appendcaption\{\} instead of the usual $\backslash$caption\{\} to adjust the 
numbering; for example, for Table A1, you would use the command \verb+\appendcaption{A1}+.
In-text callouts for each appendix figure and table will need to be written as plain text;
the usual $\backslash$ref\{\} command cannot be used.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%APPENDIX FIGURE AND TABLE EXAMPLES---PLACE AT END OF DOCUMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{table}
%\appendcaption{A1}{Here is the appendix table caption.}
%\centering
%\begin{tabular}{ccc}
%a&b&c\\
%d&e&f
%\end{tabular}
%\end{table}
%
%\begin{figure}
%\centerline{(illustration here)}
%\appendcaption{A1}{Here is the appendix figure caption.}
%\end{figure}
%

\appendix[B]
\appendixtitle{File Structure of the AMS \LaTeX\ Package}

\subsection{AMS \LaTeX\ files}
You will be provided with a tarred, zipped \LaTeX\ package containing 
17 files. These files are

\begin{description}
\item[Basic style file:] ametsoc.cls.

The file ametsoc.cls is the manuscript style file.

\begin{itemize}
\item
Using \verb+\documentclass{ametsoc}+ for your .tex document
will 
generate a PDF that follows all AMS guidelines for submission and peer
review.

\item
Using \verb+\documentclass[twocol]{ametsoc}+ for your .tex document
can be used to generate a PDF that closely
follows the layout of an AMS journal page, including single spacing and two
columns.  This journal style PDF is only for the author's personal use, and
any papers submitted in this style will not be accepted.  
\end{itemize}
Always use \verb+\documentclass{ametsoc}+ 
when generating a PDF for submission to the AMS.

\item[Template:]
template.tex, for the author to use when making his/her
paper.
The file provides a basic blank template with some
section headings for authors to easily enter their manuscript.

\item[Sample .tex and .pdf files:]
The file amspaper.tex contains the \LaTeX\ code for the sample file.  
The resulting PDF can be seen in amspaper.pdf (this file).

\item[Sample article:] article formatted in draft and two-column mode.

\begin{itemize}
\item
AMSSamp1.tex, AMSSamp1.pdf\\
Formal paper done in draft mode and the resulting .pdf.

\item
AMSSamp2.tex, AMSSamp2.pdf \\
The same paper using the \verb+[twocol]+ option and the resulting .pdf.

\item
FigOne.pdf, FigTwo.pdf, and figure01.pdf are sample figures.

\end{itemize}

\item[Bibliography Files:]

ametsoc2014.bst, database2014.bib, and references.bib.

\begin{itemize}
\item
ametsoc2014.bst is the bibliography style file.

\item
database2014.bib is an example of a bibliographic database file.

\item
references.bib should be altered with your own bibliography information.  
\end{itemize}

\item[Documention:] found in AMSDocs.pdf. Additional information
found in
readme.txt, which contains a list of the files and how they are used.

\end{description}

\subsection{Help for Authors}
Questions and feedback concerning the use of the AMS \LaTeX\ files should be
directed to latex@ametsoc.org. Additional information is available on the AMS
\LaTeX\ Submission Info web page (\url{http://www2.ametsoc.org/ams/index.cfm/publications/authors/journal-and-bams-authors/author-resources/latex-author-info/}).

\appendix[C]
\appendixtitle{Building a PDF and Submitting Your 
\LaTeX\ Manuscript Files to the AMS}

\subsection{Building your own PDF}
There are a variety of different methods and programs that will create a
final PDF from your \LaTeX\ files. The easiest method is to download one of
the freely available text editors/compilers such as TexWorks or TeXnicCenter.
TexWorks is installed with the TeXLive distribution and provides both a text
editor and the ability to compile your files into a PDF.

\subsection{Submitting your files to the AMS for peer review}
The AMS uses the Editorial Manager system for all author submissions for
peer review. Editorial Manager uses the freely available \TeX\ Live 2011
distribution. This system will automatically generate a PDF from your
submitted \LaTeX\ files and figures.

You should not upload your own PDF into
the system. If the system does not build the PDF from your files correctly,
refer to the AMS \LaTeX\ FAQ page first for possible solutions. If your PDF
still does not build correctly after trying the solutions on the FAQ page, email
latex@ametsoc.org for help.

\subsection{Other software}
As mentioned above, there is a variety of software that can be used to edit
.tex files and build a PDF.  The AMS does not support \LaTeX\/-related
WYSIWYG software, such as Scientific Workplace, or WYSIWYM software, such as
LyX.  \TeX\ Live (available online at \\ \url{http://www.tug.org/texlive/}) is
recommended for users needing an up-to-date \LaTeX\ distribution with
software that includes an editor and the ability to automatically generate a
PDF.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 This shows how to enter the commands for making a bibliography using
 BibTeX. It uses references.bib and the ametsoc2014.bst file for the style.

 \bibliographystyle{ametsoc2014}
 \bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\caption{This is a sample table caption and table layout.}\label{t1}
\begin{center}
\begin{tabular}{ccccrrcrc}
\topline
$N$ & $X$ & $Y$ & $Z$\\
\midline
 0000 & 0000 & 0010 & 0000 \\
 0005 & 0004 & 0012 & 0000 \\
 0010 & 0009 & 0020 & 0000 \\
 0015 & 0016 & 0036 & 0002 \\
 0020 & 0030 & 0066 & 0007 \\
 0025 & 0054 & 0115 & 0024 \\
\botline
\end{tabular}
\end{center}
\end{table}
%

\begin{table}
\appendcaption{A1}{Here is the appendix table caption.}
\centering
\begin{tabular}{ccc}
\topline
$1$ & $2$ & $3$ \\
\midline
a&b&c \\
d&e&f \\
\botline
\end{tabular}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h]
 \centerline{\includegraphics[width=19pc]{figure01.pdf}}
  \caption{Enter the caption for your figure here.  Repeat as
  necessary for each of your figures. Figure from \protect\cite{Knutti2008}.}\label{f1}
\end{figure}

\begin{figure}
\centerline{(illustration here)}
\appendcaption{A1}{Here is the appendix figure caption.}
\end{figure}

\begin{figure}
\centerline{(illustration here)}
\appendcaption{B1}{Here is the appendix figure caption.}
\end{figure}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% END OF AMSPAPER.TEX
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2021-01-18 A01_ice_surface_fluxes.tex
Text update 20210118

@@
-Momentum flux
+The turbulence closure scheme is Anisotropic Minimum Dissipation (Rozema) employing the extension to scalars introduced by Abkar and Moin.
+Our implementation shows similar qualitative behavior to the stable atmospheric boundary layer published in XX; some inter-model variability is expected due to different numerics.
 
-    Components of surface stress $\tau_i$
-    \begin{equation*}
-    \tau_i = \rho \overline{u_i''w''}
-    \end{equation*}
-    for i = 1,2.
-
-    Friction velocity $u_*$
-    \begin{equation*}
-    u_*^2=|\tau_0|^{1/2}
-    \end{equation*}
-    % \begin{equation*}
-    % u_*^2=(\overline{u''w''}^2 + \overline{v''w''}^2)^{1/2}
-    % \end{equation*}
-
-    Turbulence closure
-    \begin{equation*}
-    \overline{u_i''w''} = k_m \frac{\partial u_i}{\partial z}
-    \end{equation*}
-
-    There is empirical support for a linear increase in eddy diffusivity from the wall
-    \begin{equation*}
-    u_* = \frac{k z}{\Psi_m(\zeta) } \frac{\partial u}{\partial z}
-    \end{equation*}
-    where $\zeta = z/L_O$
-
-    We integrate using this relationship (or $\Psi = 1$ to get $u_*$
-    \begin{equation*}
-    \Psi_m(\zeta) = 1 + \beta_m \zeta
-    \end{equation*}
-    where $\beta_m = 4.8$ (Wyngaard 2010; Zhou et al. 2017)
-
-    We integrate using this relationship to get $u_i''w''$
-    \begin{equation*}
-    \beta_m = (\frac{1}{R_c} + \frac{f L_O}{u_* \chi_N})(1-\eta_*)
-    \end{equation*}
-    (McPhee 1981)
-
-    % Integrating for $u(z)$ (this is never needed because all we need is stress
-    % \begin{equation*}
-    % u = \frac{u_*}{k} ln(frac{z}{z_0} + \frac{\beta_m}{k}\zeta + C_m
-    %\end{equation*}
-    % \begin{equation*}
-    % u = \frac{u_*}{k} ln(frac{z}{z_0} = c_d(z)^{\frac{-1}{2}}u_*
-    % \end{equation*}
-    % The friction velocity is defined following "law of the wall"
-    % \begin{equation}
-    %     u_* = \kappa u_m / log(z_m/z_0)
-    % \end{equation}
-
-    \begin{equation*}
-    \overline{u_i''w''}(z_1) = u_* (\phi_i(\textbf{u(z_1)}))
-    \end{equation*}
-
-    McPhee (1983) presented a shape function for stress as a function of distance from the surface, which we use here to solve for momentum fluxes near the surface.
-
-    First, we choose a depth at which the horizontal velocity is thought to be representative of the boundary layer flow (i.e., at least a couple grid points away from the interface where boundary layer effects can be unrealistic).
-We denote this depth $z_m$.
-
-    The shape profile for stress is defined as a function of non-dimensional depth $\zeta$
-    \begin{equation}
-        \zeta = \frac{z}{\eta_* u_*/f}
-    \end{equation}
-
-    $\eta_*$ is a scaling parameter meant to account for the stabilizing effects of a buoyancy flux, equal to 1 when melt rates are 0 and approaching 0 when melt rates are high.
-    \begin{equation}
-        \eta_*^2 = (1+\frac{\xi_N u_*}{f L_O Ri_c})^{-1}
-    \end{equation}
-    where $L_O$ is the Monin-Obukhov length
-    \begin{equation}
-        L_O = \rho \frac{u_*^3}{\kappa F_B}
-    \end{equation}
-
-    \begin{equation}
-	F_B = g(\beta w'S' - \alpha w'\theta')
-	\end{equation}
-
-    \begin{equation}
-        \tau = exp(\frac{i \zeta}{\kappa \xi_N})^{1/2}
-    \end{equation}
-    \begin{equation}
-        \phi_1 = (u_1* RE(\tau) + u_2* IM(\tau))
-    \end{equation}
-    \begin{equation}
-        \phi_2 = (u_2* RE(\tau) + u_1* IM(\tau))
-    \end{equation}
-
-    \begin{equation}
-        u''w'' = \rho |u_*| (u_* RE(\tau) + v_* IM(\tau))
-    \end{equation}
-    \begin{equation}
-        v''w'' = \rho |u_*|(v_* RE(\tau) + u_* IM(\tau))
-    \end{equation}
+Momentum and scalar fluxes at the top of the domain are parameterized assuming law of the wall and a linear stability function in which depth is scaled by the Monin-Obukhov length, following Vreugdenhil and Taylor (2019).
+Details can be found in Appendix XX.
+Scalar fluxes at the top of the domain take the ``virtual" freshwater flux form \cite{XX}.
+The solution for ice-shelf melting at the interface follows the standard procedure of solving three equations -- local heat conservation, local salt conservation, and the interface temperature set to the freezing point -- for three unknowns, the temperature and salinity at the ice-ocean interface, and the melt rate.
+This is the so-called three-equation parameterization.
+For the freezing temperature equation we use the polynomial function from \cite{jackett_2006}.
+We also assume that the conductive heat flux into ice is zero, as it is typically no more than 10\% of the latent heat used for melting.

### 2021-01-18 A_suppl_fig.tex
Text update 20210118

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Timeseries of maximum vertical velocity fluctuation per hour for thermal driving cases}
    \label{fig:max_w2_timeseries}
\end{figure}

### 2021-01-18 main.tex
Text update 20210118

@@
 \usepackage{lineno}
+
+\usepackage{xr}
+\makeatletter
+\newcommand*{\addFileDependency}[1]{% argument=file name and extension
+  \typeout{(#1)}
+  \@addtofilelist{#1}
+  \IfFileExists{#1}{}{\typeout{No file #1.}}
+}
+\makeatother
+
+\newcommand*{\myexternaldocument}[1]{%
+    \externaldocument{#1}%
+    \addFileDependency{#1.tex}%
+    \addFileDependency{#1.aux}%
+}
+\myexternaldocument{A_suppl_fig}
+
 \linenumbers
@@
 \begin{document}
-\input{agu_begindoc.tex}
+%\input{agu_begindoc.tex}
+\title{Large-eddy simulations of the ice-shelf oceanic boundary layer}
 
-\section{Introduction}
+\correspondingauthor{Carolyn Begeman}{cbegeman@lanl.gov}
+\authors{Carolyn Branecky Begeman\affil{1},Xylar Asay-Davis\affil{1}, and Luke Van Roekel\affil{1}}
 
-\paragraph{}% from CK application
+\affiliation{1}{Los Alamos National Laboratory, Los Alamos, New Mexico, USA}
+
+\begin{keypoints}
+\item 
+\item 
+\item 
+\end{keypoints}
+
+\begin{abstract}
 Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
 Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.
-These critical processes are not captured by even the most advanced Earth System Models (ESMs), such as the DOE’s Energy Exascale Earth System Model (E3SM), of which LANL is a major developer.
 Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
@@
 
-% from postdoc proposal
+\textbf{Plain language summary}\\
+
+\end{abstract}
+\newpage
+\section{Introduction}
+
+\paragraph{}
 The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet.
 The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice.
-In turn, the Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base; accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
+The Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base.
+Thus, accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
+This representation is also critical for evaluating the sensitivity of the coupled land-ice ocean system.
+
+\paragraph{}
+The sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
+
+\paragraph{}
 One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution.
@@
 
-I propose to develop a new parameterization of ice-shelf melting by modeling turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
+\paragraph{}
+In this study, we model turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
 Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
-During the first year of the project, I will simulate the IOBL using the MIT General Circulation Model (MITgcm) in a LES ocean configuration.
 An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface.
-I will vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates when the modeled IOBL has equilibrated.
-During the second year of the project, I will implement the resulting parameterization in the Model for Prediction Across Scales Ocean (MPAS-O), the ocean component of DOE’s new Energy Exascale Earth System Model (E3SM).
-Using MPAS-O in idealized configurations, I will investigate the parameterization’s impact on sub-ice-shelf ocean circulation and the distribution of ice-shelf melting as compared with previous parameterizations.
-I will focus on the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
-Resources for this work include MPAS-O, developed at LANL, and existing allocations at a number of DOE HPC facilities (including LANL).
+We vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates.
 
-The proposed work, characterizing turbulence in the presence of a buoyancy flux and sloping boundary, addresses a fundamental problem in fluid dynamics.
-The work also has direct societal relevance because ice-ocean interactions are believed to be a major control on future sea level rise.
-This new parameterization for ice-shelf melting will support an ongoing effort at LANL and other national labs to accurately couple ice sheet and ocean models and will be exportable from MPAS-O to other models.
-Thus, in addition to significantly improving simulations of ocean circulation, Antarctic ice loss, and sea level rise in E3SM, it could provide similar advances to other Earth system modeling efforts.
+\paragraph{}
+Characterizing turbulence in the presence of a buoyancy flux and sloping boundary is a fundamental problem in fluid dynamics.
 
@@
 
-	%\paragraph{The PALM model}
+\paragraph{The PALM model}
 The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany).
@@
 For this application, the key model development was the implementation of dynamic melting fluxes.
+
+\subsection{Governing equations}
+
+%Mass conservation for incompressible flows
+%\begin{equation} \label{eq:volconserv}
+%\frac{\partial u_j}{\partial x_j} = 0
+%\end{equation}
+%The model enforces incompressibility with 
+%\begin{equation} \label{eq:pdiv}
+%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
+%\end{equation}
 
@@
 The terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum fluxes.
+% Prognostic equation for Resolved TKE
+% \begin{equation} \label{eq:eprog}
+% \frac{\partial e^*}{\partial t} = 
+% -u_j \frac{\partial e^*}{\partial x_j} 
+% - (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
+% \end{equation}
 
-	\paragraph{Sloping surface}
-	We represent a sloping ice base by rotating the gravity and Coriolis vectors while keeping the domain a rectangular prism. The ice base always slopes in the x-dimension of our domain. 
+%\paragraph{}% Sloping surface
+We represent a sloping ice base by rotating the gravity and Coriolis vectors while keeping the domain a rectangular prism. 
 %In PALM v0 the buoyancy terms were based only on temperature rather than density. 
@@
 \begin{equation} \label{eq:g}
-    	\textbf{g} = g [sin \alpha,0,cos \alpha]
+	%\textbf{g} = g [sin \alpha,0,cos \alpha]
+	\textbf{g} = g [sin \alpha sin \beta,cos \beta,cos \alpha]
 \end{equation}
@@
 \end{equation}
+$\beta$ is the angle the slope direction makes with north.
+$\alpha$ is the slope angle from horizontal
+$\phi$ is the latitude.
+The ice base always slopes in the positive x-dimension of our domain or east, thus $\beta = 0$.
 
-	The buoyancy term combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density.
+The buoyancy term in Equation \ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density.
 The along-slope pressure gradient is set by the ambient density of the water column $\rho_a$.
-This ambient density is determined using the far-field temperature and salinity values and the initial vertical hydrostatic pressure profile in the middle of the domain.
-Thus, we assume that the evolution of density in the boundary layer does not significantly affect ice-shelf slope.
-We also assume that
-	\begin{equation}
-	    \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
-	    \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
-	\end{equation}
-	In other words, we assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes.
-These density differences are verified to be within XX $kg/m^3$ for these simulations.
+This ambient density is determined using the initial far-field ocean density.
+For a non-sloping domain, $\rho_a$ = $\rho_i$
+% the far-field density remains constant during the simulation due to relaxation boundary conditions
+% temperature and salinity values and the initial vertical hydrostatic pressure profile in the middle of the domain. 
+%Thus, we assume that the evolution of density in the boundary layer does not significantly affect buoyancy/ice-shelf slope. 
+We neglect hydrostatic pressure gradients along slope.
+For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 1 bar m\textsuperscript{-1}.
+% or 10 pa/m
 This simplification has the advantage of avoiding pressure discontinuities across periodic boundary conditions. 
+%We assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes. 
+% \begin{equation}
+%     \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
+%     \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
+% \end{equation}
+%These density differences are verified to be within XX $kg/m^3$ for these simulations.
 
-	\paragraph{Surface drag}
+%\paragraph{}%Surface drag
 The last term in Equation \ref{eq:uprog} represents the loss of momentum due to drag between the ice surface and the flow, where $\tau$ is the shear stress.
-We discuss the parameterization of $\tau$ in XX.
-
-	%Mass conservation for incompressible flows
-	%\begin{equation} \label{eq:volconserv}
-	%\frac{\partial u_j}{\partial x_j} = 0
-	%\end{equation}
-	%The model enforces incompressibility with 
-	%\begin{equation} \label{eq:pdiv}
-	%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
-	%\end{equation}
+This term is parameterized by the sub-grid scheme.
 
@@
 
-	%Turbulence closure by the gradient mean approximation
-	%\begin{equation} \label{eq:momdiff}
-	%\overline{u''_i u_j''} - \frac{2}{3}e \delta_{ij} = -K_m(\frac{\partial u_i}{\partial x_j} + \frac{\partial u_j}{\partial x_i})
-    %\end{equation}
+\subsection{Turbulence closure}\label{meth:tcm}
 
-	%\begin{equation} \label{eq:ptdiff}
-	%\overline{u''_i \theta''} = -K_h \frac{\partial \theta}{\partial x_i}
-	%\end{equation}
+The turbulence closure scheme is Anisotropic Minimum Dissipation (Rozema) employing the extension to scalars introduced by Abkar and Moin.
+Our implementation shows similar qualitative behavior to the stable atmospheric boundary layer published in XX; some inter-model variability is expected due to different numerics.
 
-	%\begin{equation} \label{eq:e}
-	%e = \frac{1}{2}\overline{u'_i u'_i}
-	%\end{equation}
+Momentum fluxes are parameterized according to law of the wall following a linear stability function as in Vreugdenhil and Taylor (2019):
 
-    Prognostic equation for Resolved TKE
-	\begin{equation} \label{eq:eprog}
-	\frac{\partial e^*}{\partial t} = 
-	-u_j \frac{\partial e^*}{\partial x_j} 
-	- (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
+\begin{equation}
+    \vec{\tau} = \rho \overline{\vec{u}'w'} = \rho u_* \frac{ \kappa (u(z_1) - u_b}{\textrm{ln}(z_1/z_0)-\Psi_m(\zeta_1)}
 \end{equation}
 
-	The turbulence closure scheme is XX. We refer the readers to XX for the details.
+where $\zeta_k = z_k/L_O$, friction velocity $u_*$, $z_0$ is the roughness length, and $z_1$ is the evaluation depth at the uppermost grid cell.
+\begin{equation}
+    \Psi_m(\zeta) = 1 + \beta_m \zeta
+\end{equation}
 
-	Large-scale horizontal pressure gradients are used to drive mean flow and mean shear.
+Similarly the sub-grid fluxes of scalars are parameterized
+\begin{equation}
+    \overline{w'\theta'} = \Gamma_{\theta} u_* (\theta(z_1) - \theta_b),\: 
+    \overline{w'S'} = \Gamma_S u_* (S(z_1) - S_b)
+\end{equation}
+
+\begin{equation}
+    \Gamma_{\theta}^{-1} = (\Gamma_{\theta,turb} + \Gamma_{\theta,mol})^{-1},\:
+    \Gamma_S^{-1} = (\Gamma_{S,turb} + \Gamma_{S,mol})^{-1}
+\end{equation}
+
+\begin{equation}
+    \Gamma_{\theta,turb} = \kappa^{-1} (\textrm{ln}(z_1/z_0) - \Psi_{\theta}(\zeta_1))
+    % + \Psi(z_0/L_O)) % correction for roughness length
+\end{equation}
+\begin{equation}
+    \Gamma_{S,turb} = \kappa^{-1} (\textrm{ln}(z_1/z_0) - \Psi_S(\zeta_1))
+    % + \Psi(z_0/L_O)) % correction for roughness length
+\end{equation}
+If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($Gamma_{f}$, Table \ref{table:var}).
+
+\begin{equation}
+    \Psi_{\theta,S}(\zeta) = 1 + \beta_{\theta,S} \zeta
+\end{equation}
+The coefficients of these stability functions are chosen as in Wyngaard 2010; Zhou et al. 2017 (Table \ref{table:var}.
+
+\begin{equation}
+    \Gamma_{\theta,mol} = 12.5 \textrm{Pr}^{2/3} - 6
+\end{equation}
+\begin{equation}
+    \Gamma_{S,mol} = 12.5 \textrm{Sc}^{2/3} - 6
+\end{equation}
+where Pr is the Prandtl number and Sc is the Schmidt number. %similarly for $\Gamma_{S,mol}$ but with Schmidt number.
+
+We use ``virtual" freshwater fluxes as opposed to freshwater fluxes with mass or volume; thus, the scalar fluxes take the form \cite{XX}
+\begin{equation}
+    \overline{w'\theta'} = -c_p u_*
+    (\Gamma_{\theta} - \Gamma_S \frac{S_b - S_1}{S_b})(\theta_b-\theta)
+    %\rho_{sw}\overline{w'\theta'} = c_p(\rho_{sw} \Gamma_T u_* + \rho_{fw} m)(T(z_1) - T_b)
+\end{equation}
+
+\begin{equation}
+    \overline{w'S'} = -u_*
+    (\Gamma_S - \Gamma_S \frac{S_b - S_1}{S_b})(S_b-S)
+    %\rho_{sw}\overline{w'S'} = (\rho_{sw} \Gamma_S u_* + \rho_{fw} m)(S(z_1) - S_b)
+\end{equation}
+
+%\subsection{Prognostic melt calculation}
+The temperature and salinity at the ice-ocean interface, $\theta_b$ and $S_b$, are unknown.
+Three equations are used to solve for these quantities and the melt rate, the so-called three-equation parameterization:
+
+\begin{equation}\label{eq:melt_1}
+    \rho c_p \overline{w'\theta'}_b = -\rho_f m L_i
+    %\rho c_p \overline{w'\theta'}_b - F_{T,cond} = -\rho_{fw} m L_i
+\end{equation}
+
+\begin{equation}\label{eq:melt_2}
+    \rho \overline{w'S'}_b = −\rho_f m S_b
+\end{equation}
+
+\begin{equation}\label{eq:melt_3}
+    \theta_b = \theta_f(p,S_b)
+\end{equation}
+
+These equations specify that heat and salt are conserved at the ice-ocean interface (Equations \ref{eq:melt_1} and \ref{eq:melt_2})and the interface temperature is fixed at the local freezing temperature using the polynomial function from \cite{jackett_2006} (Equation \ref{eq:melt_3}).
+Equation \ref{eq:melt_1} assumes that the conductive heat flux into ice is 0.
+% short version in A01
+
+\subsection{Simulation set-up}
+
+The domain is a 64 m$^3$ cube with horizontal resolution of 0.5 m and vertical resolution of 0.25 m.
+The ice-ocean interface is located on the top boundary of the domain.
+Large-scale horizontal pressure gradients drive the mean flow, which is geostrophic in the far-field where buoyancy does not modify the flow.
+We choose a pressure of 800 dbar at the top of the domain, a rather arbitrary choice given that the depth of ice shelf bottoms ranges an order of magnitude (roughly -2000 m to -200 m).
+The potentially dynamically relevant differences between conducting these simulations at surface pressure and 800 dbar is that the first derivative of the freezing temperature with respect to salinity is 20\% smaller and the first derivative of density with respect to salinity is about 100\% larger.
 
 %\paragraph{Initial and boundary conditions}
-	Boundary conditions for velocity, temperature and salinity are cyclic at the side boundaries, dirichlet at the bottom boundary, and von Neumann at the top boundary. 
-	The bottom third of the domain is a sponge layer within which velocity, temperature, and salinity are relaxed toward their values at the bottom of the domain.
-The temperature and salinity at the bottom of the domain are chosen to represent typical sub-ice-shelf water masses.
-XX.
+Boundary conditions for velocity, temperature and salinity are cyclic at the side boundaries, Dirichlet at the bottom boundary, and von Neumann at the top boundary.
+The bottom third of the domain is a sponge layer within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain.
 The sponge layer results in no vertical fluxes of heat, salt, or momentum across the bottom boundary.
+The von Neumann boundary conditions at the top of the domain correspond to the sub-grid fluxes of heat, salt and momentum (Equations XX), as resolved fluxes go to zero at a no-penetration boundary.
+The drag coefficient for all simulations is 0.003, a canonical value below sea ice and ice shelves though poorly constrained \cite{XX}.
+The drag coefficient sets the roughness length $z_0$ in the boundary flux equations of Section \ref{sec:meth_sgs} through the quadratic drag ``law of the wall." A complete list of parameter choices can be found in Table \ref{table:var}.
+
+There are two sets of simulations which have a base case in common.
+The base case has low far-field thermal driving of 0.1 $^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field geostrophic flow of 20 cm s$^{-1}$ to the [XX east].
+These conditions were chosen to favor a high TKE regime, for reasons discussed in Section \ref{sec:disc}.
+To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.1 $^{\circ}$C to 0.5 $^{\circ}$C in the first set of simulations.
+In the second set of simulations we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.
+
+The far-field salinity for all runs is 35 g kg\textsuperscript{-1}.
+Initially, both temperature and salinity increase with depth over the upper two-thirds of the domain.
+The background salinity stratification dominates the density stratification, with an inverse stability ratio $R_\rho^*$ of 20.
+
+The simulation duration is 50 h, corresponding to a little over 4 inertial periods.
+By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S\ref{fig:max_w2_timeseries}).
+
+\section{Results}
+
+% Sensitivity to thermal driving
+
+The fluctuations in TKE with flow orientation under inertial oscillations are replicated when the mean pressure gradient is rotated, with increased TKE when flow is oriented downslope (not shown or supplemental).
+
+\section{Discussion}
+
+This is the second LES study of the ice-shelf ocean boundary layer in which the boundary layer turbulence declines throughout the coarse of the simulation \cite{XX}.
+This results in declining melt rates as well, making it difficult to evaluate the relationship between melting and far-field conditions at steady state -- which has been central to the goal of improving ice-shelf basal melt parameterizations with the results of high-resolution simulations.
+There are a few possible explanations for this phenomenon.
+Perhaps the best candidate is that either the sub-grid scheme or the model numerics are too dissipative, such that the TKE generated by the resolved dynamics is lost too quickly.
+Another possibility is that we are missing or underestimating a source of TKE in the model.
+Tides were not in
+
+Furthermore, the simulations shown here have a sufficiently strong salinity gradient that the potential energy stored in the temperature gradient is not converted to TKE.
+Simulations now shown here suggest that simulated TKE can be maintained when stability ratios are as low as 4, but a detailed exploration of this phenomenon is not within the scope of the current work as LES cannot allow for the development of double-diffusive convection, which may occur when the stability ratio is lower than \~ 10.
+%It appears that well-mixed boundary layers are produced for a narrower range of conditions in simulations than in observations.
 
@@
 \subsection{Tables}
-\input{table1.tex}
+\input{table1_prm-only}
 

### 2021-04-16 extract_var_palm.py
Add files via upload

@@ -1,0 +1,970 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+@author: cbegeman
+"""
+import math,os
+from netCDF4 import Dataset
+import numpy as np
+import numpy.ma as ma
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import matplotlib.ticker as tick
+import my_array_mod as ar
+import my_string_mod as strop
+import convert_NCAR_mod as ncar
+import difflib
+import gsw
+import cmocean as cmo
+
+#global var,data
+
+# parameters
+K0 = 273.15 # temperature (K) at 0 degC
+g = -9.81
+xi_N = 0.0052
+Ri_crit = 0.2
+s_yr = 24.*3600.*365.25
+s_hr = 3600.
+
+# plotting parameters
+lw1 = 2 
+lw2 = 3
+lw3 = 1 
+
+# list of variables on u grid. TODO check e
+uvar = ['xu','yv','zu','zv','zu_xy','zu_3d',
+        'U','u','u"','u*','umax','vmax','v','v"',
+        'dEdt','E','E*','dedt','e','e*','u*2','v*2',
+        'Fshear','Ftrans','Fbuoy','FbuoyT','FbuoyS','diss',
+        'w*u*u*:dz','w*p*:dz','N1','N2','S2','Ri','Rf',
+        'km','kh','l','e*','w*e*','u2v2','dudz','dvdz','dUdz']
+
+# list of variables on scalar grid
+scvar = ['x','y','z','alpha_T','drho_oceandz','drho_gswdz','dprho_gswdz',
+         'pt','pt"','pt*2','sa','sa"','prho','rho_ocean','z_BL','z_SL',
+         'rho_gsw','prho_gsw','zu1_xy','sa*2']
+# list of variables on w grid
+wvar = ['melt','melt*_xy','shf*_xy','shf*_xy_av','sasws*_xy','u*_xy','z0*_xy',
+        'dz','zw','zw_xy','zw_3d','k_offset_mcph','Sk','km_eff','kh_eff',
+        'w','w"','w*2','zmin_w2','w*3','NORM_ws3','dT',
+        'wpt','w*pt*','w"pt"','wsa','w*sa*','wu','wv',
+        'wb','w"sa"','w*u*','w"u"','w*v*','w"v"','w"theta"0',
[…]

### 2021-04-16 run_standard.py

@@ -1,0 +1,63 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+from extract_var_palm import load_data,extract_var
+import sys
+import plot_palm_mod as palm
+import numpy as np
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+base_dir = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'
+#run1 = 'test_ocean_bsign_noslp_dSdz2_medres'
+#run1 = 'test_ocean_bsign_noslp_lowres'
+#run1 = 'test_ocean_bsign_modslp_warm_medres'
+run1 = 'test_ocean_bsign_modslp_hiresz'
+filedir1 = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+run1+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+
+plotvar_t = ['umax','vmax','melt','w"u"0','w"v"0','u*','dt','E','E*','ol','k_offset_mcph']
+plotvar = ['pt','sa','u','v']
+plotvar_pr = ['pt','sa','prho','w','Sw','S2','u2v2','u','v',
+              'w*u*','w"u"','w*v*','w"v"','vel_var_ratio',
+              'e*','e','km','kh','l','wpt','wsa','w"pt"','w*pt*','w"sa"','w*sa*','wu','wv']
+plotvar_varcmp = ['velocity','variance','momflux_z','heatflux_z','saltflux_z','tke']
+plotvar_flux = ['wv','wu','wpt','wsa']
+norm_pr = ['' for i in plotvar_pr]
+norm_pr[plotvar_pr.index('pt')] = 'far_diff'
+norm_pr[plotvar_pr.index('sa')] = 'far_diff'
+norm_3d = ['' for i in plotvar_pr]
+norm_3d[plotvar_pr.index('sa')] = 'mean'
+plotvar = ['pt','sa','u','v','w','e']
+plotvar2 = ['melt*_xy','u*_xy','ol*_xy',
+            'pt1*_xy','pt_io*_xy','thermal_driving','sa1*_xy','sa_io*_xy',
+            'haline_driving']#,'usws*_xy','vsws*_xy']
+plotvar_zlevel = ['pt','sa','u','v']
+runname = ''
+zmax = -50
+#zmax = -500
+
+#tplot = [98.]
[…]

### 2021-04-16 convert_NCAR_mod.py
Add files via upload

@@ -1,0 +1,36 @@
+"""
+Created on Wed Jan 30 13:09:33 2019
+
+@author: cbegeman
+"""
+from netCDF4 import Dataset
+import numpy as np
+
+def convert_NCAR(LES1):
+    
+    s_hr = 3600
+    LES1.variables['time'] = np.multiply(LES1.variables['Time'],s_hr)
+    LES1.variables['zu'] = LES1.variables['zt']
+    LES1.variables['zw'] = LES1.variables['zm']
+    LES1.variables['pt'] = np.add(LES1.variables['mean_temperature'],273.15)
+    LES1.variables['sa'] = LES1.variables['mean_salinity']
+    LES1.variables['u'] = LES1.variables['mean_U']
+    LES1.variables['v'] = LES1.variables['mean_V']
+    LES1.variables['w'] = LES1.variables['mean_W']
+    LES1.variables['u*2'] = LES1.variables['lesResolved_uu']
+    LES1.variables['v*2'] = LES1.variables['lesResolved_vv']
+    LES1.variables['w*2'] = LES1.variables['lesResolved_ww']
+    LES1.variables['w*u*'] = LES1.variables['lesResolveduwFlux'] #1e-5
+    LES1.variables['w"u"'] = LES1.variables['subGridScheme_uw'] #1e-8
+    LES1.variables['w*v*'] = LES1.variables['lesResolvedvwFlux']
+    LES1.variables['w"v"'] = LES1.variables['subGridScheme_vw']
+    LES1.variables['w*pt*'] = LES1.variables['lesResolvedwtFlux'] #1e-5
+    LES1.variables['w"pt"'] = LES1.variables['subGridScheme_wt']
+    LES1.variables['w*sa*'] = LES1.variables['lesResolvedwsFlux']
+    LES1.variables['w"sa"'] = LES1.variables['subGridScheme_ws']
+    LES1.variables['e'] = LES1.variables['sgsE']
+    LES1.variables['e*'] = 0.5*(LES1.variables['u*2'][:] + 
+                                  LES1.variables['v*2'][:] +
+                                  LES1.variables['w*2'][:] )
+
+    return LES1

### 2021-04-16 eval_buoy_zrot.py

@@ -1,0 +1,21 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 22 07:52:34 2019
+
+@author: cbegeman
+"""
+import math,os
+from netCDF4 import Dataset
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import matplotlib.ticker as tick
+import my_array_mod as ar
+import my_string_mod as strop
+import convert_NCAR_mod as ncar
+import extract_var_palm as pv 
+
+filedir = 
+uvar = pv.compute_variance(filedir,'u')

### 2021-04-16 my_array_mod.py

@@ -1,0 +1,16 @@
+"""
+Created on Tue Jan 22 12:50:47 2019
+
+@author: cbegeman
+"""
+
+import numpy as np
+
+def last_index(self):
+    return len(self)-1;
+
+def find_nearest(array, value):
+    array = np.asarray(array)
+    idx = (np.abs(array - value)).argmin()
+    val = array[idx]
+    return val,idx;

### 2021-04-16 my_string_mod.py

@@ -1,0 +1,30 @@
+"""
+Created on Tue Jan 29 11:54:36 2019
+
+@author: cbegeman
+"""
+
+def find_all(a_str, sub):
+    start = 0
+    while True:
+        start = a_str.find(sub, start)
+        if start == -1: return
+        yield start
+        start += len(sub) or 1 # use start += 1 to find overlapping matches
+
+def rm_palm_char(j):
+    name = j + '_'
+    
+    ridx = list(find_all(j,'*'))
+    if len(ridx) >= 1:
+        name = j[0:ridx[0]] + '_res_'
+    if len(ridx) == 2:
+        name = name + j[ridx[0]+1:ridx[1]] + '_res_'
+                                        
+    sidx = list(find_all(j,'"'))
+    if len(sidx) >= 1:
+        name = j[0:sidx[0]] + '_sgs_'
+    if len(sidx) == 2:
+        name = name + j[sidx[0]+1:sidx[1]] + '_sgs_'
+    
+    return name;

### 2021-04-16 namelist_default.py

@@ -1,0 +1,183 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+ininame    = ['dx','dy','dz']
+inivalue   = ['0.5','0.5','0.5']
+
+ininame.append('latitude')
+inivalue.append('-70.')
+
+ininame.append('nx')
+inivalue.append('63')
+ininame.append('ny')
+inivalue.append('63')
+ininame.append('nz')
+inivalue.append('128')
+
+ininame.append('ocean')
+inivalue.append('.T.')
+
+ininame.append('surface_pressure')
+inivalue.append('1013.25')
+
+ininame.append('reference_state')
+inivalue.append('single_value')
+
+ininame.append('initializing_actions')
+inivalue.append('set_constant_profiles')
+
+ininame.append('alpha_surface')
+inivalue.append('0')
+ininame.append('slope_parallel_gradients')
+inivalue.append('.T.')
+ininame.append('slope_offset')
+inivalue.append('.F.')
+ininame.append('ambient_density_for_buoyancy')
+inivalue.append('.T.')
+
+ininame.append('dp_external')
+inivalue.append('.T.')
+ininame.append('dpdxy')
+inivalue.append('0,0')
+ininame.append('dp_level_b')
+inivalue.append('0')
+
+ininame.append('ug_surface')
+inivalue.append('0.0')
+ininame.append('vg_surface')
+inivalue.append('0.0')
+
+ininame.append('pt_surface')
+inivalue.append('273.13')
+ininame.append('pt_vertical_gradient')
+inivalue.append('0.0')
+ininame.append('pt_vertical_gradient_level')
+inivalue.append('0.0')
+
+ininame.append('sa_surface')
+inivalue.append('34.5')
+ininame.append('sa_vertical_gradient')
+inivalue.append('0.0')
+ininame.append('sa_vertical_gradient_level')
+inivalue.append('0.0')
+
+ininame.append('use_top_fluxes')
+inivalue.append('.T.')
+ininame.append('use_surface_fluxes')
+inivalue.append('.F.')
+
+ininame.append('constant_flux_layer')
+inivalue.append('top')
+ininame.append('most_method')
+inivalue.append('mcphee')
+ininame.append('drag_coeff')
+inivalue.append('0.003')
[…]

### 2021-04-16 pysed.py

@@ -1,0 +1,73 @@
+#!/usr/bin/env python3
+__author__ = 'Mahmoud Adel <mahmoud.adel2@gmail.com>'
+__version__ = 0.4
+__license__ = "The MIT License (MIT)"
+
+import re
+
+def replace(oldstr, newstr, infile, dryrun=False):
+    '''
+    Sed-like Replace function..
+    Usage: pysed.replace(<Old string>, <Replacement String>, <Text File>)
+    Example: pysed.replace('xyz', 'XYZ', '/path/to/file.txt')
+    Example 'DRYRUN': pysed.replace('xyz', 'XYZ', '/path/to/file.txt', dryrun=True) #This will dump the output to STDOUT instead of changing the input file.
+    '''
+    linelist = []
+    with open(infile) as f:
+        for item in f:
+            newitem = re.sub(oldstr, newstr, item)
+            linelist.append(newitem)
+    if dryrun == False:
+        with open(infile, "w") as f:
+            f.truncate()
+            for line in linelist: 
+                f.writelines(line)
+    elif dryrun == True:
+        for line in linelist: 
+            print(line) #, end='')
+    else:
+        exit("Unknown option specified to 'dryrun' argument, Usage: dryrun=<True|False>.")
+
+def rmlinematch(oldstr, infile, dryrun=False):
+    '''
+    Sed-like line deletion function based on given string..
+    Usage: pysed.rmlinematch(<Unwanted string>, <Text File>)
+    Example: pysed.rmlinematch('xyz', '/path/to/file.txt')
+    Example 'DRYRUN': pysed.rmlinematch('xyz', '/path/to/file.txt', dryrun=True) #This will dump the output to STDOUT instead of changing the input file.
+    '''
+    linelist = []
+    with open(infile) as f:
+        for item in f:
+            rmitem = re.match(r'.*{}'.format(oldstr), item)
+            if type(rmitem) == type(None): linelist.append(item)
+    if dryrun == False:
+        with open(infile, "w") as f:
+            f.truncate()
+            for line in linelist: f.writelines(line)
+    elif dryrun == True:
+        for line in linelist: print(line) #, end='')
+    else:
+        exit("Unknown option specified to 'dryrun' argument, Usage: dryrun=<True|False>.")
+
+def rmlinenumber(linenumber, infile, dryrun=False):
+    '''
+    Sed-like line deletion function based on given line number..
+    Usage: pysed.rmlinenumber(<Unwanted Line Number>, <Text File>)
[…]

### 2021-04-16 run_cmp_ug_hishear.py

@@ -1,0 +1,51 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+from extract_var_palm import load_data,extract_var
+import sys
+import plot_palm_mod as palm
+import numpy as np
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+base_dir = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'
+run1 = 'test_ocean_amb_hishear_medres'
+run2 = 'test_ocean_ug_hishear_medres'
+#run2 = 'test_ocean_amb_hisheary_hiresz'
+filedir1 = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+run1+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir2 = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+run2+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+run = ['dpdx','dpdy']
+
+plotvar_t = ['umax','vmax','melt','w"u"0','w"v"0','u*','dt','E','E*','ol','k_offset_mcph']
+plotvar_pr = ['pt','sa','prho','rho_ocean','w',
+              'w*u*','w"u"','w*v*','w"v"','vel_var_ratio',
+              'e*','e','km','kh','l','wpt','wsa','w"pt"','w*pt*','w"sa"','w*sa*','wu','wv']
+plotvar = ['pt','sa','rho_ocean','v','w','e']#'u',
+plotvar2 = ['melt*_xy','shf*_xy','sasws*_xy','u*_xy','ol*_xy',
+            'pt1*_xy','pt_io*_xy','thermal_driving','sa1*_xy','sa_io*_xy',
+            'haline_driving','usws*_xy','vsws*_xy']
+
+#tplot = np.arange(50,60,5)
+tplot = [10.] 
+#palm.plot_tseries_zlevel([filedir2],[run2],['sa','wu','U','wv'],zeval = [1.],tlim = [1.,20.])
+#palm.plot_tseries_zlevel([filedir2],[run2],['sa'],zeval = [1.],tlim = [1.,20.],norm='mean')
+#palm.plot_tseries([filedir1,filedir2], run, plotvar_t)
+#palm.plot_tseries([filedir1,filedir2], [run1,run2], ['melt'])
[…]

### 2021-04-16 run_table_mod.py

@@ -1,0 +1,59 @@
+
+import numpy as np
+import os
+import pysed as sed
+import shutil
+from namelist_default import ininame,inivalue
+import gsw
+import filecmp
+import csv
+import sys
+import math
+
+def load_rignot():
+    filename = 'rignot_2002_dT_melt.txt'
+    table_file = open(filename,'r')
+    rd = csv.reader(table_file,delimiter=' ')
+    glacier_year = table_file.readline().split(' ')
+    melt = table_file.readline().split(' ')
+    dT = table_file.readline().split(' ')
+    
+    print(np.shape(glacier_year))
+    print(np.shape(melt))
+    print(np.shape(dT))
+    print(melt[-1])
+    
+    melt_mean = np.ones((len(melt)-1))
+    melt_sd = np.ones((len(melt)-1))
+    for idx,i in enumerate(melt_mean):
+        dT[idx+1] = float(dT[idx+1])
+        melt_mean[idx] = float(melt[idx+1][0:melt[idx+1].index('_')])
+        melt_sd[idx] = float(melt[idx+1][melt[idx+1].index('_')+1:])
+    return melt_mean,melt_sd,dT[1:]
+
+def load_vals(filename):
+   table_file = open(filename,'r')
+   rd = csv.reader(table_file,delimiter=',')
+   varname = table_file.readline().split(',')
+   runname = []
+   data = list(rd)
+   numruns = len(data)
+   derivedvar = ['Lx','Ly','Lz']
+   numvars = len(data[1]) + len(derivedvar)
+   runtable = np.zeros((numruns,numvars))
+   varname[-1] = varname[-1][:-1]
+   for var in derivedvar:
+      varname.append(var)
+   for i,row in enumerate(data):
+      runname.append(row[varname.index('rundir')])
+      for j,entry in enumerate(row):
+         if j == 0 or not entry:
+            row[j] = math.nan
+         if j > 0 and type(row[j]) != float:
+            row[j] = float(row[j])
+      for var in derivedvar:
+         if var[0] == 'L':
+            L = row[varname.index('n'+var[1])] * row[varname.index('d'+var[1])]
+            row.append(L)
+      runtable[i,:] = row
+   return varname,runname,runtable

### 2021-04-16 vis_melt_standard.py

@@ -1,0 +1,88 @@
+#!/usr/bin/env python2
+
+# Author Carolyn Begeman
+# plot_netCDF_basic
+# Created 20180822
+# Last modified 20180822
+# This function tests the functionality of netCDF4 library with the data generated by PALM
+
+# plottype, plotvar as arguments
+# plottype determines whether to read in 2-d or 1-d file
+# plottype includes axslice for pertinent figures
+# import libraries
+import math,os
+from netCDF4 import Dataset
+import numpy as np
+import plot_palm_mod as palm
+#import diff_files as diff
+
+filedir5a = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_0deg_slope01_rdf01_deep_long/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir6a = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_0deg_slope01_rdf01_deep_wide/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir7a = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_0deg_slope01_rdf01_deep_500sq/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir8a = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_0deg_slope01_rdf01_koff5/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir6b = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_0deg_slop01_rdf01_lowresxy/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir1a = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_batch_022/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+filedir1b = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/test_ocean_melt_batch_023/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+
+run1a = 'res1a'
+run1b = 'res1b'
[…]

### 2021-04-19 vis_scripts/cmp_dpdxy_rot.py
Modify vis_scripts

@@ -1,0 +1,90 @@
+# -*- coding: utf-8 -*-
+"""
+"""
+
+import sys
+import numpy as np
+import matplotlib as pltlib
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+from math import log10
+import run_table_mod as table
+from run_table_mod import value_from_namelist
+import cmocean as cmo
+import run_table_mod as table
+from var_param_palm import *
+from plot_param_palm import *
+import plot_palm_mod as palm
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+base_dir = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'
+filedir = ['test_ocean_amd_mcphee_hires_slope1e-1_dpdx-3e-2_dpt1e0' 
+          ,'test_ocean_amd_mcphee_hires_rot_slope1e-1_dpdx3e-2_dpt1e0' 
+          ,'test_ocean_amd_mcphee_hires_slope1e-1_dpdy-3e-2_dpt1e0_new' 
+          ,'test_ocean_amd_mcphee_hires_slope1e-1_dpdx--3e-2_dpt1e0' 
+          ,'test_ocean_amd_mcphee_hires_slope1e-1_dpdy--3e-2_dpt1e0' 
+          ,'test_ocean_amd_mcphee_hires_rot_slope1e-1_dpdy3e-2_dpt1e0' 
+          ,'test_ocean_amd_mcphee_hires_rot_slope1e-1_dpdx-3e-2_dpt1e0' 
+          ,'test_ocean_amd_mcphee_hires_rot_slope1e-1_dpdy-3e-2_dpt1e0'] 
+linestyle = ['-','--','-','-','-','--','--','--']
+diri = ['/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+i+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/' for i in filedir]
+#run = ['all_dpdx_3e-2','dpdy_3e-2','dpdx_-3e-2','dpdy_-3e-2']
+legtitle=r''
+#runlabel = ['dpdx = 3e-2','dpdy = 3e-2','dpdx = -3e-2','dpdy = -3e-2']
+
+sens_var = ''
+[varname,runname,runtable] = table.load_vals('run_table.txt')
+run = ['' for i in filedir]
[…]

### 2021-04-19 vis_scripts/cmp_slope_hidT.py

@@ -1,0 +1,100 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+import sys
+import numpy as np
+import matplotlib as pltlib
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+from math import log10
+from run_table_mod import value_from_namelist
+from var_param_palm import K0
+import cmocean as cmo
+import run_table_mod as table
+from var_param_palm import *
+from plot_param_palm import *
+import plot_palm_mod as palm
+
+pltlib.rc_file('rcparams.txt', use_default_template=True)
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+#base_dir = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'
+base_dir = '/turquoise/usr/projects/climate/cbegeman/palm/jobs/'
+filedir = ['test_ocean_melt_batch_alpha_surface_0{:02d}'.format(i) for i in range(6,9)]
+filedir.append('test_ocean_melt_batch_dpdy_021')
+diri = [base_dir+i+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/' for i in filedir]
+legtitle=r''
+
+sens_var = 'alpha_surface'
+linestyle = ['-']
+
+run= ['' for i in filedir]
+runlabel = ['' for i in filedir]
+slope = np.zeros((len(filedir),))
+for idx,i in enumerate(filedir):
+    slope[idx] = value_from_namelist(base_dir+i,'alpha_surface')[0]
+    runlabel[idx] = '{:2.1e}'.format(slope[idx])
+    run[idx] = 'slope{:1.0e}'.format(slope[idx])
+
+cNorm  = colors.Normalize(vmin=np.min(np.log10(slope))-0.5,vmax=np.max(np.log10(slope))+0.5)
+scalarMap = cmx.ScalarMappable(norm=cNorm, cmap='cmo.ice_r')
+colorVal = np.zeros((len(slope),4))
+for idx,i in enumerate(slope):
+    colorVal[idx,:] = scalarMap.to_rgba(np.log10(i))
+
+a = np.array([[0,1]])
+plt.figure(figsize=(6, 3))
+img = plt.imshow(a, norm=cNorm, cmap='cmo.ice_r')
[…]

### 2021-04-19 vis_scripts/cmp_thermal_driving_slope1.py

@@ -1,0 +1,106 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+import sys
+import numpy as np
+import matplotlib as pltlib
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+from math import log10
+from run_table_mod import value_from_namelist
+from var_param_palm import K0
+import cmocean as cmo
+import run_table_mod as table
+from var_param_palm import *
+from plot_param_palm import *
+import plot_palm_mod as palm
+
+pltlib.rc_file('rcparams.txt', use_default_template=True)
+sens_var = 'pt'
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+base_dir = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'
+filedir = ['test_ocean_melt_batch_dpdy_021']
+for i in range(18,21):
+    filedir.append('test_ocean_melt_batch_dT_0{:02d}'.format(i))
+diri = ['/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+i+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/' for i in filedir]
+legtitle=r''
+linestyle = ['-']
+
+runlabel = ['' for i in filedir]
+pt_surf = np.zeros((len(filedir),))
+for idx,i in enumerate(filedir):
+    pt_surf[idx] = value_from_namelist(
+                   '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+i,
+                   'pt_surface')[0] - K0
+    runlabel[idx] = '{:2.1f}'.format(pt_surf[idx])
+run = runlabel
+
+cNorm  = colors.Normalize(vmin=np.min(pt_surf)-0.05,vmax=np.max(pt_surf)+0.1)
+scalarMap = cmx.ScalarMappable(norm=cNorm, cmap='cmo.thermal')
+colorVal = np.zeros((len(pt_surf),4))
+for idx,i in enumerate(pt_surf):
+    colorVal[idx,:] = scalarMap.to_rgba(i)
+
+a = np.array([[0,1]])
+plt.figure(figsize=(6, 3))
+img = plt.imshow(a, norm=cNorm, cmap='cmo.thermal')
+plt.gca().set_visible(False)
[…]

### 2021-04-19 vis_scripts/extract_var_palm.py

@@ -17,400 +17,7 @@ import convert_NCAR_mod as ncar
 import difflib
 import gsw
 import cmocean as cmo
-
-#global var,data
-
-# parameters
-K0 = 273.15 # temperature (K) at 0 degC
-g = -9.81
-xi_N = 0.0052
-Ri_crit = 0.2
-s_yr = 24.*3600.*365.25
-s_hr = 3600.
-
-# plotting parameters
-lw1 = 2 
-lw2 = 3
-lw3 = 1 
-
-# list of variables on u grid. TODO check e
-uvar = ['xu','yv','zu','zv','zu_xy','zu_3d',
-        'U','u','u"','u*','umax','vmax','v','v"',
-        'dEdt','E','E*','dedt','e','e*','u*2','v*2',
-        'Fshear','Ftrans','Fbuoy','FbuoyT','FbuoyS','diss',
-        'w*u*u*:dz','w*p*:dz','N1','N2','S2','Ri','Rf',
-        'km','kh','l','e*','w*e*','u2v2','dudz','dvdz','dUdz']
-
-# list of variables on scalar grid
-scvar = ['x','y','z','alpha_T','drho_oceandz','drho_gswdz','dprho_gswdz',
-         'pt','pt"','pt*2','sa','sa"','prho','rho_ocean','z_BL','z_SL',
-         'rho_gsw','prho_gsw','zu1_xy','sa*2']
-# list of variables on w grid
-wvar = ['melt','melt*_xy','shf*_xy','shf*_xy_av','sasws*_xy','u*_xy','z0*_xy',
-        'dz','zw','zw_xy','zw_3d','k_offset_mcph','Sk','km_eff','kh_eff',
-        'w','w"','w*2','zmin_w2','w*3','NORM_ws3','dT',
-        'wpt','w*pt*','w"pt"','wsa','w*sa*','wu','wv',
-        'wb','w"sa"','w*u*','w"u"','w*v*','w"v"','w"theta"0',
-        'z0h*_xy','ol','ol*_xy','pt1*_xy','pt_io*_xy','sa1*_xy','sa_io*_xy',
-        'w"U"0','w"u"0','w"v"0','w"pt"0','thermal_driving','pt1_t','Sw',
-        'haline_driving','usws*_xy','vsws*_xy','freezing',
-        'b11','b12','b13','b23','b22','b33','vel_var_ratio']
-# list of  variables not defined on a grid
-novar = ['time','dt']
-
[…]

### 2021-04-19 vis_scripts/plot_palm_mod.py

@@ -1,0 +1,1350 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 22 07:52:34 2019
+
+@author: cbegeman
+"""
+import math,os
+from netCDF4 import Dataset
+import numpy as np
+import matplotlib as pltlib
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import matplotlib.ticker as tick
+import my_array_mod as ar
+import my_string_mod as strop
+import convert_NCAR_mod as ncar
+from extract_var_palm import *
+from matplotlib import rc
+from run_table_mod import value_from_namelist
+import var_param_palm as pv
+from plot_param_palm import *
+
+pltlib.rc_file('rcparams.txt', use_default_template=True)
+#rc('text', usetex=True)
+#rc('font',**{'family':'sans-serif','sans-serif':['Helvetica']})
+#plt.rc('xtick',labelsize=14)
+#plt.rc('ytick',labelsize=14)
+#plt.rc('axes.formatter',useoffset=False)
+        #ax.xaxis.get_major_formatter().set_powerlimits((pw_min,pw_max))
+        #ax.yaxis.get_major_formatter().set_powerlimits((pw_min,pw_max))
+
+#------------------------------------------------------------------------------
+# END_TIME
+# Inputs:
+#   runfile path to RUN_CONTROL
+# Outputs: 
+#   end time of run in seconds of model time
+#------------------------------------------------------------------------------
+def end_time(runfile): 
+   runcontrol = open(runfile,'r')
+   linelist = runcontrol.readlines()
+   hr = int(linelist[len(linelist)-1][11:13]) 
+   minute = int(linelist[len(linelist)-1][14:16]) 
+   sec = int(linelist[len(linelist)-1][17:19])
+   run_end = hr * 3600. + minute * 60. + sec
+   return run_end
+
+#------------------------------------------------------------------------------
+# FETCH_RUN_NAMES
+# Inputs:
+#   base_run path to run directory containing sample namelist
+#   sens_var variable that is allowed to vary between runs
+# Outputs: 
+#   cell array of run directories that are similar to base_run except they have
+#   a different value for sens_var
+#------------------------------------------------------------------------------
+def fetch_run_names(base_run,sens_var,namelist = 'test_oceanml_p3d'):
[…]

### 2021-04-19 vis_scripts/plot_param_palm.py

@@ -1,0 +1,29 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Jan 22 07:52:34 2019
+
+@author: cbegeman
+"""
+# define plotting parameters
+lw1 = 2 
+lw2 = 3
+lw3 = 1 
+
+
+ls = '-' #linestyle
+#ls = 'None' #linestyle
+mk = 'None' #marker
+#mk = '.' #marker
+ms = 5 #marker
+fs = 16
+fs1 = 14
+legloc = 'upper left'
+bboxanchor = (0.0,-0.25)
+s_hr = 3600
+logmin = 1.0e-20
+
+# define default colors
+col = ['#186086','#F5793A','#A95AA1','#85C0F9','#D14A42','#2ca25f','#99d8c9','#5F86DD']
+#col = np.matrix('1 0 0;0 1 0;0 0 1')
+

### 2021-04-19 vis_scripts/run_standard.py

@@ -9,14 +9,9 @@ from extract_var_palm import load_data,extract_var
 import sys
 import plot_palm_mod as palm
 import numpy as np
+from cmp_slope_hidT import *
 
 sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
-base_dir = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'
-#run1 = 'test_ocean_bsign_noslp_dSdz2_medres'
-#run1 = 'test_ocean_bsign_noslp_lowres'
-#run1 = 'test_ocean_bsign_modslp_warm_medres'
-run1 = 'test_ocean_bsign_modslp_hiresz'
-filedir1 = '/lustre/scratch3/turquoise/cbegeman/palm/jobs/'+run1+'/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
 
 plotvar_t = ['umax','vmax','melt','w"u"0','w"v"0','u*','dt','E','E*','ol','k_offset_mcph']
 plotvar = ['pt','sa','u','v']
@@ -35,17 +30,13 @@ plotvar2 = ['melt*_xy','u*_xy','ol*_xy',
             'pt1*_xy','pt_io*_xy','thermal_driving','sa1*_xy','sa_io*_xy',
             'haline_driving']#,'usws*_xy','vsws*_xy']
 plotvar_zlevel = ['pt','sa','u','v']
-runname = ''
-zmax = -50
-#zmax = -500
-
-#tplot = [98.]
-tplot = [6.]
 #tplot = np.arange(40,99,5)
 #tplot = np.arange(5,15,5)
 
 #palm.plot_tseries([filedir1], [runname], plotvar_t)
-#palm.plot_tseries_melt_us(filedir1, runname)
+if plot_cross:
+    palm.plot_tseries_cross(diri, run, runlabel, tav=tav_ts, teval=[tcross,tmax],
+                            plotvar = ['u*','gamma_T'], col = colorVal, overwrite=True)
 #palm.plot_tseries_zlevel([filedir1], [runname], plotvar_zlevel,norm=['' for i in plotvar_zlevel], zeval=[-10.], tlim=[tplot[0],tplot[-1]])
 
 #palm.plot_pr([filedir1],[runname],plotvar = plotvar_pr,teval = [tplot[0]], ops=norm_pr,zlim=[zmax,0])
@@ -55,7 +46,7 @@ tplot = [6.]
[…]

### 2021-04-19 vis_scripts/run_table_mod.py

@@ -30,7 +30,24 @@ def load_rignot():
         melt_mean[idx] = float(melt[idx+1][0:melt[idx+1].index('_')])
         melt_sd[idx] = float(melt[idx+1][melt[idx+1].index('_')+1:])
     return melt_mean,melt_sd,dT[1:]
-
+def valfromline(line):
+    varvalue = [0.,0.]
+    string,value = line.split('=')
+    varlist = value.split(',')
+    for i,var in enumerate(varlist):
+       if ( var.strip() == '.T.'):
+           varvalue[i] = 1.
+       elif ( var.strip() == '.F.'):
+           varvalue[i] = 0.
+       elif ( var.startswith("'") ):
+           print('Other string\n')
+           break
+       elif var == '':
+           break
+       else:
+          varvalue[i] = float(var.strip())
+          break
+    return [varvalue[i]]
 def load_vals(filename):
    table_file = open(filename,'r')
    rd = csv.reader(table_file,delimiter=',')
@@ -57,3 +74,9 @@ def load_vals(filename):
             row.append(L)
       runtable[i,:] = row
    return varname,runname,runtable
+def value_from_namelist(filename,var):
+   datafile = open(filename+'/test_oceanml_p3d','r')
+   for line in datafile:
+       if var in line:
+           return valfromline(line)
+   return math.nan

### 2021-04-19 vis_scripts/var_param_palm.py

@@ -1,0 +1,428 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+@author: cbegeman
+"""
+import math,os
+from netCDF4 import Dataset
+import numpy as np
+import numpy.ma as ma
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+import matplotlib.ticker as tick
+import my_array_mod as ar
+import my_string_mod as strop
+import convert_NCAR_mod as ncar
+import difflib
+import gsw
+import cmocean as cmo
+
+#global var,data
+
+# parameters
+K0 = 273.15 # temperature (K) at 0 degC
+g = -9.81
+xi_N = 0.0052
+Ri_crit = 0.2
+s_yr = 24.*3600.*365.25
+s_hr = 3600.
+L_i = 330000. # latent heat of fusion [ J/kg ]
+cpw = 4218. # heat capacity of seawater [J/kg deg C ]
+# plotting parameters
+lw1 = 2 
+lw2 = 3
+lw3 = 1 
+
+# list of variables on u grid. TODO check e
+uvar = ['xu','yv','zu','zv','zu_xy','zu_3d',
+        'U','u','u"','u*','umax','vmax','v','v"',
+        'dEdt','E','E*','dedt','e','e*','gamma_T','gammaT','u*2','v*2',
+        'Fshear','Ftrans','Fbuoy','FbuoyT','FbuoyS','diss',
+        'w*u*u*:dz','w*p*:dz','N1','N2','S2','Ri','Rf',
+        'km','kh','l','e*','w*e*','u2v2','dudz','dvdz','dUdz']
+
+# list of variables on scalar grid
+scvar = ['x','y','z','alpha_T','drho_oceandz','drho_gswdz','dprho_gswdz',
+         'gamma_T','gammaT','pt(0)', 'pt(z_mo)','pt','pt"','pt*2','sa','sa"','prho','rho_ocean','z_BL','z_SL',
+         'rho_gsw','prho_gsw','zu1_xy','sa*2']
+# list of variables on w grid
+wvar = ['melt','melt*_xy','shf*_xy','shf*_xy_av','sasws*_xy','u*_xy','z0*_xy',
+        'dz','zw','zw_xy','zw_3d','k_offset_mcph','Sk','km_eff','kh_eff',
[…]

### 2021-04-19 A_suppl_fig.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics{}
-    \caption{Timeseries of maximum vertical velocity fluctuation per hour for thermal driving cases}
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics{Figures/w2_max_cmp_dT_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics{Figures/w2_max_cmp_dalpha_t.png}
+    \end{minipage}
+    \caption{Timeseries of maximum vertical velocity fluctuation per hour for (a) thermal driving cases and (b) slope cases.}
     \label{fig:max_w2_timeseries}
 \end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics{Figures/e_res_cmp_dpdy_dpdx_t.png}
+    \caption{Resolved turbulent kinetic energy as a function of pressure gradient orientation under 0.1$^{\circ}$ slope.}
+    \label{fig:e_orientation}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 10cm 0 0},clip, width=\textwidth]{Figures/heatflux_cmp_dT_40hr_tav1_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 10cm 0 0},clip, width=\textwidth]{Figures/heatflux_cmp_dT_48hr_tav1_z_profile.png}
+    \end{minipage}
+    \caption{Thermal driving simulations: heat flux}
+    \label{fig:Heatflux_profiles}
+\end{figure}

### 2021-04-19 main.tex

@@
 \usepackage{xr}
-\makeatletter
-\newcommand*{\addFileDependency}[1]{% argument=file name and extension
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
-\makeatother
-
-\newcommand*{\myexternaldocument}[1]{%
-    \externaldocument{#1}%
-    \addFileDependency{#1.tex}%
-    \addFileDependency{#1.aux}%
-}
-\myexternaldocument{A_suppl_fig}
+\include{A_suppl_fig.tex}
 
@@
 There are two sets of simulations which have a base case in common.
-The base case has low far-field thermal driving of 0.1 $^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field geostrophic flow of 20 cm s$^{-1}$ to the [XX east].
+The base case has low far-field thermal driving of 0.1 $^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field geostrophic flow of 20 cm s$^{-1}$ generated by a 0.03 pressure gradient.
 These conditions were chosen to favor a high TKE regime, for reasons discussed in Section \ref{sec:disc}.
@@
 By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S\ref{fig:max_w2_timeseries}).
+The turbulent intensity for cases with slopes less than 1$^{\circ}$ continues to decline, as we discuss later.
 
@@
 
-% Sensitivity to thermal driving
+% Melt sensitivity to thermal driving
+Melt rates decline over the course of the simulations (Figure \ref{fig:melt_timeseries}), preventing the identification of steady-state melt rates. 
+This decline is in response to a co-committent increase in stratification during the course of the simulation, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations (Fig.
+S\ref{fig:max_w2_timeseries}).
+We do not continue our simulations in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
+The high thermal driving case approaches steady-state more rapidly than low thermal driving cases due to increased shear production of TKE from the buoyant acceleration of the IOBL.
 
-The fluctuations in TKE with flow orientation under inertial oscillations are replicated when the mean pressure gradient is rotated, with increased TKE when flow is oriented downslope (not shown or supplemental).
+% Melt rate relationship with inertial period
+The dominant temporal frequency in melt rate is the inertial frequency; however, the melt response to those oscillations is highly nonlinear.
+Maximum melt rates occur when the mean flow is oriented between the up-slope direction and the Coriolis-favored direction, and minimum melt rates roughly 180$^{\circ}$ opposed to that.
+Melt rate fluctuations increase as thermal driving increases, which we attribute to the increasing importance of buoyancy forcing in driving a near-boundary plume and thus determining the depth-distribution of shear.
+During high-melt periods, the far-field flow is oriented up-slope and shear production of TKE is concentrated near the boundary.
+During low-melt periods, the far-field flow is oriented down-slope and shear production of TKE is concentrated a few meters away from the boundary.
+The vertical heat flux profile through the water column follows the profile of shear production of TKE (Fig.
+\ref{fig:dT_profiles}, Fig.
+S\ref{fig:TKE_balance}).
+The low-melt period is somewhat brief, roughly 1/4 of the inertial period, as the onset is delayed by the time it takes to increase near-boundary stratification.
+In simulations where the background pressure gradient orientation was varied, we also observe reduced TKE when the mean flow is down-slope, suggesting this relationship is not unique to inertial oscillations but is more closely related to the vertical velocity structure and the depth of maximum shear.
+(Fig.
+S\ref{fig:e_orientation}).
+
+The time-averaged melt rates are roughly linear with thermal driving (Figure \ref{fig:melt_sensitivity}a).
+During high-melt periods, the thermal exchange coefficient evaluated using a parameterization, is about 0.006 for all thermal driving values, less than the constant value of 0.011 reported in Jenkins et al.
+(2010) and commonly-used elsewhere, due to accounting for the degree of stratification.
+The time-averaged value decreases somewhat in the high thermal driving cases due to pronounced periods of low melt (Figure Gamma T vs.
+thermal driving).
+%The constant flux layer is ~2m.
+
+Boundary layer depths as characterized by a peak in the ratio of vertical to horizontal velocity variance range from 15 m to 25 m for the moderate to low thermal driving cases.
+
+In these simulations we find that the destruction of TKE by the stabilizing buoyancy flux is two orders of magnitude smaller than shear production of TKE.
+Given that the background flow is relatively strong for ice shelf settings, this result may be only narrowly applicable.
+However, it is consistent with \citep{davis_nicholls} who found that shear production was an order of magnitude greater than buoyancy destruction of TKE in the IOBL below Larsen C Ice Shelf.
+
+% Description of simulation features
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Figures/melt_cmp_dT_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Figures/us_cmp_dT_t.png}
+    \end{minipage}%
+    \caption{Thermal driving simulations. (a) evolution of melt rate (b) evolution of friction velocity}
+    \label{fig:dT_timeseries}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/ptfar_cmp_dT_40hr_tav1_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/safar_cmp_dT_40hr_tav1_z_profile.png}
+    \end{minipage}
+    \newline
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_40hr_tav1_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/Fshear_cmp_dT_40hr_tav1_z_profile.png}
+    \end{minipage}
+    \newline
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_48hr_tav1_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/Fshear_cmp_dT_48hr_tav1_z_profile.png}
+    \end{minipage}
+    \caption{Thermal driving simulations. (a) temperature relative to far-field temperature (b) salinity relative to far-field salinity (c) velocity (d) heat flux}
+    \label{fig:dT_profiles}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dT_tav12.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/gamma_T__e_res__dslope_tlim52.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
+    \end{minipage}%    \caption{(a) Melt rate vs. thermal driving. (b) Melt rate vs. slope}
+    \label{fig:melt_sensitivity}
+\end{figure}
 

### 2021-04-19 vis_scripts/extract_var_palm.py
Update vis_scripts

@@ -99,7 +99,7 @@ def extract_var(data,varname,data_type='pr',ops=[],
     if varname[0:2] == 'pt':
         var1 = np.subtract(var1,K0)
         varunits[varlist.index(varname)] = r'^{\circ}C'
-    elif 'melt' in varname:
+    elif 'melt' in varname and tunits=='hr':
         var1 = np.multiply(var1,s_yr)
         axis_label = varlabel[varlist.index(varname)]+ ' (m/yr)'
     if 'shf' in ops:
@@ -170,7 +170,7 @@ def extract_var(data,varname,data_type='pr',ops=[],
         var1 = np.subtract(var1,var2)
         varlabel1 = varlabel1 + r'-'
 
-    if tunits=='hr':
+    if tunits=='hr' and varname == 'time':
         var1 = np.divide(var1,3600.)
     
     axis_label = varlabel1 + varlabel2 + r'\:(' + varunits[varlist.index(varname)] + r')'
@@ -271,15 +271,19 @@ def derived_var(data,varname,slice_obj,z_offset = 0.,f = gsw.f(-70.),filedir='',
     
     elif varname == 'gamma_T':
         #gammaT = derived_var(data,'gammaT',slice_obj,data_type=data_type)
-        melt,_ = extract_var(data,'melt',data_type=data_type)
+        melt,_ = extract_var(data,'melt',data_type=data_type,tunits='s')
         pt0,_ = extract_var(data,'pt(0)',data_type=data_type)
         pt_zmo,_ = extract_var(data,'pt(z_mo)',data_type=data_type)
         us,_ = extract_var(data,'u*',data_type=data_type)
+        print('mean melt',np.mean(melt))
+        print('mean dT', np.mean(np.subtract(pt_zmo,pt0)))
+        print('mean us', np.mean(us))
+        print('L/c',L_i/cpw) 
         var1 = (L_i/cpw) * np.divide(melt, 
                                      ( np.multiply(us,
                                                    np.subtract(pt_zmo,pt0) ) ) )
     elif varname == 'gammaT':
-        melt,_ = extract_var(data,'melt',data_type=data_type)
+        melt,_ = extract_var(data,'melt',data_type=data_type,tunits = 's')
         pt0,_ = extract_var(data,'pt(0)',data_type=data_type)
         pt_zmo,_ = extract_var(data,'pt(z_mo)',data_type=data_type)
         var1 = (L_i/cpw) * np.divide(melt, 

### 2021-04-19 main.tex
Updates from Overleaf

@@
 The time-averaged melt rates are roughly linear with thermal driving (Figure \ref{fig:melt_sensitivity}a).
-During high-melt periods, the thermal exchange coefficient evaluated using a parameterization, is about 0.006 for all thermal driving values, less than the constant value of 0.011 reported in Jenkins et al.
-(2010) and commonly-used elsewhere, due to accounting for the degree of stratification.
-The time-averaged value decreases somewhat in the high thermal driving cases due to pronounced periods of low melt (Figure Gamma T vs.
-thermal driving).
-%The constant flux layer is ~2m.
+The thermal exchange coefficient as computed using Equation \ref{eq:gamma} during the last 12 hours of the simulations is between 0.005 and 0.006 for the simulated range of thermal driving values.
+The time-averaged value decreases somewhat in the high thermal driving cases due to pronounced periods of low melt as TKE declines with increasing stratification.
+
+These values are less than the thermal exchange coefficient of 0.011 derived from observations in Jenkins et al.
+(2010).
+During the first 12 hours of the simulation, simulated thermal exchange coefficients are 0.008 due to weaker stratification near the interface and higher friction velocities due to greater TKE.
 
@@
         \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
+    \end{minipage}
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4.1cm 0 0},clip,width=\textwidth]{Figures/gammaT_dT_tav12_zlim2.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/gamma_T__e_res__dslope_tlim52.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
-    \end{minipage}%    \caption{(a) Melt rate vs. thermal driving. (b) Melt rate vs. slope}
+        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/gamma_T__us__dslope_tav12_tlim52.png}
+    \end{minipage}
+    \caption{(a) Melt rate vs.
+thermal driving.
+(b) Melt rate vs.
+slope.
+(c) Thermal exchange coefficient vs.
+far-field thermal driving for thermal driving simulations.
+(d) Thermal exchange coefficient vs.
+friction velocity for sloped simulations.}
     \label{fig:melt_sensitivity}

### 2021-06-29 A_suppl_fig.tex

@@
+% Possible supplemental figures
 \begin{figure}
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics{Figures/w2_max_cmp_dT_t.png}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_44h_tav12_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics{Figures/w2_max_cmp_dalpha_t.png}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav12_z_profile.png}
+    \end{minipage}
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_44h_tav12_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_46h_tav12_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \end{minipage}
+    \caption{Vertical profile of (a,b) heat flux and (c,d) momentum flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases.
+Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).} %Change the time interval in (b) back 2h to match (a)
+    \label{fig:flux_profiles}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13_dTscale_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav13_slopescale_z_profile.png}
+    \end{minipage}
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_43h_tav13_dTscale_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_slope_46h_tav13_slopescale_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \end{minipage}
+    \caption{Scaled vertical profile of (a,b) heat flux and (c,d) momentum flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases.
+Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).}
+    %Change vertical axis limits
+    %Change all to centered on 43h and averaged 13h
+    \label{fig:Scaled_flux_profiles}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Figures/w2_max_cmp_dT_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[width=\textwidth]{Figures/w2_max_cmp_dalpha_t.png}
     \end{minipage}
@@
 
-\begin{figure}
+\begin{figure}[H]
     \centering
-    \includegraphics{Figures/e_res_cmp_dpdy_dpdx_t.png}
+    \includegraphics[width=0.5\textwidth]{Figures/e_res_cmp_dpdy_dpdx_t.png}
     \caption{Resolved turbulent kinetic energy as a function of pressure gradient orientation under 0.1$^{\circ}$ slope.}
@@
 
-\begin{figure}
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{Figures/vel_var_ratio_cmp_dslope_40hr_tav1_z_profile.png}
+    \caption{Ratio of vertical to horizontal velocity variance for slope-varying simulations.}
+    \label{fig:vel_var_ratio}
+\end{figure}
+
+\begin{figure}[H]
     \centering
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 10cm 0 0},clip, width=\textwidth]{Figures/heatflux_cmp_dT_40hr_tav1_z_profile.png}
+        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/Fbuoy_cmp_dslope_40hr_tav1_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 10cm 0 0},clip, width=\textwidth]{Figures/heatflux_cmp_dT_48hr_tav1_z_profile.png}
+        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/Fshear_cmp_dslope_40hr_tav1_z_profile.png}
     \end{minipage}
-    \caption{Thermal driving simulations: heat flux}
-    \label{fig:Heatflux_profiles}
+    \caption{TKE production by (a) buoyancy and (b) shear for slope-varying simulations.}
+    \label{fig:tke}
 \end{figure}
+
+\begin{figure}[H]
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/km_cmp_dT_44h_tav12_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/km_cmp_slope_46h_tav12_z_profile.png}
+    \end{minipage}
+    \caption{Effective vertical diffusivity for momentum flux from (a) thermal driving simulations and (b) slope-varying simulations.}
+    \label{fig:km}
+\end{figure}

### 2021-06-29 main.tex

--- 2021-01-18 main.tex
@@
-\documentclass[draft]{styles/agujournal2019}
+\documentclass[draft]{agujournal2019}
 \usepackage{url} 
 \usepackage{lineno}
-
-\usepackage{xr}
-\makeatletter
-\newcommand*{\addFileDependency}[1]{% argument=file name and extension
-  \typeout{(#1)}
-  \@addtofilelist{#1}
-  \IfFileExists{#1}{}{\typeout{No file #1.}}
-}
-\makeatother
-
-\newcommand*{\myexternaldocument}[1]{%
-    \externaldocument{#1}%
-    \addFileDependency{#1.tex}%
-    \addFileDependency{#1.aux}%
-}
-\myexternaldocument{A_suppl_fig}
-
+\usepackage{graphicx}
+%\usepackage{xr}
+\usepackage{float}
+%\externaldocument{A_suppl_fig}
+\usepackage{amsmath}
 \linenumbers
@@
 \begin{document}
-%\input{agu_begindoc.tex}
-\title{Large-eddy simulations of the ice-shelf oceanic boundary layer}
+\title{Ice-shelf ocean boundary layer dynamics from large-eddy simulations}
 
 \correspondingauthor{Carolyn Begeman}{cbegeman@lanl.gov}
-\authors{Carolyn Branecky Begeman\affil{1},Xylar Asay-Davis\affil{1}, and Luke Van Roekel\affil{1}}
+\authors{Carolyn Branecky Begeman\affil{1}, Xylar Asay-Davis\affil{1}, and Luke Van Roekel\affil{1}}
 
@@
 \begin{keypoints}
-\item 
-\item 
-\item 
+\item We simulate boundary layer turbulence with prognostic ice-shelf melting
+in cold cavity settings.
+\item Our simulations support a linear melt response to thermal driving.
+\item Buoyant mean flow can significantly enhance melt rates at ice-shelf basal slopes as low as 1 degree.
 \end{keypoints}
@@
 Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
-Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can have global-scale climate impacts; small increases in ice shelf melting decrease the ability of Antarctic ice shelves to “buttress” ice flux to the ocean, potentially allowing for runaway ice loss and sea-level rise.
-Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
+Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can affect sea-level rise by altering the ability of Antarctic ice shelves to “buttress” ice flux to the ocean.
+%Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
 Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete.
-A fundamental understanding of turbulent flow in this unusual regime is lacking, despite widespread adoption and application of existing parameterizations by the international ocean, ice sheet, and ESM communities.
+In this study, we improve our understanding of turbulence below ice shelves by means of large-eddy simulations at sub-meter resolution, capturing boundary layer mixing at scales intermediate between laboratory experiments or direct numerical simulations and regional or global ocean circulation models.
+Our simulations feature the development of an ice-ocean boundary layer through dynamic ice melting in a regime with low thermal driving, low ice-shelf slope, and strong shear driven by the geostrophic flow.
+We present a preliminary assessment of existing ice-shelf basal melt parameterizations adopted in single component or coupled ice-sheet and ocean models on the basis of a small parameter study.
+While the parameterized linear relationship between ice-shelf melt rate and far-field ocean temperature appears to be robust, we point out a little-considered relationship between ice-shelf basal slope and melting worthy of further study.
 
@@
 
-\paragraph{}
+% Motivation - SLR
 The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet.
 The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice.
-The Ice-Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base.
+The Ice-shelf/Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base.
 Thus, accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
-This representation is also critical for evaluating the sensitivity of the coupled land-ice ocean system.
+This representation is also critical for evaluating the sensitivity of the coupled land ice-ocean system to changes in ocean conditions.
+Of particular concern is the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
 
-\paragraph{}
-The sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
-
-\paragraph{}
+% Shortcomings of ocean-model representations of IOBL
 One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution.
 Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL.
-This model deficiency likely biases turbulent fluxes through the IOBL and sub-ice-shelf ocean circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting.
+This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting.
 A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.
 
-\paragraph{}
+% Overview of IOBL turbulence lit
+IOBLs present unique conditions in the global ocean, involving a stabilizing flux from phase change (ice-melting) and a boundary layer that is positively buoyant against a sloping boundary.
+The IOBL has been most extensively explored at small scales, laboratory experiments and Direct Numerical Simulations, with some recent numerical studies addressing larger scales \cite{mondal_ablation_2019, vreugdenhil_stratification_2019}.
+However, the melt parameterizations commonly in use today still derive from sea-ice conditions (i.e., in the absence of a slope) \cite{mcphee_dynamics_1987}.
+Thus a knowledge gap exists in bridging these dynamics across the IOBL and characterizing the structure of buoyant plumes.
+Recently, this has been addressed through non-turbulence-resolving 2-d or 2.5-d models \cite{jenkins_simple_2016, jenkins_shear_2021, cheng_modeling_2020}.
+Notably, \citeA{jenkins_shear_2021} found a significant discrepancy between the commonly-used K-Profile Parameterization (KPP) and a higher-order turbulence closure scheme for vertical mixing in IOBL settings, suggesting that the application of KPP in ocean models may be inappropriate in ice-shelf cavities.
+There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \cite{zonta_stably_2018}.
+
+% Overview of this study
 In this study, we model turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
-Whereas ocean models typically used to model sub-ice-shelf ocean cavities cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
-An effective parameterization of ice-shelf melting is likely to depend on ice-shelf slope, the temperature, salinity, and velocity outside the IOBL, and the depth of the ice-ocean interface.
-We vary these parameters between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates.
-
-\paragraph{}
-Characterizing turbulence in the presence of a buoyancy flux and sloping boundary is a fundamental problem in fluid dynamics.
+Whereas ocean models typically used to model sub-ice-shelf circulation cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
+An effective parameterization of ice-shelf melting is likely to rest on an understanding of how turbulent mixing in the IOBL depends on stratification and shear forcing.
+We vary far-field ocean temperature and ice-shelf slope between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates.
+In this study we focus on the high-shear, low thermal driving regime.
+The target of previous LES studies has been on low-shear settings \cite{vreugdenhil_stratification_2019}.
 
@@
 
-\paragraph{The PALM model}
-The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover (Germany).
-It has been applied to the simulation of atmospheric and ocean boundary layers.
-However, it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
-For this application, the key model development was the implementation of dynamic melting fluxes.
+\subsection{Overview of the LES model}
 
-\subsection{Governing equations}
+The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover, Germany \cite{raasch_palm-large-eddy_2001}.
+It has been applied to the simulation of atmospheric and ocean boundary layers, but it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
+For this application, our model is a new version based on PALM v5.0 \cite{maronga_parallelized_2015} with added features including a boundary flux scheme for the ice-ocean interface, rotating the gravity vector for sloped domains, and a different turbulence closure scheme.
+Here we provide a brief overview of PALM with a focus on our additions.
+For more details we refer readers to \citeA{maronga_parallelized_2015}.
 
-%Mass conservation for incompressible flows
-%\begin{equation} \label{eq:volconserv}
-%\frac{\partial u_j}{\partial x_j} = 0
-%\end{equation}
-%The model enforces incompressibility with 
-%\begin{equation} \label{eq:pdiv}
-%\frac{\partial^2 \pi^{*t}}{\partial x_i^2} = \frac{\rho_0}{\Delta t} \frac{\partial u_{i,pre}^{t + \Delta t}}{\partial x_i}
-%\end{equation}
-
-Prognostic equations:
-Momentum conservation
-\begin{equation} \label{eq:uprog}
-	\frac{\partial u_i}{\partial t} = 
+The governing equations of PALM are the following:\\
+\begin{align}
+    \textrm{Volume conservation} & &
+        \frac{\partial u_j}{\partial x_j} &= 0\label{eq:volconserv}\\
+    \textrm{Momentum conservation} & &
+        \frac{\partial u_i}{\partial t} &= 
         -\frac{\partial u_i u_j}{\partial x_i}
         -\varepsilon_{ijk} f_j u_k 
-	+ \varepsilon_{i3j} f_3 u_{g,j} 
-    + g_i \frac{\rho - \rho_a}{\rho_0}
-	- \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i}
-	- \frac{\partial}{\partial x_j}(\overline{u''_i u''_j} - \frac{2}{3}e\delta_{ij})
-	- \frac{\tau_i}{\rho}
-\end{equation}
+        + \varepsilon_{i3j} f_3 u_{g,j}\nonumber\\
+     &&& \quad + g_i \frac{\rho - \rho_a}{\rho_0} 
+        - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} \nonumber\\
+     &&& \quad - \frac{\partial}{\partial x_j}\left(\overline{u''_i u''_j} 
+        - \frac{1}{3}\overline{u''_i u''_i}\delta_{ij}\right) \label{eq:uprog}\\
+    \textrm{Heat conservation} & &
+        \frac{\partial \theta}{\partial t} &= 
+        -\frac{\partial u_j \theta}{\partial x_j} 
+        - \frac{\partial}{\partial x_j}\left(\overline{u''_i \theta''}\right) 
+        + \Phi_{\theta}\label{eq:ptprog}\\
+    \textrm{Salt conservation} & &
+        \frac{\partial S}{\partial t} &= 
+        -\frac{\partial u_j S}{\partial x_j} 
+        - \frac{\partial}{\partial x_j}\left(\overline{u''_i S''}\right) 
+        + \Phi_{S}\label{eq:saprog}
+\end{align}
 
-The terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum fluxes.
-% Prognostic equation for Resolved TKE
-% \begin{equation} \label{eq:eprog}
-% \frac{\partial e^*}{\partial t} = 
-% -u_j \frac{\partial e^*}{\partial x_j} 
-% - (\overline{u^*_i u^*_j})\frac{\partial u_i}{\partial x_j} + \frac{g_i}{\rho_0}\overline{u^*_i \rho^*}
-% \end{equation}
+The model enforces incompressibility through a predictor-corrector method to the pressure perturbation, $\pi^*$, at each time step.
+Details can be found in \cite{maronga_parallelized_2015}.
+The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum flux.
+Double primes denote sub-grid fluctuations.
 
 %\paragraph{}% Sloping surface
-We represent a sloping ice base by rotating the gravity and Coriolis vectors while keeping the domain a rectangular prism. 
-%In PALM v0 the buoyancy terms were based only on temperature rather than density. 
-Thus, 
+We represent a sloping ice base by rotating the gravity ($\textbf{g}$) and Coriolis ($\textbf{f}$) vectors while keeping the domain a rectangular prism as in \citeA{vreugdenhil_stratification_2019}. 
+Specifically, 
 \begin{equation} \label{eq:g}
 	%\textbf{g} = g [sin \alpha,0,cos \alpha]
-	\textbf{g} = g [sin \alpha sin \beta,cos \beta,cos \alpha]
+	\textbf{g} = g_z [\sin \alpha \sin \beta,\cos \beta,\cos \alpha]
 \end{equation}
 \begin{equation} \label{eq:f}
-    \textbf{f} = 2 \Omega [sin \phi sin \alpha,cos \phi,sin \phi cos \alpha]
+    \textbf{f} = 2 \Omega [\sin \phi \sin \alpha,\cos \phi,\sin \phi \cos \alpha]
 \end{equation}
-$\beta$ is the angle the slope direction makes with north.
-$\alpha$ is the slope angle from horizontal
-$\phi$ is the latitude.
-The ice base always slopes in the positive x-dimension of our domain or east, thus $\beta = 0$.
+where $g_z$ is the magnitude of gravitational acceleration in the geopotential z-direction, $\beta$ is the angle the up-slope direction makes with north, and $\alpha$ is the slope angle from horizontal.
+For the rotated Coriolis parameter $f$, $\Omega$ is the rotation rate and $\phi$ is the latitude.
 
-The buoyancy term in Equation \ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density.
-The along-slope pressure gradient is set by the ambient density of the water column $\rho_a$.
-This ambient density is determined using the initial far-field ocean density.
-For a non-sloping domain, $\rho_a$ = $\rho_i$
-% the far-field density remains constant during the simulation due to relaxation boundary conditions
-% temperature and salinity values and the initial vertical hydrostatic pressure profile in the middle of the domain. 
+The buoyancy term in Equation \ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density relative to the ambient density of the water column $\rho_a$.
+$\rho_a$ varies along slope and depth from the ice interface as a function of the hydrostatic pressure:
+\begin{equation}
+    \rho_a(x,y,z) = f_{EOS}\left(\theta^i(z),S^i(z),p(x,y,z)\right)
+\end{equation}
+where the superscript $i$ denotes the initial state. The reference density $\rho_0$ is evaluated in the center of the x-y plane ($\rho_0(z) = \rho_a(x_{mid},y_{mid},z)$). 
+%
 %Thus, we assume that the evolution of density in the boundary layer does not significantly affect buoyancy/ice-shelf slope. 
-We neglect hydrostatic pressure gradients along slope.
+We neglect hydrostatic pressure gradients along slope, except through the density term $\rho-\rho_a$.
 For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 1 bar m\textsuperscript{-1}.
@@
 
-%\paragraph{}%Surface drag
-The last term in Equation \ref{eq:uprog} represents the loss of momentum due to drag between the ice surface and the flow, where $\tau$ is the shear stress.
-This term is parameterized by the sub-grid scheme.
-
-Heat and salt conservation
-\begin{equation} \label{eq:ptprog}
-\frac{\partial \theta}{\partial t} = -\frac{\partial u_j \theta}{\partial x_j} - \frac{\partial}{\partial x_j}(\overline{u'_i \theta'}) % - F_T
-\end{equation}
-
-\begin{equation} \label{eq:saprog}
-\frac{\partial S}{\partial t} = -\frac{\partial u_j S}{\partial x_j} - \frac{\partial}{\partial x_j}(\overline{u'_i S'})
-\end{equation}
-
-Dynamic ice melting influences these equations through a modification to the SGS vertical fluxes of heat and salt at the top of the model domain, discussed XX.
+The terms on the right-hand side of the heat and salt conservation equations (Equations \ref{eq:ptprog} and \ref{eq:saprog}) are advection by the resolved flow, advection by the sub-grid scale fluctuations, and the source and sink terms  $\Phi_{\theta,S}$.
+The source and sink terms are zero in our simulations because we treat heat and salt fluxes due to melting at the boundaries through the sub-grid vertical flux term, as discussed in Section \ref{meth:tcm}.
 
@@
 
-The turbulence closure scheme is Anisotropic Minimum Dissipation (Rozema) employing the extension to scalars introduced by Abkar and Moin.
-Our implementation shows similar qualitative behavior to the stable atmospheric boundary layer published in XX; some inter-model variability is expected due to different numerics.
+The turbulence closure scheme is Anisotropic Minimum Dissipation \cite{rozema_minimum-dissipation_2015} employing the extension to scalars introduced by \citeA{abkar_minimum-dissipation_2016}.
+We validated our implementation against the stable atmospheric boundary layer test case published in \citeA{abkar_large-eddy_2017}.
+Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (damping is discussed in Section \ref{meth:setup}.
 
-Momentum fluxes are parameterized according to law of the wall following a linear stability function as in Vreugdenhil and Taylor (2019):
+Sources and sinks of momentum, heat and salt due to interactions between the flow and the ice base are all parameterized as sub-grid fluxes at the boundary.
+The resolved vertical fluxes at the top layer of the model go to zero as $w$ goes to zero according to the no-flux boundary condition and the sub-grid fluxes are determined using the scheme described below in place of the AMD scheme.
+PALM uses an Arakawa C-grid such that the ice boundary ($z=0$) is located at the edge of the top cell where the vertical velocity component resides and scalars and horizontal velocity components are located at mid-depth of the top cell ($z=-\frac{1}{2}\Delta_z$).
+We denote the interface location with subscript $b$ and the middle of the first cell below the interface with subscript $\frac{1}{2}$.
 
-\begin{equation}
-    \vec{\tau} = \rho \overline{\vec{u}'w'} = \rho u_* \frac{ \kappa (u(z_1) - u_b}{\textrm{ln}(z_1/z_0)-\Psi_m(\zeta_1)}
+Momentum fluxes are parameterized according to law of the wall following a linear stability function as in \citeA{vreugdenhil_stratification_2019}:
+%
+\begin{equation} \label{eq:tau}
+    \overline{w''u_i''}_b = u_* \frac{ \kappa \left[u_i\left(z_{\frac{1}{2}}\right) - u_b \right]}{\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right)-\Psi_m\left(\zeta_{\frac{1}{2}}\right)}
 \end{equation}
-
-where $\zeta_k = z_k/L_O$, friction velocity $u_*$, $z_0$ is the roughness length, and $z_1$ is the evaluation depth at the uppermost grid cell.
-\begin{equation}
+%
+for the horizontal velocity components (i.e., $i=1,2$).
+$\zeta_k = z_k/L_O$ is the depth from the boundary scaled by the Monin-Obukhov length, $u_*$ is the friction velocity, and $z_0$ is the roughness length.
+The Monin-Obukhov length $L_O$, computed following \citeA{mcphee_dynamics_1987}, is a function of both $u_*$ and the melt rate.
+The stability function $\Psi_m$ is linear with the scaled depth:
+\begin{equation}\label{eq:psi}
     \Psi_m(\zeta) = 1 + \beta_m \zeta
 \end{equation}
+This parameterization assumes that Coriolis forces are not dominant in the momentum balance.
 
-Similarly the sub-grid fluxes of scalars are parameterized
+Similarly the sub-grid fluxes of scalars are parameterized by
+\begin{equation} \label{eq:melt_flux}
+    \overline{w''\theta''}_b = \Gamma_{\theta} u_* \left(\theta_{\frac{1}{2}} - \theta_b\right),\: 
+    \overline{w''S''}_b = \Gamma_S u_* \left(S_{\frac{1}{2}} - S_b\right)
+\end{equation}
+%
+where the exchange coefficients are defined following \cite{mcphee_dynamics_1987}:
+\begin{equation} \label{eq:gamma}
+    \Gamma_{\theta}^{-1} = \left(\Gamma_{\theta,turb} + \Gamma_{\theta,mol}\right)^{-1},\:
+    \Gamma_S^{-1} = \left(\Gamma_{S,turb} + \Gamma_{S,mol}\right)^{-1}
+\end{equation}
+%
+The turbulent flux component follows a shape function consistent with the parameterization of momentum fluxes in Equation \ref{eq:tau}
+\begin{equation} \label{eq:gamma_turb}
+    \Gamma_{\theta,turb} = \kappa^{-1} \left[\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right) - \Psi_{\theta}\left(\zeta_{\frac{1}{2}}\right)\right], \:
+    \Gamma_{S,turb} = \kappa^{-1} \left[\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right) - \Psi_S\left(\zeta_{\frac{1}{2}}\right)\right]    % + \Psi(z_0/L_O)) % correction for roughness length
+\end{equation}
+with analogous stability functions to momentum, Equation \ref{eq:psi}
 \begin{equation}
-    \overline{w'\theta'} = \Gamma_{\theta} u_* (\theta(z_1) - \theta_b),\: 
-    \overline{w'S'} = \Gamma_S u_* (S(z_1) - S_b)
+    \Psi_{\theta}(\zeta) = 1 + \beta_{\theta}\zeta, \:
+    \Psi_{S}(\zeta) = 1 + \beta_{S}\zeta
+%    \Psi_{\theta,S}(\zeta) = 1 + \beta_{\theta,S} \zeta
 \end{equation}
-
+The coefficients of these stability functions are chosen as in \cite{zhou_self-similar_2017} and are given in Table \ref{table:var}. The molecular flux component follows \citeA{mcphee_dynamics_1987}:
 \begin{equation}
-    \Gamma_{\theta}^{-1} = (\Gamma_{\theta,turb} + \Gamma_{\theta,mol})^{-1},\:
-    \Gamma_S^{-1} = (\Gamma_{S,turb} + \Gamma_{S,mol})^{-1}
-\end{equation}
-
-\begin{equation}
-    \Gamma_{\theta,turb} = \kappa^{-1} (\textrm{ln}(z_1/z_0) - \Psi_{\theta}(\zeta_1))
-    % + \Psi(z_0/L_O)) % correction for roughness length
-\end{equation}
-\begin{equation}
-    \Gamma_{S,turb} = \kappa^{-1} (\textrm{ln}(z_1/z_0) - \Psi_S(\zeta_1))
-    % + \Psi(z_0/L_O)) % correction for roughness length
-\end{equation}
-If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($Gamma_{f}$, Table \ref{table:var}).
-
-\begin{equation}
-    \Psi_{\theta,S}(\zeta) = 1 + \beta_{\theta,S} \zeta
-\end{equation}
-The coefficients of these stability functions are chosen as in Wyngaard 2010; Zhou et al. 2017 (Table \ref{table:var}.
-
-\begin{equation}
-    \Gamma_{\theta,mol} = 12.5 \textrm{Pr}^{2/3} - 6
-\end{equation}
-\begin{equation}
+    \Gamma_{\theta,mol} = 12.5 \textrm{Pr}^{2/3} - 6, \:
     \Gamma_{S,mol} = 12.5 \textrm{Sc}^{2/3} - 6
 \end{equation}
-where Pr is the Prandtl number and Sc is the Schmidt number. %similarly for $\Gamma_{S,mol}$ but with Schmidt number.
+where Pr is the Prandtl number and Sc is the Schmidt number.
+If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($\Gamma_{f}$, Table \ref{table:var}).
 
-We use ``virtual" freshwater fluxes as opposed to freshwater fluxes with mass or volume; thus, the scalar fluxes take the form \cite{XX}
-\begin{equation}
-    \overline{w'\theta'} = -c_p u_*
-    (\Gamma_{\theta} - \Gamma_S \frac{S_b - S_1}{S_b})(\theta_b-\theta)
-    %\rho_{sw}\overline{w'\theta'} = c_p(\rho_{sw} \Gamma_T u_* + \rho_{fw} m)(T(z_1) - T_b)
-\end{equation}
+Taking into account the role of meltwater advection, Equation \ref{eq:melt_flux} is replaced by the following ``virtual'' freshwater flux form in our implementation \cite{jenkins_role_2001, asay-davis_experimental_2016}:
+\begin{eqnarray}
+    \overline{w'\theta'}_{b,v} =& -c_p u_*
+    \left[\Gamma_{\theta} - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(\theta_b-\theta_{\frac{1}{2}}\right) \label{eq:vflux_heat}\\
+    \overline{w'S'}_{b,v} =& -u_*
+    \left[\Gamma_S - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(S_b-S_{\frac{1}{2}}\right) \label{eq:vflux_salt}
+\end{eqnarray}
+%
+The temperature and salinity at the ice-ocean interface, $\theta_b$ and $S_b$, are unknown.
+Three equations are used to solve for these quantities and the melt rate $m$, the so-called three-equation parameterization:
+%
+\begin{eqnarray}
+    \rho c_p \overline{w''\theta''}_{b,v} &=& -\rho_w m L \label{eq:melt_1}\\
+    \rho \overline{w''S''}_{b,v} &=& −\rho_w m S_b \label{eq:melt_2}\\
+    \theta_b &=& \theta_f(p,S_b) \label{eq:melt_3}
+\end{eqnarray}
+%
+These equations specify that heat and salt are conserved at the ice-ocean interface (Equations \ref{eq:melt_1} and \ref{eq:melt_2}) and the interface temperature is fixed at the local freezing temperature $\theta_f$ (Equation \ref{eq:melt_3}).
+Equation \ref{eq:melt_1} assumes that the conductive heat flux into ice is negligible.
+$\rho_w$ denotes the density of freshwater.
+The freezing point is calculated using the polynomial function from \citeA{jackett_algorithms_2006}.
 
-\begin{equation}
-    \overline{w'S'} = -u_*
-    (\Gamma_S - \Gamma_S \frac{S_b - S_1}{S_b})(S_b-S)
-    %\rho_{sw}\overline{w'S'} = (\rho_{sw} \Gamma_S u_* + \rho_{fw} m)(S(z_1) - S_b)
-\end{equation}
+The PALM implementation applies the fluxes $\overline{w''u_i''}_b$, $\overline{w''\theta''}_b$, $\overline{w''S''}_b$ at the center of the first grid cell from the boundary without interpolation (i.e., $\overline{w''X''}_b = \overline{w''X''}_{\frac{1}{2}}$).
+It is noted by the PALM developers that this error was found to be small, but this error has not been evaluated for the sub-ice case.
+This error would be small if the first $\sim$10 cm is largely a constant flux layer, as hypothesized by \citeA{mcphee_turbulent_1983}.
 
-%\subsection{Prognostic melt calculation}
-The temperature and salinity at the ice-ocean interface, $\theta_b$ and $S_b$, are unknown.
-Three equations are used to solve for these quantities and the melt rate, the so-called three-equation parameterization:
-
-\begin{equation}\label{eq:melt_1}
-    \rho c_p \overline{w'\theta'}_b = -\rho_f m L_i
-    %\rho c_p \overline{w'\theta'}_b - F_{T,cond} = -\rho_{fw} m L_i
-\end{equation}
-
-\begin{equation}\label{eq:melt_2}
-    \rho \overline{w'S'}_b = −\rho_f m S_b
-\end{equation}
-
-\begin{equation}\label{eq:melt_3}
-    \theta_b = \theta_f(p,S_b)
-\end{equation}
-
-These equations specify that heat and salt are conserved at the ice-ocean interface (Equations \ref{eq:melt_1} and \ref{eq:melt_2})and the interface temperature is fixed at the local freezing temperature using the polynomial function from \cite{jackett_2006} (Equation \ref{eq:melt_3}).
-Equation \ref{eq:melt_1} assumes that the conductive heat flux into ice is 0.
-% short version in A01
-
-\subsection{Simulation set-up}
+\subsection{Simulation set-up}\label{meth:setup}
 
@@
 Large-scale horizontal pressure gradients drive the mean flow, which is geostrophic in the far-field where buoyancy does not modify the flow.
-We choose a pressure of 800 dbar at the top of the domain, a rather arbitrary choice given that the depth of ice shelf bottoms ranges an order of magnitude (roughly -2000 m to -200 m).
-The potentially dynamically relevant differences between conducting these simulations at surface pressure and 800 dbar is that the first derivative of the freezing temperature with respect to salinity is 20\% smaller and the first derivative of density with respect to salinity is about 100\% larger.
+We choose a pressure of 800 dbar at the top of the domain, an intermediate choice given that the depth of ice shelf bottoms ranges an order of magnitude (roughly -2000 m to -200 m).
+The potentially dynamically relevant differences between conducting these simulations at surface pressure and 800 dbar is that the first derivative of the freezing temperature with respect to salinity is 20\% smaller and the first derivative of density with respect to salinity is about 2 times larger.
 
 %\paragraph{Initial and boundary conditions}
-Boundary conditions for velocity, temperature and salinity are cyclic at the side boundaries, Dirichlet at the bottom boundary, and von Neumann at the top boundary.
-The bottom third of the domain is a sponge layer within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain.
-The sponge layer results in no vertical fluxes of heat, salt, or momentum across the bottom boundary.
-The von Neumann boundary conditions at the top of the domain correspond to the sub-grid fluxes of heat, salt and momentum (Equations XX), as resolved fluxes go to zero at a no-penetration boundary.
-The drag coefficient for all simulations is 0.003, a canonical value below sea ice and ice shelves though poorly constrained \cite{XX}.
-The drag coefficient sets the roughness length $z_0$ in the boundary flux equations of Section \ref{sec:meth_sgs} through the quadratic drag ``law of the wall." A complete list of parameter choices can be found in Table \ref{table:var}.
+Boundary conditions for velocity, temperature and salinity are periodic at the side boundaries, Dirichlet at the bottom boundary, and von Neumann at the top boundary.
+The bottom third of the domain is a sponge layer (Rayleigh damping) within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain \cite{klemp_numerical_1978, maronga_parallelized_2015}.
+The sponge layer results in negligible vertical fluxes of heat, salt, or momentum across the bottom boundary because scalar and velocity gradients go to 0.
+The von Neumann boundary conditions at the top of the domain correspond to the sub-grid fluxes of heat, salt and momentum (Equations~\ref{eq:tau}, \ref{eq:vflux_heat}, and \ref{eq:vflux_salt}), as resolved fluxes go to zero at a no-penetration boundary.
+The roughness length ($z_0$ in Equations~\ref{eq:tau} and \ref{eq:gamma_turb}) is chosen such that the equivalent drag coefficient assuming quadratic drag is 0.003, an intermediate value for sea ice and ice shelf bottoms, though poorly constrained \cite{holland_modeling_1999, holland_effects_2006, macayeal_numerical_1984, nicholls_measurements_2006}.
+A list of parameter choices can be found in Table~\ref{table:var}.
 
-There are two sets of simulations which have a base case in common.
-The base case has low far-field thermal driving of 0.1 $^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field geostrophic flow of 20 cm s$^{-1}$ to the [XX east].
-These conditions were chosen to favor a high TKE regime, for reasons discussed in Section \ref{sec:disc}.
-To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.1 $^{\circ}$C to 0.5 $^{\circ}$C in the first set of simulations.
-In the second set of simulations we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.
-
+We present two sets of simulations which have a base case in common.
+The base case has low far-field thermal driving of 0.1$^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field inertial oscillations of 20 cm s\textsuperscript{-1} generated by a 0.03 Pa m\textsuperscript{-1} pressure gradient.
+These conditions were chosen to favor an energetic regime, for reasons discussed in Section \ref{disc:dyn}.
+To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.1$^{\circ}$C to 0.5$^{\circ}$C in the first set of simulations.
+In the second set of simulations, we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.
+The ice base always slopes to the east in the positive x-dimension of our domain, thus $\beta = 0$.
 The far-field salinity for all runs is 35 g kg\textsuperscript{-1}.
@@
 
-The simulation duration is 50 h, corresponding to a little over 4 inertial periods.
-By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S\ref{fig:max_w2_timeseries}).
+The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h.
+By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S1).
+The turbulent intensity for cases with slopes less than 1$^{\circ}$ continues to decline, as we discuss later.
+Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.
+
+\input{table1_prm-only}
 
@@
 
-% Sensitivity to thermal driving
+% Description of time evolution
+Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs.
+This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations (Figure S1).
+We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
 
-The fluctuations in TKE with flow orientation under inertial oscillations are replicated when the mean pressure gradient is rotated, with increased TKE when flow is oriented downslope (not shown or supplemental).
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
+    \end{minipage}
+    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
+    \end{minipage}
+    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \caption{Time evolution of (a,c) melt rate and (b,d) friction velocity for (a,b) thermal driving simulations and (c,d) varying slope simulations.
+Y-axis limits differ between panels, with the black curve representing the same simulation in all panels.}
+    \label{fig:timeseries}
+\end{figure}
 
-\section{Discussion}
+We present depth-profiles of temperature, salinity, and velocity at the end of all simulations; Figure \ref{fig:dT_profiles} shows the results from the simulations in which we varied thermal driving, while Figure \ref{fig:dslope_profiles} shows those from the simulations with varying slope.
+All simulations show an evolution from the weakly stratified initial conditions to more strongly stratified conditions, particularly within the first 5 m of the ice-ocean interface (Figures \ref{fig:dT_profiles}b, \ref{fig:dslope_profiles}b).
 
-This is the second LES study of the ice-shelf ocean boundary layer in which the boundary layer turbulence declines throughout the coarse of the simulation \cite{XX}.
-This results in declining melt rates as well, making it difficult to evaluate the relationship between melting and far-field conditions at steady state -- which has been central to the goal of improving ice-shelf basal melt parameterizations with the results of high-resolution simulations.
-There are a few possible explanations for this phenomenon.
-Perhaps the best candidate is that either the sub-grid scheme or the model numerics are too dissipative, such that the TKE generated by the resolved dynamics is lost too quickly.
-Another possibility is that we are missing or underestimating a source of TKE in the model.
-Tides were not in
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
+    \end{minipage}
+    \newline\includegraphics[width=0.33\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period.
+(a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components.
+For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).}
+    \label{fig:dT_profiles}
+    % change colorbar label to \theta_\infty
+\end{figure}
 
-Furthermore, the simulations shown here have a sufficiently strong salinity gradient that the potential energy stored in the temperature gradient is not converted to TKE.
-Simulations now shown here suggest that simulated TKE can be maintained when stability ratios are as low as 4, but a detailed exploration of this phenomenon is not within the scope of the current work as LES cannot allow for the development of double-diffusive convection, which may occur when the stability ratio is lower than \~ 10.
-%It appears that well-mixed boundary layers are produced for a narrower range of conditions in simulations than in observations.
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dslope_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dslope_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dslope_43h_tav13h_z_profile.png}
+    \end{minipage}
+    \newline
+    \includegraphics[width=0.3\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \caption{Depth profiles of simulated properties as they vary with slope, averaged over the last inertial period.
+(a) temperature relative to far-field temperature (b) salinity relative to far-field salinity (c) velocity components.
+For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).
+The black curve is common to both sets of simulations (see Figure \ref{fig:dT_profiles}).}
+    \label{fig:dslope_profiles}
+\end{figure}
 
-\section{Figures and Tables}
+% Description of velocity profiles
+Ekman rotation near the boundary can be seen in all simulations (Figs.
+\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c), but for more strongly sloped runs, buoyancy plays an increasingly strong role in driving the mean flow near the boundary.
+This effect can be seen most clearly by comparing the up-slope component of the flow within several meters of the ice-ocean interface across the slope-varying simulations (Figure \ref{fig:dslope_profiles}c).
+These mean buoyancy effects increase flow velocities on the order of a few cm s\textsuperscript{-1} as slope varies from 0.01$^{\circ}$ to 1.0$^{\circ}$ (Figure \ref{fig:dslope_profiles}c).
+Flow velocities near the boundary increase on the order of 10 cm s\textsuperscript{-1} as far-field thermal driving increases from 0.1 to 0.45$^{\circ}$C at 1$^{\circ}$ slope (Figure \ref{fig:dT_profiles}c).
+This velocity increase is attributed to changes in the magnitude of buoyancy forcing at the boundary, related to differences in melt rates.
 
-\subsection{Figures}
+% BL depth
+Stratification within the boundary layer increases with thermal driving (Figure \ref{fig:dT_profiles}a,b).
+Thus, the increase in melt-induced buoyancy fluxes with thermal driving dominates over the increase in shear induced by the buoyant flow.
+Conversely, stratification decreases with increasing slope, indicating that the increase in shear induced by the buoyant flow dominates over increase in melt-induced buoyancy fluxes with slope.
+The simulated boundary layer depth has a strong relationship with local thermal driving (i.e., the difference between IOBL temperature and the freezing point), reflecting entrainment of warm water below and setting mixing lengthscales  within the IOBL.
+Boundary layer depth is identified with the local maximum in the ratio of vertical to horizontal velocity variance (e.g., Figure S2).
+This definition of the IOBL can also be considered the depth to which shear originating at the boundary influences the flow.
+In none of the simulations is the boundary layer well-mixed with respect to either temperature or salinity.
+The boundary layer depth increases through time, reaching 15 -- 25 m at the end of the simulations.
 
-\subsection{Tables}
-\input{table1_prm-only}
+% TKE budget, shear
+Shear production of turbulence dominates the TKE budget. The evolution of TKE ($E$) can be described by:
+\begin{equation}
+    \frac{dE}{dt} = F_{shear} + F_{buoy} + F_{trans} - \textrm{diss}
+\end{equation}
+Figure \ref{fig:tke_budget} shows several key terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure S3 and shows similar patterns.
+Shear production ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$ m\textsuperscript{2} s\textsuperscript{-3} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5 m of the boundary (Figure \ref{fig:tke_budget}a).
+The increase in TKE throughout the boundary layer as slope increases reflects this shear-induced turbulence (Figure \ref{fig:tke_budget}a).
+
+% TKE budget, buoyancy
+Buoyancy production of turbulence is 1 -- 2 orders of magnitude smaller than shear production, $\sim 10^{-10} \textrm{--} 10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}.
+In the sloped ice shelf, the buoyancy term can be broken into two components, the horizontal buoyancy fluxes that increase turbulence when oriented upslope and the vertical fluxes that decrease turbulence when ice is melting.
+Since our simulations only produce melting, the vertical component is always negative (dashed lines, Figure \ref{fig:tke_budget}b).
+Over the coarse of an inertial oscillation, the horizontal component of buoyancy production is generally positive when the mean flow is oriented upslope and negative when the the flow is oriented downslope.
+Interestingly, the time-averaged effect of a slope is destruction of turbulence near the boundary and production of turbulence near the base of the boundary layer (dotted lines, Figure \ref{fig:tke_budget}b).
+The net effect of both of the horizontal and vertical buoyancy components is the destruction of turbulence throughout the IOBL (solid lines, Figure \ref{fig:tke_budget}b), with the exception of the base of the IOBL where the horizontal buoyancy component augments entrainment.
+While these complexities are intriguing from a dynamical perspective, we do not explore them further here since the buoyancy term is not of leading-order in the TKE budget.
+
+% TKE budget, transport
+The transport term contains two components, advection of TKE due to pressure fluctuations and advection of TKE due to turbulence.
+The former is negligible, reaching maximum values on the order of $10^{-12}$ m\textsuperscript{2} s\textsuperscript{-3} while the latter increases turbulence at the boundary with oscillations of decreasing amplitude with distance from the boundary (Figure \ref{fig:tke_budget}c).
+
+% TKE budget, dissipation, tendency
+Dissipation, the remaining term in the TKE budget, can be inferred from the remainder of these terms and the rate of change of TKE.
+In these simulations TKE is not in steady-state, with vertically-averaged $dE/dt$ ranging from $\sim 10^{XX} \textrm{--} 10^{XX}$ m\textsuperscript{2} s\textsuperscript{-3} in the IOBL.
+Thus, dissipation is on the same order as shear production but for many runs exceeds shear production as evidenced by declining TKE.
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_46h_tav13_z_profile.png}    
+    \end{minipage}
+    \newline
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_46h_tav13_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_46h_tav13_z_profile.png}
+    \end{minipage}
+    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period.
+(b) Shear production.
+(c) Buoyancy production.
+The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted.
+(d) TKE transport.
+Positive denotes production, negative destruction.
+Note that the x-axis scales differ between panels.}
+    \label{fig:tke_budget}
+    % Change x-axis label for buoyancy production terms
+\end{figure}
+
+% discuss turbulent structures
+To demonstrate the simulated turbulent structures in this regime, we present horizontal and vertical cross-sectional  snapshots through the domain for the two slope end-members in Figure \ref{fig:cross-section}.
+Turbulent structures within the IOBL are consistent with propagating Holmboe shear instabilities under stable stratification \cite{carpenter_identifying_2010}.
+Shear is stronger within the IOBL than at the base of the IOBL due to the concentration of buoyant plume flow near the top of the IOBL.
+Consequently, the amplitude of these structures increases near the boundary for the more strongly-sloped simulations (Figures \ref{fig:cross-section}b,d).
+The difference in IOBL turbulence with slope is perhaps best seen in the turbulent structures at 1 m from the ice-ocean interface (Figure \ref{fig:cross-section}e,f).
+The structures become increasingly filamentous (i.e., near-wall streaks, e.g., \citeA{del_alamo_spectra_2003, hoyas_scaling_2006}) and coherent as slope and thus the buoyancy-driven current increase.
+Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases;  velocity fluctuations are less confined to the slope-parallel direction (Figure S2).
+% consider discussing entrainment here
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 1cm 4cm 1cm},clip,width=\textwidth]{Figures/dslope2/pt_xz_y64_zmax42_t40.png}
+    \end{minipage}%
+    \begin{minipage}{0.55\textwidth}
+        \includegraphics[trim={0 1cm 0 1cm},clip,width=\textwidth]{Figures/dT1/pt_xz_y64_zmax42_t40.png}
+    \end{minipage}
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 1cm 4cm 1cm},clip,width=\textwidth]{Figures/dslope2/sa_xz_y64_zmax42_t40.png}
+    \end{minipage}%
+    \begin{minipage}{0.55\textwidth}
+        \includegraphics[trim={0 1cm 0 1cm},clip,width=\textwidth]{Figures/dT1/sa_xz_y64_zmax42_t40.png}
+    \end{minipage}
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[trim={0 0cm 1cm 0},clip,width=\textwidth]{Figures/dslope2/v_xy_z1_zmax1_t40.png}
+    \end{minipage}%
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[trim={1cm 0cm 0cm 0},clip,width=\textwidth]{Figures/dT1/v_xy_z1_zmax1_t40.png}
+    \end{minipage}%
+    \begin{minipage}{0.05\textwidth}
+    \hfill
+    \end{minipage}
+    \caption{Instantaneous flow structures observed at 40h in (a,c,e) 0.01$^{\circ}$ slope case and (b,d,f) 1$^{\circ}$ slope case.
+(a,b) Temperature in cross section mid-way through the y-axis.
+(c,d) Salinity in cross-section mid-way through the y-axis.
+(e,f) Cross-slope velocity fluctuations at 1 m below the ice-ocean interface.
+Note that the colorbar scale is smaller in (e) than (f).}
+    % Add contours to a-d to show structures more clearly
+    \label{fig:cross-section}
+\end{figure}
+
+% Melt rate relationship with inertial period
+The dominant temporal frequency in melt rate is the inertial frequency, and the melt response to those oscillations is highly nonlinear.
+Maximum melt rates occur when the mean flow is oriented between the up-slope direction and the Coriolis-favored direction, and minimum melt rates roughly 180$^{\circ}$ opposed to that.
+These melt rate fluctuations correspond to fluctuations in TKE which are reflected in the friction velocity shown in Figure \ref{fig:timeseries}b.
+The dominant contribution to turbulence is shear production of TKE, which changes its distribution with depth as the mean flow profile evolves (Figure S3).
+During high-melt periods, the far-field flow is oriented up-slope and shear production of TKE is concentrated near the boundary (Figure \ref{fig:dT_profiles}c,d).
+During low-melt periods, the far-field flow is oriented down-slope and shear production of TKE is concentrated a few meters away from the boundary (Figure \ref{fig:tke_budget}b).
+
+% intermittent turbulence
+Melt rate fluctuations increase in amplitude as thermal driving increases and as slope increases, which we attribute to the increasing importance of buoyancy forcing in driving a near-boundary plume and thus determining the depth-distribution of shear.
+At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the mixed layer over a few hours (not shown).
+The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a hiatus in turbulence during the down-slope flow period.
+This can be seen in the dramatic reduction in friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b).
+Thus, in our simulations rotational effects cause intermittency in turbulence when the IOBL is sufficiently stratified.
+We discuss this intermittency further in Section \ref{disc:dyn}.
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/e_hovmoller.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/e_hovmoller.png}
+    \end{minipage}
+    \begin{minipage}{0.4\textwidth}
+        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/vel_var_ratio_hovmoller.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/vel_var_ratio_hovmoller.png}
+    \end{minipage}
+    \caption{Example of turbulent intermittency as seen in (a,b) TKE and (c,d) vertical velocity variance.
+(a,c) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
+(b,d) An intermittent case: 0.45$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
+    \label{fig:intermittency}
+\end{figure}
+
+% Melt rate sensitivity to thermal driving
+Time-averaged melt rates are roughly linear with thermal driving (Figure \ref{fig:melt_sensitivity}a).
+The derived, time-averaged thermal exchange coefficient (described in Section \ref{meth:tcm}) is fairly insensitive to thermal driving.
+The thermal exchange coefficient during the last 12 hours of the simulations is between 0.005 and 0.006 for the simulated range of thermal driving values.
+During the first 12 hours of the simulation, simulated thermal exchange coefficients are 0.008 due to weaker stratification near the interface, higher friction velocities, and greater TKE.
+The derived thermal exchange coefficient decreases somewhat in the high thermal driving cases due to pronounced periods of low melt as TKE declines with increasing stratification.
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dT_tav12.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
+    \end{minipage}
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4.1cm 0 0cm},clip,width=\textwidth]{Figures/gammaT_dT_tav12_zlim2.png}
+        \vspace{0.7cm}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 3.4cm 0 0cm},clip,width=\textwidth]{Figures/gamma_T__us__dslope_tav12_tlim52.png}
+        \centering
+        \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \end{minipage}
+    \caption{(a) Melt rate vs.
+thermal driving.
+(b) Melt rate vs.
+slope.
+(c) Thermal exchange coefficient vs.
+far-field thermal driving for thermal driving simulations.
+Dashed line denotes the value recommended by \citeA{jenkins_observation_2010}.
+(d) Thermal exchange coefficient vs.
+friction velocity for sloped simulations.
+Note the difference in y-axis limits from (c).
+The 0.01$^{\circ}$ and 0.1$^{\circ}$ slope cases are overlapping.}
+    \label{fig:melt_sensitivity}
+\end{figure}
+
+% Melt sensitivity to slope
+There is also a linear relationship between melt rate and ice-shelf basal slope, with threshold-like behavior at slopes less than 0.01$^{\circ}$.
+This threshold behavior in melting in the two lowest-slope cases is attributable to similar friction velocities (Figure \ref{fig:melt_sensitivity}d) arising from similar IOBL velocities and turbulence  (Figure \ref{fig:dslope_profiles}c,d).
+This behavior is discussed in more detail in Section \ref{disc:prm}.
+The differences in derived thermal exchange coefficient are not pronounced as slope varies, on the order of a 10\% change as slope increases from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:melt_sensitivity}d).
+Variability in the thermal exchange coefficient with slope is largely determined by differences in friction velocity between simulations (Fig.
+\ref{fig:melt_sensitivity}d) while there is a smaller ($\sim$20\%) opposite effect from decreasing interfacial thermal driving with increasing slope (not shown).
+These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes (Figure \ref{fig:dslope_profiles}c,d).
+
+% Scaling for flux profiles
+The relatively narrow range of conditions simulated here suggests that a depth-dependent shape function for scalar fluxes could be formulated.
+The distance from the interface is scaled by the Ekman depth:
+\begin{equation}
+    d_E = (2 K_e)^{1/2} |f_3|^{-1/2}
+\end{equation}
+where $K_{b}$ is the mean bulk viscosity in the turbulent boundary layer assuming the total fluxes follow Fick's law:
+\begin{equation}
+    \overline{w'\mathbf{u}'} = K_{b} d\mathbf{u}/dz
+\end{equation}
+$K_e$ profiles are shown in Figure S4.
+
+% Scaling heat flux profiles with thermal driving
+The linear scaling of melt rate with thermal driving suggests a linear scaling of heat flux profiles with thermal driving.
+We find that this scaling largely collapses the four thermal driving profiles, with some deviation from this shape for the run that experiences intermittent turbulence (Figure \ref{fig:heatflux_profiles}c).
+The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:heatflux_profiles}c).
+Scalar fluxes decline near the boundary for the 1$^{\circ}$ slope cases, a feature that we discuss further in Section \ref{disc:prm}.
+Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure S5).
+The vertical salt flux profiles are shown in Figure S6 and have a very similar shape to the vertical heat flux profiles.
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_44h_tav12_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav12_z_profile.png}
+    \end{minipage}
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13_dTscale_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav13_slopescale_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \end{minipage}
+    \caption{Vertical profile of heat flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases.
+(a,b) are in physical units while (c,d) are scaled by the Ekman depth, far-field thermal driving, and slope.
+The black curve is represents the same simulation in all panels.}
+    %Consider replacing (d) with scaling by sin\alpha
+    %Change scaled vertical axis limits to 0-40
+    %Change all to centered on 43h and averaged 13h
+    \label{fig:heatflux_profiles}
+\end{figure}
+
+% Scaling heat flux profiles with slope
+Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($\sin^{1/4}\alpha$, Figure \ref{fig:heatflux_profiles}d).
+We also find that the Ekman depth is a poor predictor of boundary layer depth.
+This may be due to the depth-variable shear induced by buoyancy which is not reflected in the depth-mean IOBL bulk viscosity used to compute the Ekman depth.
+%It is interesting that the boundary layer depths of the thermal driving cases at 1$^{\circ}$ slope scale similarly with the Ekman depth despite the differences in buoyancy of the IOBL (Figure \ref{fig:heatflux_profiles}c).
+It suggests that the bulk viscosity in the IOBL, used to compute the Ekman depth, is a poor predictor of entrainment as slope varies.
+
+% momentum flux profiles
+By looking at the variation of momentum flux with depth shown in Figure \ref{fig:momflux_profiles}, we can examine the relative contributions of interfacial drag and buoyant acceleration of the IOBL to the velocity profiles shown in Figure \ref{fig:dT_profiles}c,e and \ref{fig:dslope_profiles}c.
+Since the mean velocity is oriented both upslope (+$u$) and cross-slope (+$v$), positive $\overline{u'w'}$ and $\overline{v'w'}$ close to the interface indicate slowing of the current due to drag whereas negative $\overline{u'w'}$ and $\overline{v'w'}$ a few m below the interface through much of the boundary layer indicate buoyant acceleration of the IOBL.
+The amplitude of momentum fluxes increases with slope and thermal driving consistent with increases in IOBL velocity and TKE.
+Intermittency in turbulence also changes the shape of momentum flux profile, displacing momentum peaks closer to the surface as the IOBL shoals (pink curve, Figure \ref{fig:momflux_profiles}a).
+
+\begin{figure}[h!]
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_44h_tav12_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_46h_tav12_z_profile.png}
+        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+    \end{minipage}
+    \caption{Momentum flux averaged over the last inertial period for (a) thermal driving cases and (b) slope cases.
+Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).
+Positive flux denotes upward flux (i.e., drag) and }
+    \label{fig:momflux_profiles}
+    % change x-axis labels to \overline{u_i'w'}
+\end{figure}
+
+\section{Discussion}\label{disc}
+
+\subsection{IOBL turbulence} \label{disc:dyn}
+
+In the simulations presented here, turbulence declines throughout the course of the simulation; for a few highly stratified cases becoming intermittent.
+The relationship between stable stratification, shear, and the persistence of turbulence remains an open question \cite{zonta_stably_2018}.
+Thus, it is not possible a priori to determine whether the level of turbulence simulated by this LES model is appropriate for the regime space we have sampled.
+While we did conduct model validation against a stably stratified atmospheric boundary layer test case (see Section \ref{meth:tcm}), the degree of stratification at the boundary in that case did not approach that simulated in the sub-ice configuration.
+Fundamentally, we cannot guarantee that our LES is not overly dissipative such that the TKE generated by the resolved dynamics is lost too quickly relative to real-world sub-ice settings.
+
+Excess dissipation could arise either through the sub-grid scheme or the model numerics.
+We found a rapid loss of turbulence in PALM simulations when a dynamic Smagorinky turbulence closure was used, which is consistent with previous studies on the limited applicability of the standard Smagorinsky turbulence closure to strongly stratified flows due to the strong anisotropy of these flows \cite{flores_analysis_2011, jimenez_large-eddy_2005}.
+This motivated our adoption of the AMD turbulence closure scheme.
+However, we found that the buoyancy term suggested by \citeA{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
+We neglected this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019}.
+
+Strongly stratified turbulence has been associated with intermittent turbulence \cite{nieuwstadt_direct_2005, wiel_cessation_2012}, though there are also numerical experiments that fail to produce intermittency even under strongly stable stratification \cite{arya_buoyancy_1975, komori_turbulence_1983}.
+This is not the first study to find the emergence of intermittent turbulence in stably stratified, sub-ice settings \cite{vreugdenhil_stratification_2019}.
+Flow relaminarization occurs periodically in our most strongly stratified simulations; stratification coincident with high thermal driving and high melt rates.
+\citeA{donda_collapse_2015} have argued that, in strongly stratified flows, the cessation of turbulence is transient provided there are sufficiently large perturbations.
+This is consistent with our finding that the temporal variability in shear over inertial oscillations provides a sufficient perturbation to reinitiate turbulence.
+Our simulations approach a gradient Richardson number of 0.25, which is considered to be the approximate value at which turbulence neither grows nor decays \cite{rohr_growth_1988, holt_numerical_1992}.
+Thus, fluctuations in TKE are plausible at the simulated levels of stratification and shear.
+However, when turbulence is intermittent, as it is in this study, the application of LES may be inappropriate due to its inherent horizontal averaging over laminar and turbulent regions \cite{stoll_large-eddy_2008}.
+Thus, our results at the highest thermal-driving values should be interpreted with caution.
+
+In this study, we did not attempt to reproduce observed conditions at a particular ice-shelf location due to the difficulties of matching unobserved far-field forcings and the exclusion of tides from our simulations for ease of interpretation.
+Nonetheless, it appears as though well-mixed boundary layers are simulated for a narrower range of conditions in simulations than in observations.
+The background flow chosen in these simulations is quite strong at 20 cm s\textsuperscript{-1} and thermal driving is relatively low such that we expected to produce a well-mixed boundary layer as is observed in melting regions of the Filchner-Ronne Ice Shelf \cite{nicholls_oceanographic_2001}.
+However, observations to date are insufficient to provide reliable predictions of IOBL stratification \cite{malyarenko_synthesis_2020}.
+The observational picture is quite nuanced with a range of stratification observed even within one ice shelf (e.g., \citeA{hattermann_two_2012}).
+
+Our simulations are certainly missing some sources of TKE present in ice-shelf cavities which could modify IOBL structure and mixing efficiency.
+These simulations did not include tides, which provide perturbations to the mean velocity that enhance melt rates and entrainment, especially at Filchner-Ronne \cite{makinson_modeling_1999, makinson_influence_2011, mueller_tidal_2018}.
+While internal gravity waves arise in LES, they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \cite{gwyther_cold_2020}.
+Enhanced drag at the ice-shelf base could increase shear production of TKE; however under strong stratification, surface roughness elements may suppress turbulence rather than enhance it \cite{ohya_wind-tunnel_2001}.
+
+% Consider discussing boundary layer depth and entrainment
+
+% Consider leading this section with the discussion of shear-driven turbulence
+Shear-driven turbulence within the IOBL plays a central role in determining vertical heat fluxes and thus melt rates.
+In these simulations the destruction of TKE by the stabilizing buoyancy flux is two orders of magnitude smaller than shear production of TKE throughout the IOBL.
+Our finding that shear production of TKE dominates over the buoyancy term is consistent with \citeA{davis_turbulence_2019} who found that shear production was an order of magnitude greater than buoyancy destruction of TKE in the IOBL below Larsen C Ice Shelf.
+
+The flux Richardson number, $\text{Ri}_f$, the ratio of buoyancy flux to shear-driven TKE production, provides a measure of mixing efficiency.
+The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.2$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \cite{armenio_investigation_2002, peltier_mixing_2003}.
+This is consistent with our finding that the thermal exchange coefficient decreases for the high thermal driving cases which also achieve stronger IOBL stratification.
+
+\subsection{Evaluating melt sensitivity and turbulent flux representations in ocean models}\label{disc:prm}
+
+\subsubsection{Insights into melt sensitivity to ocean conditions}
+
+% Argument for validity of findings in non-steady conditions
+The decline in IOBL turbulence discussed in Section \ref{disc:dyn} results in declining melt rates, making it difficult to evaluate the relationship between melting and far-field conditions at steady state, which would provide the most direct path to assessing melt rate sensitivity to ocean conditions.
+As discussed in \citeA{jenkins_simple_2016}, achieving steady-state solutions in simulations may require prescribing large-scale gradients in temperature.
+We have not included these large-scale gradients in our simulations, but this may be an avenue for future work.
+However, we believe that our transient solutions do provide some indications of how melt rates and boundary layer properties depend on ocean temperature and ice-shelf slopes.
+One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature and slope remains consistent through time during the last two inertial periods simulated.
+Furthermore, we find similar sensitivities of melt rate to IOBL temperature and velocity in simulations with different initial conditions at times for which IOBL conditions are statistically similar.
+
+% sensitivity of melt rate to temperature
+The linear relationship we find between far-field ocean temperature and melt rates is consistent with some previous studies \cite{rignot_rapid_2002}.
+It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies an increase in far-field thermal driving.
+The quadratic relationship between melt rate and thermal driving in \citeA{holland_response_2008} is a function of both a linear relationship between the local, far-field thermal driving and melt rate and a linear relationship between far-field thermal driving and friction velocity.
+The former relationship is addressed by this study and agrees with \citeA{holland_response_2008}; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity is unchanged.
+In contrast, in sea ice settings this sensitivity was found to be significantly smaller with an exponent of 0.38 \cite{ramudu_large_2018}.
+
+To some extent, this linear relationship between far-field thermal driving and melt rate is embedded in the parameterization of heat fluxes employed at the ice base in these simulations.
+Specifically, the melt rate is prescribed to have a linear dependence on the thermal driving using the temperature in the first model layer, see Equation \ref{eq:melt_flux}.
+However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL can mediate this relationship between \textit{far-field} temperature and melt rates, and yet the dependence from these simulations is still fairly linear.
+
+% sensitivity of melt rate to slope
+The finding that slopes as low as 0.5$^{\circ}$ significantly influence melt rates is not unexpected from a consideration of momentum balance, but may be an underappreciated aspect of IOBL simulation in Antarctic ice-shelf settings.
+The linear relationship between ice-shelf slope and melt rate suggests a stronger dependence at very low slopes than that found by \cite{mondal_ablation_2019} using Direct Numerical Simulations at higher slopes ($m \propto \sin^{2/3}\alpha$).
+Further investigation would be needed beyond the small number of simulations presented here to diagnose this discrepancy.
+
+% sensitivity of melt rate to slope, at very low slopes
+The threshold-like behavior in melt rates at very low slopes is not predicted by geostrophic balance between Coriolis and buoyancy forcing, which dictates a linear relationship between $\sin\alpha$ and IOBL velocity.
+This threshold behavior could be produced if any additional buoyant acceleration produced by the small increase in slope from 0.01$^{\circ}$ to 0.1$^{\circ}$ increases dissipation, resulting in a negative feedback on IOBL turbulence.
+From a dynamical perspective, this may be an interesting target for more highly resolved LES in the near-boundary region.
+However, this threshold is located at low enough slopes that it is likely not of significance to melt rate parameterization for coarse-resolution ocean models, so we do not devote further attention to it here.
+
+\subsubsection{Thermal exchange coefficient}
+
+% Methodology for evaluating thermal exchange coefficient
+The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.25m below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties on the order of 1 m below the ice-ocean interface.
+Thus, we compute a thermal exchange coefficient using ocean properties 2 m below the ice-ocean interface.
+We substitute the friction velocity computed by Equation \ref{eq:tau} with one computed using a quadratic drag law from the velocity at 2 m and the applied drag coefficient, consistent with modeled drag implementations.
+This approach allows the closest comparison between the thermal exchange coefficient indicated by these simulations and that currently parameterized in ocean models.
+
+% discussion of low thermal exchange coeff in all runs
+The thermal exchange coefficients used in these simulations are less than the value of 0.011 derived from observations \cite{jenkins_observation_2010}.
+There are two main factors that contribute to this result.
+The first is the choice of the parameterization of fluxes at the ice-ocean interface (i.e., over sub-meter scales).
+We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov lengthscale.
+We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \cite{monin_basic_1954}, the work of McPhee \cite{mcphee_air-ice-ocean_2008} and the depth-scaling of scalar fluxes in a more highly resolved sub-ice LES \cite{vreugdenhil_stratification_2019}.
+However, we acknowledge that more validation of these parameterizations is needed.
+The second contributing factor is declining simulated TKE, which results in a $\sim$50\% reduction of thermal exchange coefficients over the coarse of these simulations.
+
+% thermal exchange coeff, thermal driving
+Our results also suggest a modest decline in the thermal exchange coefficient at higher thermal driving, which may lead to a sub-linear relationship between thermal driving and melt rate at higher thermal driving values.
+Due to the limitations of our LES modeling discussed in Section \ref{disc:dyn}, we cannot recommend under what range of thermal driving values a reduced thermal exchange coefficient may be appropriate.
+Given the climatic importance of accurately simulating high thermal driving regimes associated with dynamic ice-shelf thinning, this may be a fruitful avenue for future work.
+
+% thermal exchange coeff, slope
+The relationship between the thermal exchange coefficient and slope can be reduced to a linear relationship between thermal exchange coefficient and friction velocity.
+Our simulations are too few to evaluate whether a similar relationship holds when the source of friction velocity changes is the background flow rather than the slope.
+LES of sea ice melting does support this linear relationship between thermal exchange coefficient and friction velocity XX \cite{ramudu_large_2018}.
+In any case, the changes in the thermal exchange coefficient with slope were small, only 10\% between 0$^{\circ}$ and XX$^{\circ}$ cases.
+This suggests that, if a coarse-resolution simulation predicts friction velocity accurately, a melt parameterization with a constant thermal exchange coefficient may be adequate in Antarctic ice-shelf settings.
+Thus, the burden of melt projection accuracy may fall more heavily on parameterizing or resolving buoyant flow than on improving the slope-dependence in the parameterization of scalar fluxes (i.e., improving Equation \ref{eq:melt_flux}).
+
+\subsubsection{Depth-dependence of turbulent fluxes}
+
+% Need for modified vertical mixing parameterization
+There is reason to believe that improving ice-shelf basal melt projections using ocean models will require not only an accurate melt parameterization but also an improved vertical mixing scheme.
+\citeA{jenkins_shear_2021} demonstrated significantly different IOBL characteristics when the K-profile Parameterization (KPP) was used in contrast to a low- or high-order turbulence closure scheme.
+The bulk viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (his Figure 3).
+Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or modified KPP scheme in sub-ice settings.
+
+% model resolution challenges
+A complication in melt parameterization of slope effects is the differential ability of ocean models and their vertical grid configurations to capture IOBL flow.
+We find that this buoyant flow is concentrated in the uppermost 10 m, with peak velocities as close as 3 m from the interface.
+This flow is unlikely to be resolved by most ocean models, which have typical vertical resolutions near the interface of 10s m though some model configurations are reaching $\sim$1 m resolutions \cite{gwyther_cold_2020}.
+This then raises important questions about the parameterization of ice-ocean interface scalar and momentum fluxes.
+If the buoyancy-driven boundary current is unresolved in most coarse-resolution ocean models, then the friction velocity as computed from a quadratic drag law and the velocity at the first grid cell is likely to underestimate the true friction velocity.
+For instance, in our simulations a friction velocity computed from the far-field velocity is $\sim$XX\% greater than the interfacial friction velocity.
+Thus, more accurate melt rate projections may result prescribe a depth-dependent parameterization of vertical scalar and momentum fluxes to provide some sensitivity of melt rates to model resolution.
+
+% scalar flux profiles
+Our depth-dependent shape function for scalar fluxes agrees with the turbulent scalar flux parameterization of \citeA{mcphee_dynamics_1987}, which features a linear increase from 0 at the boundary layer depth to the flux at the surface.
+The simulations with slopes of 1$^{\circ}$ diverge from this linear behavior within a few m from the boundary.
+We attribute this to boundary effects that reduce TKE and bulk diffusivity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \cite{monin_basic_1954}.
+This shape function for scalar fluxes through the IOBL should be explored under a broader range of conditions to determine whether this linear scaling is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer.
+It's worth noting that any implementation of these depth-dependent scalar fluxes necessitates an inequality between the vertical heat and salt fluxes from the top model grid cell and the heat and salt fluxes associated with melting.
+Thus, the closure of those budgets will likely involve horizontal scalar fluxes as well.
+
+% scalar flux profiles vs. slope - does not exist
+Assuming one's vertical mixing parameterization accurately predicts the bulk viscosity of the IOBL, the Ekman depth scaling is a moderately strong predictor for IOBL depth as the thermal driving changes but a weak predictor for IOBL depth as slope changes.
+Given the presence of intermittency in our 1$^{\circ}$ slope simulations and relatively small differences in IOBL depth among our simulations, further work is needed to understand entrainment processes for the IOBL so that a depth-dependent shape function for scalar and momentum fluxes can be established.
+
+A depth-dependent function for momentum is also necessary in ice-shelf settings given that strong stratification causes momentum fluxes to significantly deviate from the quadratic drag function typically employed in ocean models.
+Even in the absence of ice-shelf slope, the near-interface stratification significantly decreases drag \cite{garcia-villalba_turbulence_2011, mcphee_revisiting_2008}.
+The addition of an ice-shelf slope to ocean models that do not fully resolve a buoyant plume further complicates the parameterization of momentum fluxes at the ice-ocean interface.
+A depth-dependent shape function for momentum fluxes which may prescribe negative (downward) momentum fluxes at the top grid cell below ice shelves for typical ocean model resolutions (see Figure \ref{fig:momflux_profiles} at, e.g., 5 m depth).
+In other words, the momentum boundary condition may need to accelerate the flow at the boundary (at least in the up-slope direction) to produce more accurate shear-driven mixing in the resolved portion of the domain when the buoyant plume is unresolved.
+
+\section{Conclusion}
 
@@
 
-This research used resources provided by the Los Alamos National Laboratory Institutional Computing Program, which is supported by the U.S.
+This work was funded by the U.S.
+Department of Energy (DOE), Office of Science, Biological and Environmental Research, and Advanced Scientific Computing Research programs.
+Carolyn Begeman received funding for this work from a Chick Keller Postdoctoral Fellowship through the Center for Earth and Space Sciences at Los Alamos National Laboratory.
+Computing resources were provided by the Los Alamos National Laboratory Institutional Computing Program, which is supported by the U.S.
 Department of Energy National Nuclear Security Administration under Contract No.
@@
 
+\newpage
+\bibliography{references}
+
 \end{document}

### 2021-06-29 main.tex
Updates from Overleaf

@@
     \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
+        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
     \end{minipage}%
     \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
+        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
     \end{minipage}
-    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
     \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
+        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
     \end{minipage}%
     \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
+        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
     \end{minipage}
-    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
     \caption{Time evolution of (a,c) melt rate and (b,d) friction velocity for (a,b) thermal driving simulations and (c,d) varying slope simulations.
@@
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}
-    \newline\includegraphics[width=0.33\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
     \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period.
@@
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dslope_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dslope_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 7.5cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dslope_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}
-    \newline
-    \includegraphics[width=0.3\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
     \caption{Depth profiles of simulated properties as they vary with slope, averaged over the last inertial period.
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_46h_tav13_z_profile.png}    
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
     \end{minipage}
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_46h_tav13_z_profile.png}
+        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_46h_tav13_z_profile.png}
+        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}

### 2021-07-01 main.tex

@@
 The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h.
-By this point, the turbulent intensity as measured by the maximum vertical velocity fluctuation, is reasonably steady-state over one inertial period for the 1$^{\circ}$-slope simulations (Figure S1).
-The turbulent intensity for cases with slopes less than 1$^{\circ}$ continues to decline, as we discuss later.
+By this point, the time-mean kinetic energy of the flow has reached steady-state.
+However, the turbulent intensity for all cases continues to decline, with more pronounced TKE loss at lower slopes (Figure \ref{fig:timeseries}a,d).
 Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.
@@
 Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs.
-This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations (Figure S1).
+This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations.
 We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
@@
     \centering
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/tke_cmp_dT_t.png}
     \end{minipage}%
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
     \end{minipage}
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/tke_cmp_dslope_t.png}
     \end{minipage}%
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
     \end{minipage}
-    \caption{Time evolution of (a,c) melt rate and (b,d) friction velocity for (a,b) thermal driving simulations and (c,d) varying slope simulations.
-Y-axis limits differ between panels, with the black curve representing the same simulation in all panels.}
+    \caption{Time evolution of (a,d) domain-averaged turbulent kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
+The black curve representing the same simulation in all panels.}
     \label{fig:timeseries}
@@
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4.5cm 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
     \end{minipage}
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 11cm 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}
-    \includegraphics[width=0.4\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
     \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period.
@@
 
-\begin{figure}[h!]
+\begin{figure}[]
     \centering
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 1cm 4cm 1cm},clip,width=\textwidth]{Figures/dslope2/pt_xz_y64_zmax42_t40.png}
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[trim={1cm 0 3cm 0},clip,width=\textwidth]{Figures/pt_slope01_xz_y64_zmax42_t40.png}
     \end{minipage}%
     \begin{minipage}{0.55\textwidth}
-        \includegraphics[trim={0 1cm 0 1cm},clip,width=\textwidth]{Figures/dT1/pt_xz_y64_zmax42_t40.png}
+        \includegraphics[trim={1.5cm 0 0.5cm 0},clip,width=\textwidth]{Figures/pt_slope1_xz_y64_zmax42_t40.png}
     \end{minipage}
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 1cm 4cm 1cm},clip,width=\textwidth]{Figures/dslope2/sa_xz_y64_zmax42_t40.png}
+    \begin{minipage}{0.45\textwidth}
+        \includegraphics[trim={1cm 0 3cm 0}, clip, width=\textwidth]{Figures/sa_slope01_xz_y64_zmax42_t40.png}
     \end{minipage}%
     \begin{minipage}{0.55\textwidth}
-        \includegraphics[trim={0 1cm 0 1cm},clip,width=\textwidth]{Figures/dT1/sa_xz_y64_zmax42_t40.png}
+        \includegraphics[trim={1.5cm 0 0.5cm 0}, clip, width=\textwidth]{Figures/sa_slope1_xz_y64_zmax42_t40.png}
     \end{minipage}
     \begin{minipage}{0.45\textwidth}
-        \includegraphics[trim={0 0cm 1cm 0},clip,width=\textwidth]{Figures/dslope2/v_xy_z1_zmax1_t40.png}
+        \includegraphics[trim={1.5cm 0 3.4cm 0},clip,width=\textwidth]{Figures/v_slope01_xy_z1_zmax1_t40.png}
     \end{minipage}%
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[trim={1cm 0cm 0cm 0},clip,width=\textwidth]{Figures/dT1/v_xy_z1_zmax1_t40.png}
+    \begin{minipage}{0.6\textwidth}
+        \centering
+        \includegraphics[trim={2cm 0 0.5cm 0},clip,width=\textwidth]{Figures/v_slope1_xy_z1_zmax1_t40.png}
     \end{minipage}%
@@
     \end{minipage}
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/vel_var_ratio_hovmoller.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/vel_var_ratio_hovmoller.png}
-    \end{minipage}
-    \caption{Example of turbulent intermittency as seen in (a,b) TKE and (c,d) vertical velocity variance.
-(a,c) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
-(b,d) An intermittent case: 0.45$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
+    \caption{Example of turbulent intermittency as seen in white regions of turbulent kinetic energy (TKE).
+(a) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
+(b) An intermittent case: 0.45$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
     \label{fig:intermittency}
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dT_tav12.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_dT_cmp_dT_43h_tav13h.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 3.5cm 0 0},clip,width=\textwidth]{Figures/melt_dslope_tav12.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_slope_cmp_dslope_43h_tav13h.png}
     \end{minipage}
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4.1cm 0 0cm},clip,width=\textwidth]{Figures/gammaT_dT_tav12_zlim2.png}
-        \vspace{0.7cm}
+        \includegraphics[trim={0 0 0 0cm},clip,width=\textwidth]{Figures/gammaT_dT_cmp_dT_43h_tav13h.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 3.4cm 0 0cm},clip,width=\textwidth]{Figures/gamma_T__us__dslope_tav12_tlim52.png}
-        \centering
-        \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+        \includegraphics[trim={0 0 0 0cm},clip,width=\textwidth]{Figures/gammaT_us_cmp_dslope_43h_tav13h.png}
     \end{minipage}
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_44h_tav12_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav12_z_profile.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13_dTscale_z_profile.png}
-        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_dTscale_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 4cm 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_slope_46h_tav13_slopescale_z_profile.png}
-        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_slopescale_z_profile.png}
     \end{minipage}
@@
 (a,b) are in physical units while (c,d) are scaled by the Ekman depth, far-field thermal driving, and slope.
-The black curve is represents the same simulation in all panels.}
+The black curve is represents the same simulation in all panels.
+The horizontal axis limits vary between panels.}
     %Consider replacing (d) with scaling by sin\alpha
@@
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_44h_tav12_z_profile.png}
-        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_thermal_driving.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_43h_tav13h_z_profile.png}
     \end{minipage}%
     \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 7.5cm 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_46h_tav12_z_profile.png}
-        \centering \includegraphics[width=0.7\textwidth,trim={1cm 0cm 1cm 5cm}, clip]{Figures/colorbar_slope.png}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}

### 2021-07-01 main.tex

@@
 (a) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
-(b) An intermittent case: 0.45$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
+(b) An intermittent case: 0.6$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
     \label{fig:intermittency}
@@
 However, we believe that our transient solutions do provide some indications of how melt rates and boundary layer properties depend on ocean temperature and ice-shelf slopes.
-One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature and slope remains consistent through time during the last two inertial periods simulated.
-Furthermore, we find similar sensitivities of melt rate to IOBL temperature and velocity in simulations with different initial conditions at times for which IOBL conditions are statistically similar.
+One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure SXX).
+On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}e-f).
+Nonetheless we are able to find relationships between the vertical heat flux profiles and ocean temperature and slope that suggest predictability of the mean effects of turbulence despite the transience of these simulations.
 

### 2021-07-12 vis_scripts/cp_flux_profile_fig.sh
Add figure res, sgs heatflux

@@ -1,19 +1,29 @@
 PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dpdy_021/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 PREFIX_SLOPE=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_alpha_surface_006/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 SUFFIX_OLD_T=_cmp_dT0.2_dT0.4_43hr_tav13_42zmax_z_profile.png
+SUFFIX_OLD_T1=_cmp_dT0.2_dT0.4_8hr_tav13_42zmax_z_profile.png
 SUFFIX_OLD_T_SCALE=_cmp_dT0.2_dT0.4_43hr_tav13_scale_z_profile.png
 SUFFIX_NEW_T=_cmp_dT_43h_tav13h_z_profile.png
+SUFFIX_NEW_T1=_cmp_dT_8h_tav13h_z_profile.png
 SUFFIX_NEW_T_SCALE=_cmp_dT_43h_tav13h_dTscale_z_profile.png
 SUFFIX_OLD_SLOPE=_cmp_slope0.10_slope0.50_43hr_tav13.0_42zmax_z_profile.png
+SUFFIX_OLD_SLOPE1=_cmp_slope0.10_slope0.50_8hr_tav13.0_42zmax_z_profile.png
 SUFFIX_OLD_SLOPE_SCALE=_cmp_slope0.10_slope0.50_43hr_tav13.0_scale_z_profile.png
 SUFFIX_NEW_SLOPE=_cmp_dslope_43h_tav13h_z_profile.png
+SUFFIX_NEW_SLOPE1=_cmp_dslope_8h_tav13h_z_profile.png
 SUFFIX_NEW_SLOPE_SCALE=_cmp_dslope_43h_tav13h_slopescale_z_profile.png
 
 cp $PREFIX_T/wpt$SUFFIX_OLD_T ../Figures/heatflux$SUFFIX_NEW_T
+cp $PREFIX_T/heatflux_z$SUFFIX_OLD_T ../Figures/heatflux_res_sgs$SUFFIX_NEW_T
[…]

### 2021-07-12 vis_scripts/flux_profile_fig.py

@@ -22,15 +22,15 @@ sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 #             legtitle=legtitle,
 #             zlim=[zmax,0], col=colorVal
 #            )
-palm.plot_pr(diri, run, ['momflux_z'],
-             runlabel=runlabel,  
-             teval = [tprofile,tprofile], 
-             tav = tav_pr, 
-             figsize = figsize2, 
-             legtitle=legtitle,
-             plot_legend=False,
-             zlim=[zmax,0], col=colorVal
-            )
+#palm.plot_pr(diri, run, ['momflux_z'],
+#             runlabel=runlabel,  
+#             teval = [tprofile,tprofile], 
+#             tav = tav_pr, 
+#             figsize = figsize2, 
+#             legtitle=legtitle,
+#             plot_legend=False,
+#             zlim=[zmax,0], col=colorVal
+#            )
 #palm.plot_pr(diri, run, ['wpt','momflux_z'],
 #             runlabel=runlabel,  
 #             teval = [tprofile,tprofile], 
@@ -43,3 +43,21 @@ palm.plot_pr(diri, run, ['momflux_z'],
 #             #zlim=[-25.,0.], 
 #             col=colorVal
 #            )
+#palm.plot_pr(diri, run, ['heatflux_z'],#'saltflux_z','momflux_u','momflux_v'],
+#             runlabel=runlabel,  
+#             teval = [tprofile,tprofile], 
+#             tav = tav_pr,
+#             figsize = figsize2, 
+#             legtitle=legtitle,
+#             plot_legend=False,
+#             zlim=[zmax,0], col=colorVal
+#            )
+palm.plot_pr(diri, run, ['heatflux_z'],#'saltflux_z','momflux_u','momflux_v'],
+             runlabel=runlabel,  
+             teval = [tmin+tav_pr/2,tmin+tav_pr/2], 
+             tav = tav_pr,
+             figsize = figsize2, 
+             legtitle=legtitle,
+             plot_legend=False,
+             zlim=[zmax,0], col=colorVal
+            )

### 2021-07-12 main.tex

@@
 \linenumbers
-\draftfalse
+%\draftfalse
 \journalname{JGR: Oceans}
@@
 \textbf{Plain language summary}\\
+Ice-shelf melting from below is controlled by the rate at which the ocean can transport heat vertically.
+Little is known about the small-scale mixing that carries this heat close to the ice base, where melting itself impedes mixing by forming a density barrier.
+This study uses ocean modeling at ultra-high resolution to study these mixing processes.
+It offers some insights into the relationship between ice-shelf melting and ocean temperature far from the ice base, which may help us project how fast ice will melt when ocean waters entering the cavity warm.
+This study adds to a growing body of research that indicates coarse resolution ocean models used for such projections may have to adjust how they handle ocean mixing to improve the fidelity of ice-shelf melting.
 
@@
 % Motivation - SLR
-The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet.
-The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice.
+The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet \cite{ipcc_climate_2014}.
+The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice \cite{reese_far_2018, rignot_ice-shelf_2013}.
 The Ice-shelf/Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base.
-Thus, accurate predictions of ice-shelf melting depend on capturing the turbulent dynamics of the IOBL.
+Thus, accurate predictions of ice-shelf melting depend on representing the turbulent dynamics of the IOBL.
 This representation is also critical for evaluating the sensitivity of the coupled land ice-ocean system to changes in ocean conditions.
-Of particular concern is the sensitivity of ice-shelf melting to increasing seawater temperature, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse.
+Of particular concern is the sensitivity of ice-shelf melting to increasing seawater temperature at depth, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse \cite{ruan_ice-shelf_2021, schmidtko_multidecadal_2014, purkey_unabated_2018, wahlin_pathways_2021}.
 
 % Shortcomings of ocean-model representations of IOBL
-One indication that ocean models do not capture these dynamics is that the modeled thickness of the IOBL differs significantly between ocean models and with model resolution.
-Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the buoyancy of the IOBL.
-This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is primarily driven by the buoyant flow of water freshened by ice-shelf melting.
-A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically-based, accurate coupling of ice sheets and oceans in climate models.
+One indication that ocean models do not capture turbulent dynamics is that the simulated thermal driving in the IOBL, the difference between ocean temperature and the local freezing point, and consequently the simulated melt rate differ significantly between ocean models and as resolution is varied within a model \cite{gwyther_cold_2020}.
+Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the lateral buoyancy gradient of the IOBL and often the vertical buoyancy gradient as well, which should reduce the efficiency of vertical mixing near the boundary.
+This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is driven in large part by the buoyant flow of water freshened by ice-shelf melting, overturning circulation also known as the ``ice pump'' \cite{webber_impact_2018}.
+A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically based, accurate coupling of ice sheets and oceans in climate models \cite{gwyther_cold_2020, dinniman_modeling_2016, naughten_future_2018, edwards_projected_2021}.
 
@@
 IOBLs present unique conditions in the global ocean, involving a stabilizing flux from phase change (ice-melting) and a boundary layer that is positively buoyant against a sloping boundary.
-The IOBL has been most extensively explored at small scales, laboratory experiments and Direct Numerical Simulations, with some recent numerical studies addressing larger scales \cite{mondal_ablation_2019, vreugdenhil_stratification_2019}.
-However, the melt parameterizations commonly in use today still derive from sea-ice conditions (i.e., in the absence of a slope) \cite{mcphee_dynamics_1987}.
-Thus a knowledge gap exists in bridging these dynamics across the IOBL and characterizing the structure of buoyant plumes.
+There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \cite{zonta_stably_2018}.
+The IOBL has been most extensively explored at small scales through laboratory experiments and Direct Numerical Simulations, with some recent numerical studies addressing intermediate scales \cite{mondal_ablation_2019, vreugdenhil_stratification_2019, middleton_numerical_2021}.
+However, this body of work has not yet matured to setting a new standard for ice-shelf melt parameterization in ocean models.
+The commonly-used ice-shelf melt parameterization today still derives from sea-ice conditions (i.e., in the absence of a slope) with tuning of some parameters for ice-shelf settings \cite{holland_modeling_1999, jenkins_observation_2010, mcphee_dynamics_1987}.
+Thus a knowledge gap exists in bridging IOBL dynamics across scales and characterizing the structure of buoyant plumes.
 Recently, this has been addressed through non-turbulence-resolving 2-d or 2.5-d models \cite{jenkins_simple_2016, jenkins_shear_2021, cheng_modeling_2020}.
-Notably, \citeA{jenkins_shear_2021} found a significant discrepancy between the commonly-used K-Profile Parameterization (KPP) and a higher-order turbulence closure scheme for vertical mixing in IOBL settings, suggesting that the application of KPP in ocean models may be inappropriate in ice-shelf cavities.
-There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \cite{zonta_stably_2018}.
+Notably, \citeA{jenkins_shear_2021} found that vertical mixing in IOBL settings was represented poorly by the commonly-used K-Profile Parameterization (KPP) in comparison to a higher-order turbulence closure scheme, suggesting that the application of KPP in ocean models may be inappropriate in ice-shelf cavities.
 
@@
 An effective parameterization of ice-shelf melting is likely to rest on an understanding of how turbulent mixing in the IOBL depends on stratification and shear forcing.
-We vary far-field ocean temperature and ice-shelf slope between model runs and characterize turbulent fluxes, IOBL thickness, and ice-shelf melt rates.
+We vary far-field ocean temperature and ice-shelf slope between model runs and characterize turbulent fluxes and ice-shelf melt rates.
 In this study we focus on the high-shear, low thermal driving regime.
-The target of previous LES studies has been on low-shear settings \cite{vreugdenhil_stratification_2019}.
+The target of previous LES studies has been on low-shear settings \cite{vreugdenhil_stratification_2019, middleton_numerical_2021}.
+Section \ref{meth} describes the LES model, its turbulence closure scheme, and the set-up of our simulations.
+Section \ref{results} presents the results of our simulations, with a focus on comparisons across the range of thermal driving and slope given.
+The discussion is given in two parts: Section \ref{disc:dyn} contextualizes the features of our simulated IOBL turbulence and discusses limitations of this study, and Section \ref{disc:prm} focuses on how this study informs parameterizations of ice-shelf melting and IOBL turbulence.
+We provide some closing thoughts in Section \ref{conclusion}.
 
-\section{Methods}
+\section{Methods}\label{meth}
 
@@
 
-The model enforces incompressibility through a predictor-corrector method to the pressure perturbation, $\pi^*$, at each time step.
-Details can be found in \cite{maronga_parallelized_2015}.
-The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow (imposing incompressibility), and sub-grid scale momentum flux.
+Detail on the solution of these equations can be found in \cite{maronga_parallelized_2015}.
+The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow using the pressure perturbation $\pi^*$ (imposing incompressibility), and sub-grid scale momentum flux.
 Double primes denote sub-grid fluctuations.
+All prognostic variables are considered filtered at the grid scale.
+This is typically denoted by the overbar, which we omit except for the sub-grid turbulent flux terms to emphasize that we only represent averaged effects.
 
@@
 
-The terms on the right-hand side of the heat and salt conservation equations (Equations \ref{eq:ptprog} and \ref{eq:saprog}) are advection by the resolved flow, advection by the sub-grid scale fluctuations, and the source and sink terms  $\Phi_{\theta,S}$.
+The terms on the right-hand side of the heat and salt conservation equations (Equations \ref{eq:ptprog} and \ref{eq:saprog}) are advection by the resolved flow, turbulent transport by the sub-grid scale fluctuations, and the source and sink terms  $\Phi_{\theta,S}$.
 The source and sink terms are zero in our simulations because we treat heat and salt fluxes due to melting at the boundaries through the sub-grid vertical flux term, as discussed in Section \ref{meth:tcm}.
@@
 
-The turbulence closure scheme is Anisotropic Minimum Dissipation \cite{rozema_minimum-dissipation_2015} employing the extension to scalars introduced by \citeA{abkar_minimum-dissipation_2016}.
+The turbulence closure scheme is Anisotropic Minimum Dissipation \cite<AMD;>{rozema_minimum-dissipation_2015} employing the extension to scalars introduced by \citeA{abkar_minimum-dissipation_2016}.
 We validated our implementation against the stable atmospheric boundary layer test case published in \citeA{abkar_large-eddy_2017}.
-Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (damping is discussed in Section \ref{meth:setup}.
+Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}.
 
@@
 The resolved vertical fluxes at the top layer of the model go to zero as $w$ goes to zero according to the no-flux boundary condition and the sub-grid fluxes are determined using the scheme described below in place of the AMD scheme.
-PALM uses an Arakawa C-grid such that the ice boundary ($z=0$) is located at the edge of the top cell where the vertical velocity component resides and scalars and horizontal velocity components are located at mid-depth of the top cell ($z=-\frac{1}{2}\Delta_z$).
+PALM is vertically discretized such that the ice boundary ($z=0$) is located at the edge of the top cell where the vertical velocity component resides and scalars and horizontal velocity components are located at mid-depth of the top cell ($z=-\frac{1}{2}\Delta_z$).
 We denote the interface location with subscript $b$ and the middle of the first cell below the interface with subscript $\frac{1}{2}$.
 
-Momentum fluxes are parameterized according to law of the wall following a linear stability function as in \citeA{vreugdenhil_stratification_2019}:
+Subgrid momentum fluxes are parameterized according to law of the wall following a linear stability function for stabilizing buoyancy forcing as in \citeA{vreugdenhil_stratification_2019}:
 %
@@
 \end{equation}
-The coefficients of these stability functions are chosen as in \cite{zhou_self-similar_2017} and are given in Table \ref{table:var}. The molecular flux component follows \citeA{mcphee_dynamics_1987}:
+The coefficients of these stability functions are chosen as in \citeA{zhou_self-similar_2017} and are given in Table \ref{table:var}. The molecular flux component follows \citeA{mcphee_dynamics_1987}:
 \begin{equation}
@@
 We present two sets of simulations which have a base case in common.
-The base case has low far-field thermal driving of 0.1$^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field inertial oscillations of 20 cm s\textsuperscript{-1} generated by a 0.03 Pa m\textsuperscript{-1} pressure gradient.
+The base case has low far-field thermal driving of 0.15$^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field inertial oscillations of 20 cm s\textsuperscript{-1} generated by a 0.03 Pa m\textsuperscript{-1} pressure gradient.
 These conditions were chosen to favor an energetic regime, for reasons discussed in Section \ref{disc:dyn}.
-To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.1$^{\circ}$C to 0.5$^{\circ}$C in the first set of simulations.
+To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.15$^{\circ}$C to 0.6$^{\circ}$C in the first set of simulations.
+Far-field thermal driving $\Delta \theta_\infty$ is defined as $\theta_{\infty} - \theta_f(S_{\infty})$.
 In the second set of simulations, we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.
@@
 The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h.
-By this point, the time-mean kinetic energy of the flow has reached steady-state.
-However, the turbulent intensity for all cases continues to decline, with more pronounced TKE loss at lower slopes (Figure \ref{fig:timeseries}a,d).
+By the end of our simulations, the time-mean kinetic energy of the flow has reached steady-state.
+However, the turbulent intensity for all cases continues to decline, with more pronounced turbulence kinetic energy (TKE) loss at lower slopes (Figure \ref{fig:timeseries}a,d).
 Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.
+
+We compute an effective thermal exchange coefficient that differs from that employed by the sub-grid scheme to represent the efficiency of heat exchange that may need to be represented to produce accurate melt rates in a model that does not have the vertical resolution or sophisticated turbulence closure that we employ here.
+This derived thermal exchange coefficient, $\Gamma_{T,der}$, can be computed using Equations~\ref{eq:melt_flux} and \ref{eq:melt_1} from the simulated melt rate and ocean properties at any depth rather than $z_{\frac{1}{2}}$.
+We substitute the friction velocity computed by Equation~\ref{eq:tau} with one computed using a quadratic drag law from the velocity at $z < z_{\frac{1}{2}}$ and the applied drag coefficient, consistent with modeled drag implementations.
 
@@
 
-\section{Results}
+\section{Results}\label{results}
 
@@
 We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
+Our simulations generally show resolved turbulent fluxes exceeding the subgrid turbulent fluxes, but over the last inertial period the subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
 
@@
     \end{minipage}
-    \caption{Time evolution of (a,d) domain-averaged turbulent kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
-The black curve representing the same simulation in all panels.}
+    \caption{Time evolution of (a,d) domain-averaged turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
+The black curve represents the same simulation in all panels.}
+    % Consider shading the analysis window
+    % TODO add panel labels
     \label{fig:timeseries}
@@
 (a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components.
-For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).}
+For panel (c), solid lines are in the y direction (positive north), dashed in x-direction (positive east, up-slope).}
     \label{fig:dT_profiles}
-    % change colorbar label to \theta_\infty
+    % TODO add panel labels
 \end{figure}
@@
     \label{fig:dslope_profiles}
+    % TODO add panel labels
 \end{figure}
@@
 This effect can be seen most clearly by comparing the up-slope component of the flow within several meters of the ice-ocean interface across the slope-varying simulations (Figure \ref{fig:dslope_profiles}c).
-These mean buoyancy effects increase flow velocities on the order of a few cm s\textsuperscript{-1} as slope varies from 0.01$^{\circ}$ to 1.0$^{\circ}$ (Figure \ref{fig:dslope_profiles}c).
-Flow velocities near the boundary increase on the order of 10 cm s\textsuperscript{-1} as far-field thermal driving increases from 0.1 to 0.45$^{\circ}$C at 1$^{\circ}$ slope (Figure \ref{fig:dT_profiles}c).
+These mean buoyancy effects increase flow velocities on the order of a few cm s\textsuperscript{-1} as slope varies from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:dslope_profiles}c).
+Flow velocities near the boundary increase on the order of 10 cm s\textsuperscript{-1} as far-field thermal driving increases from 0.5 to 0.6$^{\circ}$C at 1$^{\circ}$ slope (Figure \ref{fig:dT_profiles}c).
 This velocity increase is attributed to changes in the magnitude of buoyancy forcing at the boundary, related to differences in melt rates.
+The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c integrates inertial oscillations of the geostrophic velocity at 20 cm s\textsuperscript{-1}.
 
 % BL depth
-Stratification within the boundary layer increases with thermal driving (Figure \ref{fig:dT_profiles}a,b).
+Stratification within the boundary layer increases with thermal driving (Figure~\ref{fig:dT_profiles}a,b).
 Thus, the increase in melt-induced buoyancy fluxes with thermal driving dominates over the increase in shear induced by the buoyant flow.
-Conversely, stratification decreases with increasing slope, indicating that the increase in shear induced by the buoyant flow dominates over increase in melt-induced buoyancy fluxes with slope.
+Conversely, stratification decreases with increasing slope, indicating that the increase in shear induced by the buoyant flow dominates over the increase in melt-induced buoyancy fluxes with slope.
 The simulated boundary layer depth has a strong relationship with local thermal driving (i.e., the difference between IOBL temperature and the freezing point), reflecting entrainment of warm water below and setting mixing lengthscales  within the IOBL.
-Boundary layer depth is identified with the local maximum in the ratio of vertical to horizontal velocity variance (e.g., Figure S2).
+Boundary layer depth is identified with the local maximum in the ratio of vertical to horizontal velocity variance (e.g., Figure~S1).
 This definition of the IOBL can also be considered the depth to which shear originating at the boundary influences the flow.
@@
 % TKE budget, shear
-Shear production of turbulence dominates the TKE budget. The evolution of TKE ($E$) can be described by:
+Shear production of turbulence dominates the TKE budget. The evolution of TKE can be described by three source terms and dissipation:
 \begin{equation}
-    \frac{dE}{dt} = F_{shear} + F_{buoy} + F_{trans} - \textrm{diss}
+    \frac{d(\textrm{TKE})}{dt} = F_{shear} + F_{buoy} + F_{trans} - \textrm{diss}
 \end{equation}
-Figure \ref{fig:tke_budget} shows several key terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure S3 and shows similar patterns.
-Shear production ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$ m\textsuperscript{2} s\textsuperscript{-3} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5 m of the boundary (Figure \ref{fig:tke_budget}a).
+Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure S2 and shows similar patterns.
+Shear production ($F_{shear}$) ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$ m\textsuperscript{2} s\textsuperscript{-3} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5 m of the boundary (Figure \ref{fig:tke_budget}a).
 The increase in TKE throughout the boundary layer as slope increases reflects this shear-induced turbulence (Figure \ref{fig:tke_budget}a).
@@
 % TKE budget, buoyancy
-Buoyancy production of turbulence is 1 -- 2 orders of magnitude smaller than shear production, $\sim 10^{-10} \textrm{--} 10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}.
-In the sloped ice shelf, the buoyancy term can be broken into two components, the horizontal buoyancy fluxes that increase turbulence when oriented upslope and the vertical fluxes that decrease turbulence when ice is melting.
+Buoyancy production of turbulence ($F_{buoy}$) is 1 -- 2 orders of magnitude smaller than shear production, $\sim\!10^{-10} \textrm{--} 10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}.
+For a sloped ice shelf, the buoyancy term can be broken into two components, the horizontal buoyancy fluxes that increase turbulence when these fluxes are oriented upslope and the vertical buoyancy fluxes that decrease turbulence when ice is melting.
 Since our simulations only produce melting, the vertical component is always negative (dashed lines, Figure \ref{fig:tke_budget}b).
@@
 Interestingly, the time-averaged effect of a slope is destruction of turbulence near the boundary and production of turbulence near the base of the boundary layer (dotted lines, Figure \ref{fig:tke_budget}b).
-The net effect of both of the horizontal and vertical buoyancy components is the destruction of turbulence throughout the IOBL (solid lines, Figure \ref{fig:tke_budget}b), with the exception of the base of the IOBL where the horizontal buoyancy component augments entrainment.
+The net effect of both horizontal and vertical buoyancy components is the destruction of turbulence throughout the IOBL (solid lines, Figure \ref{fig:tke_budget}b), with the exception of the base of the IOBL where the horizontal buoyancy component augments entrainment.
 While these complexities are intriguing from a dynamical perspective, we do not explore them further here since the buoyancy term is not of leading-order in the TKE budget.
@@
 % TKE budget, transport
-The transport term contains two components, advection of TKE due to pressure fluctuations and advection of TKE due to turbulence.
+The transport term ($F_{trans}$) contains two components, advection of TKE due to pressure fluctuations and turbulent advection of TKE.
 The former is negligible, reaching maximum values on the order of $10^{-12}$ m\textsuperscript{2} s\textsuperscript{-3} while the latter increases turbulence at the boundary with oscillations of decreasing amplitude with distance from the boundary (Figure \ref{fig:tke_budget}c).
@@
 % TKE budget, dissipation, tendency
-Dissipation, the remaining term in the TKE budget, can be inferred from the remainder of these terms and the rate of change of TKE.
-In these simulations TKE is not in steady-state, with vertically-averaged $dE/dt$ ranging from $\sim 10^{XX} \textrm{--} 10^{XX}$ m\textsuperscript{2} s\textsuperscript{-3} in the IOBL.
-Thus, dissipation is on the same order as shear production but for many runs exceeds shear production as evidenced by declining TKE.
+Dissipation ($diss$), the remaining term in the TKE budget, can be inferred from the remainder of these terms and the rate of change of TKE.
+In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$ m\textsuperscript{2} s\textsuperscript{-3} as seen in Figure \ref{fig:timeseries}a,c.
+Dissipation in the IOBL is on the same order as shear production ($10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}), as all other terms in the TKE budget are small.
 
@@
     \end{minipage}
-    \caption{(a) Simulated turbulent kinetic energy for variable slope simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period.
+    \caption{(a) Simulated turbulence kinetic energy (TKE) for variable slope simulations averaged over the last inertial period and (b-d) TKE source terms over the same period.
 (b) Shear production.
@@
     \label{fig:tke_budget}
-    % Change x-axis label for buoyancy production terms
+    % TODO add panel labels
 \end{figure}
@@
 The structures become increasingly filamentous (i.e., near-wall streaks, e.g., \citeA{del_alamo_spectra_2003, hoyas_scaling_2006}) and coherent as slope and thus the buoyancy-driven current increase.
-Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases;  velocity fluctuations are less confined to the slope-parallel direction (Figure S2).
+Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases;  velocity fluctuations are less confined to the slope-parallel direction (Figure S3).
 % consider discussing entrainment here
@@
 Note that the colorbar scale is smaller in (e) than (f).}
-    % Add contours to a-d to show structures more clearly
+    % Consider contours to a-d to show structures more clearly
+    % TODO add panel labels
     \label{fig:cross-section}
@@
 These melt rate fluctuations correspond to fluctuations in TKE which are reflected in the friction velocity shown in Figure \ref{fig:timeseries}b.
-The dominant contribution to turbulence is shear production of TKE, which changes its distribution with depth as the mean flow profile evolves (Figure S3).
-During high-melt periods, the far-field flow is oriented up-slope and shear production of TKE is concentrated near the boundary (Figure \ref{fig:dT_profiles}c,d).
-During low-melt periods, the far-field flow is oriented down-slope and shear production of TKE is concentrated a few meters away from the boundary (Figure \ref{fig:tke_budget}b).
+The dominant contribution to turbulence is shear production of TKE, which changes its distribution with depth as the mean flow profile evolves.
+During high-melt periods, the far-field flow is oriented up-slope and shear production of TKE is concentrated near the boundary.
+During low-melt periods, the far-field flow is oriented down-slope and shear production of TKE is concentrated a few meters away from the boundary.
 
@@
 Melt rate fluctuations increase in amplitude as thermal driving increases and as slope increases, which we attribute to the increasing importance of buoyancy forcing in driving a near-boundary plume and thus determining the depth-distribution of shear.
-At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the mixed layer over a few hours (not shown).
-The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a hiatus in turbulence during the down-slope flow period.
-This can be seen in the dramatic reduction in friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b).
-Thus, in our simulations rotational effects cause intermittency in turbulence when the IOBL is sufficiently stratified.
-We discuss this intermittency further in Section \ref{disc:dyn}.
+At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the mixed layer over a few hours (Figure \ref{fig:intermittency}b).
+The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a dramatic reduction in vertical velocity fluctuations during the down-slope flow period.
+This can be seen in the time series of friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b).
+Below the mixed layer, there is periodic intermittency in turbulence interrupted by the penetration of shear-induced turbulence when the IOBL buoyantly accelerates.
+For this reason, we do not examine IOBL entrainment in this study.
+We discuss these rotational effects on turbulent intensity further in Section \ref{disc:dyn}.
 
@@
     \end{minipage}
-    \caption{Example of turbulent intermittency as seen in white regions of turbulent kinetic energy (TKE).
+    \caption{Example of turbulent intermittency as seen in white regions of turbulence kinetic energy (TKE).
 (a) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
@@
     \label{fig:intermittency}
+    % TODO add panel labels
 \end{figure}
@@
 % Melt rate sensitivity to thermal driving
-Time-averaged melt rates are roughly linear with thermal driving (Figure \ref{fig:melt_sensitivity}a).
-The derived, time-averaged thermal exchange coefficient (described in Section \ref{meth:tcm}) is fairly insensitive to thermal driving.
-The thermal exchange coefficient during the last 12 hours of the simulations is between 0.005 and 0.006 for the simulated range of thermal driving values.
-During the first 12 hours of the simulation, simulated thermal exchange coefficients are 0.008 due to weaker stratification near the interface, higher friction velocities, and greater TKE.
-The derived thermal exchange coefficient decreases somewhat in the high thermal driving cases due to pronounced periods of low melt as TKE declines with increasing stratification.
+Time-averaged melt rates depend fairly linearly on far-field thermal driving (Figure \ref{fig:melt_sensitivity}a).
+This is mostly attributable to a linear relationship between melt rate and interfacial thermal driving, as differences in friction velocity and the thermal exchange coefficient are small and do not have a systematic relationship with far-field thermal driving.
+The derived, time-averaged thermal exchange coefficient ($\Gamma_{T,der}$) on the other hand does have a weakly negative relationship with far-field thermal driving, reflecting decrease efficiency of heat exchange with increasing near-interface stratification.
+We discuss these derived thermal exchange coefficients further in Section \ref{disc:prm_gamma}.
 
@@
     \end{minipage}
-    \caption{(a) Melt rate vs.
-thermal driving.
-(b) Melt rate vs.
-slope.
-(c) Thermal exchange coefficient vs.
-far-field thermal driving for thermal driving simulations.
+    \caption{Melt rate sensitivity to (a) far-field thermal driving and (b) sine of the basal slope.
+(c,d) Key controls on the value of the thermal exchange coefficient ($\Gamma_{T,der}$) that would accurately predict melt rates given accurate measurements of velocity and temperature 2 m from the ice base.
+(c) Far-field thermal driving is inversely related to $\Gamma_{T,der}$.
 Dashed line denotes the value recommended by \citeA{jenkins_observation_2010}.
-(d) Thermal exchange coefficient vs.
-friction velocity for sloped simulations.
+The largest points correspond to the fourth and last inertial cycle with progressively smaller points for previous inertial cycles.
+(d) For variations in slope, the simulated friction velocity (solid points) is linearly related to $\Gamma_{T,der}$.
+The inferred friction velocity used to compute $\Gamma_{T,der}$ are shown with open points.
 Note the difference in y-axis limits from (c).
@@
     \label{fig:melt_sensitivity}
+    % TODO add panel labels
 \end{figure}
@@
 There is also a linear relationship between melt rate and ice-shelf basal slope, with threshold-like behavior at slopes less than 0.01$^{\circ}$.
+This linear relationship is due primarily to a linear relationship between friction velocity and melt rate while there is a smaller ($\sim\!1/3$ size) opposite effect from decreasing interfacial thermal driving with increasing slope (not shown).
 This threshold behavior in melting in the two lowest-slope cases is attributable to similar friction velocities (Figure \ref{fig:melt_sensitivity}d) arising from similar IOBL velocities and turbulence  (Figure \ref{fig:dslope_profiles}c,d).
-This behavior is discussed in more detail in Section \ref{disc:prm}.
+This behavior is discussed in more detail in Section \ref{disc:prm_sens}.
 The differences in derived thermal exchange coefficient are not pronounced as slope varies, on the order of a 10\% change as slope increases from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:melt_sensitivity}d).
-Variability in the thermal exchange coefficient with slope is largely determined by differences in friction velocity between simulations (Fig.
-\ref{fig:melt_sensitivity}d) while there is a smaller ($\sim$20\%) opposite effect from decreasing interfacial thermal driving with increasing slope (not shown).
-These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes (Figure \ref{fig:dslope_profiles}c,d).
+These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes.
+
+Vertical scalar fluxes are shown in Figure \ref{fig:heatflux_profiles}a,b.
+The vertical heat flux has a maximum at the ice-ocean interface and decreases throughout the IOBL, with small values below the pycnocline.
+Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure S4).
+The vertical salt flux profiles are shown in Figure S5 and have a very similar shape to the vertical heat flux profiles.
 
@@
 \begin{equation}
-    d_E = (2 K_e)^{1/2} |f_3|^{-1/2}
+    d_E = (2 K_b)^{1/2} |f_3|^{-1/2}
 \end{equation}
@@
 \end{equation}
-$K_e$ profiles are shown in Figure S4.
+$K_b$ profiles are shown in Figure S6.
 
@@
 The linear scaling of melt rate with thermal driving suggests a linear scaling of heat flux profiles with thermal driving.
-We find that this scaling largely collapses the four thermal driving profiles, with some deviation from this shape for the run that experiences intermittent turbulence (Figure \ref{fig:heatflux_profiles}c).
+We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (Figure \ref{fig:timeseries}c, \ref{fig:heatflux_profiles}c,  pink curves).
 The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:heatflux_profiles}c).
-Scalar fluxes decline near the boundary for the 1$^{\circ}$ slope cases, a feature that we discuss further in Section \ref{disc:prm}.
-Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure S5).
-The vertical salt flux profiles are shown in Figure S6 and have a very similar shape to the vertical heat flux profiles.
+Scalar fluxes decline near the boundary for the 1$^{\circ}$ slope cases, a feature that we discuss further in Section \ref{disc:prm_vmix}.
 
@@
 The horizontal axis limits vary between panels.}
-    %Consider replacing (d) with scaling by sin\alpha
-    %Change scaled vertical axis limits to 0-40
-    %Change all to centered on 43h and averaged 13h
     \label{fig:heatflux_profiles}
+    % TODO add panel labels
 \end{figure}
@@
 % Scaling heat flux profiles with slope
-Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($\sin^{1/4}\alpha$, Figure \ref{fig:heatflux_profiles}d).
+Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($(\sin\alpha)^{1/4}$, Figure \ref{fig:heatflux_profiles}d).
+There is strong agreement between the scaled vertical heat flux profiles at different slopes, though the threshold behavior at low slopes noted in melt rates is replicated here.
 We also find that the Ekman depth is a poor predictor of boundary layer depth.
 This may be due to the depth-variable shear induced by buoyancy which is not reflected in the depth-mean IOBL bulk viscosity used to compute the Ekman depth.
-%It is interesting that the boundary layer depths of the thermal driving cases at 1$^{\circ}$ slope scale similarly with the Ekman depth despite the differences in buoyancy of the IOBL (Figure \ref{fig:heatflux_profiles}c).
-It suggests that the bulk viscosity in the IOBL, used to compute the Ekman depth, is a poor predictor of entrainment as slope varies.
+Our study was not designed to evaluate IOBL entrainment, which would be better explored by varying the level of background stratification, so we devote no further attention to it here.
+We discuss scaling of vertical fluxes and the possibility of their parameterization in Section \ref{disc:prm_vmix}.
 
 % momentum flux profiles
-By looking at the variation of momentum flux with depth shown in Figure \ref{fig:momflux_profiles}, we can examine the relative contributions of interfacial drag and buoyant acceleration of the IOBL to the velocity profiles shown in Figure \ref{fig:dT_profiles}c,e and \ref{fig:dslope_profiles}c.
+By looking at the variation of momentum flux with depth shown in Figure \ref{fig:momflux_profiles}, we can examine the relative contributions of interfacial drag and buoyant acceleration of the IOBL to the velocity profiles shown in Figure \ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c.
 Since the mean velocity is oriented both upslope (+$u$) and cross-slope (+$v$), positive $\overline{u'w'}$ and $\overline{v'w'}$ close to the interface indicate slowing of the current due to drag whereas negative $\overline{u'w'}$ and $\overline{v'w'}$ a few m below the interface through much of the boundary layer indicate buoyant acceleration of the IOBL.
@@
     \label{fig:momflux_profiles}
-    % change x-axis labels to \overline{u_i'w'}
+    % TODO add panel labels
 \end{figure}
@@
 
-\subsection{IOBL turbulence} \label{disc:dyn}
+\subsection{Understanding IOBL turbulence and the limitations of an LES approach} \label{disc:dyn}
 
@@
 Excess dissipation could arise either through the sub-grid scheme or the model numerics.
-We found a rapid loss of turbulence in PALM simulations when a dynamic Smagorinky turbulence closure was used, which is consistent with previous studies on the limited applicability of the standard Smagorinsky turbulence closure to strongly stratified flows due to the strong anisotropy of these flows \cite{flores_analysis_2011, jimenez_large-eddy_2005}.
-This motivated our adoption of the AMD turbulence closure scheme.
-However, we found that the buoyancy term suggested by \citeA{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
-We neglected this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019}.
+We found a rapid loss of turbulence in PALM simulations when a dynamic Smagorinky turbulence closure was used, which is consistent with previous studies on the limited applicability of the standard Smagorinsky turbulence closure to strongly stratified flows due to the strong anisotropy of those flows \cite{flores_analysis_2011, jimenez_large-eddy_2005}.
+This motivated our adoption of the AMD turbulence closure scheme \cite{abkar_minimum-dissipation_2016}.
+However, we found that the buoyancy term added to this scheme by \citeA{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
+We removed this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019}.
 
@@
 This is consistent with our finding that the temporal variability in shear over inertial oscillations provides a sufficient perturbation to reinitiate turbulence.
-Our simulations approach a gradient Richardson number of 0.25, which is considered to be the approximate value at which turbulence neither grows nor decays \cite{rohr_growth_1988, holt_numerical_1992}.
+Our simulations approach a gradient Richardson number ($Ri_g$) of 0.25, which is considered to be the approximate value at which turbulence neither grows nor decays \cite{rohr_growth_1988, holt_numerical_1992}.
 Thus, fluctuations in TKE are plausible at the simulated levels of stratification and shear.
@@
 
-In this study, we did not attempt to reproduce observed conditions at a particular ice-shelf location due to the difficulties of matching unobserved far-field forcings and the exclusion of tides from our simulations for ease of interpretation.
-Nonetheless, it appears as though well-mixed boundary layers are simulated for a narrower range of conditions in simulations than in observations.
+In this study, we did not attempt to reproduce observed conditions at a particular ice-shelf location due to the difficulties of matching unobserved far-field forcings and the exclusion of tides from our simulations.
+Nonetheless, it appears as though well-mixed boundary layers are seen for a narrower range of conditions in simulations than in observations.
 The background flow chosen in these simulations is quite strong at 20 cm s\textsuperscript{-1} and thermal driving is relatively low such that we expected to produce a well-mixed boundary layer as is observed in melting regions of the Filchner-Ronne Ice Shelf \cite{nicholls_oceanographic_2001}.
-However, observations to date are insufficient to provide reliable predictions of IOBL stratification \cite{malyarenko_synthesis_2020}.
-The observational picture is quite nuanced with a range of stratification observed even within one ice shelf (e.g., \citeA{hattermann_two_2012}).
-
-Our simulations are certainly missing some sources of TKE present in ice-shelf cavities which could modify IOBL structure and mixing efficiency.
-These simulations did not include tides, which provide perturbations to the mean velocity that enhance melt rates and entrainment, especially at Filchner-Ronne \cite{makinson_modeling_1999, makinson_influence_2011, mueller_tidal_2018}.
-While internal gravity waves arise in LES, they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \cite{gwyther_cold_2020}.
-Enhanced drag at the ice-shelf base could increase shear production of TKE; however under strong stratification, surface roughness elements may suppress turbulence rather than enhance it \cite{ohya_wind-tunnel_2001}.
+However, observations to date are insufficient to fully characterize the regime space for a well-mixed IOBL \cite{malyarenko_synthesis_2020}.
+The observational picture is quite nuanced with a range of stratification observed even within one ice shelf \cite{hattermann_two_2012}.
 
@@
 
-\subsection{Evaluating melt sensitivity and turbulent flux representations in ocean models}\label{disc:prm}
+Our simulations are certainly missing some sources of TKE present in ice-shelf cavities which could modify IOBL structure and mixing efficiency.
+These simulations did not include tides, which provide perturbations to the mean velocity that enhance melt rates and entrainment, especially at Filchner-Ronne \cite{makinson_modeling_1999, makinson_influence_2011, mueller_tidal_2018}.
+While internal gravity waves arise in LES, they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \cite{gwyther_cold_2020, robertson_tidally_2013, padman_ocean_2018, mueller_impact_2012}.
+Enhanced drag at the ice-shelf base could increase shear production of TKE; however under strong stratification, surface roughness elements may suppress turbulence rather than enhance it \cite{ohya_wind-tunnel_2001}.
 
-\subsubsection{Insights into melt sensitivity to ocean conditions}
+\subsection{Representing the IOBL and projecting ice-shelf melt rates with ocean models}\label{disc:prm}
+
+\subsubsection{Insights into melt rate sensitivity to ocean conditions}\label{disc:prm_sens}
 
 % Argument for validity of findings in non-steady conditions
-The decline in IOBL turbulence discussed in Section \ref{disc:dyn} results in declining melt rates, making it difficult to evaluate the relationship between melting and far-field conditions at steady state, which would provide the most direct path to assessing melt rate sensitivity to ocean conditions.
+The decline in IOBL turbulence discussed in Section \ref{disc:dyn} results in declining melt rates.
+Thus, we could not evaluate the relationship between melting and far-field conditions at steady state, which would have offered the most direct path to assessing melt rate sensitivity to ocean conditions.
 As discussed in \citeA{jenkins_simple_2016}, achieving steady-state solutions in simulations may require prescribing large-scale gradients in temperature.
@@
 However, we believe that our transient solutions do provide some indications of how melt rates and boundary layer properties depend on ocean temperature and ice-shelf slopes.
-One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure SXX).
+One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure S7).
 On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}e-f).
@@
 % sensitivity of melt rate to temperature
-The linear relationship we find between far-field ocean temperature and melt rates is consistent with some previous studies \cite{rignot_rapid_2002}.
-It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies an increase in far-field thermal driving.
-The quadratic relationship between melt rate and thermal driving in \citeA{holland_response_2008} is a function of both a linear relationship between the local, far-field thermal driving and melt rate and a linear relationship between far-field thermal driving and friction velocity.
-The former relationship is addressed by this study and agrees with \citeA{holland_response_2008}; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity is unchanged.
-In contrast, in sea ice settings this sensitivity was found to be significantly smaller with an exponent of 0.38 \cite{ramudu_large_2018}.
+The linear relationship we find between local, far-field ocean temperature and melt rates is consistent with some previous studies in ice-shelf settings \cite{rignot_rapid_2002, holland_response_2008, vreugdenhil_stratification_2019}.
+A slightly higher exponent of $4/3$ is reported for the local, near-field thermal driving in the regime in which convective rather than shear instabilities control melting \cite{kerr_dissolution_2015}.
+In contrast, in sea-ice settings this sensitivity of melt rates to local thermal driving was found to be significantly smaller with an exponent of 0.38 \cite{ramudu_large_2018}.
+It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies a widespread increase in thermal driving (i.e., changes to the water masses entering the ice-shelf cavity).
+The relationship between melt rate and distant thermal driving is a function of both the relationship between the local thermal driving and melt rate and the relationship between distant thermal driving and friction velocity \cite{holland_response_2008}.
+The former relationship is addressed by this study; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity is unchanged.
+We note that the often cited quadratic relationship between thermal driving and melting pertains to this distant thermal driving  \cite{holland_response_2008}; studies generally find this exponent to be between 1.5 and 2 \cite{little_how_2009, jourdain_ocean_2017, favier_assessment_2019}.
 
 To some extent, this linear relationship between far-field thermal driving and melt rate is embedded in the parameterization of heat fluxes employed at the ice base in these simulations.
-Specifically, the melt rate is prescribed to have a linear dependence on the thermal driving using the temperature in the first model layer, see Equation \ref{eq:melt_flux}.
-However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL can mediate this relationship between \textit{far-field} temperature and melt rates, and yet the dependence from these simulations is still fairly linear.
+Specifically, the melt rate is prescribed to have a linear dependence on the thermal driving using the temperature in the first model layer, see Equation~\ref{eq:melt_flux}.
+However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL all mediate this relationship between \textit{far-field} temperature and melt rates, and yet the dependence from these simulations is still fairly linear.
 
 % sensitivity of melt rate to slope
-The finding that slopes as low as 0.5$^{\circ}$ significantly influence melt rates is not unexpected from a consideration of momentum balance, but may be an underappreciated aspect of IOBL simulation in Antarctic ice-shelf settings.
-The linear relationship between ice-shelf slope and melt rate suggests a stronger dependence at very low slopes than that found by \cite{mondal_ablation_2019} using Direct Numerical Simulations at higher slopes ($m \propto \sin^{2/3}\alpha$).
-Further investigation would be needed beyond the small number of simulations presented here to diagnose this discrepancy.
+The relationship between melt rate and ice-shelf basal slope ($m \propto (\sin\alpha)^{n}$) combines two effects: the effect of ice-shelf slope on the IOBL's mean velocity profile and the effect of ice-shelf slope on IOBL turbulence.
+In the three-equation parameterization of ice-shelf melting, the former has the strongest effect on the friction velocity, derived from the mean flow velocity at a given depth; whereas the latter figures in the value of the scalar exchange coefficients, with higher values indicating more efficient turbulent transport.
+We return to the implications of our study for exchange coefficients in Section \ref{disc:prm_gamma}.
+As noted previously in this section, while our simulations capture some of this IOBL acceleration, they do not reach a steady-state mean velocity profile.
+Thus, we cannot fully assess the the effect of ice-shelf slope on the IOBL's mean velocity profile.
+This effect is addressed by \citeA{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citeA{little_how_2009} with $n=0.94$ for the range of slopes considered here.
+Our finding that $n=1$ may be applicable to the shear-dominated regime, in contrast to the sensitivity of $n=2/3$ found in the convection-dominated regime at higher slopes than those simulated here (5$^{\circ}$ -- 90$^{\circ}$) \cite{mondal_ablation_2019, mcconnochie_dissolution_2018}.
+However, we emphasize that further investigation is needed beyond the small number of simulations presented here to validate our results.
 
 % sensitivity of melt rate to slope, at very low slopes
-The threshold-like behavior in melt rates at very low slopes is not predicted by geostrophic balance between Coriolis and buoyancy forcing, which dictates a linear relationship between $\sin\alpha$ and IOBL velocity.
-This threshold behavior could be produced if any additional buoyant acceleration produced by the small increase in slope from 0.01$^{\circ}$ to 0.1$^{\circ}$ increases dissipation, resulting in a negative feedback on IOBL turbulence.
+The threshold-like behavior in melt rates at very low slopes is not predicted by geostrophic balance between Coriolis and buoyancy forcing, which dictates a linear relationship between $\sin\alpha$ and IOBL velocity \cite{jenkins_simple_2016}, nor the scaling analysis of \citeA{magorrian_turbulent_2016}.
+This threshold behavior could be produced if any additional buoyant acceleration produced by the small increase in slope from 0.01$^{\circ}$ to 0.1$^{\circ}$ increases both shear and dissipation, resulting in a negative feedback on IOBL turbulence.
+This is not evident in our simulations, which do not show significant differences in TKE budgets between the two runs (Figure \ref{fig:tke_budget}).
 From a dynamical perspective, this may be an interesting target for more highly resolved LES in the near-boundary region.
@@
 
-\subsubsection{Thermal exchange coefficient}
+\subsubsection{Toward non-constant exchange coefficients in melt parameterization}\label{disc:prm_gamma}
 
 % Methodology for evaluating thermal exchange coefficient
-The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.25m below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties on the order of 1 m below the ice-ocean interface.
-Thus, we compute a thermal exchange coefficient using ocean properties 2 m below the ice-ocean interface.
-We substitute the friction velocity computed by Equation \ref{eq:tau} with one computed using a quadratic drag law from the velocity at 2 m and the applied drag coefficient, consistent with modeled drag implementations.
-This approach allows the closest comparison between the thermal exchange coefficient indicated by these simulations and that currently parameterized in ocean models.
+The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.25m below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties meters to tens of m below the ice-ocean interface.
+To demonstrate the implications of this study for modeling endeavors, we computed the thermal exchange coefficient that yields the simulated melt rate using ocean properties (temperature and velocity) 2 m below the ice-ocean interface.
+This depth was chosen to capture the faster portions of IOBL flow, representing a best-case scenario for high resolution ocean models, though this depth choice is somewhat arbitrary.
 
 % discussion of low thermal exchange coeff in all runs
-The thermal exchange coefficients used in these simulations are less than the value of 0.011 derived from observations \cite{jenkins_observation_2010}.
+These derived thermal exchange coefficients are shown in Figure~\ref{fig:melt_sensitivity}c,d.
+The derived thermal exchange coefficients are all less than the value of 0.011 derived from observations \cite{jenkins_observation_2010}.
 There are two main factors that contribute to this result.
 The first is the choice of the parameterization of fluxes at the ice-ocean interface (i.e., over sub-meter scales).
-We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov lengthscale.
-We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \cite{monin_basic_1954}, the work of McPhee \cite{mcphee_air-ice-ocean_2008} and the depth-scaling of scalar fluxes in a more highly resolved sub-ice LES \cite{vreugdenhil_stratification_2019}.
-However, we acknowledge that more validation of these parameterizations is needed.
-The second contributing factor is declining simulated TKE, which results in a $\sim$50\% reduction of thermal exchange coefficients over the coarse of these simulations.
+We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov lengthscale (Equation~\ref{eq:Kh}).
+We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \cite{monin_basic_1954, mcphee_air-ice-ocean_2008}, and the depth-scaling of scalar fluxes in a more highly resolved sub-ice LES \cite{vreugdenhil_stratification_2019}.
+Consequently, that study also found that thermal exchange coefficients were less than the \citeA{jenkins_observation_2010} value for all but the lowest thermal driving case.
+However, we acknowledge that more validation of the sub-grid boundary flux parameterizations is needed.
+The second contributing factor is declining simulated TKE, which reduces thermal exchange coefficients over the course of these simulations (Figure \ref{fig:melt_sensitivity}c).
 
 % thermal exchange coeff, thermal driving
-Our results also suggest a modest decline in the thermal exchange coefficient at higher thermal driving, which may lead to a sub-linear relationship between thermal driving and melt rate at higher thermal driving values.
-Due to the limitations of our LES modeling discussed in Section \ref{disc:dyn}, we cannot recommend under what range of thermal driving values a reduced thermal exchange coefficient may be appropriate.
+Our results also suggest a modest decline in the thermal exchange coefficient at higher thermal driving.
+This may lead to a sub-linear relationship between thermal driving and melt rate at higher thermal driving values, though this not evident in our simulations.
+The decline in exchange coefficient with thermal driving agrees with \citeA{vreugdenhil_stratification_2019}, though their sensitivity is greater than that seen in this study (their Figure 8).
+As shown in Figure \ref{fig:melt_sensitivity}c, this relationship holds during all inertial periods, with the exception of the highest thermal driving case at the last inertial period.
+This high derived thermal exchange coefficient corresponds to the interval of anomalously high TKE shown in Figure \ref{fig:intermittency}b.
+Due to the limitations of our LES modeling discussed in Section \ref{disc:dyn}, we cannot recommend a best fit relationship between thermal exchange coefficient and thermal driving.
 Given the climatic importance of accurately simulating high thermal driving regimes associated with dynamic ice-shelf thinning, this may be a fruitful avenue for future work.
@@
 % thermal exchange coeff, slope
-The relationship between the thermal exchange coefficient and slope can be reduced to a linear relationship between thermal exchange coefficient and friction velocity.
-Our simulations are too few to evaluate whether a similar relationship holds when the source of friction velocity changes is the background flow rather than the slope.
-LES of sea ice melting does support this linear relationship between thermal exchange coefficient and friction velocity XX \cite{ramudu_large_2018}.
-In any case, the changes in the thermal exchange coefficient with slope were small, only 10\% between 0$^{\circ}$ and XX$^{\circ}$ cases.
-This suggests that, if a coarse-resolution simulation predicts friction velocity accurately, a melt parameterization with a constant thermal exchange coefficient may be adequate in Antarctic ice-shelf settings.
-Thus, the burden of melt projection accuracy may fall more heavily on parameterizing or resolving buoyant flow than on improving the slope-dependence in the parameterization of scalar fluxes (i.e., improving Equation \ref{eq:melt_flux}).
+We find a linear relationship between the derived thermal exchange coefficient, indicating that thermal exchange is more efficient at higher slopes.
+We note that this relationship also holds for the derived friction velocity from a quadratic drag law, which is greater due to the neglect of stratification effects (Figure \ref{fig:melt_sensitivity}d).
+This enhanced turbulent efficiency is due to enhanced shear instabilities, and is reflected in turbulent diffusivities parameterized by the AMD scheme.
+Much greater variability in turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure S4).
 
-\subsubsection{Depth-dependence of turbulent fluxes}
+The changes in the thermal exchange coefficient with slope were small, from 0.0045 to 0.007 between 0.1$^{\circ}$ and 1$^{\circ}$ cases.
+For a coarse-resolution simulation, we anticipate that the failure to capture this slope sensitivity will not be a leading source of error in melt projections.
+Reproducing an accurate friction velocity is likely of a greater concern.
+Thus, the burden of melt projection accuracy may fall more heavily on parameterizing or resolving buoyant flow than on improving the slope dependence in the parameterization of scalar fluxes (i.e., improving Equation~\ref{eq:melt_flux}).
+
+These simulations do not reveal whether a similar, linear relationship between friction velocity and thermal exchange coefficient holds when the background flow is varied rather than the slope.
+LES of sea ice melting, for which there is no slope, suggests a sublinear relationship between thermal exchange coefficient and friction velocity ($\Gamma_T \propto u_*^{0.5}, \overline{w^\prime \theta^\prime} \propto u_*^{1.5}$, \citeA{ramudu_large_2018}).
+More studies will be required to determine this scaling.
+
+\subsubsection{Toward a vertical mixing scheme for the IOBL}\label{disc:prm_vmix}
 
@@
 There is reason to believe that improving ice-shelf basal melt projections using ocean models will require not only an accurate melt parameterization but also an improved vertical mixing scheme.
-\citeA{jenkins_shear_2021} demonstrated significantly different IOBL characteristics when the K-profile Parameterization (KPP) was used in contrast to a low- or high-order turbulence closure scheme.
-The bulk viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (his Figure 3).
+\citeA{jenkins_shear_2021} demonstrated significantly different IOBL characteristics when KPP is the turbulence closure scheme in contrast to a low- or high-order scheme.
+The eddy viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (his Figure 3).
 Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or modified KPP scheme in sub-ice settings.
@@
 We find that this buoyant flow is concentrated in the uppermost 10 m, with peak velocities as close as 3 m from the interface.
-This flow is unlikely to be resolved by most ocean models, which have typical vertical resolutions near the interface of 10s m though some model configurations are reaching $\sim$1 m resolutions \cite{gwyther_cold_2020}.
-This then raises important questions about the parameterization of ice-ocean interface scalar and momentum fluxes.
+This flow is unlikely to be resolved by most ocean models, which have typical vertical resolutions near the interface of 10s m though some model configurations are reaching $\sim\!$1 m resolutions \cite{gwyther_cold_2020}.
+This then raises additional considerations for the parameterization of ice-ocean interface scalar and momentum fluxes.
 If the buoyancy-driven boundary current is unresolved in most coarse-resolution ocean models, then the friction velocity as computed from a quadratic drag law and the velocity at the first grid cell is likely to underestimate the true friction velocity.
-For instance, in our simulations a friction velocity computed from the far-field velocity is $\sim$XX\% greater than the interfacial friction velocity.
-Thus, more accurate melt rate projections may result prescribe a depth-dependent parameterization of vertical scalar and momentum fluxes to provide some sensitivity of melt rates to model resolution.
+For instance, a simulation that lacks this buoyancy-induced current may look more like our negligible (0.01$^{\circ}$) slope simulations than those with a slope, and consequently underestimate melt rates.
+Thus, more accurate melt rate projections may result from employing a depth-dependent parameterization of vertical scalar and momentum fluxes to provide some sensitivity of melt rates to model resolution.
 
 % scalar flux profiles
-Our depth-dependent shape function for scalar fluxes agrees with the turbulent scalar flux parameterization of \citeA{mcphee_dynamics_1987}, which features a linear increase from 0 at the boundary layer depth to the flux at the surface.
-The simulations with slopes of 1$^{\circ}$ diverge from this linear behavior within a few m from the boundary.
+Our simulated depth-dependent shape function for vertical scalar fluxes agrees with the shape of the turbulent scalar flux parameterization of \citeA{mcphee_dynamics_1987} within the first $\sim\!$5 Ekman depths, which features a linear decrease in vertical fluxes with distance from the boundary within the IOBL.
+The low thermal-driving simulations with slopes of 1$^{\circ}$ diverge from this linear behavior within a few m from the boundary.
 We attribute this to boundary effects that reduce TKE and bulk diffusivity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \cite{monin_basic_1954}.
-This shape function for scalar fluxes through the IOBL should be explored under a broader range of conditions to determine whether this linear scaling is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer.
-It's worth noting that any implementation of these depth-dependent scalar fluxes necessitates an inequality between the vertical heat and salt fluxes from the top model grid cell and the heat and salt fluxes associated with melting.
+Since these differences in bulk diffusivity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes.
+This scaling for IOBL fluxes should be explored under a broader range of conditions to determine whether it is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer.
+
+A few complexities are immediately apparent in pursuing this path toward vertical scalar flux parameterization.
+One is that a functional form for the eddy diffusivity is also needed to compute the Ekman depth.
+Another is that any implementation of these depth-dependent scalar fluxes necessitates an inequality between the vertical heat and salt fluxes from the top model grid cell and the heat and salt fluxes associated with melting.
 Thus, the closure of those budgets will likely involve horizontal scalar fluxes as well.
 
-% scalar flux profiles vs. slope - does not exist
-Assuming one's vertical mixing parameterization accurately predicts the bulk viscosity of the IOBL, the Ekman depth scaling is a moderately strong predictor for IOBL depth as the thermal driving changes but a weak predictor for IOBL depth as slope changes.
-Given the presence of intermittency in our 1$^{\circ}$ slope simulations and relatively small differences in IOBL depth among our simulations, further work is needed to understand entrainment processes for the IOBL so that a depth-dependent shape function for scalar and momentum fluxes can be established.
-
 A depth-dependent function for momentum is also necessary in ice-shelf settings given that strong stratification causes momentum fluxes to significantly deviate from the quadratic drag function typically employed in ocean models.
-Even in the absence of ice-shelf slope, the near-interface stratification significantly decreases drag \cite{garcia-villalba_turbulence_2011, mcphee_revisiting_2008}.
+Near-interface stratification significantly decreases drag \cite{garcia-villalba_turbulence_2011, mcphee_revisiting_2008}.
+Representing this reduction in drag through the drag coefficient necessarily removes the melt-rate dependence of drag through stratification.
 The addition of an ice-shelf slope to ocean models that do not fully resolve a buoyant plume further complicates the parameterization of momentum fluxes at the ice-ocean interface.
 A depth-dependent shape function for momentum fluxes which may prescribe negative (downward) momentum fluxes at the top grid cell below ice shelves for typical ocean model resolutions (see Figure \ref{fig:momflux_profiles} at, e.g., 5 m depth).
-In other words, the momentum boundary condition may need to accelerate the flow at the boundary (at least in the up-slope direction) to produce more accurate shear-driven mixing in the resolved portion of the domain when the buoyant plume is unresolved.
+In other words, when the buoyant plume is unresolved, the momentum boundary condition may need to accelerate the flow at the boundary (at least in the up-slope direction) to produce more accurate shear-driven mixing in the resolved portion of the domain.
 
-\section{Conclusion}
+\section{Conclusion}\label{conclusion}
+
+In this study we presented a small parameter study of IOBL turbulence as captured by an LES model and chiefly explored the sensitivity of ice-shelf melting to ocean temperature and ice-shelf basal slope.
+To our knowledge, this is the first study to explore turbulent effects of low slopes on ice melting at scales spanning 10s m from the ice base, allowing for IOBL development.
+These vertical scales allow us to examine the depth-dependence of vertical turbulent fluxes, a key component for the development and validation of vertical mixing parameterizations in ice-shelf settings.
+Building on \citeA{jenkins_shear_2021}, our results suggest an improvement on the standard KPP vertical mixing scheme is needed, but a larger simulation campaign and field validation effort would be required to place such a scheme on strong footing.
+
+The thermal exchange coefficient is a key parameter that determines the sensitivity of ice-shelf melting to changing ocean conditions in ocean models.
+While a constant value is not theoretically supported, it remains the standard choice due to a lack of consensus regarding the appropriate scaling.
+We concur with a previous study that the thermal exchange coefficient is dependent on thermal driving such that melt rates are less sensitive to changes in ocean temperature \cite{vreugdenhil_stratification_2019}.
+We also suggest that the thermal exchange coefficient should be enhanced at higher slopes to account for shear instabilities that are unresolved by coarse-resolution ocean models, with the caveat that our simulations did not reach steady-state.
+Ultimately, we acknowledge that there is currently no universal guidance for parameterizing sub-grid scalar and momentum fluxes near the ice base for ocean models, each of which capture IOBL flow differently depending on resolution, vertical coordinate, numerical representations of the pressure gradient, and likely other aspects of the implementation \cite{gwyther_cold_2020}.
+Thus, progress toward accurate ice-shelf melt projections will require not only the theoretical advances in understanding melt rate sensitivity but also advances in numerical modeling to bring resolution- (scale-) awareness to melt parameterization.
 

### 2021-07-12 vis_scripts/melt_diagnostics.py
Script to diagnose melt rate

@@ -1,0 +1,38 @@
+# -*- coding: utf-8 -*-
+"""
+Timeseries figure
+
+"""
+
+from extract_var_palm import load_data,extract_var
+import sys
+import plot_palm_mod as palm
+import numpy as np
+from plot_param_palm import figsize3
+#from cmp_thermal_driving_slope1 import *
+from cmp_slope_hidT import *
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+
+palm.plot_tseries(diri, run, ['thermal_driving_i'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax])
+palm.plot_tseries_cross(diri, run, runlabel, 
+                        plotvar = ['thermal_driving_i','melt'], 
+                        data_type = ['ts','ts'],
+                        tav=tav_ts, teval=[tprofile,tprofile],
+                        plot_legend=False, legtitle = legtitle,
+                        figsize = figsize2, plot_cycles=True, 
+                        col = colorVal, overwrite=True)
+palm.plot_tseries_cross(diri, run, runlabel, 
+                        plotvar = ['u*','melt'], 
+                        data_type = ['ts','ts'],
+                        tav=tav_ts, teval=[tprofile,tprofile],
+                        plot_legend=False, legtitle = legtitle,
+                        figsize = figsize2, plot_cycles=True, 
+                        col = colorVal, overwrite=True)
+palm.plot_tseries_cross(diri, run, runlabel, 
+                        plotvar = ['gamma_T','melt'], 
+                        data_type = ['ts','ts'],
+                        tav=tav_ts, teval=[tprofile,tprofile],
+                        plot_legend=False, legtitle = legtitle,
+                        figsize = figsize2, plot_cycles=True, 
+                        col = colorVal, overwrite=True)

### 2021-07-12 main.tex
Updates from Overleaf

@@
 We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
-Our simulations generally show resolved turbulent fluxes exceeding the subgrid turbulent fluxes, but over the last inertial period the subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
+Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
 

### 2021-07-14 vis_scripts/cp_hovmoller_fig.sh
Update vis scripts for hovmoller contour

@@ -1,9 +1,10 @@
-PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dpdy_021/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
-PREFIX_SLOPE=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dT_020/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
-SUFFIX_OLD_T=_dT0.4_tlim2-50_42zmax_hovmoller.png
+#PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dpdy_021/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
+PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dT_020/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
+PREFIX_SLOPE=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_alpha_surface_006/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
+SUFFIX_OLD_T=_dT0.4_tlim2-50_42zmax_contour_diss_hovmoller.png
 SUFFIX_NEW_T=_hovmoller.png
-SUFFIX_OLD_SLOPE=$SUFFIX_OLD_T
-SUFFIX_NEW_SLOPE=$SUFFIX_NEW_T
+SUFFIX_OLD_SLOPE=_slope0.50_tlim2-50_42zmax_contour_diss_hovmoller.png
+SUFFIX_NEW_SLOPE=_hovmoller.png
 
-cp $PREFIX_T/e_res$SUFFIX_OLD_T ../Figures/e_dT01$SUFFIX_NEW_T
-cp $PREFIX_SLOPE/e_res$SUFFIX_OLD_SLOPE ../Figures/e_dt06$SUFFIX_NEW_SLOPE
+cp $PREFIX_T/e_res$SUFFIX_OLD_T ../Figures/dT4/e$SUFFIX_NEW_T
+cp $PREFIX_SLOPE/e_res$SUFFIX_OLD_SLOPE ../Figures/dslope2/e$SUFFIX_NEW_SLOPE

### 2021-07-14 vis_scripts/extract_var_palm.py

@@ -68,7 +68,7 @@ def extract_var(data,var_name,data_type='pr',ops=[],
                 yval=[9999.,9999.],zval=[9999.,9999.],
                 tunits = 'hr', tav = 0., 
                 varaxes = ['t'], p0 = 10., filedir=''):
-    print('extract_var',var_name,data_type,slice_obj)
+    #print('extract_var',var_name,data_type,slice_obj)
     if data_type == 'pr':
         tav_native = 1.
     else:
@@ -307,7 +307,9 @@ def derived_var(data,varname,slice_obj_input,z_offset = 0.,f = gsw.f(-70.),filed
             var1 = np.divide(w2,u2) + np.divide(w2,v2) 
     
     elif varname == 'diss':
-        var1 = np.add(0,1)
+        dedt,_ = extract_var(data,'dEdt',data_type=data_type)
+        Fshear,_ = extract_var(data,'Fshear',data_type=data_type)
+        var1 = np.subtract(Fshear,dedt)
     
     elif varname == 'zE':
         #var1 = data.variables['zu'][slice_obj[0]]
@@ -318,9 +320,9 @@ def derived_var(data,varname,slice_obj_input,z_offset = 0.,f = gsw.f(-70.),filed
         #var1 = np.divide(var1,dE)
 
     elif varname == 'dEdt':
-        var1 = data.variables['e'][:]
-        dt = data.variables['time'][1:] - data.variables['time'][0:-1]
-        de = data.variables['e'][1:,:] - data.variables['e'][0:-1,:]
+        var1 = data.variables['e*'][:] 
+        dt = data.variables['time'][1:] - data.variables['time'][:-1]
+        de = data.variables['e*'][1:,:] - data.variables['e*'][:-1,:]
         for idx,i in enumerate(dt):
            var1[idx+1,:] = de[idx]/i
     
@@ -676,7 +678,7 @@ def derived_var(data,varname,slice_obj_input,z_offset = 0.,f = gsw.f(-70.),filed
 def slice_var(data,varname,data_type='pr',tunits='hr',
               tval=[-9999,-9999],xval=[9999,9999],
               yval=[9999,9999],zval=[9999,9999],grid='sc'): 
-    print('slice_var: ',varname,data_type)
+    #print('slice_var: ',varname,data_type)
     if varname in dervar:
         varname = source_var[varlist.index(varname)]
         #print('slice_var source_var: ',varname)

### 2021-07-14 vis_scripts/hovmoller_fig.py

@@ -15,14 +15,20 @@ from cmp_thermal_driving_slope1 import *
 
 sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 
-#palm.plot_hovmoller(diri,run,['e*'],
-#                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, clim=[-7.5,-4.25], 
+palm.plot_hovmoller(diri,run,['e*'],
+                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, clim=[-7.5,-4.25], 
+                    figsize = figsize2_box
+#                    #contour_var = 'vel_var_ratio', contour_val = 0.1
+                    ,contour_var = 'diss', contour_val = 1e-9
+                   )
+#palm.plot_hovmoller(diri,run,['u*2','v*2'],
+#                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, 
 #                    figsize = figsize2_box
 #                    #contour_var = 'vel_var_ratio', contour_val = 0.1
 #                   )
-palm.plot_hovmoller(diri,run,['u*2','v*2'],
-                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, 
-                    figsize = figsize2_box
-                    #contour_var = 'vel_var_ratio', contour_val = 0.1
-                   )
+#palm.plot_hovmoller(diri,run,['diss'],
+#                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, 
+#                    figsize = figsize2_box
+#                    ,contour_var = 'diss', contour_val = 1e-9, clim=[1e-9,1e-7]
+#                   )
 #palm.plot_hovmoller(diri,run,['vel_var_ratio'],tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, clim=[0.1,2])

### 2021-07-14 vis_scripts/plot_palm_mod.py

@@ -1060,6 +1060,20 @@ def plot_hovmoller(filedir, runname, plotvar,tunits='hr',
                 var1 = np.log10(var1)
                 c_axis_label = r'$\log_{10}$'+c_axis_label
 
+            if contour_var != '':
+                if contour_var != j:
+                    var2,_ = extract_var(data1,contour_var,#ops=ops[plotvar.index(j)],
+                                         data_type = 'pr',tunits=tunits, 
+                                         tval=tlim, zval=zlim)
+                else:
+                    var2 = var1
+                contour_z = np.ones((len(t)))*np.min(zw)
+                for idx_t,ti in enumerate(t):
+                    idx_z = 0
+                    while var2[idx_t,idx_z] < contour_val and idx_z < len(zw)-1:
+                        contour_z[idx_t] = zw[idx_z]
+                        idx_z += 1
+                ax.plot(np.add(t,0.5),contour_z,'--',color='thistle',linewidth=lw1)
             Z = np.shape((len(zu)+1,len(t)+1))# row is z,col is t 
             T = np.shape((len(zu)+1,len(t)+1))# row is z,col is t 
             zw = ma.append(zw[0]+(zw[0]-zw[1]),zw)
@@ -1074,12 +1088,6 @@ def plot_hovmoller(filedir, runname, plotvar,tunits='hr',
             pmesh = ax.pcolormesh(T,Z,var1,cmap = pv.varcmap[pv.varlist.index(j)], norm=cNorm)
             data1.close()
            
-            if contour_var != '':
-                var2,_ = extract_var(data1,contour_var,#ops=ops[plotvar.index(j)],
-                                     data_type = 'pr',tunits=tunits, 
-                                     tval=tlim, zval=zlim)
-                ax.contour(zw[:-1],t[:-1],var2,[contour_val],colors='k')
-                print(np.min(var2),np.max(var2))
             if zlim[0] != -9999.:
                 ax.set_ylim(zlim)
             if tlim[0] != -9999.:

### 2021-07-14 main.tex

@@
 %\externaldocument{A_suppl_fig}
-\usepackage{amsmath}
+%\usepackage{amsmath}
+\usepackage{mathtools}
 \linenumbers
-%\draftfalse
+\draftfalse
 \journalname{JGR: Oceans}
@@
 We validated our implementation against the stable atmospheric boundary layer test case published in \citeA{abkar_large-eddy_2017}.
-Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}.
+Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}).
 
@@
 Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
+Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE loss (Figure S1d).
 
@@
     \end{minipage}
-    \caption{Time evolution of (a,d) domain-averaged turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
-The black curve represents the same simulation in all panels.}
+    \caption{Time evolution of (a,d) domain-averaged, resolved turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
+The black curve represents the same simulation in all panels.
+The time axis excludes the initial spin-up period.
+}
     % Consider shading the analysis window
@@
 This velocity increase is attributed to changes in the magnitude of buoyancy forcing at the boundary, related to differences in melt rates.
-The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c integrates inertial oscillations of the geostrophic velocity at 20 cm s\textsuperscript{-1}.
+The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c integrates inertial oscillations of the geostrophic velocity with a characteristic magnitude of 20 cm s\textsuperscript{-1}.
 
 % BL depth
+In none of the simulations do we observe a well-mixed the boundary layer well-mixed with respect to scalars, with varying degrees of stratification over the first 20 m from the boundary.
+Thus, we characterize the IOBL using a definition of the mixing layer depth as depth at which the dissipation rate drops below 10\textsuperscript{-9} m\textsuperscript{2} s\textsuperscript{-3} \cite{franks_has_2014, sutherland_mixed_2014}.
+Since shear is the primary source of TKE as discussed later in this section, the IOBL here can also be thought of as portion of the water column where shear originating at the boundary influences the flow.
+The boundary layer depth increases through time, reaching 15 -- 25 m at the end of the simulations.
+
 Stratification within the boundary layer increases with thermal driving (Figure~\ref{fig:dT_profiles}a,b).
@@
 The simulated boundary layer depth has a strong relationship with local thermal driving (i.e., the difference between IOBL temperature and the freezing point), reflecting entrainment of warm water below and setting mixing lengthscales  within the IOBL.
-Boundary layer depth is identified with the local maximum in the ratio of vertical to horizontal velocity variance (e.g., Figure~S1).
-This definition of the IOBL can also be considered the depth to which shear originating at the boundary influences the flow.
-In none of the simulations is the boundary layer well-mixed with respect to either temperature or salinity.
-The boundary layer depth increases through time, reaching 15 -- 25 m at the end of the simulations.
 
 % TKE budget, shear
-Shear production of turbulence dominates the TKE budget. The evolution of TKE can be described by three source terms and dissipation:
-\begin{equation}
-    \frac{d(\textrm{TKE})}{dt} = F_{shear} + F_{buoy} + F_{trans} - \textrm{diss}
-\end{equation}
+Shear production of turbulence dominates the TKE budget. The evolution of resolved TKE can be described by three source terms and dissipation:
+\[
+    \frac{de}{dt} = 
+        \underbrace{
+            -\overline{u^{\prime}w^{\prime}}\frac{du}{dz} -\overline{v^{\prime}w^{\prime}}\frac{dv}{dz}}
+        _{F_{shear}} - 
+        \underbrace{
+            \frac{g_z}{\rho}\overline{\rho^{\prime}w^{\prime}}        -\frac{g_x}{\rho}\overline{\rho^{\prime}u^{\prime}}}
+        _{F_{buoy}} + 
+        \underbrace{
+            \frac{d}{dz}(\overline{w^{\prime}p^{\prime}} +
+                     \overline{w}^{\prime}e^{\prime})}
+        _{F_{trans}} -
+        \hspace{-2mm}\underbrace{\frac{}{}\vareps}_{diss}
+\]
+
 Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure S2 and shows similar patterns.
@@
 Dissipation ($diss$), the remaining term in the TKE budget, can be inferred from the remainder of these terms and the rate of change of TKE.
+Since we evaluate resolved TKE ($e$), dissipation here represents the transfer of energy to the sub-grid scales; there is no flow of energy from sub-grid to resolved scales.
 In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$ m\textsuperscript{2} s\textsuperscript{-3} as seen in Figure \ref{fig:timeseries}a,c.
@@
 Note that the colorbar scale is smaller in (e) than (f).}
-    % Consider contours to a-d to show structures more clearly
     % TODO add panel labels
@@
 Melt rate fluctuations increase in amplitude as thermal driving increases and as slope increases, which we attribute to the increasing importance of buoyancy forcing in driving a near-boundary plume and thus determining the depth-distribution of shear.
-At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the mixed layer over a few hours (Figure \ref{fig:intermittency}b).
+At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the IOBL over a few hours (Figure \ref{fig:intermittency}b).
 The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a dramatic reduction in vertical velocity fluctuations during the down-slope flow period.
 This can be seen in the time series of friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b).
-Below the mixed layer, there is periodic intermittency in turbulence interrupted by the penetration of shear-induced turbulence when the IOBL buoyantly accelerates.
-For this reason, we do not examine IOBL entrainment in this study.
+In all simulations, there is periodic intermittency in turbulence below the IOBL interrupted by the penetration of shear-induced turbulence when the IOBL buoyantly accelerates.
 We discuss these rotational effects on turbulent intensity further in Section \ref{disc:dyn}.
@@
     \label{fig:intermittency}
-    % TODO add panel labels
+    % TODO add panel labels, add IOBL contour
 \end{figure}
@@
 This is mostly attributable to a linear relationship between melt rate and interfacial thermal driving, as differences in friction velocity and the thermal exchange coefficient are small and do not have a systematic relationship with far-field thermal driving.
-The derived, time-averaged thermal exchange coefficient ($\Gamma_{T,der}$) on the other hand does have a weakly negative relationship with far-field thermal driving, reflecting decrease efficiency of heat exchange with increasing near-interface stratification.
+On the other hand, the derived, time-averaged thermal exchange coefficient representing the efficiency of heat exchange from -2 m depth to the ice base ($\Gamma_{T,der}$) does have a weakly negative relationship with far-field thermal driving (Figure \ref{fig:melt_sensitivity}c).
+This indicates a decrease in the efficiency of heat exchange with increasing near-interface stratification.
+The highest thermal driving case shows an anomalously high thermal exchange coefficient over the last inertial period, which features high TKE shown in Figure \ref{fig:intermittency}b.
 We discuss these derived thermal exchange coefficients further in Section \ref{disc:prm_gamma}.
@@
 This linear relationship is due primarily to a linear relationship between friction velocity and melt rate while there is a smaller ($\sim\!1/3$ size) opposite effect from decreasing interfacial thermal driving with increasing slope (not shown).
-This threshold behavior in melting in the two lowest-slope cases is attributable to similar friction velocities (Figure \ref{fig:melt_sensitivity}d) arising from similar IOBL velocities and turbulence  (Figure \ref{fig:dslope_profiles}c,d).
+These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes.
+We observe threshold behavior in melting in the two lowest-slope cases, can be attributed to similar friction velocities arising from similar IOBL velocities and turbulence (Figure \ref{fig:melt_sensitivity}d and Figure \ref{fig:dslope_profiles}c,d).
 This behavior is discussed in more detail in Section \ref{disc:prm_sens}.
 The differences in derived thermal exchange coefficient are not pronounced as slope varies, on the order of a 10\% change as slope increases from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:melt_sensitivity}d).
-These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes.
 
@@
 \begin{equation}
-    d_E = (2 K_b)^{1/2} |f_3|^{-1/2}
+    d_E = (2 K_e)^{1/2} |f_3|^{-1/2}
 \end{equation}
-where $K_{b}$ is the mean bulk viscosity in the turbulent boundary layer assuming the total fluxes follow Fick's law:
+where $K_e$ is the mean eddy viscosity in the turbulent boundary layer assuming the total fluxes follow Fick's law:
 \begin{equation}
-    \overline{w'\mathbf{u}'} = K_{b} d\mathbf{u}/dz
+    \overline{w'\mathbf{u}'} = K_e d\mathbf{u}/dz
 \end{equation}
-$K_b$ profiles are shown in Figure S6.
+$K_e$ profiles are shown in Figure~S6.
 
@@
 We also find that the Ekman depth is a poor predictor of boundary layer depth.
-This may be due to the depth-variable shear induced by buoyancy which is not reflected in the depth-mean IOBL bulk viscosity used to compute the Ekman depth.
+This may be due to the depth-variable shear induced by buoyancy which is not reflected in the depth-mean IOBL eddy viscosity used to compute the Ekman depth.
 Our study was not designed to evaluate IOBL entrainment, which would be better explored by varying the level of background stratification, so we devote no further attention to it here.
@@
 The amplitude of momentum fluxes increases with slope and thermal driving consistent with increases in IOBL velocity and TKE.
-Intermittency in turbulence also changes the shape of momentum flux profile, displacing momentum peaks closer to the surface as the IOBL shoals (pink curve, Figure \ref{fig:momflux_profiles}a).
 
@@
 However, we found that the buoyancy term added to this scheme by \citeA{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
-We removed this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019}.
+We removed this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019} but enables us to extend the domain allow for the development of a $\sim$20 m-thick IOBL.
 
@@
 The flux Richardson number, $\text{Ri}_f$, the ratio of buoyancy flux to shear-driven TKE production, provides a measure of mixing efficiency.
-The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.2$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \cite{armenio_investigation_2002, peltier_mixing_2003}.
-This is consistent with our finding that the thermal exchange coefficient decreases for the high thermal driving cases which also achieve stronger IOBL stratification.
+The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.25$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \cite{armenio_investigation_2002, peltier_mixing_2003}.
+This is consistent with our finding that the derived, 2 m-depth thermal exchange coefficient decreases for the high thermal driving cases which also achieve stronger IOBL stratification.
 
@@
 These simulations did not include tides, which provide perturbations to the mean velocity that enhance melt rates and entrainment, especially at Filchner-Ronne \cite{makinson_modeling_1999, makinson_influence_2011, mueller_tidal_2018}.
-While internal gravity waves arise in LES, they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \cite{gwyther_cold_2020, robertson_tidally_2013, padman_ocean_2018, mueller_impact_2012}.
+While internal gravity waves arise in LES, in our LES model they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \cite{gwyther_cold_2020, robertson_tidally_2013, padman_ocean_2018, mueller_impact_2012}.
 Enhanced drag at the ice-shelf base could increase shear production of TKE; however under strong stratification, surface roughness elements may suppress turbulence rather than enhance it \cite{ohya_wind-tunnel_2001}.
@@
 Thus, we cannot fully assess the the effect of ice-shelf slope on the IOBL's mean velocity profile.
-This effect is addressed by \citeA{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citeA{little_how_2009} with $n=0.94$ for the range of slopes considered here.
+This effect is addressed by \citeA{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citeA{little_how_2009} who found $n=0.94$ for the range of slopes considered here.
 Our finding that $n=1$ may be applicable to the shear-dominated regime, in contrast to the sensitivity of $n=2/3$ found in the convection-dominated regime at higher slopes than those simulated here (5$^{\circ}$ -- 90$^{\circ}$) \cite{mondal_ablation_2019, mcconnochie_dissolution_2018}.
@@
 The decline in exchange coefficient with thermal driving agrees with \citeA{vreugdenhil_stratification_2019}, though their sensitivity is greater than that seen in this study (their Figure 8).
-As shown in Figure \ref{fig:melt_sensitivity}c, this relationship holds during all inertial periods, with the exception of the highest thermal driving case at the last inertial period.
-This high derived thermal exchange coefficient corresponds to the interval of anomalously high TKE shown in Figure \ref{fig:intermittency}b.
+As shown in Figure \ref{fig:melt_sensitivity}c, this relationship holds during all inertial periods, with an exception during an interval of strong turbulence (see Section \ref{results}).
 Due to the limitations of our LES modeling discussed in Section \ref{disc:dyn}, we cannot recommend a best fit relationship between thermal exchange coefficient and thermal driving.
-Given the climatic importance of accurately simulating high thermal driving regimes associated with dynamic ice-shelf thinning, this may be a fruitful avenue for future work.
+Given the climatic importance of accurately simulating high thermal driving regimes associated with dynamic ice-shelf thinning, LES coupled with observational validation across thermal driving regimes may be a fruitful avenue for future work.
 
 % thermal exchange coeff, slope
-We find a linear relationship between the derived thermal exchange coefficient, indicating that thermal exchange is more efficient at higher slopes.
-We note that this relationship also holds for the derived friction velocity from a quadratic drag law, which is greater due to the neglect of stratification effects (Figure \ref{fig:melt_sensitivity}d).
+We find a linear relationship between the derived thermal exchange coefficient and the slope of the ice-shelf base, indicating that thermal exchange is more efficient at higher slopes.
+This relationship also holds for the derived friction velocity from a quadratic drag law (Figure \ref{fig:melt_sensitivity}d).
+Note that these quadratic-drag friction velocities are greater than the model's parameterization of friction velocity as the former neglects stratification effects while the latter includes them.
 This enhanced turbulent efficiency is due to enhanced shear instabilities, and is reflected in turbulent diffusivities parameterized by the AMD scheme.
@@
 The eddy viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (his Figure 3).
-Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or modified KPP scheme in sub-ice settings.
+Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or a modified KPP scheme in sub-ice settings, such as one based on the shape functions presented here.
 
@@
 The low thermal-driving simulations with slopes of 1$^{\circ}$ diverge from this linear behavior within a few m from the boundary.
-We attribute this to boundary effects that reduce TKE and bulk diffusivity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \cite{monin_basic_1954}.
-Since these differences in bulk diffusivity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes.
-This scaling for IOBL fluxes should be explored under a broader range of conditions to determine whether it is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer.
+We attribute this to boundary effects that reduce TKE and eddy viscosity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \cite{monin_basic_1954}.
+Since these differences in eddy viscosity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes.
+This scaling for IOBL fluxes should be explored under a broader range of conditions to determine whether it is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer in the IOBL.
 

### 2021-07-14 vis_scripts/var_param_palm.py
fixup

@@ -137,7 +137,7 @@ varlabel[varlist.index('b13')]          = r'b_{13}'
 varlabel[varlist.index('b23')]          = r'b_{23}'
 varlabel[varlist.index('b22')]          = r'b_{22}'
 varlabel[varlist.index('b33')]          = r'b_{33}'
-varlabel[varlist.index('diss')]         = r'\vareps'
+varlabel[varlist.index('diss')]         = r'\epsilon'#r'\vareps'
 varlabel[varlist.index('drho_oceandz')] = r'd\rho/dz'
 varlabel[varlist.index('drho_gswdz')]   = r'd\rho/dz'
 varlabel[varlist.index('dprho_gswdz')]  = r'd\sigma/dz'
@@ -245,7 +245,7 @@ varunits[varlist.index('gammaT')]       = r''
 varunits[varlist.index('gamma_T')]      = r''
 varunits[varlist.index('gamma_T_2m')]   = r''
 varunits[varlist.index('b33')]          = r''
-varunits[varlist.index('diss')]         = r'm^2/s^3'
+varunits[varlist.index('diss')]         = r'm^2\:s^{-3}'
 varunits[varlist.index('dz')]           = r'm^{-1}'
 varunits[varlist.index('dt')]           = r's'
 varunits[varlist.index('e')]            = r'm^2\:s^{-2}'
@@ -451,6 +451,7 @@ source_var[varlist.index('thermal_driving_i')] = 'u*'
 source_var[varlist.index('thermal_driving_infty')] = 'u*'
 source_var[varlist.index('dT')]              = 'melt'
 source_var[varlist.index('haline_driving')]  = 'sa_io*_xy'
+source_var[varlist.index('diss')]            = 'u'
 source_var[varlist.index('Fshear')]          = 'u'
 source_var[varlist.index('Ftrans')]          = 'u'
 source_var[varlist.index('Fbuoy')]           = 'wpt'

### 2021-07-15 vis_scripts/cp_profile_suppl_fig.sh
Update scripts for k_e fig

@@ -9,9 +9,9 @@ SUFFIX_OLD_SLOPE_AV=_cmp_slope0.10_slope0.50_43hr_tav13.0_42zmax_z_profile.png
 SUFFIX_NEW_SLOPE=_cmp_dslope_40h_z_profile.png
 SUFFIX_NEW_SLOPE_AV=_cmp_dslope_43h_tav13h_z_profile.png
 
-cp $PREFIX_T/vel_var_ratio$SUFFIX_OLD_T ../Figures/vel_var_ratio$SUFFIX_NEW_T
-cp $PREFIX_T/km_eff$SUFFIX_OLD_T_AV ../Figures/km$SUFFIX_NEW_T_AV
-cp $PREFIX_T/k_all$SUFFIX_OLD_T_AV ../Figures/k$SUFFIX_NEW_T_AV
-cp $PREFIX_SLOPE/vel_var_ratio$SUFFIX_OLD_SLOPE ../Figures/vel_var_ratio$SUFFIX_NEW_SLOPE
-cp $PREFIX_SLOPE/km_eff$SUFFIX_OLD_SLOPE_AV ../Figures/km$SUFFIX_NEW_SLOPE_AV
-cp $PREFIX_SLOPE/k_all$SUFFIX_OLD_SLOPE_AV ../Figures/k$SUFFIX_NEW_SLOPE_AV
+#cp $PREFIX_T/vel_var_ratio$SUFFIX_OLD_T ../Figures/vel_var_ratio$SUFFIX_NEW_T
+#cp $PREFIX_T/k_all$SUFFIX_OLD_T_AV ../Figures/k$SUFFIX_NEW_T_AV
+#cp $PREFIX_SLOPE/vel_var_ratio$SUFFIX_OLD_SLOPE ../Figures/vel_var_ratio$SUFFIX_NEW_SLOPE
+#cp $PREFIX_SLOPE/k_all$SUFFIX_OLD_SLOPE_AV ../Figures/k$SUFFIX_NEW_SLOPE_AV
+cp $PREFIX_T/km_eff_cmp_dT0.2_dT0.4_43hr_tav13_24zmax_z_profile.png ../Figures/km$SUFFIX_NEW_T_AV
+cp $PREFIX_SLOPE/km_eff_cmp_slope0.10_slope0.50_43hr_tav13.0_24zmax_z_profile.png ../Figures/km$SUFFIX_NEW_SLOPE_AV

### 2021-07-15 vis_scripts/extract_var_palm.py

@@ -67,7 +67,7 @@ def extract_var(data,var_name,data_type='pr',ops=[],
                 tval=[-9999.,-9999.],xval=[9999.,9999.],
                 yval=[9999.,9999.],zval=[9999.,9999.],
                 tunits = 'hr', tav = 0., 
-                varaxes = ['t'], p0 = 10., filedir=''):
+                varaxes = ['t'], p0 = 10., data_dir=''):
     #print('extract_var',var_name,data_type,slice_obj)
     if data_type == 'pr':
         tav_native = 1.
@@ -77,7 +77,7 @@ def extract_var(data,var_name,data_type='pr',ops=[],
        tav = 0.
     if data_type == 'parameter':
         #slice_obj_der,_ = slice_var(data,source_var[varlist.index(var_name)],data_type='ts')
-        var1 = derived_var(data,var_name,[],filedir=filedir,p0=p0,
+        var1 = derived_var(data,var_name,[],filedir=data_dir,p0=p0,
                            data_type=data_type)
         axis_label = varlabel[varlist.index(var_name)]
         if (varunits[varlist.index(var_name)] != r''):
@@ -99,7 +99,7 @@ def extract_var(data,var_name,data_type='pr',ops=[],
         slice_obj_der,_ = slice_var(data,source_var[varlist.index(var_name)],data_type=data_type)
         var1 = derived_var(data,var_name,
                            slice_obj_der,
-                           filedir=filedir,p0=p0,
+                           filedir=data_dir,p0=p0,
                            data_type=data_type,tlim=[tval[0]-tav/2.,tval[1]+tav/2.])
         #if np.shape(data_type)==np.shape(slice_obj):
     else:
@@ -118,7 +118,12 @@ def extract_var(data,var_name,data_type='pr',ops=[],
         tmask = np.multiply(t>(ti - tav/2.),t<=(ti + tav/2.))
         #print('____extract_var time mean: '+var_name+' shp = ',np.shape(var1),'tmask',t[tmask])
         var1_shape = np.shape(var1)
+        var1 = var1.data
         if len(var1_shape) == 2:#data_type == 'pr':
+            print('shape tmask',np.shape(tmask))
+            print('shape var1 tav',np.shape(var1))
+            print('tmask',t[tmask])
[…]

### 2021-07-15 vis_scripts/profile_suppl_fig.py

@@ -27,14 +27,14 @@ palm.plot_pr(diri, run, ['km_eff'],
              tav = tav_pr,
              figsize = figsize2, 
              legtitle=legtitle,
-             zlim=[zmax,0], col=colorVal
+             zlim=[-24,0], col=colorVal
             )
-palm.plot_pr(diri, run, ['k_all'],
-             runlabel=runlabel,  
-             teval = [tprofile,tprofile], 
-             tav = tav_pr, 
-             figsize = figsize2, 
-             legtitle=legtitle,
-             plot_legend=False,
-             zlim=[zmax,0], col=colorVal
-            )
+#palm.plot_pr(diri, run, ['k_all'],
+#             runlabel=runlabel,  
+#             teval = [tprofile,tprofile], 
+#             tav = tav_pr, 
+#             figsize = figsize2, 
+#             legtitle=legtitle,
+#             plot_legend=False,
+#             zlim=[zmax,0], col=colorVal
+#            )

### 2021-07-15 vis_scripts/var_param_palm.py

@@ -137,6 +137,7 @@ varlabel[varlist.index('b13')]          = r'b_{13}'
 varlabel[varlist.index('b23')]          = r'b_{23}'
 varlabel[varlist.index('b22')]          = r'b_{22}'
 varlabel[varlist.index('b33')]          = r'b_{33}'
+varlabel[varlist.index('dEdt')]         = r'de/dt'
 varlabel[varlist.index('diss')]         = r'\epsilon'#r'\vareps'
 varlabel[varlist.index('drho_oceandz')] = r'd\rho/dz'
 varlabel[varlist.index('drho_gswdz')]   = r'd\rho/dz'
@@ -158,7 +159,7 @@ varlabel[varlist.index('Fshear')]       = r'F_{shear}'
 varlabel[varlist.index('Ftrans')]       = r'F_{trans}'
 varlabel[varlist.index('haline_driving')]=r'S - S_i'
 varlabel[varlist.index('kh_eff')]       = r'k_h'
-varlabel[varlist.index('km_eff')]       = r'k_m'
+varlabel[varlist.index('km_eff')]       = r'k_e'
 varlabel[varlist.index('kh')]           = r'k_h SGS'
 varlabel[varlist.index('ks')]           = r'k_s SGS'
 varlabel[varlist.index('km')]           = r'k_m SGS'
@@ -245,6 +246,7 @@ varunits[varlist.index('gammaT')]       = r''
 varunits[varlist.index('gamma_T')]      = r''
 varunits[varlist.index('gamma_T_2m')]   = r''
 varunits[varlist.index('b33')]          = r''
+varunits[varlist.index('dEdt')]         = r'm^2\:s^{-3}'
 varunits[varlist.index('diss')]         = r'm^2\:s^{-3}'
 varunits[varlist.index('dz')]           = r'm^{-1}'
 varunits[varlist.index('dt')]           = r's'
@@ -370,6 +372,13 @@ varcmap[varlist.index('w')] = 'cmo.balance'
 varcmap[varlist.index('u"')] = 'cmo.balance'
 varcmap[varlist.index('v"')] = 'cmo.balance'
 varcmap[varlist.index('w"')] = 'cmo.balance'
+varcmap[varlist.index('dEdt')] = 'cmo.balance'
+varcmap[varlist.index('w*u*u*:dz')] = 'cmo.balance'
[…]

### 2021-07-15 vis_scripts/plot_palm_mod.py
Update plot_palm for BL

@@ -496,7 +496,7 @@ def plot_tseries(filedir, runname, plotvar,
                var,var_label = extract_var(data1,j,data_type = 'ts',
                                   tunits=tunits,tval=tlim,
                                   grid=pv.vartype[pv.varlist.index(j)],
-                                  filedir=k)
+                                  data_dir=k)
                print(np.shape(var),np.mean(var))
                if len(varname) > 1:
                    y_axis_label = r'$'+pv.vars_axis_label[pv.varsname.index(i)]+r'$'
@@ -577,7 +577,7 @@ def plot_tseries_cross(filedir, runname, runlabel,
         print('y_var')
         y_var,y_axis_label = extract_var(y_data,plotvar[1],
                                          slice_obj=slice_obj_input,
-                                         data_type=data_type[1],filedir=diri,
+                                         data_type=data_type[1],data_dir=diri,
                                          tval=teval,tav=tav)
         x_data = load_data(diri,data_type=data_type[0])
         if data_type[0] != 'parameter':
@@ -588,7 +588,7 @@ def plot_tseries_cross(filedir, runname, runlabel,
         print('x_var')
         x_var,x_axis_label = extract_var(x_data,plotvar[0],
                                          slice_obj=slice_obj_x,
-                                         data_type=data_type[0],filedir=diri,
+                                         data_type=data_type[0],data_dir=diri,
                                          tval=teval,tav=tav)
         if color_by_time:
             t,cbar_label = extract_var(y_data,'time',data_type=data_type[1],tunits=tunits,tval=teval,
@@ -617,11 +617,11 @@ def plot_tseries_cross(filedir, runname, runlabel,
                 if data_type[0] != 'parameter':
                     x_var,_ = extract_var(y_data,plotvar[1],
                                             slice_obj=slice_obj_input,
-                                            data_type=data_type[1],filedir=diri,
+                                            data_type=data_type[1],data_dir=diri,
                                             tval=teval-tav*j,tav=tav)
                 add_var,_ = extract_var(y_data,plotvar[1],
                                         slice_obj=slice_obj_input,
-                                        data_type=data_type[1],filedir=diri,
+                                        data_type=data_type[1],data_dir=diri,
[…]

### 2021-07-15 vis_scripts/cp_flux_profile_fig.sh
Update zlimits on vel_var_ratio

@@ -13,17 +13,19 @@ SUFFIX_NEW_SLOPE=_cmp_dslope_43h_tav13h_z_profile.png
 SUFFIX_NEW_SLOPE1=_cmp_dslope_8h_tav13h_z_profile.png
 SUFFIX_NEW_SLOPE_SCALE=_cmp_dslope_43h_tav13h_slopescale_z_profile.png
 
-cp $PREFIX_T/wpt$SUFFIX_OLD_T ../Figures/heatflux$SUFFIX_NEW_T
-cp $PREFIX_T/heatflux_z$SUFFIX_OLD_T ../Figures/heatflux_res_sgs$SUFFIX_NEW_T
-cp $PREFIX_T/heatflux_z$SUFFIX_OLD_T1 ../Figures/heatflux_res_sgs$SUFFIX_NEW_T1
-cp $PREFIX_T/wpt$SUFFIX_OLD_T_SCALE ../Figures/heatflux$SUFFIX_NEW_T_SCALE
-cp $PREFIX_T/wsa$SUFFIX_OLD_T ../Figures/wsa$SUFFIX_NEW_T
-#cp $PREFIX_T/saltflux_z$SUFFIX_OLD_T ../Figures/saltflux_res_sgs$SUFFIX_NEW_T
-cp $PREFIX_T/momflux_z$SUFFIX_OLD_T ../Figures/momflux$SUFFIX_NEW_T
-cp $PREFIX_SLOPE/wpt$SUFFIX_OLD_SLOPE ../Figures/heatflux$SUFFIX_NEW_SLOPE
-cp $PREFIX_SLOPE/heatflux_z$SUFFIX_OLD_SLOPE ../Figures/heatflux_res_sgs$SUFFIX_NEW_SLOPE
-cp $PREFIX_SLOPE/heatflux_z$SUFFIX_OLD_SLOPE1 ../Figures/heatflux_res_sgs$SUFFIX_NEW_SLOPE1
-cp $PREFIX_SLOPE/wpt$SUFFIX_OLD_SLOPE_SCALE ../Figures/heatflux$SUFFIX_NEW_SLOPE_SCALE
-cp $PREFIX_SLOPE/wsa$SUFFIX_OLD_SLOPE ../Figures/wsa$SUFFIX_NEW_SLOPE
[…]

### 2021-07-15 vis_scripts/cp_hovmoller_fig.sh

@@ -1,10 +1,12 @@
 #PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dpdy_021/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dT_020/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 PREFIX_SLOPE=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_alpha_surface_006/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
-SUFFIX_OLD_T=_dT0.4_tlim2-50_42zmax_contour_diss_hovmoller.png
+SUFFIX_OLD_T=_dT0.4_tlim2-50_42zmax_BL_contour_diss_hovmoller.png
 SUFFIX_NEW_T=_hovmoller.png
-SUFFIX_OLD_SLOPE=_slope0.50_tlim2-50_42zmax_contour_diss_hovmoller.png
+SUFFIX_OLD_SLOPE=_slope0.50_tlim2-50_42zmax_BL_contour_diss_hovmoller.png
 SUFFIX_NEW_SLOPE=_hovmoller.png
 
 cp $PREFIX_T/e_res$SUFFIX_OLD_T ../Figures/dT4/e$SUFFIX_NEW_T
 cp $PREFIX_SLOPE/e_res$SUFFIX_OLD_SLOPE ../Figures/dslope2/e$SUFFIX_NEW_SLOPE
+#cp $PREFIX_T/dEdt$SUFFIX_OLD_T ../Figures/dT4/dedt$SUFFIX_NEW_T
+#cp $PREFIX_SLOPE/dEdt$SUFFIX_OLD_SLOPE ../Figures/dslope2/dedt$SUFFIX_NEW_SLOPE

### 2021-07-15 vis_scripts/cp_profile_suppl_fig.sh

@@ -1,17 +1,19 @@
 PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_dpdy_021/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 PREFIX_SLOPE=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_alpha_surface_006/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 SUFFIX_OLD_T_AV=_cmp_dT0.2_dT0.4_43hr_tav13_42zmax_z_profile.png
-SUFFIX_OLD_T=_cmp_dT0.2_dT0.4_40hr_42zmax_z_profile.png
-SUFFIX_NEW_T_AV=_cmp_dT_43h_tav13h_z_profile.png
-SUFFIX_NEW_T=_cmp_dT_40h_z_profile.png
-SUFFIX_OLD_SLOPE=_cmp_slope0.10_slope0.50_40hr_42zmax_z_profile.png
+SUFFIX_OLD_T=_cmp_dT0.2_dT0.4_43hr_tav13_20zmax_z_profile.png
+SUFFIX_NEW_T_AV=_dT_43h_tav13h_z_profile.png
+SUFFIX_NEW_T=_dT_43h_tav13h_z_profile.png
+SUFFIX_OLD_SLOPE=_cmp_slope0.10_slope0.50_43hr_tav13.0_20zmax_z_profile.png
 SUFFIX_OLD_SLOPE_AV=_cmp_slope0.10_slope0.50_43hr_tav13.0_42zmax_z_profile.png
-SUFFIX_NEW_SLOPE=_cmp_dslope_40h_z_profile.png
-SUFFIX_NEW_SLOPE_AV=_cmp_dslope_43h_tav13h_z_profile.png
+SUFFIX_NEW_SLOPE=_dslope_43h_tav13h_z_profile.png
+SUFFIX_NEW_SLOPE_AV=_dslope_43h_tav13h_z_profile.png
 
-#cp $PREFIX_T/vel_var_ratio$SUFFIX_OLD_T ../Figures/vel_var_ratio$SUFFIX_NEW_T
[…]

### 2021-07-15 vis_scripts/extract_var_palm.py

@@ -323,7 +323,8 @@ def derived_var(data,varname,slice_obj_input,z_offset = 0.,f = gsw.f(-70.),filed
         ti = np.argmin(np.abs(t-50.))
         #var1,_ = extract_var(data,'z',slice_obj=slice_obj)#,grid='zu'
         K_ref,_ = extract_var(data,'km_eff',data_type=data_type)#,slice_obj=slice_obj,tav=tav)
-        K_eff = np.nanmean(K_ref[ti-12:ti+1,-80:])
+        K_ref = K_ref.data
+        var1 = np.nanmean(K_ref[ti-12:ti+1,-80:])
         #var1 = np.divide(var1,dE)
 
     elif varname == 'dEdt':
@@ -677,7 +678,7 @@ def derived_var(data,varname,slice_obj_input,z_offset = 0.,f = gsw.f(-70.),filed
         u2 = data.variables['u*2'][:]
         v2 = data.variables['v*2'][:]
         w2 = data.variables['w*2'][:]
-        var1 = np.divide(2.0*w2,(u2+v2))
+        var1 = np.divide(2.0*w2,np.maximum(w2/5.,(u2+v2)))
     else:
         print(varname,' not available')
     return var1#[slice_obj]

### 2021-07-15 vis_scripts/flux_profile_fig.py

@@ -9,8 +9,8 @@ from extract_var_palm import load_data,extract_var
 import sys
 import plot_palm_mod as palm
 import numpy as np
-#from cmp_thermal_driving_slope1 import *
-from cmp_slope_hidT import *
+from cmp_thermal_driving_slope1 import *
+#from cmp_slope_hidT import *
 
 sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 
@@ -22,15 +22,16 @@ sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 #             legtitle=legtitle,
 #             zlim=[zmax,0], col=colorVal
 #            )
-#palm.plot_pr(diri, run, ['momflux_z'],
-#             runlabel=runlabel,  
-#             teval = [tprofile,tprofile], 
-#             tav = tav_pr, 
-#             figsize = figsize2, 
-#             legtitle=legtitle,
-#             plot_legend=False,
-#             zlim=[zmax,0], col=colorVal
-#            )
+palm.plot_pr(diri, run, ['momflux_z'],
+             runlabel=runlabel,  
+             teval = [tprofile,tprofile], 
+             tav = tav_pr, 
+             zscale = 'Ekman', 
+             figsize = figsize2, 
+             legtitle=legtitle,
+             plot_legend=False,
+             zlim=[zmax,0], col=colorVal
+            )
 #palm.plot_pr(diri, run, ['wpt','momflux_z'],
 #             runlabel=runlabel,  
 #             teval = [tprofile,tprofile], 
@@ -52,12 +53,12 @@ sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 #             plot_legend=False,
 #             zlim=[zmax,0], col=colorVal
 #            )
-palm.plot_pr(diri, run, ['heatflux_z'],#'saltflux_z','momflux_u','momflux_v'],
-             runlabel=runlabel,  
-             teval = [tmin+tav_pr/2,tmin+tav_pr/2], 
-             tav = tav_pr,
-             figsize = figsize2, 
-             legtitle=legtitle,
-             plot_legend=False,
-             zlim=[zmax,0], col=colorVal
-            )
+#palm.plot_pr(diri, run, ['heatflux_z'],#'saltflux_z','momflux_u','momflux_v'],
+#             runlabel=runlabel,  
+#             teval = [tmin+tav_pr/2,tmin+tav_pr/2], 
+#             tav = tav_pr,
[…]

### 2021-07-15 vis_scripts/hovmoller_fig.py

@@ -15,20 +15,25 @@ from cmp_thermal_driving_slope1 import *
 
 sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 
-palm.plot_hovmoller(diri,run,['e*'],
-                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, clim=[-7.5,-4.25], 
-                    figsize = figsize2_box
-#                    #contour_var = 'vel_var_ratio', contour_val = 0.1
-                    ,contour_var = 'diss', contour_val = 1e-9
+palm.plot_hovmoller(diri,run,['w*2'],
+                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True,
+                    figsize = figsize2_box, plot_BL=True
                    )
+#palm.plot_hovmoller(diri,run,['e*'],
+#                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, clim=[-7.5,-4.25], 
+#                    figsize = figsize2_box, plot_BL=True
+#                    ,contour_var = 'diss', contour_val = 1e-9
+#                   )
 #palm.plot_hovmoller(diri,run,['u*2','v*2'],
 #                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, 
 #                    figsize = figsize2_box
 #                    #contour_var = 'vel_var_ratio', contour_val = 0.1
 #                   )
-#palm.plot_hovmoller(diri,run,['diss'],
+#palm.plot_hovmoller(diri,run,['w*u*u*:dz','w*p*:dz'],#['Fshear','Fbuoy','Ftrans','diss','dEdt'],
 #                    tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, 
 #                    figsize = figsize2_box
-#                    ,contour_var = 'diss', contour_val = 1e-9, clim=[1e-9,1e-7]
+#                    ,contour_var = 'diss', contour_val = 1e-9, contour_col = 'k',
+#                    #clim=[-5e-9,5e-9]
+#                    clim=[-1e-9,1e-9]
 #                   )
 #palm.plot_hovmoller(diri,run,['vel_var_ratio'],tlim = [tmin,tmax], runlabel=runlabel,zlim=[zmax,0],overwrite=True, clim=[0.1,2])

### 2021-07-15 vis_scripts/profile_suppl_fig.py

@@ -14,21 +14,31 @@ from cmp_slope_hidT import *
 
 sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 
-#palm.plot_pr(diri, run, ['vel_var_ratio'],#,'km_eff'
-#             runlabel=runlabel,  
-#             teval = [40,40], 
-#             figsize = figsize2, 
-#             legtitle=legtitle,
-#             zlim=[zmax,0], col=colorVal
-#            )
-palm.plot_pr(diri, run, ['km_eff'],
+palm.plot_pr(diri, run, ['vel_var_ratio'],#,'km_eff'
              runlabel=runlabel,  
+#             teval = [40,40], 
              teval = [tprofile,tprofile], 
              tav = tav_pr,
              figsize = figsize2, 
              legtitle=legtitle,
-             zlim=[-24,0], col=colorVal
+             xlim = [0,1], zlim=[-20,0], col=colorVal
             )
+#palm.plot_pr(diri, run, ['wsa'],
+#             runlabel=runlabel,  
+#             teval = [tprofile,tprofile], 
+#             tav = tav_pr,
+#             figsize = figsize2, 
+#             legtitle=legtitle,
+#             zlim=[zmax,0], col=colorVal
+#            )
+#palm.plot_pr(diri, run, ['km_eff'],
+#             runlabel=runlabel,  
+#             teval = [tprofile,tprofile], 
+#             tav = tav_pr,
+#             figsize = figsize2, 
+#             legtitle=legtitle,
+#             zlim=[-24,0], col=colorVal
+#            )
 #palm.plot_pr(diri, run, ['k_all'],
 #             runlabel=runlabel,  
 #             teval = [tprofile,tprofile], 

### 2021-07-15 vis_scripts/plot_palm_mod.py
Add analysis window to timeseries fig

@@ -435,8 +435,9 @@ def plot_TS(filedir,runname,teval = [-9999.], tunits = 'hr',
 #   printformat plot file extension (optional). Defaults to png.
 #------------------------------------------------------------------------------
 def plot_tseries(filedir, runname, plotvar, 
-                 tlim = [9999.,9999.],tav=0.,tunits='hr',
-                 runlabel=[''], legtitle = '',legvar = '', plot_legend=True,
+                 tlim = [9999.,9999.],tav=0.,tunits='hr',tshade = [9999,9999],
+                 ylim = [-9999,-9999], runlabel=[''], 
+                 leglocation = 'best', legtitle = '',legvar = '', plot_legend=True,
                  col=col, linestyle = ['-'], marker = mk, figsize=(6.4,4.8),
                  outputdir = [], overwrite=True, printformat = 'png'):
     
@@ -497,7 +498,6 @@ def plot_tseries(filedir, runname, plotvar,
                                   tunits=tunits,tval=tlim,
                                   grid=pv.vartype[pv.varlist.index(j)],
                                   data_dir=k)
-               print(np.shape(var),np.mean(var))
                if len(varname) > 1:
                    y_axis_label = r'$'+pv.vars_axis_label[pv.varsname.index(i)]+r'$'
                    linestyle[idx] = pv.vars_ls[pv.varsname.index(i)][jidx]
@@ -514,11 +514,17 @@ def plot_tseries(filedir, runname, plotvar,
                        linewidth=lw,color = col[idx])
 
         if plot_legend:
-            #ax.legend(loc=legloc, bbox_to_anchor = bboxanchor, title=legtitle)
-            ax.legend(bbox_to_anchor = bboxanchor, title=legtitle)
+            ax.legend(loc=leglocation, bbox_to_anchor = (1,1), title=legtitle)
         ax.set_xlabel(x_axis_label,fontsize = fs)
-        if tlim[0] != -9999.:
+        if ylim[0] != -9999.:
+           ax.set_ylim(ylim)
+        if tlim[0] != 9999.:
            ax.set_xlim(tlim)
+        if tshade[0] != 9999.:
+           #ylim = ax.get_ylim()
+           ax.fill([tshade[0],tshade[0],tshade[1],tshade[1]],
+                   [ylim[0],ylim[1],ylim[1],ylim[0]],
+                   'k',alpha = 0.2)#,lineStyle='None')
[…]

### 2021-07-15 vis_scripts/timeseries_fig.py

@@ -9,11 +9,11 @@ import sys
 import plot_palm_mod as palm
 import numpy as np
 from plot_param_palm import figsize3
-#from cmp_thermal_driving_slope1 import *
-from cmp_slope_hidT import *
+from cmp_thermal_driving_slope1 import *
+#from cmp_slope_hidT import *
 
 sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 
-palm.plot_tseries(diri, run, ['E*'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax], plot_legend=False, ylim=[4e-7,3e-5])
-palm.plot_tseries(diri, run, ['melt'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax], plot_legend=False, linestyle = ['None' for i in diri], marker = '.', ylim=[2e-3,7])
-palm.plot_tseries(diri, run, ['u*'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax], ylim=[0,6e-3])
+#palm.plot_tseries(diri, run, ['E*'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax], plot_legend=False, ylim=[4e-7,3e-5], tshade = [50-13,50])
+#palm.plot_tseries(diri, run, ['melt'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax], plot_legend=False, linestyle = ['None' for i in diri], marker = '.', ylim=[2e-3,7], tshade = [50-13,50])
+palm.plot_tseries(diri, run, ['u*'], runlabel = runlabel, legtitle = legtitle, col=colorVal, figsize = figsize3,tlim = [tmin,tmax], ylim=[0,8e-3], tshade = [50-13,50], leglocation = 'upper right')

### 2021-08-02 vis_scripts/flux_profile_fig.py
Resize flux figures

@@ -18,31 +18,30 @@ sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
 #             runlabel=runlabel,  
 #             teval = [tprofile,tprofile], 
 #             tav = tav_pr,
-#             figsize = figsize2, 
+#             figsize = figsize3, 
 #             legtitle=legtitle,
 #             zlim=[zmax,0], col=colorVal
 #            )
-palm.plot_pr(diri, run, ['momflux_z'],
+palm.plot_pr(diri, run, ['wpt'],
              runlabel=runlabel,  
              teval = [tprofile,tprofile], 
              tav = tav_pr, 
+             xscale_input = xscale_input, 
+             xscale_label = xscale_label, 
              zscale = 'Ekman', 
-             figsize = figsize2, 
-             legtitle=legtitle,
+             figsize = figsize3, 
              plot_legend=False,
-             zlim=[zmax,0], col=colorVal
+             zlim=[-25.,0.], 
+             col=colorVal,overwrite=True
             )
-#palm.plot_pr(diri, run, ['wpt','momflux_z'],
+#palm.plot_pr(diri, run, ['momflux_z'],
 #             runlabel=runlabel,  
 #             teval = [tprofile,tprofile], 
 #             tav = tav_pr, 
-#             xscale_input = xscale_input, 
-#             xscale_label = xscale_label, 
-#             zscale = 'Ekman', 
-#             figsize = figsize2, 
+#             figsize = figsize3, 
+#             legtitle=legtitle,
 #             plot_legend=False,
-#             #zlim=[-25.,0.], 
-#             col=colorVal
+#             zlim=[zmax,0], col=colorVal
 #            )
 #palm.plot_pr(diri, run, ['heatflux_z'],#'saltflux_z','momflux_u','momflux_v'],
 #             runlabel=runlabel,  

### 2021-08-02 main.tex

@@
-\documentclass[draft]{agujournal2019}
-\usepackage{url} 
-\usepackage{lineno}
-\usepackage{graphicx}
-%\usepackage{xr}
-\usepackage{float}
-%\externaldocument{A_suppl_fig}
-%\usepackage{amsmath}
-\usepackage{mathtools}
-\linenumbers
-\draftfalse
-\journalname{JGR: Oceans}
+\documentclass[tc, manuscript]{copernicus}
+
+% current word count 2021-07-15 8,500 = 17 PU
+% caption word count 2021-07-15 
+% figures 7 = 7 PU
+% excess charge for PU over 25
 
@@
 
-\correspondingauthor{Carolyn Begeman}{cbegeman@lanl.gov}
-\authors{Carolyn Branecky Begeman\affil{1}, Xylar Asay-Davis\affil{1}, and Luke Van Roekel\affil{1}}
+\correspondence{Carolyn Begeman (cbegeman@lanl.gov)}
 
-\affiliation{1}{Los Alamos National Laboratory, Los Alamos, New Mexico, USA}
+\Author[1]{Carolyn Branecky}{Begeman}
+\Author[1]{Xylar}{Asay-Davis}
+\Author[1]{Luke}{Van Roekel}
 
-\begin{keypoints}
-\item We simulate boundary layer turbulence with prognostic ice-shelf melting
-in cold cavity settings.
-\item Our simulations support a linear melt response to thermal driving.
-\item Buoyant mean flow can significantly enhance melt rates at ice-shelf basal slopes as low as 1 degree.
-\end{keypoints}
+\affil[1]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, New Mexico, USA 87545}
+
+\runningtitle{IOBL dynamics}
+
+\runningauthor{Begeman et al.}
+
+\received{}
+\pubdiscuss{}
+\revised{}
+\accepted{}
+\published{}
+
+\firstpage{1}
+
+\maketitle
 
@@
 Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can affect sea-level rise by altering the ability of Antarctic ice shelves to “buttress” ice flux to the ocean.
-%Direct measurements of ocean properties below ice shelves are exceedingly rare, expensive to perform, and difficult to generalize to larger areas.
-Further, the few available measurements indicate that existing boundary layer theory on sub-ice-shelf turbulence (based largely on observations below sea ice) is incomplete.
 In this study, we improve our understanding of turbulence below ice shelves by means of large-eddy simulations at sub-meter resolution, capturing boundary layer mixing at scales intermediate between laboratory experiments or direct numerical simulations and regional or global ocean circulation models.
-Our simulations feature the development of an ice-ocean boundary layer through dynamic ice melting in a regime with low thermal driving, low ice-shelf slope, and strong shear driven by the geostrophic flow.
+Our simulations feature the development of an ice-shelf ocean boundary layer through dynamic ice melting in a regime with low thermal driving, low ice-shelf basal slope, and strong shear driven by the geostrophic flow.
 We present a preliminary assessment of existing ice-shelf basal melt parameterizations adopted in single component or coupled ice-sheet and ocean models on the basis of a small parameter study.
 While the parameterized linear relationship between ice-shelf melt rate and far-field ocean temperature appears to be robust, we point out a little-considered relationship between ice-shelf basal slope and melting worthy of further study.
+\end{abstract}
 
-\textbf{Plain language summary}\\
-Ice-shelf melting from below is controlled by the rate at which the ocean can transport heat vertically.
-Little is known about the small-scale mixing that carries this heat close to the ice base, where melting itself impedes mixing by forming a density barrier.
-This study uses ocean modeling at ultra-high resolution to study these mixing processes.
-It offers some insights into the relationship between ice-shelf melting and ocean temperature far from the ice base, which may help us project how fast ice will melt when ocean waters entering the cavity warm.
-This study adds to a growing body of research that indicates coarse resolution ocean models used for such projections may have to adjust how they handle ocean mixing to improve the fidelity of ice-shelf melting.
-
-\end{abstract}
-\newpage
-\section{Introduction}
+\introduction
 
 % Motivation - SLR
-The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet \cite{ipcc_climate_2014}.
-The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice \cite{reese_far_2018, rignot_ice-shelf_2013}.
-The Ice-shelf/Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base.
+The largest source of uncertainty in future sea level rise is the potential loss of ice from the Antarctic Ice Sheet \citep{ipcc_climate_2014}.
+The rate of grounded ice loss is highly sensitive to the melting of ice shelves, which drain over 80\% of Antarctica’s grounded ice \citep{reese_far_2018, rignot_ice-shelf_2013}.
+The Ice-shelf Ocean Boundary Layer (IOBL) controls ice-shelf melting by regulating oceanic heat and salt fluxes to the ice shelf base.
 Thus, accurate predictions of ice-shelf melting depend on representing the turbulent dynamics of the IOBL.
 This representation is also critical for evaluating the sensitivity of the coupled land ice-ocean system to changes in ocean conditions.
-Of particular concern is the sensitivity of ice-shelf melting to increasing seawater temperature at depth, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse \cite{ruan_ice-shelf_2021, schmidtko_multidecadal_2014, purkey_unabated_2018, wahlin_pathways_2021}.
+Of particular concern is the sensitivity of ice-shelf melting to increasing seawater temperature at depth, a trend observed along a wide swath of the West Antarctic coastline and a potential trigger for West Antarctic Ice Sheet collapse \citep{purkey_unabated_2018, ruan_ice-shelf_2021, schmidtko_multidecadal_2014, wahlin_pathways_2021}.
 
-% Shortcomings of ocean-model representations of IOBL
-One indication that ocean models do not capture turbulent dynamics is that the simulated thermal driving in the IOBL, the difference between ocean temperature and the local freezing point, and consequently the simulated melt rate differ significantly between ocean models and as resolution is varied within a model \cite{gwyther_cold_2020}.
-Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the lateral buoyancy gradient of the IOBL and often the vertical buoyancy gradient as well, which should reduce the efficiency of vertical mixing near the boundary.
-This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is driven in large part by the buoyant flow of water freshened by ice-shelf melting, overturning circulation also known as the ``ice pump'' \cite{webber_impact_2018}.
-A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically based, accurate coupling of ice sheets and oceans in climate models \cite{gwyther_cold_2020, dinniman_modeling_2016, naughten_future_2018, edwards_projected_2021}.
+% TODO coauthor order
+One indication that ocean models do not capture turbulent dynamics in the IOBL is that the simulated thermal driving, the difference between ocean temperature and the local freezing point, and consequently the simulated melt rate differ significantly between ocean models and as resolution is varied within a model \citep{gwyther_cold_2020}.
+Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the effects of the lateral buoyancy gradient of the IOBL, and often of the vertical buoyancy gradient, on the efficiency of vertical mixing near the boundary.
+This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is driven in large part by the buoyant flow of water freshened by ice-shelf melting, an overturning circulation also known as the ``ice pump'' \citep{webber_impact_2018}.
+A new parameterization of ice-shelf melting that accounts for the dynamics of IOBL turbulence is needed to achieve a more physically based, accurate coupling of ice sheets and oceans in climate models \citep{dinniman_modeling_2016, edwards_projected_2021, gwyther_cold_2020, naughten_future_2018}.
 
@@
 IOBLs present unique conditions in the global ocean, involving a stabilizing flux from phase change (ice-melting) and a boundary layer that is positively buoyant against a sloping boundary.
-There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \cite{zonta_stably_2018}.
-The IOBL has been most extensively explored at small scales through laboratory experiments and Direct Numerical Simulations, with some recent numerical studies addressing intermediate scales \cite{mondal_ablation_2019, vreugdenhil_stratification_2019, middleton_numerical_2021}.
+There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \citep{zonta_stably_2018}.
+The IOBL has most frequently been explored at small scales through laboratory experiments and direct numerical simulations, with some recent numerical studies addressing intermediate scales \citep{middleton_numerical_2021, mondal_ablation_2019, vreugdenhil_stratification_2019}.
 However, this body of work has not yet matured to setting a new standard for ice-shelf melt parameterization in ocean models.
-The commonly-used ice-shelf melt parameterization today still derives from sea-ice conditions (i.e., in the absence of a slope) with tuning of some parameters for ice-shelf settings \cite{holland_modeling_1999, jenkins_observation_2010, mcphee_dynamics_1987}.
-Thus a knowledge gap exists in bridging IOBL dynamics across scales and characterizing the structure of buoyant plumes.
-Recently, this has been addressed through non-turbulence-resolving 2-d or 2.5-d models \cite{jenkins_simple_2016, jenkins_shear_2021, cheng_modeling_2020}.
-Notably, \citeA{jenkins_shear_2021} found that vertical mixing in IOBL settings was represented poorly by the commonly-used K-Profile Parameterization (KPP) in comparison to a higher-order turbulence closure scheme, suggesting that the application of KPP in ocean models may be inappropriate in ice-shelf cavities.
+Today, the most commonly used ice-shelf melt parameterization still derives from sea-ice conditions (i.e., in the absence of a slope) with some parameters tuned for ice-shelf settings \citep{holland_modeling_1999, jenkins_observation_2010, mcphee_dynamics_1987}.
+A knowledge gap exists in bridging IOBL dynamics across scales and characterizing the structure of buoyant plumes.
+Recently, this has been addressed through non-turbulence-resolving 2-d or 2.5-d models \citep{cheng_modeling_2020, jenkins_simple_2016, jenkins_shear_2021}.
+Notably, \citet{jenkins_shear_2021} found that vertical mixing in IOBL settings was represented poorly by the commonly-used K-Profile Parameterization (KPP) in comparison to a higher-order turbulence closure scheme, suggesting that the application of KPP in ocean models may be inappropriate in ice-shelf cavities.
 
@@
 In this study, we model turbulent heat, salt, and momentum fluxes through the IOBL using Large-Eddy Simulation (LES).
-Whereas ocean models typically used to model sub-ice-shelf circulation cannot capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
+Whereas the ocean models typically used to model sub-ice-shelf circulation lack both the resolution and appropriate parameterizations needed to capture the relevant turbulent scales for boundary layer dynamics, LES captures the dominant energy-containing scales of turbulence and represents smaller, unresolved scales with varying degrees of complexity.
 An effective parameterization of ice-shelf melting is likely to rest on an understanding of how turbulent mixing in the IOBL depends on stratification and shear forcing.
@@
 In this study we focus on the high-shear, low thermal driving regime.
-The target of previous LES studies has been on low-shear settings \cite{vreugdenhil_stratification_2019, middleton_numerical_2021}.
-Section \ref{meth} describes the LES model, its turbulence closure scheme, and the set-up of our simulations.
-Section \ref{results} presents the results of our simulations, with a focus on comparisons across the range of thermal driving and slope given.
-The discussion is given in two parts: Section \ref{disc:dyn} contextualizes the features of our simulated IOBL turbulence and discusses limitations of this study, and Section \ref{disc:prm} focuses on how this study informs parameterizations of ice-shelf melting and IOBL turbulence.
-We provide some closing thoughts in Section \ref{conclusion}.
+The target of previous LES studies has been on low-shear settings \citep{middleton_numerical_2021, vreugdenhil_stratification_2019}.
+Section~\ref{meth} describes the LES model, its turbulence closure scheme, and the set-up of our simulations.
+Section~\ref{results} presents the results of our simulations, with a focus on comparisons across the sampled range of thermal driving and slope.
+The discussion is given in two parts: Section~\ref{disc:dyn} contextualizes the features of our simulated IOBL turbulence and discusses limitations of this study, and Section~\ref{disc:prm} focuses on how this study informs parameterizations of ice-shelf melting and IOBL turbulence.
+We provide some closing thoughts in Section 5.
 
@@
 
-The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover, Germany \cite{raasch_palm-large-eddy_2001}.
-It has been applied to the simulation of atmospheric and ocean boundary layers, but it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
-For this application, our model is a new version based on PALM v5.0 \cite{maronga_parallelized_2015} with added features including a boundary flux scheme for the ice-ocean interface, rotating the gravity vector for sloped domains, and a different turbulence closure scheme.
-Here we provide a brief overview of PALM with a focus on our additions.
-For more details we refer readers to \citeA{maronga_parallelized_2015}.
+The PArallelized Large eddy simulation Model (PALM) was developed at the Institute of Meteorology and Climatology at Leibniz Universitat Hannover, Germany \citep{raasch_palm-large-eddy_2001} for simulation of atmospheric and ocean boundary layers.
+For this application to sub-ice-shelf settings, we developed a new version based on PALM v5.0 \citep{maronga_parallelized_2015} with added features including a boundary flux scheme for the ice-ocean interface, rotating the gravity and Coriolis vectors for sloped domains, and a different turbulence closure scheme.
+Here, we provide a brief overview of PALM with a focus on our additions.
+For more details we refer readers to \citet{maronga_parallelized_2015}.
 
@@
 \begin{align}
-    \textrm{Volume conservation} & &
-        \frac{\partial u_j}{\partial x_j} &= 0\label{eq:volconserv}\\
     \textrm{Momentum conservation} & &
@@
         + \varepsilon_{i3j} f_3 u_{g,j}\nonumber\\
-     &&& \quad + g_i \frac{\rho - \rho_a}{\rho_0} 
+     &&& \quad \, + g_i \frac{\rho - \rho_a}{\rho_0} 
         - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} \nonumber\\
-     &&& \quad - \frac{\partial}{\partial x_j}\left(\overline{u''_i u''_j} 
+     &&& \quad \, - \frac{\partial}{\partial x_j}\left(\overline{u''_i u''_j} 
         - \frac{1}{3}\overline{u''_i u''_i}\delta_{ij}\right) \label{eq:uprog}\\
+    \textrm{Volume conservation} & &
+        \frac{\partial u_j}{\partial x_j} &= 0\label{eq:volconserv}\\
     \textrm{Heat conservation} & &
@@
 
-Detail on the solution of these equations can be found in \cite{maronga_parallelized_2015}.
 The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow using the pressure perturbation $\pi^*$ (imposing incompressibility), and sub-grid scale momentum flux.
+All prognostic variables are considered filtered at the grid scale.
+This is typically denoted by the overbar, which we omit except for the sub-grid turbulent flux terms to emphasize that we only represent averaged effects with a turbulence closure scheme.
 Double primes denote sub-grid fluctuations.
-All prognostic variables are considered filtered at the grid scale.
-This is typically denoted by the overbar, which we omit except for the sub-grid turbulent flux terms to emphasize that we only represent averaged effects.
 
-%\paragraph{}% Sloping surface
-We represent a sloping ice base by rotating the gravity ($\textbf{g}$) and Coriolis ($\textbf{f}$) vectors while keeping the domain a rectangular prism as in \citeA{vreugdenhil_stratification_2019}. 
+We represent a sloping ice base by rotating the gravity ($\vec{g}$) and Coriolis ($\vec{f}$) vectors while keeping the domain a rectangular prism as in \citet{vreugdenhil_stratification_2019}. 
 Specifically, 
-\begin{equation} \label{eq:g}
-	%\textbf{g} = g [sin \alpha,0,cos \alpha]
-	\textbf{g} = g_z [\sin \alpha \sin \beta,\cos \beta,\cos \alpha]
-\end{equation}
-\begin{equation} \label{eq:f}
-    \textbf{f} = 2 \Omega [\sin \phi \sin \alpha,\cos \phi,\sin \phi \cos \alpha]
-\end{equation}
+\begin{align}
+	\vec{g} &= g_z [\sin \alpha \sin \beta, \sin \alpha \cos \beta,\cos \alpha]\label{eq:g}\\
+    \vec{f} &= 2 \Omega [\sin \phi \sin \alpha \sin \beta,\cos \phi \sin \alpha \cos \beta,\sin \phi \cos \alpha]\label{eq:f}
+\end{align}
 where $g_z$ is the magnitude of gravitational acceleration in the geopotential z-direction, $\beta$ is the angle the up-slope direction makes with north, and $\alpha$ is the slope angle from horizontal.
-For the rotated Coriolis parameter $f$, $\Omega$ is the rotation rate and $\phi$ is the latitude.
+For the rotated Coriolis vector $\vec{f}$, $\Omega$ is the rotation rate and $\phi$ is the latitude.
+Unless otherwise specified, quantities are oriented with the simulated grid.
 
-The buoyancy term in Equation \ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density relative to the ambient density of the water column $\rho_a$.
-$\rho_a$ varies along slope and depth from the ice interface as a function of the hydrostatic pressure:
+The buoyancy term in Equation~\ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density relative to the ambient density of the water column $\rho_a$.
+$\rho_a$ varies along slope and with depth from the ice interface as a function of the hydrostatic pressure:
 \begin{equation}
@@
 \end{equation}
-where the superscript $i$ denotes the initial state. The reference density $\rho_0$ is evaluated in the center of the x-y plane ($\rho_0(z) = \rho_a(x_{mid},y_{mid},z)$). 
-%
-%Thus, we assume that the evolution of density in the boundary layer does not significantly affect buoyancy/ice-shelf slope. 
-We neglect hydrostatic pressure gradients along slope, except through the density term $\rho-\rho_a$.
-For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 1 bar m\textsuperscript{-1}.
-% or 10 pa/m
-This simplification has the advantage of avoiding pressure discontinuities across periodic boundary conditions. 
-%We assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes. 
-% \begin{equation}
-%     \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
-%     \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
-% \end{equation}
-%These density differences are verified to be within XX $kg/m^3$ for these simulations.
+where the superscript $i$ denotes the initial state.
+The reference density $\rho_0$ is evaluated in the center of the x-y plane ($\rho_0(z) = \rho_a(x_{mid},y_{mid},z)$).
+We neglect hydrostatic pressure gradients along slope, except through $\rho_a$ in the buoyancy term.
+For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 100\,\unit{Pa\,m^{-1}}.
+This simplification has the advantage of avoiding pressure discontinuities across periodic boundary.
 
@@
 
-The turbulence closure scheme is Anisotropic Minimum Dissipation \cite<AMD;>{rozema_minimum-dissipation_2015} employing the extension to scalars introduced by \citeA{abkar_minimum-dissipation_2016}.
-We validated our implementation against the stable atmospheric boundary layer test case published in \citeA{abkar_large-eddy_2017}.
-Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}).
+The turbulence closure scheme is Anisotropic Minimum Dissipation \cite[AMD;][]{rozema_minimum-dissipation_2015} employing the extension to scalars introduced by \citet{abkar_minimum-dissipation_2016}.
+We validated our implementation against the stable atmospheric boundary layer test case published in \citet{abkar_large-eddy_2017}.
+Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from $10^{-5}$ to $10^{-4}$\,\unit{m^2\,s^{-1}} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}).
 
 Sources and sinks of momentum, heat and salt due to interactions between the flow and the ice base are all parameterized as sub-grid fluxes at the boundary.
-The resolved vertical fluxes at the top layer of the model go to zero as $w$ goes to zero according to the no-flux boundary condition and the sub-grid fluxes are determined using the scheme described below in place of the AMD scheme.
+The resolved vertical fluxes at the top layer of the model go to zero as $w$ goes to zero according to the no-flux boundary condition, and the sub-grid fluxes are determined using the scheme described below in place of the AMD scheme at the top layer.
 PALM is vertically discretized such that the ice boundary ($z=0$) is located at the edge of the top cell where the vertical velocity component resides and scalars and horizontal velocity components are located at mid-depth of the top cell ($z=-\frac{1}{2}\Delta_z$).
@@
 
-Subgrid momentum fluxes are parameterized according to law of the wall following a linear stability function for stabilizing buoyancy forcing as in \citeA{vreugdenhil_stratification_2019}:
+Subgrid momentum fluxes are parameterized according to law of the wall following a linear stability function for stabilizing buoyancy forcing as in \citet{vreugdenhil_stratification_2019}:
 %
 \begin{equation} \label{eq:tau}
-    \overline{w''u_i''}_b = u_* \frac{ \kappa \left[u_i\left(z_{\frac{1}{2}}\right) - u_b \right]}{\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right)-\Psi_m\left(\zeta_{\frac{1}{2}}\right)}
+    \overline{w''u_i''}_b = u_* \frac{ \kappa \left[u_i\left(z_{\frac{1}{2}}\right) - u_{i,b} \right]}{\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right)-\Psi_m\left(\zeta_{\frac{1}{2}}\right)}
 \end{equation}
@@
 $\zeta_k = z_k/L_O$ is the depth from the boundary scaled by the Monin-Obukhov length, $u_*$ is the friction velocity, and $z_0$ is the roughness length.
-The Monin-Obukhov length $L_O$, computed following \citeA{mcphee_dynamics_1987}, is a function of both $u_*$ and the melt rate.
+The horizontal velocity at the boundary $u_{i,b}$ is always 0.
+The Monin-Obukhov length $L_O$, computed following \citet{mcphee_dynamics_1987}, is a function of both $u_*$ and the melt rate.
 The stability function $\Psi_m$ is linear with the scaled depth:
@@
 \end{equation}
-This parameterization assumes that Coriolis forces are not dominant in the momentum balance.
+This parameterization assumes that Coriolis forces are not locally dominant in the momentum balance.
 
-Similarly the sub-grid fluxes of scalars are parameterized by
+Similarly, the sub-grid fluxes of scalars are parameterized by
 \begin{equation} \label{eq:melt_flux}
@@
 %
-where the exchange coefficients are defined following \cite{mcphee_dynamics_1987}:
+where the exchange coefficients are defined following \citet{mcphee_dynamics_1987}:
 \begin{equation} \label{eq:gamma}
@@
     \Gamma_{\theta,turb} = \kappa^{-1} \left[\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right) - \Psi_{\theta}\left(\zeta_{\frac{1}{2}}\right)\right], \:
-    \Gamma_{S,turb} = \kappa^{-1} \left[\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right) - \Psi_S\left(\zeta_{\frac{1}{2}}\right)\right]    % + \Psi(z_0/L_O)) % correction for roughness length
+    \Gamma_{S,turb} = \kappa^{-1} \left[\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right) - \Psi_S\left(\zeta_{\frac{1}{2}}\right)\right]
 \end{equation}
-with analogous stability functions to momentum, Equation \ref{eq:psi}
+with analogous stability functions to momentum, Equation \ref{eq:psi},
 \begin{equation}
@@
     \Psi_{S}(\zeta) = 1 + \beta_{S}\zeta
-%    \Psi_{\theta,S}(\zeta) = 1 + \beta_{\theta,S} \zeta
 \end{equation}
-The coefficients of these stability functions are chosen as in \citeA{zhou_self-similar_2017} and are given in Table \ref{table:var}. The molecular flux component follows \citeA{mcphee_dynamics_1987}:
-\begin{equation}
-    \Gamma_{\theta,mol} = 12.5 \textrm{Pr}^{2/3} - 6, \:
-    \Gamma_{S,mol} = 12.5 \textrm{Sc}^{2/3} - 6
-\end{equation}
-where Pr is the Prandtl number and Sc is the Schmidt number.
-If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($\Gamma_{f}$, Table \ref{table:var}).
+The coefficients of these stability functions are chosen as in \citet{zhou_self-similar_2017} and are given in Table~S1.
+The molecular flux components are constant in our simulations following \citet{mcphee_dynamics_1987} and are also given in Table~S1.
+If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($\Gamma_{f}$, Table~S1).
 
-Taking into account the role of meltwater advection, Equation \ref{eq:melt_flux} is replaced by the following ``virtual'' freshwater flux form in our implementation \cite{jenkins_role_2001, asay-davis_experimental_2016}:
-\begin{eqnarray}
-    \overline{w'\theta'}_{b,v} =& -c_p u_*
+Taking into account the role of meltwater advection, Equation \ref{eq:melt_flux} is replaced by the following ``virtual'' freshwater flux form in our implementation \citep{asay-davis_experimental_2016, jenkins_role_2001}:
+\begin{align}
+    \overline{w''\theta''}_{b} =& -c_p u_*
     \left[\Gamma_{\theta} - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(\theta_b-\theta_{\frac{1}{2}}\right) \label{eq:vflux_heat}\\
-    \overline{w'S'}_{b,v} =& -u_*
+    \overline{w'S'}_{b} =& -u_*
     \left[\Gamma_S - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(S_b-S_{\frac{1}{2}}\right) \label{eq:vflux_salt}
-\end{eqnarray}
+\end{align}
 %
@@
 %
-\begin{eqnarray}
-    \rho c_p \overline{w''\theta''}_{b,v} &=& -\rho_w m L \label{eq:melt_1}\\
-    \rho \overline{w''S''}_{b,v} &=& −\rho_w m S_b \label{eq:melt_2}\\
-    \theta_b &=& \theta_f(p,S_b) \label{eq:melt_3}
-\end{eqnarray}
+\begin{align}
+    \rho c_p \overline{w''\theta''}_{b,v} &= -\rho_w m L \label{eq:melt_1}\\
+    \rho \overline{w''S''}_{b,v} &= −\rho_w m S_b \label{eq:melt_2}\\
+    \theta_b &= \theta_f(p,S_b) \label{eq:melt_3}
+\end{align}
 %
-These equations specify that heat and salt are conserved at the ice-ocean interface (Equations \ref{eq:melt_1} and \ref{eq:melt_2}) and the interface temperature is fixed at the local freezing temperature $\theta_f$ (Equation \ref{eq:melt_3}).
-Equation \ref{eq:melt_1} assumes that the conductive heat flux into ice is negligible.
+These equations specify that heat and salt are conserved at the ice-ocean interface (Equations~\ref{eq:melt_1} and \ref{eq:melt_2}) and the interface temperature is fixed at the local freezing temperature $\theta_f$ (Equation~\ref{eq:melt_3}).
+Equation~\ref{eq:melt_1} assumes that the conductive heat flux into ice is negligible.
 $\rho_w$ denotes the density of freshwater.
-The freezing point is calculated using the polynomial function from \citeA{jackett_algorithms_2006}.
+The freezing point is calculated using the polynomial function from \citet{jackett_algorithms_2006}.
 
 The PALM implementation applies the fluxes $\overline{w''u_i''}_b$, $\overline{w''\theta''}_b$, $\overline{w''S''}_b$ at the center of the first grid cell from the boundary without interpolation (i.e., $\overline{w''X''}_b = \overline{w''X''}_{\frac{1}{2}}$).
-It is noted by the PALM developers that this error was found to be small, but this error has not been evaluated for the sub-ice case.
-This error would be small if the first $\sim$10 cm is largely a constant flux layer, as hypothesized by \citeA{mcphee_turbulent_1983}.
+It is noted by the PALM developers that this error was found to be small, but we have not confirmed this for the sub-ice case.
+This error would be small if the first $\sim$10\,\unit{cm} were largely a constant flux layer, as hypothesized by \citet{mcphee_turbulent_1983}.
 
@@
 
-The domain is a 64 m$^3$ cube with horizontal resolution of 0.5 m and vertical resolution of 0.25 m.
+The domain is a 64 m$^3$ cube with horizontal resolution of 0.5\,\unit{m} and vertical resolution of 0.25\,\unit{m}.
 The ice-ocean interface is located on the top boundary of the domain.
 Large-scale horizontal pressure gradients drive the mean flow, which is geostrophic in the far-field where buoyancy does not modify the flow.
-We choose a pressure of 800 dbar at the top of the domain, an intermediate choice given that the depth of ice shelf bottoms ranges an order of magnitude (roughly -2000 m to -200 m).
-The potentially dynamically relevant differences between conducting these simulations at surface pressure and 800 dbar is that the first derivative of the freezing temperature with respect to salinity is 20\% smaller and the first derivative of density with respect to salinity is about 2 times larger.
+We choose a pressure of 800\,\unit{dbar} at the top of the domain, an intermediate choice given that the depth of ice shelf bottoms ranges an order of magnitude (roughly -2000\,\unit{m} to -200\,\unit{m}).
+The potentially dynamically relevant differences between conducting these simulations at surface pressure and 800\,\unit{dbar} is that the first derivative of the freezing temperature with respect to salinity is 20\% smaller and the first derivative of density with respect to salinity is about 2 times larger.
 
@@
 Boundary conditions for velocity, temperature and salinity are periodic at the side boundaries, Dirichlet at the bottom boundary, and von Neumann at the top boundary.
-The bottom third of the domain is a sponge layer (Rayleigh damping) within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain \cite{klemp_numerical_1978, maronga_parallelized_2015}.
+The bottom third of the domain is a sponge layer (Rayleigh damping) within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain \citep{klemp_numerical_1978, maronga_parallelized_2015}.
 The sponge layer results in negligible vertical fluxes of heat, salt, or momentum across the bottom boundary because scalar and velocity gradients go to 0.
 The von Neumann boundary conditions at the top of the domain correspond to the sub-grid fluxes of heat, salt and momentum (Equations~\ref{eq:tau}, \ref{eq:vflux_heat}, and \ref{eq:vflux_salt}), as resolved fluxes go to zero at a no-penetration boundary.
-The roughness length ($z_0$ in Equations~\ref{eq:tau} and \ref{eq:gamma_turb}) is chosen such that the equivalent drag coefficient assuming quadratic drag is 0.003, an intermediate value for sea ice and ice shelf bottoms, though poorly constrained \cite{holland_modeling_1999, holland_effects_2006, macayeal_numerical_1984, nicholls_measurements_2006}.
-A list of parameter choices can be found in Table~\ref{table:var}.
+The roughness length ($z_0$ in Equations~\ref{eq:tau} and \ref{eq:gamma_turb}) is chosen such that the equivalent drag coefficient assuming quadratic drag is 0.003, an intermediate value for sea ice and ice shelf bottoms, though poorly constrained \citep{holland_modeling_1999, holland_effects_2006, macayeal_numerical_1984, nicholls_measurements_2006}.
+A list of parameter choices can be found in Table~S1.
 
 We present two sets of simulations which have a base case in common.
-The base case has low far-field thermal driving of 0.15$^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field inertial oscillations of 20 cm s\textsuperscript{-1} generated by a 0.03 Pa m\textsuperscript{-1} pressure gradient.
-These conditions were chosen to favor an energetic regime, for reasons discussed in Section \ref{disc:dyn}.
-To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.15$^{\circ}$C to 0.6$^{\circ}$C in the first set of simulations.
-Far-field thermal driving $\Delta \theta_\infty$ is defined as $\theta_{\infty} - \theta_f(S_{\infty})$.
-In the second set of simulations, we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.
-The ice base always slopes to the east in the positive x-dimension of our domain, thus $\beta = 0$.
-The far-field salinity for all runs is 35 g kg\textsuperscript{-1}.
+The base case has low far-field thermal driving of 0.15\unit{^{\circ}C} and a relatively high slope for Antarctic ice shelves of 1\unit{^{\circ}} and vigorous far-field inertial oscillations of 20\,\unit{cm\,s^{-1}} generated by a 0.03\,\unit{Pa\,m^{-1}} pressure gradient.
+These conditions were chosen to favor an energetic regime, for reasons discussed in Section~\ref{disc:dyn}.
+To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.15\unit{^{\circ}C} to 0.6\unit{^{\circ}C} in the first set of simulations.
+The far-field thermal driving, $\Delta \theta_\infty$, is defined as the difference between the far-field temperature ($\theta_{\infty}$) and the freezing temperature based on the far-field salinity ($\theta_f(S_{\infty})$).
+In the second set of simulations, we reduce the slope from 1\unit{^{\circ}} to 0.01\unit{^{\circ}}.
+The ice base always slopes to the east in the positive x-dimension of our domain, thus $\beta = 90$\unit{^{\circ}}.
+The far-field salinity for all runs is 35\,\unit{g\,kg^{-1}}.
 Initially, both temperature and salinity increase with depth over the upper two-thirds of the domain.
@@
 
-The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h.
+The simulation duration is 50\,\unit{h}, corresponding to $\sim$4 inertial periods of 13\,\unit{h}.
 By the end of our simulations, the time-mean kinetic energy of the flow has reached steady-state.
-However, the turbulent intensity for all cases continues to decline, with more pronounced turbulence kinetic energy (TKE) loss at lower slopes (Figure \ref{fig:timeseries}a,d).
-Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.
+However, the turbulent intensity for all cases continues to decline, with more pronounced turbulence kinetic energy (TKE) loss at lower slopes (Figure~\ref{fig:timeseries}a,d).
+Unless stated otherwise, the results are presented as averages over the last simulated inertial period and over the domain excluding the sponge layer.
 
-We compute an effective thermal exchange coefficient that differs from that employed by the sub-grid scheme to represent the efficiency of heat exchange that may need to be represented to produce accurate melt rates in a model that does not have the vertical resolution or sophisticated turbulence closure that we employ here.
-This derived thermal exchange coefficient, $\Gamma_{T,der}$, can be computed using Equations~\ref{eq:melt_flux} and \ref{eq:melt_1} from the simulated melt rate and ocean properties at any depth rather than $z_{\frac{1}{2}}$.
-We substitute the friction velocity computed by Equation~\ref{eq:tau} with one computed using a quadratic drag law from the velocity at $z < z_{\frac{1}{2}}$ and the applied drag coefficient, consistent with modeled drag implementations.
-
-\input{table1_prm-only}
+We compute an effective thermal exchange coefficient that differs from that employed by the sub-grid scheme to represent the efficiency of heat exchange that may need to be represented to produce accurate melt rates in an ocean model that does not have the vertical resolution or sophisticated turbulence closure that we employ here.
+This derived thermal exchange coefficient, $\Gamma_{T,der}$, can be computed using Equations~\ref{eq:melt_flux} and \ref{eq:melt_1} from the simulated melt rate and ocean properties at any depth below $z_{\frac{1}{2}}$, here chosen at -2\,\unit{m}.
+We substitute the friction velocity computed by Equation~\ref{eq:tau} with one computed using a quadratic drag law from the velocity simulated 2\,\unit{m} below the boundary and the applied drag coefficient, consistent with drag implementations in coarse-resolution ocean models.
 
@@
 % Description of time evolution
-Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs.
+Melt rates decline over the course of the simulations (Figure~\ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs.
 This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations.
-We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
-Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
-Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE loss (Figure S1d).
+We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we could computationally afford.
+Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes by at least a factor of two, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure~S1).
+Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE has been lost ($\leq\!0.1$\unit{^{\circ}C} slopes, Figure~S1d).
 
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/tke_cmp_dT_t.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_cmp_dT_t.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/us_cmp_dT_t.png}
-    \end{minipage}
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/tke_cmp_dslope_t.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_cmp_dslope_t.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/us_cmp_dslope_t.png}
-    \end{minipage}
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig1.pdf}
 \caption{Time evolution of (a,d) domain-averaged, resolved turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
-The black curve represents the same simulation in all panels.
-The time axis excludes the initial spin-up period.
-}
-    % Consider shading the analysis window
-    % TODO add panel labels
+The black curve represents the same simulation in all panels in this and subsequent figures.
+The analysis window, the last inertial period, is shaded.}
 \label{fig:timeseries}
-\end{figure}
-
-We present depth-profiles of temperature, salinity, and velocity at the end of all simulations; Figure \ref{fig:dT_profiles} shows the results from the simulations in which we varied thermal driving, while Figure \ref{fig:dslope_profiles} shows those from the simulations with varying slope.
-All simulations show an evolution from the weakly stratified initial conditions to more strongly stratified conditions, particularly within the first 5 m of the ice-ocean interface (Figures \ref{fig:dT_profiles}b, \ref{fig:dslope_profiles}b).
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/pt_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/sa_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period.
-(a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components.
-For panel (c), solid lines are in the y direction (positive north), dashed in x-direction (positive east, up-slope).}
-    \label{fig:dT_profiles}
-    % TODO add panel labels
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/pt_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/sa_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.33\textwidth}
-        \includegraphics[trim={0 0cm 0 0},clip, width=\textwidth]{Figures/velocity_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \caption{Depth profiles of simulated properties as they vary with slope, averaged over the last inertial period.
-(a) temperature relative to far-field temperature (b) salinity relative to far-field salinity (c) velocity components.
-For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).
-The black curve is common to both sets of simulations (see Figure \ref{fig:dT_profiles}).}
-    \label{fig:dslope_profiles}
-    % TODO add panel labels
-\end{figure}
+\end{figure*}
 
 % Description of velocity profiles
+We present depth-profiles of temperature, salinity, and velocity at the end of all simulations (Figure \ref{fig:dT_profiles}).
+The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c,f removes a periodic signal from inertial oscillations of the geostrophic velocity with a characteristic magnitude of 20\,\unit{cm\,s^{-1}}.
 Ekman rotation near the boundary can be seen in all simulations (Figs.
-\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c), but for more strongly sloped runs, buoyancy plays an increasingly strong role in driving the mean flow near the boundary.
-This effect can be seen most clearly by comparing the up-slope component of the flow within several meters of the ice-ocean interface across the slope-varying simulations (Figure \ref{fig:dslope_profiles}c).
-These mean buoyancy effects increase flow velocities on the order of a few cm s\textsuperscript{-1} as slope varies from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:dslope_profiles}c).
-Flow velocities near the boundary increase on the order of 10 cm s\textsuperscript{-1} as far-field thermal driving increases from 0.5 to 0.6$^{\circ}$C at 1$^{\circ}$ slope (Figure \ref{fig:dT_profiles}c).
-This velocity increase is attributed to changes in the magnitude of buoyancy forcing at the boundary, related to differences in melt rates.
-The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c integrates inertial oscillations of the geostrophic velocity with a characteristic magnitude of 20 cm s\textsuperscript{-1}.
+\ref{fig:dT_profiles}c,f), but for more strongly sloped runs, buoyancy plays an increasingly strong role in driving the mean flow near the boundary.
+This effect can be seen most clearly by comparing the up-slope component of the flow within several meters of the ice-ocean interface across the slope-varying simulations (Figure \ref{fig:dT_profiles}f).
+These mean buoyancy effects increase flow velocities on the order of a few \unit{cm\,s^{-1}} as slope varies from 0.01\unit{^{\circ}} to 1\unit{^{\circ}}.
+Flow velocities near the boundary increase on the order of 10\,\unit{cm\,s^{-1}} as far-field thermal driving increases from 0.5 to 0.6\unit{^{\circ}C} at 1\unit{^{\circ}} slope (Figure \ref{fig:dT_profiles}c).
+This velocity increase is attributed to changes in the magnitude of buoyancy forcing near the boundary, related to differences in melt rates.
+The vertical momentum flux profiles shown in Figure~\ref{fig:flux_profiles}a,c reveal that flow is accelerated (negative fluxes) over much of the IOBL, with drag dominating only within the first few meters below the boundary.
 
-% BL depth
-In none of the simulations do we observe a well-mixed the boundary layer well-mixed with respect to scalars, with varying degrees of stratification over the first 20 m from the boundary.
-Thus, we characterize the IOBL using a definition of the mixing layer depth as depth at which the dissipation rate drops below 10\textsuperscript{-9} m\textsuperscript{2} s\textsuperscript{-3} \cite{franks_has_2014, sutherland_mixed_2014}.
-Since shear is the primary source of TKE as discussed later in this section, the IOBL here can also be thought of as portion of the water column where shear originating at the boundary influences the flow.
-The boundary layer depth increases through time, reaching 15 -- 25 m at the end of the simulations.
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig2.pdf}
+\caption{Depth profiles of simulated properties as they vary with (a-c) thermal driving and (d-f) slope, averaged over the last inertial period.
+(a,d) temperature relative to far-field temperature, (b,e) salinity relative to far-field salinity, and (c,f) velocity in the y-direction (solid line, positive north, cross-slope) and in x-direction (dashed line, positive east, up-slope).
+}
+\label{fig:dT_profiles}
+\end{figure*}
 
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig3.pdf}
+\caption{Vertical profiles of (a,c) momentum flux, (b,e) heat flux, and (c,f) scaled heat flux averaged over the last inertial period.
+The first row shows temperature cases, the second row shows slope cases.
+Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).
+Positive flux denotes upward flux (i.e., drag).
+The horizontal axis limits vary between panels.}
+\label{fig:flux_profiles}
+\end{figure*}
+
+All simulations show an evolution from the weakly stratified initial conditions to more strongly stratified conditions, particularly within the first 5\,\unit{m} of the ice-ocean interface (Figures \ref{fig:dT_profiles}b,e).
+In none of the simulations do we observe a well-mixed boundary layer with respect to scalars.
+Rather, the simulations show varying degrees of stratification over the first 20\,\unit{m} from the boundary.
 Stratification within the boundary layer increases with thermal driving (Figure~\ref{fig:dT_profiles}a,b).
-Thus, the increase in melt-induced buoyancy fluxes with thermal driving dominates over the increase in shear induced by the buoyant flow.
+Thus, the effect on stratification of the increase in melt-induced buoyancy fluxes with thermal driving dominates over the increase in shear induced by the buoyant flow.
 Conversely, stratification decreases with increasing slope, indicating that the increase in shear induced by the buoyant flow dominates over the increase in melt-induced buoyancy fluxes with slope.
-The simulated boundary layer depth has a strong relationship with local thermal driving (i.e., the difference between IOBL temperature and the freezing point), reflecting entrainment of warm water below and setting mixing lengthscales  within the IOBL.
 
 % TKE budget, shear
-Shear production of turbulence dominates the TKE budget. The evolution of resolved TKE can be described by three source terms and dissipation:
-\[
+Shear production of turbulence dominates the TKE budget. The evolution of TKE can be described by three source terms and dissipation:
+\begin{equation}\label{eq:tke}\textrm{\[
     \frac{de}{dt} = 
@@
         \underbrace{
-            \frac{g_z}{\rho}\overline{\rho^{\prime}w^{\prime}}        -\frac{g_x}{\rho}\overline{\rho^{\prime}u^{\prime}}}
+            \frac{g_3}{\rho}\overline{\rho^{\prime}w^{\prime}}        -\frac{g_1}{\rho}\overline{\rho^{\prime}u^{\prime}}}
         _{F_{buoy}} + 
@@
         _{F_{trans}} -
-        \hspace{-2mm}\underbrace{\frac{}{}\vareps}_{diss}
-\]
+        \hspace{-2mm}\underbrace{\frac{}{}\varepsilon}_{diss}
+\]}\raisetag{24pt}
+\end{equation}
 
-Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure S2 and shows similar patterns.
-Shear production ($F_{shear}$) ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$ m\textsuperscript{2} s\textsuperscript{-3} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5 m of the boundary (Figure \ref{fig:tke_budget}a).
+Here, we characterize the evolution of resolved TKE and primes designate resolved fluctuations.
+Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure~S2 and shows similar patterns.
+Shear production ($F_{shear}$) ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$\,\unit{m^2\,s^{-3}} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5\,\unit{m} of the boundary (Figure \ref{fig:tke_budget}a).
 The increase in TKE throughout the boundary layer as slope increases reflects this shear-induced turbulence (Figure \ref{fig:tke_budget}a).
@@
 % TKE budget, buoyancy
-Buoyancy production of turbulence ($F_{buoy}$) is 1 -- 2 orders of magnitude smaller than shear production, $\sim\!10^{-10} \textrm{--} 10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}.
-For a sloped ice shelf, the buoyancy term can be broken into two components, the horizontal buoyancy fluxes that increase turbulence when these fluxes are oriented upslope and the vertical buoyancy fluxes that decrease turbulence when ice is melting.
-Since our simulations only produce melting, the vertical component is always negative (dashed lines, Figure \ref{fig:tke_budget}b).
+Buoyancy production of turbulence ($F_{buoy}$) is 1 -- 2 orders of magnitude smaller than shear production, $\sim\!10^{-10} \textrm{--} 10^{-9}$\,\unit{m^2\,s^{-3}}.
+For a sloped ice shelf, the buoyancy term can be broken into two components, the horizontal buoyancy fluxes that increase turbulence when these fluxes are oriented upslope and the vertical buoyancy fluxes that decrease turbulence when ice is melting (Equation \ref{eq:tke}).
+Since our simulations only produce melting, the vertical component is always negative (dashed lines, Figure \ref{fig:tke_budget}c).
 Over the coarse of an inertial oscillation, the horizontal component of buoyancy production is generally positive when the mean flow is oriented upslope and negative when the the flow is oriented downslope.
-Interestingly, the time-averaged effect of a slope is destruction of turbulence near the boundary and production of turbulence near the base of the boundary layer (dotted lines, Figure \ref{fig:tke_budget}b).
+Interestingly, the time-averaged effect of a slope is destruction of turbulence near the boundary and production of turbulence near the base of the boundary layer (dotted lines, Figure \ref{fig:tke_budget}c).
 The net effect of both horizontal and vertical buoyancy components is the destruction of turbulence throughout the IOBL (solid lines, Figure \ref{fig:tke_budget}b), with the exception of the base of the IOBL where the horizontal buoyancy component augments entrainment.
@@
 The transport term ($F_{trans}$) contains two components, advection of TKE due to pressure fluctuations and turbulent advection of TKE.
-The former is negligible, reaching maximum values on the order of $10^{-12}$ m\textsuperscript{2} s\textsuperscript{-3} while the latter increases turbulence at the boundary with oscillations of decreasing amplitude with distance from the boundary (Figure \ref{fig:tke_budget}c).
+The former is negligible, reaching maximum values on the order of $10^{-12}$\,\unit{m^2\,s^{-3}} while the latter increases turbulence at the boundary with oscillations of decreasing amplitude with distance from the boundary (Figure \ref{fig:tke_budget}d).
 
@@
 Dissipation ($diss$), the remaining term in the TKE budget, can be inferred from the remainder of these terms and the rate of change of TKE.
-Since we evaluate resolved TKE ($e$), dissipation here represents the transfer of energy to the sub-grid scales; there is no flow of energy from sub-grid to resolved scales.
-In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$ m\textsuperscript{2} s\textsuperscript{-3} as seen in Figure \ref{fig:timeseries}a,c.
-Dissipation in the IOBL is on the same order as shear production ($10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}), as all other terms in the TKE budget are small.
+Since we evaluate resolved TKE ($e$), dissipation here represents the transfer of energy to the sub-grid scales; there is no flow of energy from sub-grid to resolved scales in the turbulence closure scheme.
+In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$\,\unit{m^2\,s^{-3}} as seen in Figure \ref{fig:timeseries}a,c.
+Dissipation in the IOBL is on the same order as shear production ($10^{-9}$\,\unit{m^2\,s^{-3}}), as all other terms in the TKE budget are small.
 
-\begin{figure}
-    \centering
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
-    \end{minipage}
-    \newline
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \caption{(a) Simulated turbulence kinetic energy (TKE) for variable slope simulations averaged over the last inertial period and (b-d) TKE source terms over the same period.
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig4.pdf}
+\caption{(a) Simulated turbulence kinetic energy (TKE) and (b-d) TKE source terms for variable slope simulations averaged over the last inertial period.
 (b) Shear production.
-(c) Buoyancy production.
-The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted.
+(c) Buoyancy production: total (solid lines), vertical component (dashed), and upslope component (dotted).
 (d) TKE transport.
-Positive denotes production, negative destruction.
+Positive denotes production, negative destruction of TKE.
 Note that the x-axis scales differ between panels.}
 \label{fig:tke_budget}
-    % TODO add panel labels
-\end{figure}
+\end{figure*}
 
@@
 To demonstrate the simulated turbulent structures in this regime, we present horizontal and vertical cross-sectional  snapshots through the domain for the two slope end-members in Figure \ref{fig:cross-section}.
-Turbulent structures within the IOBL are consistent with propagating Holmboe shear instabilities under stable stratification \cite{carpenter_identifying_2010}.
+Turbulent structures within the IOBL are consistent with propagating Holmboe shear instabilities under stable stratification \citep{carpenter_identifying_2010}.
 Shear is stronger within the IOBL than at the base of the IOBL due to the concentration of buoyant plume flow near the top of the IOBL.
-Consequently, the amplitude of these structures increases near the boundary for the more strongly-sloped simulations (Figures \ref{fig:cross-section}b,d).
-The difference in IOBL turbulence with slope is perhaps best seen in the turbulent structures at 1 m from the ice-ocean interface (Figure \ref{fig:cross-section}e,f).
-The structures become increasingly filamentous (i.e., near-wall streaks, e.g., \citeA{del_alamo_spectra_2003, hoyas_scaling_2006}) and coherent as slope and thus the buoyancy-driven current increase.
-Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases;  velocity fluctuations are less confined to the slope-parallel direction (Figure S3).
-% consider discussing entrainment here
+Consequently, the amplitude of these structures increases near the boundary for the more strongly-sloped simulations (Figures \ref{fig:cross-section}).
+The difference in IOBL turbulence with slope is perhaps best seen in the turbulent structures at 1\,\unit{m} from the ice-ocean interface (Figure \ref{fig:cross-section}e,f).
+The structures become increasingly filamentous (i.e., near-wall streaks, e.g., \citet{del_alamo_spectra_2003, hoyas_scaling_2006}) and coherent as slope and thus the velocity of the buoyancy-driven current increase.
+Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases; velocity fluctuations are less confined to the slope-parallel direction (Figure~S3).
 
-\begin{figure}[]
-    \centering
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[trim={1cm 0 3cm 0},clip,width=\textwidth]{Figures/pt_slope01_xz_y64_zmax42_t40.png}
-    \end{minipage}%
-    \begin{minipage}{0.55\textwidth}
-        \includegraphics[trim={1.5cm 0 0.5cm 0},clip,width=\textwidth]{Figures/pt_slope1_xz_y64_zmax42_t40.png}
-    \end{minipage}
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[trim={1cm 0 3cm 0}, clip, width=\textwidth]{Figures/sa_slope01_xz_y64_zmax42_t40.png}
-    \end{minipage}%
-    \begin{minipage}{0.55\textwidth}
-        \includegraphics[trim={1.5cm 0 0.5cm 0}, clip, width=\textwidth]{Figures/sa_slope1_xz_y64_zmax42_t40.png}
-    \end{minipage}
-    \begin{minipage}{0.45\textwidth}
-        \includegraphics[trim={1.5cm 0 3.4cm 0},clip,width=\textwidth]{Figures/v_slope01_xy_z1_zmax1_t40.png}
-    \end{minipage}%
-    \begin{minipage}{0.6\textwidth}
-        \centering
-        \includegraphics[trim={2cm 0 0.5cm 0},clip,width=\textwidth]{Figures/v_slope1_xy_z1_zmax1_t40.png}
-    \end{minipage}%
-    \begin{minipage}{0.05\textwidth}
-    \hfill
-    \end{minipage}
-    \caption{Instantaneous flow structures observed at 40h in (a,c,e) 0.01$^{\circ}$ slope case and (b,d,f) 1$^{\circ}$ slope case.
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig5.pdf}
+\caption{Instantaneous flow structures observed at 40h in (a,c,e) 0.01\unit{^{\circ}} slope case and (b,d,f) 1\unit{^{\circ}} slope case.
 (a,b) Temperature in cross section mid-way through the y-axis.
 (c,d) Salinity in cross-section mid-way through the y-axis.
-(e,f) Cross-slope velocity fluctuations at 1 m below the ice-ocean interface.
-Note that the colorbar scale is smaller in (e) than (f).}
-    % TODO add panel labels
+(e,f) Resolved cross-slope velocity fluctuations at 1\,\unit{m} below the ice-ocean interface.}
 \label{fig:cross-section}
-\end{figure}
+\end{figure*}
+
+% BL depth
+We define the base of the IOBL as the depth where the thermal driving relative to the far-field freezing point is 99\% of the far-field thermal driving.
+The IOBL depth increases through time, reaching 13 -- 19\,\unit{m} at the end of the simulations.
+The simulated boundary layer depth increases with the far-field thermal driving (from 13 to 19\,\unit{m}) and with ice-shelf basal slope (from 15 to 19\,\unit{m}), reflecting the increase in flow velocities across those parameter changes which drives entrainment into the IOBL.
+Figure \ref{fig:intermittency} shows the temporal evolution of IOBL depth for a few simulations, with steady IOBL growth at low slopes and punctuated growth at higher slopes corresponding to trends in TKE.
+
+Given the temporal variability in TKE in these simulations, we use a threshold in dissipation rate to characterize the mixing layer depth, as distinct from the mixed layer depth.
+This criterion has been deployed for stratifying ocean boundary layers \citep{franks_has_2015, sutherland_mixed_2014}.
+We consider the mixing layer as the depth interval over which the horizontal- and hourly-averaged dissipation rate exceeds $10^{-9}$\,\unit{m^2\,s^{-3}}.
+This mixing layer depth shows greater temporal variability than the IOBL depth as defined by scalar concentration, and drops below that IOBL depth during periods of enhanced entrainment (Figure \ref{fig:intermittency}).
+
+There are also time periods over which the dissipation rate drops below $10^{-9}$\,\unit{m^2\,s^{-3}} throughout the water column, indicating intermittency in turbulence.
+We note that these intervals of low dissipation do not correspond to complete loss of TKE, nor a shoaling of the IOBL depth as we have defined it (Figure \ref{fig:intermittency}).
+At higher slopes ($\geq 0.5^{\circ}$), this intermittency is interrupted as inertial oscillations enhance up-slope IOBL flow, increasing shear-driven mixing.
+This mixing front begins at the boundary and propagates to the base of the IOBL over a few hours (Figure \ref{fig:intermittency}b).
+For the less stratified, low-slope cases, the intermittency in turbulence is more frequent, as the IOBL flows more slowly and generates less TKE production by shear (Figure \ref{fig:intermittency}a).
+We discuss this intermittency and its possible implications further in Section \ref{disc:dyn}.
+
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig6.pdf}
+\caption{Horizontally-averaged turbulence characteristics for (a) 0.1\unit{^{\circ}C} thermal driving, 0.01\unit{^{\circ}} slope case and (b) 0.6\unit{^{\circ}C} thermal driving, 1\unit{^{\circ}} slope case.
+Turbulence is considered intermittent when the dissipation contour of $10^{-9}$\,\unit{m^2\,s^{-3}} (dashed line) reaches the boundary.
+Significant turbulence kinetic energy (TKE, green-yellow shading) can be present when dissipation is low.
+Higher TKE at -25\,\unit{m} at later times in (a) is due to turbulent transport, while the higher TKE at later times in (b) is due to shear production.
+IOBL depth is contoured in black.
+}
+\label{fig:intermittency}
+\end{figure*}
 
@@
 The dominant temporal frequency in melt rate is the inertial frequency, and the melt response to those oscillations is highly nonlinear.
-Maximum melt rates occur when the mean flow is oriented between the up-slope direction and the Coriolis-favored direction, and minimum melt rates roughly 180$^{\circ}$ opposed to that.
+Maximum melt rates occur when the mean flow is oriented between the up-slope direction and the Coriolis-favored direction, and minimum melt rates roughly 180\unit{^{\circ}} opposed to that.
 These melt rate fluctuations correspond to fluctuations in TKE which are reflected in the friction velocity shown in Figure \ref{fig:timeseries}b.
@@
 During low-melt periods, the far-field flow is oriented down-slope and shear production of TKE is concentrated a few meters away from the boundary.
-
-% intermittent turbulence
 Melt rate fluctuations increase in amplitude as thermal driving increases and as slope increases, which we attribute to the increasing importance of buoyancy forcing in driving a near-boundary plume and thus determining the depth-distribution of shear.
-At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the IOBL over a few hours (Figure \ref{fig:intermittency}b).
-The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a dramatic reduction in vertical velocity fluctuations during the down-slope flow period.
-This can be seen in the time series of friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b).
-In all simulations, there is periodic intermittency in turbulence below the IOBL interrupted by the penetration of shear-induced turbulence when the IOBL buoyantly accelerates.
-We discuss these rotational effects on turbulent intensity further in Section \ref{disc:dyn}.
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/e_hovmoller.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/e_hovmoller.png}
-    \end{minipage}
-    \caption{Example of turbulent intermittency as seen in white regions of turbulence kinetic energy (TKE).
-(a) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
-(b) An intermittent case: 0.6$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
-    \label{fig:intermittency}
-    % TODO add panel labels, add IOBL contour
-\end{figure}
+The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a dramatic reduction in melt rates during the down-slope flow period.
+This coincides with reduced friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b) and reduced vertical velocity fluctuations (not shown).
 
 % Melt rate sensitivity to thermal driving
-Time-averaged melt rates depend fairly linearly on far-field thermal driving (Figure \ref{fig:melt_sensitivity}a).
+Time-averaged melt rates depend fairly linearly on far-field thermal driving (Figure \ref{fig:melt_sensitivity}a, $R^2=0.97$).
 This is mostly attributable to a linear relationship between melt rate and interfacial thermal driving, as differences in friction velocity and the thermal exchange coefficient are small and do not have a systematic relationship with far-field thermal driving.
-On the other hand, the derived, time-averaged thermal exchange coefficient representing the efficiency of heat exchange from -2 m depth to the ice base ($\Gamma_{T,der}$) does have a weakly negative relationship with far-field thermal driving (Figure \ref{fig:melt_sensitivity}c).
+On the other hand, the derived, time-averaged thermal exchange coefficient representing the efficiency of heat exchange from -2\,\unit{m} depth to the ice base ($\Gamma_{T,der}$) does have a weakly negative relationship with far-field thermal driving (Figure \ref{fig:melt_sensitivity}c).
 This indicates a decrease in the efficiency of heat exchange with increasing near-interface stratification.
@@
 
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_dT_cmp_dT_43h_tav13h.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/melt_slope_cmp_dslope_43h_tav13h.png}
-    \end{minipage}
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0cm},clip,width=\textwidth]{Figures/gammaT_dT_cmp_dT_43h_tav13h.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0cm},clip,width=\textwidth]{Figures/gammaT_us_cmp_dslope_43h_tav13h.png}
-    \end{minipage}
+\begin{figure*}[t]
+\includegraphics[width=12cm]{fig7.pdf}
 \caption{Melt rate sensitivity to (a) far-field thermal driving and (b) sine of the basal slope.
-(c,d) Key controls on the value of the thermal exchange coefficient ($\Gamma_{T,der}$) that would accurately predict melt rates given accurate measurements of velocity and temperature 2 m from the ice base.
 (c) Far-field thermal driving is inversely related to $\Gamma_{T,der}$.
-Dashed line denotes the value recommended by \citeA{jenkins_observation_2010}.
-The largest points correspond to the fourth and last inertial cycle with progressively smaller points for previous inertial cycles.
+Dashed line denotes the value recommended by \citet{jenkins_observation_2010}.
+The largest points correspond to the fourth inertial cycle with progressively smaller points for previous inertial cycles.
 (d) For variations in slope, the simulated friction velocity (solid points) is linearly related to $\Gamma_{T,der}$.
@@
 Note the difference in y-axis limits from (c).
-The 0.01$^{\circ}$ and 0.1$^{\circ}$ slope cases are overlapping.}
+The 0.01\unit{^{\circ}} and 0.1\unit{^{\circ}} slope cases are overlapping.}
 \label{fig:melt_sensitivity}
-    % TODO add panel labels
-\end{figure}
+\end{figure*}
 
 % Melt sensitivity to slope
-There is also a linear relationship between melt rate and ice-shelf basal slope, with threshold-like behavior at slopes less than 0.01$^{\circ}$.
+There is also a linear relationship between melt rate and ice-shelf basal slope, with threshold-like behavior at slopes less than 0.01\unit{^{\circ}}.
 This linear relationship is due primarily to a linear relationship between friction velocity and melt rate while there is a smaller ($\sim\!1/3$ size) opposite effect from decreasing interfacial thermal driving with increasing slope (not shown).
 These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes.
-We observe threshold behavior in melting in the two lowest-slope cases, can be attributed to similar friction velocities arising from similar IOBL velocities and turbulence (Figure \ref{fig:melt_sensitivity}d and Figure \ref{fig:dslope_profiles}c,d).
+We observe threshold behavior in melting in the two lowest-slope cases, which can be attributed to similar friction velocities arising from similar IOBL velocities and turbulence (Figure \ref{fig:melt_sensitivity}d and Figure \ref{fig:dT_profiles}f).
 This behavior is discussed in more detail in Section \ref{disc:prm_sens}.
-The differences in derived thermal exchange coefficient are not pronounced as slope varies, on the order of a 10\% change as slope increases from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:melt_sensitivity}d).
+The differences in derived thermal exchange coefficient with varying slope are on the order of a 40\% change as slope increases from 0.01\unit{^{\circ}} to 1\unit{^{\circ}} (Figure \ref{fig:melt_sensitivity}d).
 
-Vertical scalar fluxes are shown in Figure \ref{fig:heatflux_profiles}a,b.
+Vertical heat fluxes are shown in Figure \ref{fig:flux_profiles}b,e.
 The vertical heat flux has a maximum at the ice-ocean interface and decreases throughout the IOBL, with small values below the pycnocline.
-Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure S4).
-The vertical salt flux profiles are shown in Figure S5 and have a very similar shape to the vertical heat flux profiles.
+Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure~S4).
+The vertical salt flux profiles are shown in Figure~S5 and have a very similar shape to the vertical heat flux profiles.
 
@@
 \begin{equation}
-    \overline{w'\mathbf{u}'} = K_e d\mathbf{u}/dz
+    \overline{w'\vec{u}'} = K_e d\vec{u}/dz
 \end{equation}
@@
 The linear scaling of melt rate with thermal driving suggests a linear scaling of heat flux profiles with thermal driving.
-We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (Figure \ref{fig:timeseries}c, \ref{fig:heatflux_profiles}c,  pink curves).
-The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:heatflux_profiles}c).
-Scalar fluxes decline near the boundary for the 1$^{\circ}$ slope cases, a feature that we discuss further in Section \ref{disc:prm_vmix}.
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_dTscale_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_slopescale_z_profile.png}
-    \end{minipage}
-    \caption{Vertical profile of heat flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases.
-(a,b) are in physical units while (c,d) are scaled by the Ekman depth, far-field thermal driving, and slope.
-The black curve is represents the same simulation in all panels.
-The horizontal axis limits vary between panels.}
-    \label{fig:heatflux_profiles}
-    % TODO add panel labels
-\end{figure}
+We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (pink curves in Figures \ref{fig:timeseries}c, \ref{fig:flux_profiles}c).
+The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:flux_profiles}c).
+Scalar fluxes decline near the boundary for the 1\unit{^{\circ}} slope cases, a feature that we discuss further in Section \ref{disc:prm_vmix}.
 
 % Scaling heat flux profiles with slope
-Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($(\sin\alpha)^{1/4}$, Figure \ref{fig:heatflux_profiles}d).
+Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($(\sin\alpha)^{1/4}$, Figure \ref{fig:flux_profiles}f).
 There is strong agreement between the scaled vertical heat flux profiles at different slopes, though the threshold behavior at low slopes noted in melt rates is replicated here.
@@
 This may be due to the depth-variable shear induced by buoyancy which is not reflected in the depth-mean IOBL eddy viscosity used to compute the Ekman depth.
-Our study was not designed to evaluate IOBL entrainment, which would be better explored by varying the level of background stratification, so we devote no further attention to it here.
-We discuss scaling of vertical fluxes and the possibility of their parameterization in Section \ref{disc:prm_vmix}.
-
-% momentum flux profiles
-By looking at the variation of momentum flux with depth shown in Figure \ref{fig:momflux_profiles}, we can examine the relative contributions of interfacial drag and buoyant acceleration of the IOBL to the velocity profiles shown in Figure \ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c.
-Since the mean velocity is oriented both upslope (+$u$) and cross-slope (+$v$), positive $\overline{u'w'}$ and $\overline{v'w'}$ close to the interface indicate slowing of the current due to drag whereas negative $\overline{u'w'}$ and $\overline{v'w'}$ a few m below the interface through much of the boundary layer indicate buoyant acceleration of the IOBL.
-The amplitude of momentum fluxes increases with slope and thermal driving consistent with increases in IOBL velocity and TKE.
-
-\begin{figure}[h!]
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \caption{Momentum flux averaged over the last inertial period for (a) thermal driving cases and (b) slope cases.
-Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).
-Positive flux denotes upward flux (i.e., drag) and }
-    \label{fig:momflux_profiles}
-    % TODO add panel labels
-\end{figure}
+We discuss the scaling of vertical fluxes and the possibility of their parameterization in Section \ref{disc:prm_vmix}.
 
@@
 
-In the simulations presented here, turbulence declines throughout the course of the simulation; for a few highly stratified cases becoming intermittent.
-The relationship between stable stratification, shear, and the persistence of turbulence remains an open question \cite{zonta_stably_2018}.
+In the simulations presented here, turbulence declines throughout the course of the simulation, becoming intermittent.
+The relationship between stable stratification, shear, and the persistence of turbulence remains an open question \citep{zonta_stably_2018}.
 Thus, it is not possible a priori to determine whether the level of turbulence simulated by this LES model is appropriate for the regime space we have sampled.
@@
 Excess dissipation could arise either through the sub-grid scheme or the model numerics.
-We found a rapid loss of turbulence in PALM simulations when a dynamic Smagorinky turbulence closure was used, which is consistent with previous studies on the limited applicability of the standard Smagorinsky turbulence closure to strongly stratified flows due to the strong anisotropy of those flows \cite{flores_analysis_2011, jimenez_large-eddy_2005}.
-This motivated our adoption of the AMD turbulence closure scheme \cite{abkar_minimum-dissipation_2016}.
-However, we found that the buoyancy term added to this scheme by \citeA{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
-We removed this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019} but enables us to extend the domain allow for the development of a $\sim$20 m-thick IOBL.
+We found a rapid loss of turbulence in PALM simulations when a dynamic Smagorinky turbulence closure was used, which is consistent with previous studies on the limited applicability of the Smagorinsky turbulence closure to strongly stratified flows due to the strong anisotropy of those flows \citep{flores_analysis_2011, jimenez_large-eddy_2005}.
+This motivated our adoption of the AMD turbulence closure scheme \citep{abkar_minimum-dissipation_2016}.
+However, we found that the buoyancy term added to this scheme by \citet{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
+We removed this term, as it was negligible in the simulations of \citet{vreugdenhil_stratification_2019} (personal communication), but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here.
+Though the resolution of our simulations is significantly lower than that used by \citet{vreugdenhil_stratification_2019}, it enables us to extend the domain from their 2\,\unit{m} to 64\,\unit{m} to allow for the development of a thick IOBL.
 
-Strongly stratified turbulence has been associated with intermittent turbulence \cite{nieuwstadt_direct_2005, wiel_cessation_2012}, though there are also numerical experiments that fail to produce intermittency even under strongly stable stratification \cite{arya_buoyancy_1975, komori_turbulence_1983}.
-This is not the first study to find the emergence of intermittent turbulence in stably stratified, sub-ice settings \cite{vreugdenhil_stratification_2019}.
-Flow relaminarization occurs periodically in our most strongly stratified simulations; stratification coincident with high thermal driving and high melt rates.
-\citeA{donda_collapse_2015} have argued that, in strongly stratified flows, the cessation of turbulence is transient provided there are sufficiently large perturbations.
-This is consistent with our finding that the temporal variability in shear over inertial oscillations provides a sufficient perturbation to reinitiate turbulence.
-Our simulations approach a gradient Richardson number ($Ri_g$) of 0.25, which is considered to be the approximate value at which turbulence neither grows nor decays \cite{rohr_growth_1988, holt_numerical_1992}.
+Strongly stratified turbulence has been associated with intermittent turbulence \citep{nieuwstadt_direct_2005, wiel_cessation_2012}, though there are also numerical experiments that fail to produce intermittency even under strongly stable stratification \citep{arya_buoyancy_1975, komori_turbulence_1983}.
+This is not the first study to find the emergence of intermittent turbulence in stably stratified, sub-ice settings \citep{vreugdenhil_stratification_2019}.
+\citet{donda_collapse_2015} have argued that, in strongly stratified flows, the cessation of turbulence is transient provided there are sufficiently large perturbations.
+This is consistent with our finding that the temporal variability in shear over inertial oscillations provides sufficient perturbations to reinitiate turbulence.
+Our simulations approach a gradient Richardson number ($\text{Ri}_g$) of 0.25, which is considered to be the approximate value at which turbulence neither grows nor decays \citep{holt_numerical_1992, rohr_growth_1988}.
 Thus, fluctuations in TKE are plausible at the simulated levels of stratification and shear.
-However, when turbulence is intermittent, as it is in this study, the application of LES may be inappropriate due to its inherent horizontal averaging over laminar and turbulent regions \cite{stoll_large-eddy_2008}.
-Thus, our results at the highest thermal-driving values should be interpreted with caution.
+However, when turbulence is intermittent, as it is in this study, the application of LES may be inappropriate due to its inherent horizontal averaging over laminar and turbulent regions \citep{stoll_large-eddy_2008}.
+Thus, our results should be interpreted with caution.
 
@@
 Nonetheless, it appears as though well-mixed boundary layers are seen for a narrower range of conditions in simulations than in observations.
-The background flow chosen in these simulations is quite strong at 20 cm s\textsuperscript{-1} and thermal driving is relatively low such that we expected to produce a well-mixed boundary layer as is observed in melting regions of the Filchner-Ronne Ice Shelf \cite{nicholls_oceanographic_2001}.
-However, observations to date are insufficient to fully characterize the regime space for a well-mixed IOBL \cite{malyarenko_synthesis_2020}.
-The observational picture is quite nuanced with a range of stratification observed even within one ice shelf \cite{hattermann_two_2012}.
+The geostrophic flow chosen in these simulations is quite strong at 20\,\unit{cm\,s^{-1}} and thermal driving is relatively low such that we expected to produce a well-mixed boundary layer as is observed in melting regions of the Filchner-Ronne Ice Shelf \citep{nicholls_oceanographic_2001}.
+However, observations to date are insufficient to fully characterize the regime space for a well-mixed IOBL \citep{malyarenko_synthesis_2020}.
+The observational picture is quite nuanced with a range of stratification observed even within one ice shelf \citep{hattermann_two_2012}.
 
-% Consider discussing boundary layer depth and entrainment
-
-% Consider leading this section with the discussion of shear-driven turbulence
 Shear-driven turbulence within the IOBL plays a central role in determining vertical heat fluxes and thus melt rates.
 In these simulations the destruction of TKE by the stabilizing buoyancy flux is two orders of magnitude smaller than shear production of TKE throughout the IOBL.
-Our finding that shear production of TKE dominates over the buoyancy term is consistent with \citeA{davis_turbulence_2019} who found that shear production was an order of magnitude greater than buoyancy destruction of TKE in the IOBL below Larsen C Ice Shelf.
+Our finding that shear production of TKE dominates over the buoyancy term is consistent with \citet{davis_turbulence_2019} who found that shear production was an order of magnitude greater than buoyancy destruction of TKE in the IOBL below Larsen C Ice Shelf.
 
 The flux Richardson number, $\text{Ri}_f$, the ratio of buoyancy flux to shear-driven TKE production, provides a measure of mixing efficiency.
-The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.25$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \cite{armenio_investigation_2002, peltier_mixing_2003}.
-This is consistent with our finding that the derived, 2 m-depth thermal exchange coefficient decreases for the high thermal driving cases which also achieve stronger IOBL stratification.
+The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.25$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \citep{armenio_investigation_2002, peltier_mixing_2003}.
+This is consistent with our finding that the derived, 2\,\unit{m}-depth thermal exchange coefficient decreases for the high thermal driving cases which also achieve stronger IOBL stratification.
 
 Our simulations are certainly missing some sources of TKE present in ice-shelf cavities which could modify IOBL structure and mixing efficiency.
-These simulations did not include tides, which provide perturbations to the mean velocity that enhance melt rates and entrainment, especially at Filchner-Ronne \cite{makinson_modeling_1999, makinson_influence_2011, mueller_tidal_2018}.
-While internal gravity waves arise in LES, in our LES model they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \cite{gwyther_cold_2020, robertson_tidally_2013, padman_ocean_2018, mueller_impact_2012}.
-Enhanced drag at the ice-shelf base could increase shear production of TKE; however under strong stratification, surface roughness elements may suppress turbulence rather than enhance it \cite{ohya_wind-tunnel_2001}.
+These simulations did not include tides, which provide perturbations to the mean velocity that enhance melt rates and entrainment, especially at Filchner-Ronne \citep{makinson_modeling_1999, makinson_influence_2011, mueller_tidal_2018}.
+While internal gravity waves arise in LES, in our LES model they may be of smaller amplitude and play a lesser role in mixing than they would in a real ice-shelf settings due to the absence of large-scale external forcings such as tides and storms, seafloor topography, as well as possible resonance with the cavity geometry \citep{gwyther_cold_2020, mueller_impact_2012, padman_ocean_2018, robertson_tidally_2013}.
+Enhanced drag at the ice-shelf base could increase shear production of TKE; however under strong stratification, surface roughness elements may suppress turbulence rather than enhance it \citep{ohya_wind-tunnel_2001}.
 
@@
 Thus, we could not evaluate the relationship between melting and far-field conditions at steady state, which would have offered the most direct path to assessing melt rate sensitivity to ocean conditions.
-As discussed in \citeA{jenkins_simple_2016}, achieving steady-state solutions in simulations may require prescribing large-scale gradients in temperature.
+As discussed in \citet{jenkins_simple_2016}, achieving steady-state solutions in simulations may require prescribing large-scale gradients in temperature.
 We have not included these large-scale gradients in our simulations, but this may be an avenue for future work.
 However, we believe that our transient solutions do provide some indications of how melt rates and boundary layer properties depend on ocean temperature and ice-shelf slopes.
-One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure S7).
-On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}e-f).
+One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure~S7).
+On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}e,f).
 Nonetheless we are able to find relationships between the vertical heat flux profiles and ocean temperature and slope that suggest predictability of the mean effects of turbulence despite the transience of these simulations.
@@
 % sensitivity of melt rate to temperature
-The linear relationship we find between local, far-field ocean temperature and melt rates is consistent with some previous studies in ice-shelf settings \cite{rignot_rapid_2002, holland_response_2008, vreugdenhil_stratification_2019}.
-A slightly higher exponent of $4/3$ is reported for the local, near-field thermal driving in the regime in which convective rather than shear instabilities control melting \cite{kerr_dissolution_2015}.
-In contrast, in sea-ice settings this sensitivity of melt rates to local thermal driving was found to be significantly smaller with an exponent of 0.38 \cite{ramudu_large_2018}.
-It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies a widespread increase in thermal driving (i.e., changes to the water masses entering the ice-shelf cavity).
-The relationship between melt rate and distant thermal driving is a function of both the relationship between the local thermal driving and melt rate and the relationship between distant thermal driving and friction velocity \cite{holland_response_2008}.
-The former relationship is addressed by this study; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity is unchanged.
-We note that the often cited quadratic relationship between thermal driving and melting pertains to this distant thermal driving  \cite{holland_response_2008}; studies generally find this exponent to be between 1.5 and 2 \cite{little_how_2009, jourdain_ocean_2017, favier_assessment_2019}.
+The linear relationship we find between local, far-field ocean temperature and melt rates is consistent with some previous studies in ice-shelf settings \citep{holland_response_2008, rignot_rapid_2002, vreugdenhil_stratification_2019}.
+A slightly higher exponent of $4/3$ is also consistent with our data ($R^2=0.95$); a value reported for the regime in which convective instabilities control melting while our simulations feature shear instabilities \citep{kerr_dissolution_2015}.
+In contrast, in sea-ice settings this sensitivity of melt rates to local thermal driving was found to be significantly smaller with an exponent of 0.38 \citep{ramudu_large_2018}.
+It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies a distant increase in thermal driving (i.e., changes to the water masses entering the ice-shelf cavity).
+The relationship between melt rate and distant thermal driving is a function of both the relationship between the local thermal driving and melt rate and the relationship between distant thermal driving and friction velocity \citep{holland_response_2008}.
+The former relationship is addressed by this study; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity remains constant.
+We note that the often cited quadratic relationship between thermal driving and melting pertains to this distant thermal driving  \citep{holland_response_2008}; studies generally find this exponent to be between 1.5 and 2 \citep{favier_assessment_2019, jourdain_ocean_2017, little_how_2009}.
 
 To some extent, this linear relationship between far-field thermal driving and melt rate is embedded in the parameterization of heat fluxes employed at the ice base in these simulations.
-Specifically, the melt rate is prescribed to have a linear dependence on the thermal driving using the temperature in the first model layer, see Equation~\ref{eq:melt_flux}.
-However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL all mediate this relationship between \textit{far-field} temperature and melt rates, and yet the dependence from these simulations is still fairly linear.
+Specifically, the melt rate is prescribed to have a linear dependence on the \textit{local} thermal driving, based on the temperature in the first model layer (Equation~\ref{eq:melt_flux}).
+However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL all mediate the relationship between \textit{far-field} thermal driving and melt rates, and yet the dependence of melt rate on far-field thermal driving from these simulations is still fairly linear.
 
@@
 The relationship between melt rate and ice-shelf basal slope ($m \propto (\sin\alpha)^{n}$) combines two effects: the effect of ice-shelf slope on the IOBL's mean velocity profile and the effect of ice-shelf slope on IOBL turbulence.
-In the three-equation parameterization of ice-shelf melting, the former has the strongest effect on the friction velocity, derived from the mean flow velocity at a given depth; whereas the latter figures in the value of the scalar exchange coefficients, with higher values indicating more efficient turbulent transport.
+In the three-equation parameterization of ice-shelf melting, the former has the strongest effect on the friction velocity as derived from the mean flow velocity at a given depth; whereas the latter is represented by the scalar exchange coefficients, with higher values indicating more efficient turbulent transport.
 We return to the implications of our study for exchange coefficients in Section \ref{disc:prm_gamma}.
@@
 Thus, we cannot fully assess the the effect of ice-shelf slope on the IOBL's mean velocity profile.
-This effect is addressed by \citeA{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citeA{little_how_2009} who found $n=0.94$ for the range of slopes considered here.
-Our finding that $n=1$ may be applicable to the shear-dominated regime, in contrast to the sensitivity of $n=2/3$ found in the convection-dominated regime at higher slopes than those simulated here (5$^{\circ}$ -- 90$^{\circ}$) \cite{mondal_ablation_2019, mcconnochie_dissolution_2018}.
+This effect is addressed by \citet{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citet{little_how_2009}, who found $n=0.94$ for the range of slopes considered here.
+Our finding that $n=1$ may be applicable to the shear-dominated regime, in contrast to the sensitivity of $n=2/3$ found in the convection-dominated regime at higher slopes than those simulated here \citep[5\unit{^{\circ}} -- 90\unit{^{\circ}};][]{mcconnochie_dissolution_2018, mondal_ablation_2019}.
 However, we emphasize that further investigation is needed beyond the small number of simulations presented here to validate our results.
@@
 % sensitivity of melt rate to slope, at very low slopes
-The threshold-like behavior in melt rates at very low slopes is not predicted by geostrophic balance between Coriolis and buoyancy forcing, which dictates a linear relationship between $\sin\alpha$ and IOBL velocity \cite{jenkins_simple_2016}, nor the scaling analysis of \citeA{magorrian_turbulent_2016}.
-This threshold behavior could be produced if any additional buoyant acceleration produced by the small increase in slope from 0.01$^{\circ}$ to 0.1$^{\circ}$ increases both shear and dissipation, resulting in a negative feedback on IOBL turbulence.
+The threshold-like behavior in melt rates at very low slopes is not predicted by geostrophic balance between Coriolis and buoyancy forcing, which dictates a linear relationship between $\sin\alpha$ and IOBL velocity \citep{jenkins_simple_2016}, nor the scaling analysis of \citet{magorrian_turbulent_2016}.
+This threshold behavior could be produced if any additional buoyant acceleration produced by the small increase in slope from 0.01\unit{^{\circ}} to 0.1\unit{^{\circ}} increases both shear and dissipation, resulting in a negative feedback on IOBL turbulence.
 This is not evident in our simulations, which do not show significant differences in TKE budgets between the two runs (Figure \ref{fig:tke_budget}).
@@
 % Methodology for evaluating thermal exchange coefficient
-The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.25m below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties meters to tens of m below the ice-ocean interface.
-To demonstrate the implications of this study for modeling endeavors, we computed the thermal exchange coefficient that yields the simulated melt rate using ocean properties (temperature and velocity) 2 m below the ice-ocean interface.
+The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.125\,\unit{m} below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties meters to tens of \unit{m} below the ice-ocean interface.
+To demonstrate the implications of this study for modeling endeavors, we computed the thermal exchange coefficient that yields the simulated melt rate using ocean properties (temperature and velocity) 2\,\unit{m} below the ice-ocean interface.
 This depth was chosen to capture the faster portions of IOBL flow, representing a best-case scenario for high resolution ocean models, though this depth choice is somewhat arbitrary.
@@
 These derived thermal exchange coefficients are shown in Figure~\ref{fig:melt_sensitivity}c,d.
-The derived thermal exchange coefficients are all less than the value of 0.011 derived from observations \cite{jenkins_observation_2010}.
+The derived thermal exchange coefficients are all less than the value of 0.011 derived from observations \citep{jenkins_observation_2010}.
 There are two main factors that contribute to this result.
 The first is the choice of the parameterization of fluxes at the ice-ocean interface (i.e., over sub-meter scales).
-We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov lengthscale (Equation~\ref{eq:Kh}).
-We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \cite{monin_basic_1954, mcphee_air-ice-ocean_2008}, and the depth-scaling of scalar fluxes in a more highly resolved sub-ice LES \cite{vreugdenhil_stratification_2019}.
-Consequently, that study also found that thermal exchange coefficients were less than the \citeA{jenkins_observation_2010} value for all but the lowest thermal driving case.
+We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov length (Equation~\ref{eq:psi}).
+We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \citep{monin_basic_1954, mcphee_air-ice-ocean_2008}, and the depth-dependence of scalar fluxes in a more highly resolved sub-ice LES \citep{vreugdenhil_stratification_2019}.
+Consequently, \citet{vreugdenhil_stratification_2019} also found that thermal exchange coefficients were less than the \citet{jenkins_observation_2010} value for all but the lowest thermal driving case.
 However, we acknowledge that more validation of the sub-grid boundary flux parameterizations is needed.
@@
 This may lead to a sub-linear relationship between thermal driving and melt rate at higher thermal driving values, though this not evident in our simulations.
-The decline in exchange coefficient with thermal driving agrees with \citeA{vreugdenhil_stratification_2019}, though their sensitivity is greater than that seen in this study (their Figure 8).
+The decline in exchange coefficient with thermal driving agrees with \citet{vreugdenhil_stratification_2019}, though their sensitivity is greater than that seen in this study (their Figure 8).
 As shown in Figure \ref{fig:melt_sensitivity}c, this relationship holds during all inertial periods, with an exception during an interval of strong turbulence (see Section \ref{results}).
@@
 % thermal exchange coeff, slope
-We find a linear relationship between the derived thermal exchange coefficient and the slope of the ice-shelf base, indicating that thermal exchange is more efficient at higher slopes.
+We find a linear relationship between the derived thermal exchange coefficient and the slope of the ice-shelf base, indicating that mixing is more efficient at higher slopes.
 This relationship also holds for the derived friction velocity from a quadratic drag law (Figure \ref{fig:melt_sensitivity}d).
@@
 This enhanced turbulent efficiency is due to enhanced shear instabilities, and is reflected in turbulent diffusivities parameterized by the AMD scheme.
-Much greater variability in turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure S4).
+Much greater variability in sub-grid turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure~S4).
 
-The changes in the thermal exchange coefficient with slope were small, from 0.0045 to 0.007 between 0.1$^{\circ}$ and 1$^{\circ}$ cases.
+The changes in the thermal exchange coefficient with slope were relatively small, from 0.0045 to 0.007 between 0.1\unit{^{\circ}} and 1\unit{^{\circ}} cases.
 For a coarse-resolution simulation, we anticipate that the failure to capture this slope sensitivity will not be a leading source of error in melt projections.
@@
 These simulations do not reveal whether a similar, linear relationship between friction velocity and thermal exchange coefficient holds when the background flow is varied rather than the slope.
-LES of sea ice melting, for which there is no slope, suggests a sublinear relationship between thermal exchange coefficient and friction velocity ($\Gamma_T \propto u_*^{0.5}, \overline{w^\prime \theta^\prime} \propto u_*^{1.5}$, \citeA{ramudu_large_2018}).
-More studies will be required to determine this scaling.
+LES of sea ice melting, for which there is no slope, suggests a sublinear relationship between thermal exchange coefficient and friction velocity \citep[$\Gamma_T \propto u_*^{0.5},\:\overline{w^\prime \theta^\prime} \propto u_*^{1.5}$;][]{ramudu_large_2018}.
+More studies are  required to determine this scaling.
 
@@
 There is reason to believe that improving ice-shelf basal melt projections using ocean models will require not only an accurate melt parameterization but also an improved vertical mixing scheme.
-\citeA{jenkins_shear_2021} demonstrated significantly different IOBL characteristics when KPP is the turbulence closure scheme in contrast to a low- or high-order scheme.
-The eddy viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (his Figure 3).
-Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or a modified KPP scheme in sub-ice settings, such as one based on the shape functions presented here.
+\citet{jenkins_shear_2021} demonstrated significantly different IOBL characteristics when KPP is the turbulence closure scheme in contrast to a low- or high-order scheme.
+The eddy viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citet{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (compare our Figure S6 with his Figure 3).
+Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or a modified KPP scheme in sub-ice settings, such as one based on the depth-dependence of vertical turbulent fluxes presented here (Figure \ref{fig:flux_profiles}).
 
@@
 A complication in melt parameterization of slope effects is the differential ability of ocean models and their vertical grid configurations to capture IOBL flow.
-We find that this buoyant flow is concentrated in the uppermost 10 m, with peak velocities as close as 3 m from the interface.
-This flow is unlikely to be resolved by most ocean models, which have typical vertical resolutions near the interface of 10s m though some model configurations are reaching $\sim\!$1 m resolutions \cite{gwyther_cold_2020}.
-This then raises additional considerations for the parameterization of ice-ocean interface scalar and momentum fluxes.
+We find that this buoyant flow is concentrated in the uppermost 10 m, with peak velocities as close as 3\,\unit{m} from the interface.
+This flow is unlikely to be resolved by most ocean models, which have typical vertical resolutions near the interface of 10s\,\unit{m} though some model configurations are reaching $\sim\!$1\,\unit{m} resolutions \citep{gwyther_cold_2020}.
 If the buoyancy-driven boundary current is unresolved in most coarse-resolution ocean models, then the friction velocity as computed from a quadratic drag law and the velocity at the first grid cell is likely to underestimate the true friction velocity.
-For instance, a simulation that lacks this buoyancy-induced current may look more like our negligible (0.01$^{\circ}$) slope simulations than those with a slope, and consequently underestimate melt rates.
+For instance, a simulation that lacks this buoyancy-induced current may look more like our negligible (0.01\unit{^{\circ}}) slope simulations than those with a slope, and consequently underestimate melt rates.
 Thus, more accurate melt rate projections may result from employing a depth-dependent parameterization of vertical scalar and momentum fluxes to provide some sensitivity of melt rates to model resolution.
@@
 % scalar flux profiles
-Our simulated depth-dependent shape function for vertical scalar fluxes agrees with the shape of the turbulent scalar flux parameterization of \citeA{mcphee_dynamics_1987} within the first $\sim\!$5 Ekman depths, which features a linear decrease in vertical fluxes with distance from the boundary within the IOBL.
-The low thermal-driving simulations with slopes of 1$^{\circ}$ diverge from this linear behavior within a few m from the boundary.
-We attribute this to boundary effects that reduce TKE and eddy viscosity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \cite{monin_basic_1954}.
-Since these differences in eddy viscosity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes.
-This scaling for IOBL fluxes should be explored under a broader range of conditions to determine whether it is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer in the IOBL.
+Our simulated depth-dependence for vertical scalar fluxes agrees with the shape of the turbulent scalar flux parameterization of \citet{mcphee_dynamics_1987}, which features a linear decrease in fluxes with distance from the boundary within the IOBL.
+The low thermal-driving simulations with slopes of 1\unit{^{\circ}} diverge from this linear behavior within a few\,\unit{m} from the boundary.
+We attribute this to boundary effects that reduce TKE and eddy viscosity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \citep{monin_basic_1954}.
+It is unclear whether a constant flux layer is absent under some conditions or whether our simulations do not resolve it for those highly-stratified cases.
+Since these differences in eddy viscosity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes (Figure \ref{fig:flux_profiles}c,f).
+This linear depth-scaling for IOBL fluxes should be explored under a broader range of conditions and at higher resolution to determine whether it is broadly applicable and whether vertical mixing parameterizations need to improve their representation of the constant flux layer in the IOBL.
 
-A few complexities are immediately apparent in pursuing this path toward vertical scalar flux parameterization.
+A few complexities are immediately apparent in pursuing a depth-dependent shape function for vertical scalar flux parameterization.
 One is that a functional form for the eddy diffusivity is also needed to compute the Ekman depth.
@@
 A depth-dependent function for momentum is also necessary in ice-shelf settings given that strong stratification causes momentum fluxes to significantly deviate from the quadratic drag function typically employed in ocean models.
-Near-interface stratification significantly decreases drag \cite{garcia-villalba_turbulence_2011, mcphee_revisiting_2008}.
-Representing this reduction in drag through the drag coefficient necessarily removes the melt-rate dependence of drag through stratification.
-The addition of an ice-shelf slope to ocean models that do not fully resolve a buoyant plume further complicates the parameterization of momentum fluxes at the ice-ocean interface.
-A depth-dependent shape function for momentum fluxes which may prescribe negative (downward) momentum fluxes at the top grid cell below ice shelves for typical ocean model resolutions (see Figure \ref{fig:momflux_profiles} at, e.g., 5 m depth).
+Near-interface stratification significantly decreases drag \citep{garcia-villalba_turbulence_2011, mcphee_revisiting_2008}.
+Tuning the drag coefficient to fit present-day melt rates neglects the functional dependence of drag on melt rate through stratification (as represented by the Monin-Obukhov length).
+The presence of an ice-shelf slope in ocean models that do not fully resolve a buoyant plume further complicates the parameterization of momentum fluxes at the ice-ocean interface.
+A depth-dependent shape function for momentum fluxes which may prescribe negative (downward) momentum fluxes at the top grid cell below ice shelves for typical ocean model resolutions (see Figure \ref{fig:flux_profiles}a,d at, e.g., 5\,\unit{m} depth).
 In other words, when the buoyant plume is unresolved, the momentum boundary condition may need to accelerate the flow at the boundary (at least in the up-slope direction) to produce more accurate shear-driven mixing in the resolved portion of the domain.
 
-\section{Conclusion}\label{conclusion}
+\conclusions
 
 In this study we presented a small parameter study of IOBL turbulence as captured by an LES model and chiefly explored the sensitivity of ice-shelf melting to ocean temperature and ice-shelf basal slope.
-To our knowledge, this is the first study to explore turbulent effects of low slopes on ice melting at scales spanning 10s m from the ice base, allowing for IOBL development.
+To our knowledge, this is the first study to explore turbulent effects of low slopes on ice melting at scales spanning 10s\,\unit{m} from the ice base, allowing for IOBL development.
 These vertical scales allow us to examine the depth-dependence of vertical turbulent fluxes, a key component for the development and validation of vertical mixing parameterizations in ice-shelf settings.
-Building on \citeA{jenkins_shear_2021}, our results suggest an improvement on the standard KPP vertical mixing scheme is needed, but a larger simulation campaign and field validation effort would be required to place such a scheme on strong footing.
+Building on \citet{jenkins_shear_2021}, our results suggest an improvement on the standard KPP vertical mixing scheme is needed, but a larger simulation campaign and field validation effort would be required to place such a scheme on strong footing.
 
@@
 While a constant value is not theoretically supported, it remains the standard choice due to a lack of consensus regarding the appropriate scaling.
-We concur with a previous study that the thermal exchange coefficient is dependent on thermal driving such that melt rates are less sensitive to changes in ocean temperature \cite{vreugdenhil_stratification_2019}.
+We concur with a previous study that the thermal exchange coefficient is dependent on thermal driving such that melt rates are less sensitive to changes in ocean temperature \citep{vreugdenhil_stratification_2019}.
 We also suggest that the thermal exchange coefficient should be enhanced at higher slopes to account for shear instabilities that are unresolved by coarse-resolution ocean models, with the caveat that our simulations did not reach steady-state.
-Ultimately, we acknowledge that there is currently no universal guidance for parameterizing sub-grid scalar and momentum fluxes near the ice base for ocean models, each of which capture IOBL flow differently depending on resolution, vertical coordinate, numerical representations of the pressure gradient, and likely other aspects of the implementation \cite{gwyther_cold_2020}.
-Thus, progress toward accurate ice-shelf melt projections will require not only the theoretical advances in understanding melt rate sensitivity but also advances in numerical modeling to bring resolution- (scale-) awareness to melt parameterization.
 
-\section{Acknowledgements}
+Ultimately, we acknowledge that there is currently no universal guidance for parameterizing sub-grid scalar and momentum fluxes near the ice base for ocean models, each of which capture IOBL flow differently depending on resolution, vertical coordinate, numerical representations of the pressure gradient, and likely other aspects of the implementation \citep{gwyther_cold_2020}.
+Thus, progress toward accurate ice-shelf melt projections will require not only theoretical advances in understanding melt rate sensitivity but also advances in numerical modeling to bring resolution- (scale-) awareness to melt parameterization.
 
-This work was funded by the U.S.
-Department of Energy (DOE), Office of Science, Biological and Environmental Research, and Advanced Scientific Computing Research programs.
-Carolyn Begeman received funding for this work from a Chick Keller Postdoctoral Fellowship through the Center for Earth and Space Sciences at Los Alamos National Laboratory.
-Computing resources were provided by the Los Alamos National Laboratory Institutional Computing Program, which is supported by the U.S.
-Department of Energy National Nuclear Security Administration under Contract No.
+\codeavailability{The modified version of PALM used for this study is currently under review at Los Alamos National Laboratory for open access release.}
+
+\authorcontribution{All authors conceived and designed the study.
+Begeman conducted and analyzed the simulations with input from Asay-Davis and Van Roekel.
+Begeman wrote the manuscript with input from Asay-Davis and Van Roekel.}
+
+\competinginterests{The authors declare that they have no conflict of interest.}
+
+\begin{acknowledgements}
+This research was supported by the Los Alamos National
+Laboratory (LANL) through its Center for Space and Earth Science
+(CSES). CSES is funded by LANL’s Laboratory Directed Research
+and Development (LDRD) program under project number
+20210528CR.
+This research was also supported by the LDRD program of LANL under project numbers 20210289ER and 20180549ECR.
+Support for simulation data analysis pertaining to ice-shelf melt parameterization and manuscript preparation was provided through the Scientific Discovery through Advanced Computing (SciDAC) program funded by the US Department of Energy (DOE), Office of Science, Advanced Scientific Computing Research and Biological and Environmental Research Programs.
+Computing resources were provided by the LANL Institutional Computing Program, which is supported by the U.S.
+DOE National Nuclear Security Administration under Contract No.
 89233218CNA000001.
+\end{acknowledgements}
 
-\newpage
-\bibliography{references}
+\bibliographystyle{copernicus}
+\bibliography{references.bib}
 

### 2021-08-02 vis_scripts/plot_param_palm.py
viz scripts updates for large flux profile fig

@@ -23,10 +23,13 @@ bboxanchor = (0.0,-0.25)
 s_hr = 3600
 logmin = 1.0e-20
 
-figsize2_wide = (5,2.5)
-figsize2_box = (5,3)
-figsize2 = (4.25,4)
-figsize3 = (8.5/3,3)
+col2_width = 12 #cm
+col1_width = 8.3 #cm
+figsize2_wide = (col2_width/2,2.5)
+figsize2_box = (col2_width/2,3)
+figsize1 = (col1_width,4)
+figsize2 = (col2_width/2,col2_width/2)
+figsize3 = (col2_width/3,col2_width/3)
 
 # define default colors
 col = ['#186086','#F5793A','#A95AA1','#85C0F9','#D14A42','#2ca25f','#99d8c9','#5F86DD']

### 2021-08-02 vis_scripts/cp_flux_profile_fig.sh
viz scripts updates for large flux profile fig

@@ -2,30 +2,30 @@ PREFIX_T=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batc
 PREFIX_SLOPE=/turquoise/usr/projects/climate/cbegeman/palm/jobs/test_ocean_melt_batch_alpha_surface_006/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml
 SUFFIX_OLD_T=_cmp_dT0.2_dT0.4_43hr_tav13_42zmax_z_profile.png
 SUFFIX_OLD_T1=_cmp_dT0.2_dT0.4_8hr_tav13_42zmax_z_profile.png
-SUFFIX_OLD_T_SCALE=_cmp_dT0.2_dT0.4_43hr_tav13_scale_z_profile.png
+SUFFIX_OLD_T_SCALE=_cmp_dT0.2_dT0.4_43hr_tav13_25zmax_scale_z_profile.png
 SUFFIX_NEW_T=_cmp_dT_43h_tav13h_z_profile.png
 SUFFIX_NEW_T1=_cmp_dT_8h_tav13h_z_profile.png
 SUFFIX_NEW_T_SCALE=_cmp_dT_43h_tav13h_dTscale_z_profile.png
 SUFFIX_OLD_SLOPE=_cmp_slope0.10_slope0.50_43hr_tav13.0_42zmax_z_profile.png
 SUFFIX_OLD_SLOPE1=_cmp_slope0.10_slope0.50_8hr_tav13.0_42zmax_z_profile.png
-SUFFIX_OLD_SLOPE_SCALE=_cmp_slope0.10_slope0.50_43hr_tav13.0_scale_z_profile.png
+SUFFIX_OLD_SLOPE_SCALE=_cmp_slope0.10_slope0.50_43hr_tav13.0_25zmax_scale_z_profile.png
 SUFFIX_NEW_SLOPE=_cmp_dslope_43h_tav13h_z_profile.png
 SUFFIX_NEW_SLOPE1=_cmp_dslope_8h_tav13h_z_profile.png
 SUFFIX_NEW_SLOPE_SCALE=_cmp_dslope_43h_tav13h_slopescale_z_profile.png
 
[…]

### 2021-08-02 vis_scripts/extract_var_palm.py

@@ -120,10 +120,10 @@ def extract_var(data,var_name,data_type='pr',ops=[],
         var1_shape = np.shape(var1)
         var1 = var1.data
         if len(var1_shape) == 2:#data_type == 'pr':
-            print('shape tmask',np.shape(tmask))
-            print('shape var1 tav',np.shape(var1))
-            print('tmask',t[tmask])
-            print('type var1',type(var1))
+            #print('shape tmask',np.shape(tmask))
+            #print('shape var1 tav',np.shape(var1))
+            #print('tmask',t[tmask])
+            #print('type var1',type(var1))
             #print(np.shape(var1[tmask,:]),varaxes.index('t'))
             _,nz = np.shape(var1)
             for i in range(nz):
@@ -319,12 +319,14 @@ def derived_var(data,varname,slice_obj_input,z_offset = 0.,f = gsw.f(-70.),filed
         var1 = np.subtract(np.add(Fshear,Ftrans,Fbuoy),dedt)
     
     elif varname == 'zE':
-        t = data.variables['time'][:]
+        t = data.variables['time'][:]/3600.
         ti = np.argmin(np.abs(t-50.))
         #var1,_ = extract_var(data,'z',slice_obj=slice_obj)#,grid='zu'
         K_ref,_ = extract_var(data,'km_eff',data_type=data_type)#,slice_obj=slice_obj,tav=tav)
         K_ref = K_ref.data
-        var1 = np.nanmean(K_ref[ti-12:ti+1,-80:])
+        print('ti',ti)
+        print('shp(K_ref)',np.shape(K_ref))
+        var1 = np.sqrt(2*np.nanmean(K_ref[ti-12:ti+1,-80:]))/np.sqrt(abs(f))
         #var1 = np.divide(var1,dE)
 
     elif varname == 'dEdt':

### 2021-08-02 vis_scripts/plot_palm_mod.py

@@ -6,6 +6,7 @@ Created on Tue Jan 22 07:52:34 2019
 @author: cbegeman
 """
 import math,os
+from scipy.optimize import curve_fit
 from netCDF4 import Dataset
 import numpy as np
 import numpy.ma as ma
@@ -549,7 +550,8 @@ def plot_tseries_cross(filedir, runname, runlabel,
                        plotvar = ['us','melt'], data_type = ['ts','ts'],
                        teval = [-9999.,-9999.], tunits='hr', tav=0.,
                        figsize = (6.4,4.8), plot_cycles=False,
-                       plot_jenkins=False, plot_legend = True, legtitle='',
+                       plot_jenkins=False, fit_power_law=False,
+                       plot_legend = True, legtitle='',
                        color_by_time = False, col = col, 
                        overwrite=False, outputdir = '', printformat = 'png'):
         
@@ -564,6 +566,8 @@ def plot_tseries_cross(filedir, runname, runlabel,
         name = name + '_tav' + str(int(tav))
     if plot_cycles:
         name = name + '_tcycles'
+    if fit_power_law:
+        name = name + '_fit'
     filenamesave = name + '.' + printformat
     if outputdir == '':
        outputdir = filedir[0]
@@ -574,13 +578,12 @@ def plot_tseries_cross(filedir, runname, runlabel,
 
     fig = plt.figure(figsize=figsize)
     ax = fig.add_subplot(111)
-                
+    data_all = np.zeros((2,len(filedir))) 
     for i,diri in enumerate(filedir):
         y_data = load_data(diri,data_type=data_type[1])
         if data_type[1] != 'parameter':
             slice_obj_input,varaxes = slice_var(y_data,'time',data_type=data_type[1],
                                                 tunits=tunits,tval=teval)
-        print('y_var')
         y_var,y_axis_label = extract_var(y_data,plotvar[1],
                                          slice_obj=slice_obj_input,
                                          data_type=data_type[1],data_dir=diri,
@@ -591,11 +594,12 @@ def plot_tseries_cross(filedir, runname, runlabel,
                                                 tunits=tunits,tval=teval)
         else:
             slice_obj_x = []
-        print('x_var')
         x_var,x_axis_label = extract_var(x_data,plotvar[0],
                                          slice_obj=slice_obj_x,
[…]

### 2021-10-06 Response_reviewers_rev1.tex
Updates from Overleaf

\documentclass[tc, manuscript]{copernicus}

\setcounter{figure}{0}
\begin{document}

\title{Response to reviewers for ``Ice-shelf ocean boundary layer dynamics from large-eddy simulations"}

\runningtitle{IOBL dynamics}

\runningauthor{Begeman et al.}

\correspondence{Carolyn Begeman (cbegeman@lanl.gov)}

\Author[1]{Carolyn Branecky}{Begeman}
\Author[1]{Xylar}{Asay-Davis}
\Author[1]{Luke}{Van Roekel}

\affil[1]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, New Mexico, USA 87545}

\firstpage{1}

\maketitle

\section{Response to Reviewer 1}

Abstract:

Line 2: “Yet these small scale processes, which regulate heat transfer between….”\\
Should be heat and salt transfer.\\
\textit{The suggested change has been made.}

Introduction:

Line 27: “….an overturning circulation known as “ice pump” “
Could talk about the refreezing process.\\
\textit{We have added the following sentence to this paragraph:}
``Supercooling of the IOBL and frazil ice accretion to the ice-shelf base are also regionally important processes for cold cavities, but are not the focus of this work \citep{galton-fenzi_modeling_2012, jordan_conditional_2015}.''

Line 31: “ IOBLs present unique conditions in the global ocean, involving a stabilizing flux from phase change” The stabilizing flux mostly comes from the freshening of the boundary layer not from ‘phase-change’.\\
\textit{We intended to specifically refer to the stabilizing buoyancy flux at the boundary associated with ice-shelf melting. We hope this revision is more clear:}\\
``IOBLs present unique conditions in the global ocean, involving a stabilizing buoyancy flux from melting ice and a boundary layer that is positively buoyant against a sloping boundary.''

Line 36: “ Numerical studies addressing intermediate scale”
Please define ‘Intermediate scale’. Also to my knowledge Mondal et al., 2019 was a DNS study that resolved the Kolmogorov scale.\\
\textit{We have avoided this vague term in our revision. The revised sentence reads:}\\
``IOBL turbulence has been explored through laboratory experiments, direct numerical simulations, and large-eddy simulations \citep{middleton_numerical_2021, mondal_ablation_2019, vreugdenhil_stratification_2019, mcconnochie_dissolution_2018}.''

should clearly mention the author used a Lewis number =1.\\
\textit{This comment wasn't entirely clear to us. If the reviewer is referring to this study, it isn't the case that the Lewis number=1 either in the melt parameterization or the AMD turbulence closure model.}

It would be interesting to see how friction length changes over slope, assuming eddy viscousity is estimated as a product of friction velocity and mixing length.\\
%XX

Methods:

General Comment: I would love a schematic of the model set up.\\
\textit{We have added a schematic figure, now labeled Figure 1.}

Overview of the LES model: It would help the readers if you clearly mention whether you have used a linear or non-linear equation of state.\\
\textit{Thanks for catching the omission. We have added the following text:}\\
``We use the nonlinear equation of state from  \citet{jackett_algorithms_2006} to compute densities.''

Simulation set-up:

Line 150: What about the time step?
\textit{We have added the following text:}
``PALM employs adaptive timestepping; timesteps for the simulations presented here range from 0.5 s to 2.75 s after 2 h.''
\textit{We also realized that the following information might be useful to the reader:}
``We initiate turbulence over first 50 min of the simulation with perturbations to the horizontal velocity components on the order of 0.01 m/s.''

Line 167: I don’t think 1 degree is a relatively high slope for Antarctic ice-shelves.
\textit{That's fair. We have deleted the judgment so that it now reads:}
``and a slope of 1\unit{^{\circ}}''

Result:

A plot with temporal evolution of melt rate, obukhov lengthscales could help the reader.
\textit{We have included a plot with the temporal evolution of melt rates, Figure 1 c,f. We believe that the obukhov lengthscale doesn't provide much additional context beyond that given by the melt rate and friction velocity in Figure 1, as it is computed from them. However, we added the following text to provide some context for the reader:}
``Average melt rates over the last inertial period range from 0.3--2.5\unit\,{m} (Fig. \ref{fig:timeseries}a,d) and average Monin-Obukhov lengthscales are 3--5\,\unit{m} (not shown).''

Discussion :

Line 397: 'The relationship between melt rate and distant thermal driving' : the sentence is hard to read.
\textit{To make our point clear, we have rewritten the latter portion of this paragraph:}
``The relationship between average ice-shelf melt rates and the thermal driving for the cavity as a whole can be conceptualized in two components. The first is the relationship between the local thermal driving and melt rate, determined primarily by the local ocean turbulence. The second is the relationship between distant thermal driving (i.e., the water masses entering the ice-shelf cavity) and the strength of sub-ice-shelf circulation \citep{holland_response_2008}. Only the former is addressed by this study. Our simulations do not capture the large-scale increase in overturning circulation that accompanies an increase in distant thermal driving. Our simulations partially capture the increase in IOBL velocity due to an increase in thermal driving but the far-field velocity is unaffected. We note that the often cited quadratic relationship between distant thermal driving and melt rate involves both local turbulent processes and large-scale processes \citep{holland_response_2008}; studies generally find this exponent on distant thermal driving to be between 1.5 and 2 \citep{favier_assessment_2019, jourdain_ocean_2017, little_how_2009}.''

\section{Response to Reviewer 2}

This manuscript addresses boundary layer dynamics at the ice-ocean interface motivated by obtaining novel parameterizations of ice-shelf melting. This is a highly important topic: increasing complexity of ice and ocean models will not improve the estimates of melt rates with inappropriate representation of the processes in the boundary layer. Although the method chosen in the paper (LES using relatively low resolution) gives the results of limited applicability, which is admitted by the authors, it provides some important insights. The manuscript can be published if the authors address the following points

Major points:

Section 2.3: Please add the figure illustrating simulation setup for your base case. Add more detail in this figure: currently even the sizes of the domain are not written anywhere.

\textit{We have added a schematic figure (Figure 1). This text specifying the domain size was included in the original manuscript, but it would be easy to miss. With the new figure, it should be more visible}\\
``The domain is a 64 m$^3$ cube''

L 100: please add more detail about validation in the appendix. It would be useful to have an idea how the chosen model works compared to other model (which one? Was it DNS or measurements or another LES model?).

\textit{We have added a figure to the supplemental materials (Figure S1) and the following text to the manuscript. We don't feel that too much information is needed about model set-up because we follow Abkar and Moin (2017) exactly.}\\
``We validated our implementation against the stable atmospheric boundary layer test case published in \citet{abkar_large-eddy_2017} and \citet{stoll_large-eddy_2008}. We follow \citet[]['s]{abkar_large-eddy_2017}'s model set-up exactly and chose their moderate resolution with 72x72x72 grid points. Our results are in good agreement with \citet[]['s]{abkar_large-eddy_2017} solution employing another LES model with AMD (boundary layer height differs by <10\%) and other LES models with different turbulence closures (Fig. S1, their Fig. 1 and references therein).''

L 150: How does the resolution influence the results? Why this particular resolution was chosen?

L 157-158: It would be helpful to write the boundary conditions explicitly, not just Dirichlet/von Neumann. 
\textit{We have modified this paragraph to explicitly state the boundary conditions, and rearrange some of the text accordingly. The relevant sentences are:}
``We set von Neumann boundary conditions at the top boundary corresponding to the dynamic sub-grid momentum and scalar fluxes (Equations~\ref{eq:tau}, \ref{eq:vflux_heat}, and \ref{eq:vflux_salt}), as resolved fluxes go to zero at a no-penetration boundary. ... Boundary conditions are Dirichlet at the bottom boundary, set to the far-field temperature, salinity, and geostrophic velocity. ... The flow is periodic along the x and y dimensions.''
If there is a flow developing along the ice face due to buoyancy, how justified is the use of the periodic boundary conditions?
\textit{In the literature, periodic boundary conditions in the context of simulations of the IOBL have been employed either to represent the domain moving with the IOBL in a Lagrangian sense (Chen et al. 2021. The Cryosphere Discussions.) or the domain remaining fixed in space and the periodic boundary conditions providing the opportunity for the development of turbulence and of equilibrium conditions (Vreugdenhil and Taylor, 2019; Rosevear et al. 2021). We take the latter view, with the intent to bring the flow to equilibrium with the forcing by the end of the simulations. As discussed in Section 4.1, equilibrium was not achieved. }

The whole Sec. 2.2, called ‘Turbulence closure’, is about boundary conditions at the ice-ocean interface.
\textit{We agree that this may not be the clearest descriptor of this section. We move the first paragraph to the previous section and rename this section ``Boundary conditions for ice-shelf melting.''}

Section Results should be split into smaller subsections with separate titles to make it more reader-friendly.
\textit{Good suggestion. We have added the following subsections: Overview of the mean simulated state, Turbulent kinetic energy budget, Boundary layer turbulence, Melting and its relation to thermal driving and slope, Vertical structure of turbulent fluxes.}

Minor points:

Please check the equations. Several equations have misprints:
\textit{Thank you for reviewing the equations so carefully. We have made the changes you requested}

Eq (1), rhs: 1st term: should be $x_j$ and not $x_i$; 3rd term: what does index g in $u_g$ mean?
\textit{We have added the following text to define $u_g$:}
``The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow with a geostrophic velocity $u_g$, ...''

Eq (3),(4): 2nd terms in the rhs: should be $u_j$ not $u_i$;
\textit{Change has been made.}

Eq (11): not clear, does this mean that gamma is the sum of the molecular and turbulent coefficients? 
\textit{The text has been modified to make this equation more clear:}
``where the exchange coefficients are defined with two terms, one representing turbulent transfer within the turbulent surface layer and one representing molecular transfer within the viscous sublayer following \citet{mcphee_dynamics_1987} (their Equation 11):.''
Why the form with power ‘-1’ is chosen if that power can be removed from this equation. In addition, I have not found this or similar expression in McPhee et al (1987), please clarify.
\textit{The power of -1 was not necessary in these equations an has been removed. This form (without the -1 power) can be found in Equation 11 of McPhee et al. (1987) where the second term is the molecular contribution.}

Eq (14) $c_p$ should be removed, it makes the expression dimensionally inconsistent.
\textit{Change has been made.}

L 146: ‘It is noted by the PALM developers that this error was found to be small’ –please provide a reference here.
\textit{This note is embedded in the code itself.}
\url{https://github.com/lanl/palm_lanl/blob/7f1444073b20ae81b451d4ab469d13e66b5358b7/trunk/SOURCE/surface_layer_fluxes_mod.f90#L2513-L2519}

L 168: far field thermal driving is 0.15C, but in the figures elsewhere, there is no such case, only 0.1C. I believe one of those is a misprint.

L 147: ‘This error would be small if the first ∼10 cm were largely a constant flux layer, as hypothesized by McPhee (1983).’ – I do not understand this sentence. Clearly, if 10 cm were a constant flux layer, then the mentioned fluxes would be equal. What was hypothesized by McPhee?
\textit{We have edited the text to be a bit more specific about what we mean. We hoped to convey that the surface layer is thought to deviate only slightly from a constant flux layer. We also changed the citation to McPhee (1981), which contains this argument in more detail (though the 1983 paper provides the extension to scalar fluxes).}``This error would be small if the first $\sim$10\,\unit{cm} were nearly a constant flux layer; \citet{mcphee_analytic_1981} hypothesized that the sub-ice surface layer would be nearly but not exactly a constant flux layer.''

L 205: ‘thermal driving increases from 0.5 to 0.6C ’: there is no 0.5C case in the figure.
XX

Fig. 1: the caption does not match the figure: (a) is not TKE but friction velocity etc.
\textit{We have replaced figure 1 with the version with TKE in panels a,d.}

L 347: critical gradient Richardson number for development of hydrodynamic instabilities, and further transition to turbulence, $Ri_g$=0.25, has been first obtained by Miles and Howard in 1961.
\textit{Thanks for the tip. This reference has been added.}

\section{Community comments}
I believe sections 1 and 2 would benefit greatly from a figure showing a sketch of the simulated flow, and some relevant physical quantities and conditions, e.g. the angles alpha and beta, etc.

\textit{We have added a schematic figure, now labeled Figure 1.}

Also, if I'm not mistaking, the numerical methods used by the LES solver are not discussed. They should at least be mentioned briefly.
\textit{This is a good suggestion, particularly as PALM has several methods available for advection, timestepping, and pressure. We have added the following text:}
``We employ PALM's implementation of the \citet{piacsek_conservation_1970} second-order advection scheme for momentum and scalars and a third-order Runge-Kutta timestepping scheme. We also use the \citet{temperton_generalized_1992} Fast-Fourier Transform algorithm for the pressure solver.''

\subsection{Unsolicited changes}
\textit{We have also added the following citations:}
Rosevear XX
\end{document}

### 2021-10-06 main_JGR.tex

--- 2021-07-14 main.tex
@@
-\documentclass[draft]{agujournal2019}
+\documentclass[draft]{styles/agujournal2019}
 \usepackage{url} 
@@
 \usepackage{graphicx}
-%\usepackage{xr}
 \usepackage{float}
-%\externaldocument{A_suppl_fig}
-%\usepackage{amsmath}
 \usepackage{mathtools}
@@
 \journalname{JGR: Oceans}
+
+% current word count 2021-07-15 8,500 = 17 PU
+% caption word count 2021-07-15 
+% figures 7 = 7 PU
+% excess charge for PU over 25
 
@@
 % Shortcomings of ocean-model representations of IOBL
-One indication that ocean models do not capture turbulent dynamics is that the simulated thermal driving in the IOBL, the difference between ocean temperature and the local freezing point, and consequently the simulated melt rate differ significantly between ocean models and as resolution is varied within a model \cite{gwyther_cold_2020}.
+One indication that ocean models do not capture turbulent dynamics in the IOBL is that the simulated thermal driving, the difference between ocean temperature and the local freezing point, and consequently the simulated melt rate differ significantly between ocean models and as resolution is varied within a model \cite{gwyther_cold_2020}.
 Furthermore, ocean models predict ice-shelf melting using parameterizations that neglect the lateral buoyancy gradient of the IOBL and often the vertical buoyancy gradient as well, which should reduce the efficiency of vertical mixing near the boundary.
-This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is driven in large part by the buoyant flow of water freshened by ice-shelf melting, overturning circulation also known as the ``ice pump'' \cite{webber_impact_2018}.
+This model deficiency likely biases turbulent fluxes through the IOBL and ocean cavity circulation, which is driven in large part by the buoyant flow of water freshened by ice-shelf melting, an overturning circulation also known as the ``ice pump'' \cite{webber_impact_2018}.
 A new parameterization of ice-shelf melting that accounts for boundary layer dynamics is needed to achieve a more physically based, accurate coupling of ice sheets and oceans in climate models \cite{gwyther_cold_2020, dinniman_modeling_2016, naughten_future_2018, edwards_projected_2021}.
@@
 There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \cite{zonta_stably_2018}.
-The IOBL has been most extensively explored at small scales through laboratory experiments and Direct Numerical Simulations, with some recent numerical studies addressing intermediate scales \cite{mondal_ablation_2019, vreugdenhil_stratification_2019, middleton_numerical_2021}.
+The IOBL has been most extensively explored at small scales through laboratory experiments and direct numerical simulations, with some recent numerical studies addressing intermediate scales \cite{mondal_ablation_2019, vreugdenhil_stratification_2019, middleton_numerical_2021}.
 However, this body of work has not yet matured to setting a new standard for ice-shelf melt parameterization in ocean models.
-The commonly-used ice-shelf melt parameterization today still derives from sea-ice conditions (i.e., in the absence of a slope) with tuning of some parameters for ice-shelf settings \cite{holland_modeling_1999, jenkins_observation_2010, mcphee_dynamics_1987}.
-Thus a knowledge gap exists in bridging IOBL dynamics across scales and characterizing the structure of buoyant plumes.
+Today, the most commonly used ice-shelf melt parameterization still derives from sea-ice conditions (i.e., in the absence of a slope) with some parameters tuned for ice-shelf settings \cite{holland_modeling_1999, jenkins_observation_2010, mcphee_dynamics_1987}.
+A knowledge gap exists in bridging IOBL dynamics across scales and characterizing the structure of buoyant plumes.
 Recently, this has been addressed through non-turbulence-resolving 2-d or 2.5-d models \cite{jenkins_simple_2016, jenkins_shear_2021, cheng_modeling_2020}.
@@
 The target of previous LES studies has been on low-shear settings \cite{vreugdenhil_stratification_2019, middleton_numerical_2021}.
-Section \ref{meth} describes the LES model, its turbulence closure scheme, and the set-up of our simulations.
-Section \ref{results} presents the results of our simulations, with a focus on comparisons across the range of thermal driving and slope given.
-The discussion is given in two parts: Section \ref{disc:dyn} contextualizes the features of our simulated IOBL turbulence and discusses limitations of this study, and Section \ref{disc:prm} focuses on how this study informs parameterizations of ice-shelf melting and IOBL turbulence.
+Section~\ref{meth} describes the LES model, its turbulence closure scheme, and the set-up of our simulations.
+Section~\ref{results} presents the results of our simulations, with a focus on comparisons across the sampled range of thermal driving and slope.
+The discussion is given in two parts: Section~\ref{disc:dyn} contextualizes the features of our simulated IOBL turbulence and discusses limitations of this study, and Section~\ref{disc:prm} focuses on how this study informs parameterizations of ice-shelf melting and IOBL turbulence.
 We provide some closing thoughts in Section \ref{conclusion}.
@@
 It has been applied to the simulation of atmospheric and ocean boundary layers, but it has never been used specifically to treat a sub-ice-shelf ocean boundary layer.
-For this application, our model is a new version based on PALM v5.0 \cite{maronga_parallelized_2015} with added features including a boundary flux scheme for the ice-ocean interface, rotating the gravity vector for sloped domains, and a different turbulence closure scheme.
-Here we provide a brief overview of PALM with a focus on our additions.
+For this application, we developed a new version based on PALM v5.0 \cite{maronga_parallelized_2015} with added features including a boundary flux scheme for the ice-ocean interface, rotating the gravity vector for sloped domains, and a different turbulence closure scheme.
+Here, we provide a brief overview of PALM with a focus on our additions.
 For more details we refer readers to \citeA{maronga_parallelized_2015}.
@@
         + \varepsilon_{i3j} f_3 u_{g,j}\nonumber\\
-     &&& \quad + g_i \frac{\rho - \rho_a}{\rho_0} 
+     &&& \quad \, + g_i \frac{\rho - \rho_a}{\rho_0} 
         - \frac{1}{\rho_0}\frac{\partial \pi^*}{\partial x_i} \nonumber\\
-     &&& \quad - \frac{\partial}{\partial x_j}\left(\overline{u''_i u''_j} 
+     &&& \quad \, - \frac{\partial}{\partial x_j}\left(\overline{u''_i u''_j} 
         - \frac{1}{3}\overline{u''_i u''_i}\delta_{ij}\right) \label{eq:uprog}\\
@@
 
-Detail on the solution of these equations can be found in \cite{maronga_parallelized_2015}.
 The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow using the pressure perturbation $\pi^*$ (imposing incompressibility), and sub-grid scale momentum flux.
@@
 	%\textbf{g} = g [sin \alpha,0,cos \alpha]
-	\textbf{g} = g_z [\sin \alpha \sin \beta,\cos \beta,\cos \alpha]
+	\textbf{g} = g_z [\sin \alpha \sin \beta, \sin \alpha \cos \beta,\cos \alpha]
 \end{equation}
 \begin{equation} \label{eq:f}
-    \textbf{f} = 2 \Omega [\sin \phi \sin \alpha,\cos \phi,\sin \phi \cos \alpha]
+    \textbf{f} = 2 \Omega [\sin \phi \sin \alpha \sin \beta,\cos \phi \sin \alpha \cos \beta,\sin \phi \cos \alpha]
 \end{equation}
@@
 
-The buoyancy term in Equation \ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density relative to the ambient density of the water column $\rho_a$.
-$\rho_a$ varies along slope and depth from the ice interface as a function of the hydrostatic pressure:
+The buoyancy term in Equation~\ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density relative to the ambient density of the water column $\rho_a$.
+$\rho_a$ varies along slope and with depth from the ice interface as a function of the hydrostatic pressure:
 \begin{equation}
@@
 \end{equation}
-where the superscript $i$ denotes the initial state. The reference density $\rho_0$ is evaluated in the center of the x-y plane ($\rho_0(z) = \rho_a(x_{mid},y_{mid},z)$). 
-%
-%Thus, we assume that the evolution of density in the boundary layer does not significantly affect buoyancy/ice-shelf slope. 
-We neglect hydrostatic pressure gradients along slope, except through the density term $\rho-\rho_a$.
-For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 1 bar m\textsuperscript{-1}.
-% or 10 pa/m
-This simplification has the advantage of avoiding pressure discontinuities across periodic boundary conditions. 
-%We assume that density differences between ambient and simulated conditions does not significantly change as a function of along-slope pressure changes. 
-% \begin{equation}
-%     \rho(T(x,z),S(x,z),p(x,z)) - \rho_a(T_a,S_a,p(x,z)) \approx 
-%     \rho(T(x,z),S(x,z),p(x_{mid},z) - \rho_a(T_a,S_a,p(x_{mid},z))
-% \end{equation}
-%These density differences are verified to be within XX $kg/m^3$ for these simulations.
+where the superscript $i$ denotes the initial state.
+The reference density $\rho_0$ is evaluated in the center of the x-y plane ($\rho_0(z) = \rho_a(x_{mid},y_{mid},z)$).
+We neglect hydrostatic pressure gradients along slope, except through $\rho_a$ in the buoyancy term.
+For the maximum slope simulated in this study, the maximum hydrostatic pressure gradient is on the order of 100\,Pa\,m\textsuperscript{-1}.
+This simplification has the advantage of avoiding pressure discontinuities across periodic boundary.
 
@@
 We validated our implementation against the stable atmospheric boundary layer test case published in \citeA{abkar_large-eddy_2017}.
-Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4} m\textsuperscript{2} s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}).
+Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from 10\textsuperscript{-5} to 10\textsuperscript{-4}\,m\textsuperscript{2}\,s\textsuperscript{-1} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}).
 
 Sources and sinks of momentum, heat and salt due to interactions between the flow and the ice base are all parameterized as sub-grid fluxes at the boundary.
-The resolved vertical fluxes at the top layer of the model go to zero as $w$ goes to zero according to the no-flux boundary condition and the sub-grid fluxes are determined using the scheme described below in place of the AMD scheme.
+The resolved vertical fluxes at the top layer of the model go to zero as $w$ goes to zero according to the no-flux boundary condition, and the sub-grid fluxes are determined using the scheme described below in place of the AMD scheme at the top layer.
 PALM is vertically discretized such that the ice boundary ($z=0$) is located at the edge of the top cell where the vertical velocity component resides and scalars and horizontal velocity components are located at mid-depth of the top cell ($z=-\frac{1}{2}\Delta_z$).
@@
 \begin{equation} \label{eq:tau}
-    \overline{w''u_i''}_b = u_* \frac{ \kappa \left[u_i\left(z_{\frac{1}{2}}\right) - u_b \right]}{\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right)-\Psi_m\left(\zeta_{\frac{1}{2}}\right)}
+    \overline{w''u_i''}_b = u_* \frac{ \kappa \left[u_i\left(z_{\frac{1}{2}}\right) - u_{i,b} \right]}{\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right)-\Psi_m\left(\zeta_{\frac{1}{2}}\right)}
 \end{equation}
@@
 $\zeta_k = z_k/L_O$ is the depth from the boundary scaled by the Monin-Obukhov length, $u_*$ is the friction velocity, and $z_0$ is the roughness length.
+The horizontal velocity at the boundary $u_{i,b}$ is always zero.
 The Monin-Obukhov length $L_O$, computed following \citeA{mcphee_dynamics_1987}, is a function of both $u_*$ and the melt rate.
@@
 
-Similarly the sub-grid fluxes of scalars are parameterized by
+Similarly, the sub-grid fluxes of scalars are parameterized by
 \begin{equation} \label{eq:melt_flux}
@@
 %
-where the exchange coefficients are defined following \cite{mcphee_dynamics_1987}:
+where the exchange coefficients are defined following \citeA{mcphee_dynamics_1987}:
 \begin{equation} \label{eq:gamma}
@@
 \end{equation}
-The coefficients of these stability functions are chosen as in \citeA{zhou_self-similar_2017} and are given in Table \ref{table:var}. The molecular flux component follows \citeA{mcphee_dynamics_1987}:
-\begin{equation}
-    \Gamma_{\theta,mol} = 12.5 \textrm{Pr}^{2/3} - 6, \:
-    \Gamma_{S,mol} = 12.5 \textrm{Sc}^{2/3} - 6
-\end{equation}
-where Pr is the Prandtl number and Sc is the Schmidt number.
-If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($\Gamma_{f}$, Table \ref{table:var}).
+The coefficients of these stability functions are chosen as in \citeA{zhou_self-similar_2017} and are given in Table~S1.
+The molecular flux components are constant in our simulations following \citeA{mcphee_dynamics_1987} and are also given in Table~S1.
+If a portion of the ice face experiences freezing, $\Gamma_\theta$ and $\Gamma_S$ are set to a higher value indicating destabilizing fluxes ($\Gamma_{f}$, Table~S1).
 
-Taking into account the role of meltwater advection, Equation \ref{eq:melt_flux} is replaced by the following ``virtual'' freshwater flux form in our implementation \cite{jenkins_role_2001, asay-davis_experimental_2016}:
+Taking into account the role of meltwater advection, Equation \ref{eq:melt_flux} is replaced by the following ``virtual'' freshwater flux form in our implementation since the freshwater flux is not a volume flux \cite{jenkins_role_2001, asay-davis_experimental_2016}:
 \begin{eqnarray}
-    \overline{w'\theta'}_{b,v} =& -c_p u_*
+    \overline{w''\theta''}_b =& -c_p u_*
     \left[\Gamma_{\theta} - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(\theta_b-\theta_{\frac{1}{2}}\right) \label{eq:vflux_heat}\\
-    \overline{w'S'}_{b,v} =& -u_*
+    \overline{w'S'}_b =& -u_*
     \left[\Gamma_S - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(S_b-S_{\frac{1}{2}}\right) \label{eq:vflux_salt}
@@
 %
-These equations specify that heat and salt are conserved at the ice-ocean interface (Equations \ref{eq:melt_1} and \ref{eq:melt_2}) and the interface temperature is fixed at the local freezing temperature $\theta_f$ (Equation \ref{eq:melt_3}).
-Equation \ref{eq:melt_1} assumes that the conductive heat flux into ice is negligible.
+These equations specify that heat and salt are conserved at the ice-ocean interface (Equations~\ref{eq:melt_1} and \ref{eq:melt_2}) and the interface temperature is fixed at the local freezing temperature $\theta_f$ (Equation~\ref{eq:melt_3}).
+Equation~\ref{eq:melt_1} assumes that the conductive heat flux into ice is negligible.
 $\rho_w$ denotes the density of freshwater.
@@
 The PALM implementation applies the fluxes $\overline{w''u_i''}_b$, $\overline{w''\theta''}_b$, $\overline{w''S''}_b$ at the center of the first grid cell from the boundary without interpolation (i.e., $\overline{w''X''}_b = \overline{w''X''}_{\frac{1}{2}}$).
-It is noted by the PALM developers that this error was found to be small, but this error has not been evaluated for the sub-ice case.
-This error would be small if the first $\sim$10 cm is largely a constant flux layer, as hypothesized by \citeA{mcphee_turbulent_1983}.
+It is noted by the PALM developers that this error was found to be small, but we have not confirmed this for the sub-ice case.
+This error would be small if the first $\sim$10 \unit{cm} were largely a constant flux layer, as hypothesized by \citeA{mcphee_turbulent_1983}.
 
@@
 The roughness length ($z_0$ in Equations~\ref{eq:tau} and \ref{eq:gamma_turb}) is chosen such that the equivalent drag coefficient assuming quadratic drag is 0.003, an intermediate value for sea ice and ice shelf bottoms, though poorly constrained \cite{holland_modeling_1999, holland_effects_2006, macayeal_numerical_1984, nicholls_measurements_2006}.
-A list of parameter choices can be found in Table~\ref{table:var}.
+A list of parameter choices can be found in Table~S1.
 
 We present two sets of simulations which have a base case in common.
-The base case has low far-field thermal driving of 0.15$^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field inertial oscillations of 20 cm s\textsuperscript{-1} generated by a 0.03 Pa m\textsuperscript{-1} pressure gradient.
-These conditions were chosen to favor an energetic regime, for reasons discussed in Section \ref{disc:dyn}.
+The base case has low far-field thermal driving of 0.15$^{\circ}$C and a relatively high slope for Antarctic ice shelves of 1$^{\circ}$ and vigorous far-field inertial oscillations of 20\,cm\,s\textsuperscript{-1} generated by a 0.03\,Pa\,m\textsuperscript{-1} pressure gradient.
+These conditions were chosen to favor an energetic regime, for reasons discussed in Section~\ref{disc:dyn}.
 To examine the relationship between thermal driving and melt rate, as well as turbulent flow characteristics, we vary the far-field thermal driving from 0.15$^{\circ}$C to 0.6$^{\circ}$C in the first set of simulations.
-Far-field thermal driving $\Delta \theta_\infty$ is defined as $\theta_{\infty} - \theta_f(S_{\infty})$.
+The far-field thermal driving, $\Delta \theta_\infty$, is defined as the difference between the far-field temperature ($\theta_{\infty}$) and the freezing temperature based on the far-field salinity ($\theta_f(S_{\infty})$).
 In the second set of simulations, we reduce the slope from 1$^{\circ}$ to 0.01$^{\circ}$.
-The ice base always slopes to the east in the positive x-dimension of our domain, thus $\beta = 0$.
-The far-field salinity for all runs is 35 g kg\textsuperscript{-1}.
+The ice base always slopes to the east in the positive x-dimension of our domain, thus $\beta = 90^{\circ}$.
+The far-field salinity for all runs is 35\,g\,kg\textsuperscript{-1}.
 Initially, both temperature and salinity increase with depth over the upper two-thirds of the domain.
@@
 
-The simulation duration is $\sim$50 h, corresponding to $\sim$4 inertial periods of 13 h.
+The simulation duration is 50 h, corresponding to $\sim$4 inertial periods of 13 h.
 By the end of our simulations, the time-mean kinetic energy of the flow has reached steady-state.
-However, the turbulent intensity for all cases continues to decline, with more pronounced turbulence kinetic energy (TKE) loss at lower slopes (Figure \ref{fig:timeseries}a,d).
-Many of the results presented are averaged over the last simulated inertial period and only the depths outside the sponge layer are shown.
+However, the turbulent intensity for all cases continues to decline, with more pronounced turbulence kinetic energy (TKE) loss at lower slopes (Figure~\ref{fig:timeseries}a,d).
+Unless stated otherwise, the results are presented as averages over the last simulated inertial period and over the domain excluding the sponge layer.
 
@@
 
-\input{table1_prm-only}
-
 \section{Results}\label{results}
@@
 % Description of time evolution
-Melt rates decline over the course of the simulations (Figure \ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs.
+Melt rates decline over the course of the simulations (Figure~\ref{fig:timeseries}), preventing the identification of steady-state melt rates for most runs.
 This decline is in response to the concomitant increase in stratification during the course of the simulations, which decreases vertical heat fluxes by reducing vertical turbulent fluctuations.
-We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we have used here.
-Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure S1).
-Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE loss (Figure S1d).
+We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we could computationally afford.
+Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes by at least a factor of two, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure~S1).
+Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE has been lost ($\leq\!0.1^{\circ}$ slopes, Figure~S1d).
 
@@
     \caption{Time evolution of (a,d) domain-averaged, resolved turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
-The black curve represents the same simulation in all panels.
-The time axis excludes the initial spin-up period.
-}
-    % Consider shading the analysis window
+The black curve represents the same simulation in all panels in this and subsequent figures.
+The analysis window, the last inertial period, is shaded.}
     % TODO add panel labels
@@
 
-We present depth-profiles of temperature, salinity, and velocity at the end of all simulations; Figure \ref{fig:dT_profiles} shows the results from the simulations in which we varied thermal driving, while Figure \ref{fig:dslope_profiles} shows those from the simulations with varying slope.
-All simulations show an evolution from the weakly stratified initial conditions to more strongly stratified conditions, particularly within the first 5 m of the ice-ocean interface (Figures \ref{fig:dT_profiles}b, \ref{fig:dslope_profiles}b).
+% Description of velocity profiles
+We present depth-profiles of temperature, salinity, and velocity at the end of all simulations (Figure \ref{fig:dT_profiles}).
+The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c,f removes a periodic signal from inertial oscillations of the geostrophic velocity with a characteristic magnitude of 20\,cm\,s\textsuperscript{-1}.
+Ekman rotation near the boundary can be seen in all simulations (Figs.
+\ref{fig:dT_profiles}c,f), but for more strongly sloped runs, buoyancy plays an increasingly strong role in driving the mean flow near the boundary.
+This effect can be seen most clearly by comparing the up-slope component of the flow within several meters of the ice-ocean interface across the slope-varying simulations (Figure \ref{fig:dT_profiles}f).
+These mean buoyancy effects increase flow velocities on the order of a few cm\,s\textsuperscript{-1} as slope varies from 0.01$^{\circ}$ to 1$^{\circ}$.
+Flow velocities near the boundary increase on the order of 10\,cm\,s\textsuperscript{-1} as far-field thermal driving increases from 0.5 to 0.6$^{\circ}$C at 1$^{\circ}$ slope (Figure \ref{fig:dT_profiles}c).
+This velocity increase is attributed to changes in the magnitude of buoyancy forcing near the boundary, related to differences in melt rates.
+The vertical momentum flux profiles shown in Figure~\ref{fig:flux_profiles}a,c reveal that flow is accelerated (negative fluxes) over much of the IOBL, with drag only dominating within the first few meters of the boundary.
 
@@
     \end{minipage}
-    \caption{Depth profiles of simulated properties as they vary with thermal driving, averaged over the last inertial period.
-(a) temperature relative to far-field temperature, (b) salinity relative to far-field salinity, and (c) velocity components.
-For panel (c), solid lines are in the y direction (positive north), dashed in x-direction (positive east, up-slope).}
-    \label{fig:dT_profiles}
-    % TODO add panel labels
-\end{figure}
-
-\begin{figure}[h!]
-    \centering
+    \newline
     \begin{minipage}{0.33\textwidth}
@@
     \end{minipage}
-    \caption{Depth profiles of simulated properties as they vary with slope, averaged over the last inertial period.
-(a) temperature relative to far-field temperature (b) salinity relative to far-field salinity (c) velocity components.
-For panel (c), solid lines are in the positive y direction, dashed in positive x-direction (up-slope).
-The black curve is common to both sets of simulations (see Figure \ref{fig:dT_profiles}).}
-    \label{fig:dslope_profiles}
+    \caption{Depth profiles of simulated properties as they vary with (a-c) thermal driving and (d-f) slope, averaged over the last inertial period.
+(a,d) temperature relative to far-field temperature, (b,e) salinity relative to far-field salinity, and (c,f) velocity in the y-direction (solid line, positive north, cross-slope) and in x-direction (dashed line, positive east, up-slope).
+}
+    \label{fig:dT_profiles}
     % TODO add panel labels
@@
 
-% Description of velocity profiles
-Ekman rotation near the boundary can be seen in all simulations (Figs.
-\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c), but for more strongly sloped runs, buoyancy plays an increasingly strong role in driving the mean flow near the boundary.
-This effect can be seen most clearly by comparing the up-slope component of the flow within several meters of the ice-ocean interface across the slope-varying simulations (Figure \ref{fig:dslope_profiles}c).
-These mean buoyancy effects increase flow velocities on the order of a few cm s\textsuperscript{-1} as slope varies from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:dslope_profiles}c).
-Flow velocities near the boundary increase on the order of 10 cm s\textsuperscript{-1} as far-field thermal driving increases from 0.5 to 0.6$^{\circ}$C at 1$^{\circ}$ slope (Figure \ref{fig:dT_profiles}c).
-This velocity increase is attributed to changes in the magnitude of buoyancy forcing at the boundary, related to differences in melt rates.
-The time-averaged far-field velocity shown in Figures~\ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c integrates inertial oscillations of the geostrophic velocity with a characteristic magnitude of 20 cm s\textsuperscript{-1}.
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_dTscale_z_profile.png}
+    \end{minipage}
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_z_profile.png}
+    \end{minipage}%
+    \begin{minipage}{0.33\textwidth}
+        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_slopescale_z_profile.png}
+    \end{minipage}
+    \caption{Vertical profiles of (a,c) momentum flux, (b,e) heat flux, and (c,f) scaled heat flux averaged over the last inertial period.
+The first row shows temperature cases, the second row shows slope cases.
+Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).
+Positive flux denotes upward flux (i.e., drag).
+The horizontal axis limits vary between panels.}
+    \label{fig:flux_profiles}
+    % TODO add panel labels
+\end{figure}
 
-% BL depth
-In none of the simulations do we observe a well-mixed the boundary layer well-mixed with respect to scalars, with varying degrees of stratification over the first 20 m from the boundary.
-Thus, we characterize the IOBL using a definition of the mixing layer depth as depth at which the dissipation rate drops below 10\textsuperscript{-9} m\textsuperscript{2} s\textsuperscript{-3} \cite{franks_has_2014, sutherland_mixed_2014}.
-Since shear is the primary source of TKE as discussed later in this section, the IOBL here can also be thought of as portion of the water column where shear originating at the boundary influences the flow.
-The boundary layer depth increases through time, reaching 15 -- 25 m at the end of the simulations.
-
+All simulations show an evolution from the weakly stratified initial conditions to more strongly stratified conditions, particularly within the first 5 m of the ice-ocean interface (Figures \ref{fig:dT_profiles}b,e).
+In none of the simulations do we observe a well-mixed boundary layer with respect to scalars.
+Rather, the simulations show varying degrees of stratification over the first 20 m from the boundary.
 Stratification within the boundary layer increases with thermal driving (Figure~\ref{fig:dT_profiles}a,b).
@@
 Conversely, stratification decreases with increasing slope, indicating that the increase in shear induced by the buoyant flow dominates over the increase in melt-induced buoyancy fluxes with slope.
-The simulated boundary layer depth has a strong relationship with local thermal driving (i.e., the difference between IOBL temperature and the freezing point), reflecting entrainment of warm water below and setting mixing lengthscales  within the IOBL.
 
@@
         _{F_{trans}} -
-        \hspace{-2mm}\underbrace{\frac{}{}\vareps}_{diss}
+        \hspace{-2mm}\underbrace{\frac{}{}\varepsilon}_{diss}
 \]
-
-Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure S2 and shows similar patterns.
-Shear production ($F_{shear}$) ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$ m\textsuperscript{2} s\textsuperscript{-3} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5 m of the boundary (Figure \ref{fig:tke_budget}a).
+Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure~S2 and shows similar patterns.
+Shear production ($F_{shear}$) ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$\,m\textsuperscript{2}\,s\textsuperscript{-3} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5 m of the boundary (Figure \ref{fig:tke_budget}a).
 The increase in TKE throughout the boundary layer as slope increases reflects this shear-induced turbulence (Figure \ref{fig:tke_budget}a).
@@
 % TKE budget, buoyancy
-Buoyancy production of turbulence ($F_{buoy}$) is 1 -- 2 orders of magnitude smaller than shear production, $\sim\!10^{-10} \textrm{--} 10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}.
+Buoyancy production of turbulence ($F_{buoy}$) is 1 -- 2 orders of magnitude smaller than shear production, $\sim\!10^{-10} \textrm{--} 10^{-9}$\,m\textsuperscript{2}\,s\textsuperscript{-3}.
 For a sloped ice shelf, the buoyancy term can be broken into two components, the horizontal buoyancy fluxes that increase turbulence when these fluxes are oriented upslope and the vertical buoyancy fluxes that decrease turbulence when ice is melting.
-Since our simulations only produce melting, the vertical component is always negative (dashed lines, Figure \ref{fig:tke_budget}b).
+Since our simulations only produce melting, the vertical component is always negative (dashed lines, Figure \ref{fig:tke_budget}c).
 Over the coarse of an inertial oscillation, the horizontal component of buoyancy production is generally positive when the mean flow is oriented upslope and negative when the the flow is oriented downslope.
-Interestingly, the time-averaged effect of a slope is destruction of turbulence near the boundary and production of turbulence near the base of the boundary layer (dotted lines, Figure \ref{fig:tke_budget}b).
+Interestingly, the time-averaged effect of a slope is destruction of turbulence near the boundary and production of turbulence near the base of the boundary layer (dotted lines, Figure \ref{fig:tke_budget}c).
 The net effect of both horizontal and vertical buoyancy components is the destruction of turbulence throughout the IOBL (solid lines, Figure \ref{fig:tke_budget}b), with the exception of the base of the IOBL where the horizontal buoyancy component augments entrainment.
@@
 The transport term ($F_{trans}$) contains two components, advection of TKE due to pressure fluctuations and turbulent advection of TKE.
-The former is negligible, reaching maximum values on the order of $10^{-12}$ m\textsuperscript{2} s\textsuperscript{-3} while the latter increases turbulence at the boundary with oscillations of decreasing amplitude with distance from the boundary (Figure \ref{fig:tke_budget}c).
+The former is negligible, reaching maximum values on the order of $10^{-12}$\,m\textsuperscript{2}\,s\textsuperscript{-3} while the latter increases turbulence at the boundary with oscillations of decreasing amplitude with distance from the boundary (Figure \ref{fig:tke_budget}d).
 
@@
 Since we evaluate resolved TKE ($e$), dissipation here represents the transfer of energy to the sub-grid scales; there is no flow of energy from sub-grid to resolved scales.
-In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$ m\textsuperscript{2} s\textsuperscript{-3} as seen in Figure \ref{fig:timeseries}a,c.
-Dissipation in the IOBL is on the same order as shear production ($10^{-9}$ m\textsuperscript{2} s\textsuperscript{-3}), as all other terms in the TKE budget are small.
+In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$\,m\textsuperscript{2}\,s\textsuperscript{-3} as seen in Figure \ref{fig:timeseries}a,c.
+Dissipation in the IOBL is on the same order as shear production ($10^{-9}$\,m\textsuperscript{2}\,s\textsuperscript{-3}), as all other terms in the TKE budget are small.
 
@@
     \centering
-    \begin{minipage}{0.5\textwidth}
+    \begin{minipage}{0.33\textwidth}
         \includegraphics[trim={0 0 0 0},clip, width=\textwidth]{Figures/eres_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
+    \begin{minipage}{0.33\textwidth}
         \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fshear_cmp_dslope_43h_tav13h_z_profile.png}    
@@
     \newline
-    \begin{minipage}{0.5\textwidth}
+    \begin{minipage}{0.33\textwidth}
         \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Fbuoy_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
+    \begin{minipage}{0.33\textwidth}
         \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/Ftrans_cmp_dslope_43h_tav13h_z_profile.png}
     \end{minipage}
-    \caption{(a) Simulated turbulence kinetic energy (TKE) for variable slope simulations averaged over the last inertial period and (b-d) TKE source terms over the same period.
+    \caption{(a) Simulated turbulence kinetic energy (TKE) and (b-d) TKE source terms for variable slope simulations averaged over the last inertial period.
 (b) Shear production.
-(c) Buoyancy production.
-The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted.
+(c) Buoyancy production: total (solid lines), vertical component (dashed), and upslope component (dotted).
 (d) TKE transport.
-Positive denotes production, negative destruction.
+Positive denotes production, negative destruction of TKE.
 Note that the x-axis scales differ between panels.}
@@
 The structures become increasingly filamentous (i.e., near-wall streaks, e.g., \citeA{del_alamo_spectra_2003, hoyas_scaling_2006}) and coherent as slope and thus the buoyancy-driven current increase.
-Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases;  velocity fluctuations are less confined to the slope-parallel direction (Figure S3).
-% consider discussing entrainment here
+Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases; velocity fluctuations are less confined to the slope-parallel direction (Figure~S3).
 
@@
 (c,d) Salinity in cross-section mid-way through the y-axis.
-(e,f) Cross-slope velocity fluctuations at 1 m below the ice-ocean interface.
-Note that the colorbar scale is smaller in (e) than (f).}
+(e,f) Cross-slope velocity fluctuations at 1 m below the ice-ocean interface.}
     % TODO add panel labels
     \label{fig:cross-section}
+\end{figure}
+
+% BL depth
+We define the base of the IOBL as the depth where the thermal driving relative to the far-field freezing point is 99\% of the far-field thermal driving.
+The IOBL depth increases through time, reaching 13 -- 19 m at the end of the simulations.
+The simulated boundary layer depth increases with the far-field thermal driving (from 13 -- 19 m) and with ice-shelf basal slope (from 15 -- 19 m), reflecting the increase in flow velocities across those parameter changes which drives entrainment into the IOBL.
+\ref{fig:intermittency} shows the temporal evolution of IOBL depth for a few simulations, with steady IOBL growth at low slopes and punctuated growth at higher slopes corresponding to trends in TKE.
+
+Given the temporal variability in TKE in these simulations, we use a threshold in dissipation rate to characterize the mixing layer depth, as distinct from the mixed layer depth.
+This criterion has been deployed for stratifying ocean boundary layers \cite{franks_has_2015, sutherland_mixed_2014}.
+We consider the mixing layer as the depth interval over which the horizontal- and hourly-averaged dissipation rate exceeds 10\textsuperscript{-9}\,m\textsuperscript{-2}\,s\textsuperscript{-3}.
+This mixing layer depth shows greater temporal variability than the IOBL depth as defined by scalar concentration, and drops below that IOBL depth during periods of enhanced entrainment (Figure \ref{fig:intermittency}).
+
+There are also time periods over which the dissipation rate drops below 10\textsuperscript{-9}\,m\textsuperscript{2}\,s\textsuperscript{-3} throughout the water column, indicating intermittency in turbulence.
+We note that these intervals of low dissipation do not correspond to complete loss of TKE, nor a shoaling of the IOBL depth as we have defined it (Figure \ref{fig:intermittency}).
+At higher slopes ($\geq 0.5^{\circ}$), this intermittency is interrupted as inertial oscillations enhance up-slope IOBL flow, increasing shear-driven mixing.
+This mixing front begins at the boundary and propagates to the base of the IOBL over a few hours (Figure \ref{fig:intermittency}b).
+For the less stratified, low-slope cases, the intermittency in turbulence is more frequent, as the IOBL flows more slowly and generates less TKE production by shear (Figure \ref{fig:intermittency}a).
+We discuss this intermittency and its possible implications further in Section \ref{disc:dyn}.
+
+\begin{figure}[h!]
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 0cm 0cm 0cm},clip,width=\textwidth]{Figures/dslope2/e_hovmoller.png}
+    \end{minipage}%
+    \begin{minipage}{0.5\textwidth}
+        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/e_hovmoller.png}
+    \end{minipage}
+    \caption{Horizontally-averaged turbulence characteristics for (a) 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope case and (b) 0.6$^{\circ}C$ thermal driving, 1$^{\circ}$ slope case.
+Turbulence is considered intermittent when the dissipation contour of 10\textsuperscript{-9}\,m\textsuperscript{2}\,s\textsuperscript{-3} (dashed line) reaches the boundary.
+Significant turbulence kinetic energy (TKE, green-yellow shading) can be present when dissipation is low.
+Higher TKE at -25 m at later times in (a) is due to turbulent transport, while the higher TKE at later times in (b) is due to shear production.
+IOBL depth is contoured in black.
+}
+    \label{fig:intermittency}
+    % TODO add panel labels
 \end{figure}
@@
 During low-melt periods, the far-field flow is oriented down-slope and shear production of TKE is concentrated a few meters away from the boundary.
-
-% intermittent turbulence
 Melt rate fluctuations increase in amplitude as thermal driving increases and as slope increases, which we attribute to the increasing importance of buoyancy forcing in driving a near-boundary plume and thus determining the depth-distribution of shear.
-At higher slopes ($\geq 0.5^{\circ}$), inertial oscillations enhance shear mixing first near the boundary; this mixing front then propagates to the base of the IOBL over a few hours (Figure \ref{fig:intermittency}b).
-The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a dramatic reduction in vertical velocity fluctuations during the down-slope flow period.
-This can be seen in the time series of friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b).
-In all simulations, there is periodic intermittency in turbulence below the IOBL interrupted by the penetration of shear-induced turbulence when the IOBL buoyantly accelerates.
-We discuss these rotational effects on turbulent intensity further in Section \ref{disc:dyn}.
-
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.4\textwidth}
-        \includegraphics[trim={0 0cm 3cm 0cm},clip,width=\textwidth]{Figures/dslope2/e_hovmoller.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0cm 0 0cm},clip,width=\textwidth]{Figures/dT4/e_hovmoller.png}
-    \end{minipage}
-    \caption{Example of turbulent intermittency as seen in white regions of turbulence kinetic energy (TKE).
-(a) A non-intermittent case: 0.1$^{\circ}C$ thermal driving, 0.01$^{\circ}$ slope.
-(b) An intermittent case: 0.6$^{\circ}C$ thermal driving, 1$^{\circ}$ slope.}
-    \label{fig:intermittency}
-    % TODO add panel labels, add IOBL contour
-\end{figure}
+The two simulations associated with the highest thermal driving values, and the highest near-boundary stratification, experience a dramatic reduction in melt rates during the down-slope flow period.
+This coincides with reduced friction velocity (i.e., shear stress) at the ice interface (Figure \ref{fig:timeseries}b) and reduced vertical velocity fluctuations (not shown).
 
 % Melt rate sensitivity to thermal driving
-Time-averaged melt rates depend fairly linearly on far-field thermal driving (Figure \ref{fig:melt_sensitivity}a).
+Time-averaged melt rates depend fairly linearly on far-field thermal driving (Figure \ref{fig:melt_sensitivity}a, $R^2=0.97$).
 This is mostly attributable to a linear relationship between melt rate and interfacial thermal driving, as differences in friction velocity and the thermal exchange coefficient are small and do not have a systematic relationship with far-field thermal driving.
@@
     \caption{Melt rate sensitivity to (a) far-field thermal driving and (b) sine of the basal slope.
-(c,d) Key controls on the value of the thermal exchange coefficient ($\Gamma_{T,der}$) that would accurately predict melt rates given accurate measurements of velocity and temperature 2 m from the ice base.
 (c) Far-field thermal driving is inversely related to $\Gamma_{T,der}$.
 Dashed line denotes the value recommended by \citeA{jenkins_observation_2010}.
-The largest points correspond to the fourth and last inertial cycle with progressively smaller points for previous inertial cycles.
+The largest points correspond to the fourth inertial cycle with progressively smaller points for previous inertial cycles.
 (d) For variations in slope, the simulated friction velocity (solid points) is linearly related to $\Gamma_{T,der}$.
@@
     % TODO add panel labels
+    % TODO add linear fits to a,b,d
 \end{figure}
@@
 These differences in friction velocity arise from higher IOBL velocities and turbulence at higher slopes.
-We observe threshold behavior in melting in the two lowest-slope cases, can be attributed to similar friction velocities arising from similar IOBL velocities and turbulence (Figure \ref{fig:melt_sensitivity}d and Figure \ref{fig:dslope_profiles}c,d).
+We observe threshold behavior in melting in the two lowest-slope cases, which can be attributed to similar friction velocities arising from similar IOBL velocities and turbulence (Figure \ref{fig:melt_sensitivity}d and Figure \ref{fig:dT_profiles}f).
 This behavior is discussed in more detail in Section \ref{disc:prm_sens}.
-The differences in derived thermal exchange coefficient are not pronounced as slope varies, on the order of a 10\% change as slope increases from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:melt_sensitivity}d).
+The differences in derived thermal exchange coefficient with varying slope are not pronounced, on the order of a 10\% change as slope increases from 0.01$^{\circ}$ to 1$^{\circ}$ (Figure \ref{fig:melt_sensitivity}d).
 
-Vertical scalar fluxes are shown in Figure \ref{fig:heatflux_profiles}a,b.
+Vertical heat fluxes are shown in Figure \ref{fig:flux_profiles}b,e.
 The vertical heat flux has a maximum at the ice-ocean interface and decreases throughout the IOBL, with small values below the pycnocline.
-Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure S4).
-The vertical salt flux profiles are shown in Figure S5 and have a very similar shape to the vertical heat flux profiles.
+Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure~S4).
+The vertical salt flux profiles are shown in Figure~S5 and have a very similar shape to the vertical heat flux profiles.
 
@@
 The linear scaling of melt rate with thermal driving suggests a linear scaling of heat flux profiles with thermal driving.
-We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (Figure \ref{fig:timeseries}c, \ref{fig:heatflux_profiles}c,  pink curves).
-The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:heatflux_profiles}c).
+We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (Figure \ref{fig:timeseries}c, \ref{fig:flux_profiles}c,  pink curves).
+The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:flux_profiles}c).
 Scalar fluxes decline near the boundary for the 1$^{\circ}$ slope cases, a feature that we discuss further in Section \ref{disc:prm_vmix}.
 
-\begin{figure}[h!]
-    \centering
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dT_43h_tav13h_dTscale_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/heatflux_cmp_dslope_43h_tav13h_slopescale_z_profile.png}
-    \end{minipage}
-    \caption{Vertical profile of heat flux averaged over the last inertial period for (a,c) temperature cases and (b,d) slope cases.
-(a,b) are in physical units while (c,d) are scaled by the Ekman depth, far-field thermal driving, and slope.
-The black curve is represents the same simulation in all panels.
-The horizontal axis limits vary between panels.}
-    \label{fig:heatflux_profiles}
-    % TODO add panel labels
-\end{figure}
-
 % Scaling heat flux profiles with slope
-Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($(\sin\alpha)^{1/4}$, Figure \ref{fig:heatflux_profiles}d).
+Despite melt rates scaling reasonably well with the basal slope ($\sin \alpha$), the vertical heat flux profile does not, showing a much lower sensitivity to slope ($(\sin\alpha)^{1/4}$, Figure \ref{fig:flux_profiles}f).
 There is strong agreement between the scaled vertical heat flux profiles at different slopes, though the threshold behavior at low slopes noted in melt rates is replicated here.
@@
 
-% momentum flux profiles
-By looking at the variation of momentum flux with depth shown in Figure \ref{fig:momflux_profiles}, we can examine the relative contributions of interfacial drag and buoyant acceleration of the IOBL to the velocity profiles shown in Figure \ref{fig:dT_profiles}c and \ref{fig:dslope_profiles}c.
-Since the mean velocity is oriented both upslope (+$u$) and cross-slope (+$v$), positive $\overline{u'w'}$ and $\overline{v'w'}$ close to the interface indicate slowing of the current due to drag whereas negative $\overline{u'w'}$ and $\overline{v'w'}$ a few m below the interface through much of the boundary layer indicate buoyant acceleration of the IOBL.
-The amplitude of momentum fluxes increases with slope and thermal driving consistent with increases in IOBL velocity and TKE.
-
-\begin{figure}[h!]
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dT_43h_tav13h_z_profile.png}
-    \end{minipage}%
-    \begin{minipage}{0.5\textwidth}
-        \includegraphics[trim={0 0 0 0},clip,width=\textwidth]{Figures/momflux_cmp_dslope_43h_tav13h_z_profile.png}
-    \end{minipage}
-    \caption{Momentum flux averaged over the last inertial period for (a) thermal driving cases and (b) slope cases.
-Momentum flux is expressed in two components:  $\overline{u'w'}$ (dashed) and $\overline{v'w'}$ (solid).
-Positive flux denotes upward flux (i.e., drag) and }
-    \label{fig:momflux_profiles}
-    % TODO add panel labels
-\end{figure}
-
 \section{Discussion}\label{disc}
@@
 
-In the simulations presented here, turbulence declines throughout the course of the simulation; for a few highly stratified cases becoming intermittent.
+In the simulations presented here, turbulence declines throughout the course of the simulation, becoming intermittent.
 The relationship between stable stratification, shear, and the persistence of turbulence remains an open question \cite{zonta_stably_2018}.
@@
 However, we found that the buoyancy term added to this scheme by \citeA{abkar_large-eddy_2017} had an unrealistically high magnitude in the vicinity of the ice base where gradients are large.
-We removed this term as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here, which is significantly lower than that used by \citeA{vreugdenhil_stratification_2019} but enables us to extend the domain allow for the development of a $\sim$20 m-thick IOBL.
+We removed this term, as \citeA{vreugdenhil_stratification_2019} found it to be negligible, but our unrealistic solution for this term suggests that AMD scheme may not perform optimally at the resolution employed here.
+Though the resolution of our simulations is significantly lower than that used by \citeA{vreugdenhil_stratification_2019}, it enables us to extend the domain from their 2 m to 64 m to allow for the development of a thicker IOBL.
 
@@
 This is not the first study to find the emergence of intermittent turbulence in stably stratified, sub-ice settings \cite{vreugdenhil_stratification_2019}.
-Flow relaminarization occurs periodically in our most strongly stratified simulations; stratification coincident with high thermal driving and high melt rates.
 \citeA{donda_collapse_2015} have argued that, in strongly stratified flows, the cessation of turbulence is transient provided there are sufficiently large perturbations.
-This is consistent with our finding that the temporal variability in shear over inertial oscillations provides a sufficient perturbation to reinitiate turbulence.
+This is consistent with our finding that the temporal variability in shear over inertial oscillations provides sufficient perturbations to reinitiate turbulence.
 Our simulations approach a gradient Richardson number ($Ri_g$) of 0.25, which is considered to be the approximate value at which turbulence neither grows nor decays \cite{rohr_growth_1988, holt_numerical_1992}.
@@
 However, when turbulence is intermittent, as it is in this study, the application of LES may be inappropriate due to its inherent horizontal averaging over laminar and turbulent regions \cite{stoll_large-eddy_2008}.
-Thus, our results at the highest thermal-driving values should be interpreted with caution.
+Thus, our results at the highest thermal-driving values for which stratification is strongest should be interpreted with caution.
 
@@
 Nonetheless, it appears as though well-mixed boundary layers are seen for a narrower range of conditions in simulations than in observations.
-The background flow chosen in these simulations is quite strong at 20 cm s\textsuperscript{-1} and thermal driving is relatively low such that we expected to produce a well-mixed boundary layer as is observed in melting regions of the Filchner-Ronne Ice Shelf \cite{nicholls_oceanographic_2001}.
+The background flow chosen in these simulations is quite strong at 20\,cm\,s\textsuperscript{-1} and thermal driving is relatively low such that we expected to produce a well-mixed boundary layer as is observed in melting regions of the Filchner-Ronne Ice Shelf \cite{nicholls_oceanographic_2001}.
 However, observations to date are insufficient to fully characterize the regime space for a well-mixed IOBL \cite{malyarenko_synthesis_2020}.
@@
 
-% Consider discussing boundary layer depth and entrainment
-
-% Consider leading this section with the discussion of shear-driven turbulence
 Shear-driven turbulence within the IOBL plays a central role in determining vertical heat fluxes and thus melt rates.
@@
 However, we believe that our transient solutions do provide some indications of how melt rates and boundary layer properties depend on ocean temperature and ice-shelf slopes.
-One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure S7).
+One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure~S7).
 On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}e-f).
@@
 The linear relationship we find between local, far-field ocean temperature and melt rates is consistent with some previous studies in ice-shelf settings \cite{rignot_rapid_2002, holland_response_2008, vreugdenhil_stratification_2019}.
-A slightly higher exponent of $4/3$ is reported for the local, near-field thermal driving in the regime in which convective rather than shear instabilities control melting \cite{kerr_dissolution_2015}.
+A slightly higher exponent of $4/3$, which is also consistent with our data ($R^2=0.95$), is reported for the local, near-field thermal driving in the regime in which convective rather than shear instabilities control melting \cite{kerr_dissolution_2015}.
 In contrast, in sea-ice settings this sensitivity of melt rates to local thermal driving was found to be significantly smaller with an exponent of 0.38 \cite{ramudu_large_2018}.
-It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies a widespread increase in thermal driving (i.e., changes to the water masses entering the ice-shelf cavity).
+It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies a distant increase in thermal driving (i.e., changes to the water masses entering the ice-shelf cavity).
 The relationship between melt rate and distant thermal driving is a function of both the relationship between the local thermal driving and melt rate and the relationship between distant thermal driving and friction velocity \cite{holland_response_2008}.
-The former relationship is addressed by this study; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity is unchanged.
+The former relationship is addressed by this study; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity remains constant.
 We note that the often cited quadratic relationship between thermal driving and melting pertains to this distant thermal driving  \cite{holland_response_2008}; studies generally find this exponent to be between 1.5 and 2 \cite{little_how_2009, jourdain_ocean_2017, favier_assessment_2019}.
@@
 To some extent, this linear relationship between far-field thermal driving and melt rate is embedded in the parameterization of heat fluxes employed at the ice base in these simulations.
-Specifically, the melt rate is prescribed to have a linear dependence on the thermal driving using the temperature in the first model layer, see Equation~\ref{eq:melt_flux}.
-However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL all mediate this relationship between \textit{far-field} temperature and melt rates, and yet the dependence from these simulations is still fairly linear.
+Specifically, the melt rate is prescribed to have a linear dependence on the \textit{local} thermal driving, based on the temperature in the first model layer (Equation~\ref{eq:melt_flux}).
+However, the level of stratification near the ice base, the buoyant acceleration of the IOBL plume and the transport of heat from depth to the IOBL all mediate the relationship between \textit{far-field} temperature and melt rates, and yet the dependence from these simulations is still fairly linear.
 
@@
 The relationship between melt rate and ice-shelf basal slope ($m \propto (\sin\alpha)^{n}$) combines two effects: the effect of ice-shelf slope on the IOBL's mean velocity profile and the effect of ice-shelf slope on IOBL turbulence.
-In the three-equation parameterization of ice-shelf melting, the former has the strongest effect on the friction velocity, derived from the mean flow velocity at a given depth; whereas the latter figures in the value of the scalar exchange coefficients, with higher values indicating more efficient turbulent transport.
+In the three-equation parameterization of ice-shelf melting, the former has the strongest effect on the friction velocity, derived from the mean flow velocity at a given depth; whereas the latter is represented by the scalar exchange coefficients, with higher values indicating more efficient turbulent transport.
 We return to the implications of our study for exchange coefficients in Section \ref{disc:prm_gamma}.
@@
 Thus, we cannot fully assess the the effect of ice-shelf slope on the IOBL's mean velocity profile.
-This effect is addressed by \citeA{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citeA{little_how_2009} who found $n=0.94$ for the range of slopes considered here.
-Our finding that $n=1$ may be applicable to the shear-dominated regime, in contrast to the sensitivity of $n=2/3$ found in the convection-dominated regime at higher slopes than those simulated here (5$^{\circ}$ -- 90$^{\circ}$) \cite{mondal_ablation_2019, mcconnochie_dissolution_2018}.
+This effect is addressed by \citeA{magorrian_turbulent_2016}, whose scaling analysis predicted $n=3/2$, and \citeA{little_how_2009}, who found $n=0.94$ for the range of slopes considered here.
+Our finding that $n=1$ may be applicable to the shear-dominated regime, in contrast to the sensitivity of $n=2/3$ found in the convection-dominated regime at higher slopes than those simulated here \cite<5$^{\circ}$ -- 90$^{\circ}$;>{mondal_ablation_2019, mcconnochie_dissolution_2018}.
 However, we emphasize that further investigation is needed beyond the small number of simulations presented here to validate our results.
@@
 % Methodology for evaluating thermal exchange coefficient
-The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.25m below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties meters to tens of m below the ice-ocean interface.
+The thermal exchange coefficient as computed using Equation \ref{eq:gamma} at 0.125\,m below the ice-ocean interface (the uppermost grid cell) differs from that which would be implemented by coarse-resolution models or derived from oceanographic observations, both of which only know ocean properties meters to tens of m below the ice-ocean interface.
 To demonstrate the implications of this study for modeling endeavors, we computed the thermal exchange coefficient that yields the simulated melt rate using ocean properties (temperature and velocity) 2 m below the ice-ocean interface.
@@
 The first is the choice of the parameterization of fluxes at the ice-ocean interface (i.e., over sub-meter scales).
-We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov lengthscale (Equation~\ref{eq:Kh}).
-We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \cite{monin_basic_1954, mcphee_air-ice-ocean_2008}, and the depth-scaling of scalar fluxes in a more highly resolved sub-ice LES \cite{vreugdenhil_stratification_2019}.
+We chose a stability-dependent parameterization in which the buoyancy forcing from melting enters through the Monin-Obukhov length (Equation~\ref{eq:psi}).
+We believe there is a stronger case for the flux parameterization we implement than for a constant thermal exchange coefficient in light of the success of Monin-Obukhov Similarity Theory \cite{monin_basic_1954, mcphee_air-ice-ocean_2008}, and the depth-dependence of scalar fluxes in a more highly resolved sub-ice LES \cite{vreugdenhil_stratification_2019}.
 Consequently, that study also found that thermal exchange coefficients were less than the \citeA{jenkins_observation_2010} value for all but the lowest thermal driving case.
@@
 This enhanced turbulent efficiency is due to enhanced shear instabilities, and is reflected in turbulent diffusivities parameterized by the AMD scheme.
-Much greater variability in turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure S4).
+Much greater variability in sub-grid turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure~S4).
 
@@
 These simulations do not reveal whether a similar, linear relationship between friction velocity and thermal exchange coefficient holds when the background flow is varied rather than the slope.
-LES of sea ice melting, for which there is no slope, suggests a sublinear relationship between thermal exchange coefficient and friction velocity ($\Gamma_T \propto u_*^{0.5}, \overline{w^\prime \theta^\prime} \propto u_*^{1.5}$, \citeA{ramudu_large_2018}).
+LES of sea ice melting, for which there is no slope, suggests a sublinear relationship between thermal exchange coefficient and friction velocity \cite<$\Gamma_T \propto u_*^{0.5},\:\overline{w^\prime \theta^\prime} \propto u_*^{1.5}$;>{ramudu_large_2018}.
 More studies will be required to determine this scaling.
@@
 \citeA{jenkins_shear_2021} demonstrated significantly different IOBL characteristics when KPP is the turbulence closure scheme in contrast to a low- or high-order scheme.
-The eddy viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (his Figure 3).
-Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or a modified KPP scheme in sub-ice settings, such as one based on the shape functions presented here.
+The eddy viscosity simulated by our LES model shows better agreement with the viscosity solutions from \citeA{jenkins_shear_2021} employing the low- and high-order turbulence closure schemes than that employing KPP (compare our Figure S6 with his Figure 3).
+Thus, this study offers additional support for the use of a more sophisticated turbulence closure scheme or a modified KPP scheme in sub-ice settings, such as one based on the depth-dependence of vertical turbulent fluxes presented here (Figure \ref{fig:flux_profiles}).
 
@@
 This flow is unlikely to be resolved by most ocean models, which have typical vertical resolutions near the interface of 10s m though some model configurations are reaching $\sim\!$1 m resolutions \cite{gwyther_cold_2020}.
-This then raises additional considerations for the parameterization of ice-ocean interface scalar and momentum fluxes.
 If the buoyancy-driven boundary current is unresolved in most coarse-resolution ocean models, then the friction velocity as computed from a quadratic drag law and the velocity at the first grid cell is likely to underestimate the true friction velocity.
@@
 % scalar flux profiles
-Our simulated depth-dependent shape function for vertical scalar fluxes agrees with the shape of the turbulent scalar flux parameterization of \citeA{mcphee_dynamics_1987} within the first $\sim\!$5 Ekman depths, which features a linear decrease in vertical fluxes with distance from the boundary within the IOBL.
+Our simulated depth-dependence for vertical scalar fluxes agrees with the shape of the turbulent scalar flux parameterization of \citeA{mcphee_dynamics_1987}, which features a linear decrease in fluxes with distance from the boundary within the IOBL.
 The low thermal-driving simulations with slopes of 1$^{\circ}$ diverge from this linear behavior within a few m from the boundary.
 We attribute this to boundary effects that reduce TKE and eddy viscosity close to the boundary, reminiscent of the constant flux layer predicted by Monin-Obukhov Similarity Theory \cite{monin_basic_1954}.
-Since these differences in eddy viscosity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes.
-This scaling for IOBL fluxes should be explored under a broader range of conditions to determine whether it is broadly applicable and whether vertical mixing parameterizations need to account for a constant flux layer in the IOBL.
+It is unclear whether a constant flux layer is absent under some conditions or whether our simulations do not resolve it for those highly-stratified cases.
+Since these differences in eddy viscosity are incorporated into the Ekman depth scaling, the scaled heat flux profiles all show quasi-linear slopes (Figure \ref{fig:flux_profiles}c,f).
+This linear depth-scaling for IOBL fluxes should be explored under a broader range of conditions and at higher resolution to determine whether it is broadly applicable and whether vertical mixing parameterizations need to improve their representation of the constant flux layer in the IOBL.
 
-A few complexities are immediately apparent in pursuing this path toward vertical scalar flux parameterization.
+A few complexities are immediately apparent in pursuing a depth-dependent shape function for vertical scalar flux parameterization.
 One is that a functional form for the eddy diffusivity is also needed to compute the Ekman depth.
@@
 Near-interface stratification significantly decreases drag \cite{garcia-villalba_turbulence_2011, mcphee_revisiting_2008}.
-Representing this reduction in drag through the drag coefficient necessarily removes the melt-rate dependence of drag through stratification.
-The addition of an ice-shelf slope to ocean models that do not fully resolve a buoyant plume further complicates the parameterization of momentum fluxes at the ice-ocean interface.
-A depth-dependent shape function for momentum fluxes which may prescribe negative (downward) momentum fluxes at the top grid cell below ice shelves for typical ocean model resolutions (see Figure \ref{fig:momflux_profiles} at, e.g., 5 m depth).
+Tuning the drag coefficient to fit present-day melt rates neglects the functional dependence of drag on melt rate through stratification (as represented by the Monin-Obukhov length).
+The presence of an ice-shelf slope in ocean models that do not fully resolve a buoyant plume further complicates the parameterization of momentum fluxes at the ice-ocean interface.
+A depth-dependent shape function for momentum fluxes which may prescribe negative (downward) momentum fluxes at the top grid cell below ice shelves for typical ocean model resolutions (see Figure \ref{fig:flux_profiles}a,d at, e.g., 5 m depth).
 In other words, when the buoyant plume is unresolved, the momentum boundary condition may need to accelerate the flow at the boundary (at least in the up-slope direction) to produce more accurate shear-driven mixing in the resolved portion of the domain.
@@
 We also suggest that the thermal exchange coefficient should be enhanced at higher slopes to account for shear instabilities that are unresolved by coarse-resolution ocean models, with the caveat that our simulations did not reach steady-state.
+
 Ultimately, we acknowledge that there is currently no universal guidance for parameterizing sub-grid scalar and momentum fluxes near the ice base for ocean models, each of which capture IOBL flow differently depending on resolution, vertical coordinate, numerical representations of the pressure gradient, and likely other aspects of the implementation \cite{gwyther_cold_2020}.
@@
 
-This work was funded by the U.S.
-Department of Energy (DOE), Office of Science, Biological and Environmental Research, and Advanced Scientific Computing Research programs.
-Carolyn Begeman received funding for this work from a Chick Keller Postdoctoral Fellowship through the Center for Earth and Space Sciences at Los Alamos National Laboratory.
-Computing resources were provided by the Los Alamos National Laboratory Institutional Computing Program, which is supported by the U.S.
-Department of Energy National Nuclear Security Administration under Contract No.
+This research was supported by the Los Alamos National
+Laboratory (LANL) through its Center for Space and Earth Science
+(CSES). CSES is funded by LANL’s Laboratory Directed Research
+and Development (LDRD) program under project number
+20210528CR.
+This research was also supported by the LDRD program of LANL under project numbers 20210289ER and 20180549ECR.
+Support for simulation data analysis pertaining to ice-shelf melt parameterization and manuscript preparation was provided through the Scientific Discovery through Advanced Computing (SciDAC) program funded by the US Department of Energy (DOE), Office of Science, Advanced Scientific Computing Research and Biological and Environmental Research Programs.
+Computing resources were provided by the LANL Institutional Computing Program, which is supported by the U.S.
+DOE National Nuclear Security Administration under Contract No.
 89233218CNA000001.

### 2021-10-06 Response_reviewers_rev1.tex

@@
 It would be interesting to see how friction length changes over slope, assuming eddy viscousity is estimated as a product of friction velocity and mixing length.\\
-%XX
+\textit{Unfortunately, we have not output all of the 2-d friction velocity and momentum flux fields at the ice boundary necessary to compute a friction length as you define it.
+Furthermore, since the eddy viscosity at the boundary is defined by our subgrid near-wall scheme (Section \ref{meth:tcm}), the key controls are gradients in velocity and stratification.
+We can show that the horizontally-averaged friction velocity has a close relationship with the resolved TKE 2m from the boundary (figure below).
+}
+\begin{figure}
+    \centering
+    \includegraphics{Figures/us_eres_dslope_t43h_tav13h_fit.png}
+    \caption{Caption}
+    \label{fig:R1}
+\end{figure}
 

### 2021-10-06 main_rev1.tex

--- 2021-08-02 main.tex
@@
 Small scale, turbulent flow below ice shelves is regionally isolated and difficult to measure and simulate.
-Yet these small scale processes, which regulate heat transfer between the ocean and ice shelves, can affect sea-level rise by altering the ability of Antarctic ice shelves to “buttress” ice flux to the ocean.
+Yet these small scale processes, which regulate heat and salt transfer between the ocean and ice shelves, can affect sea-level rise by altering the ability of Antarctic ice shelves to “buttress” ice flux to the ocean.
 In this study, we improve our understanding of turbulence below ice shelves by means of large-eddy simulations at sub-meter resolution, capturing boundary layer mixing at scales intermediate between laboratory experiments or direct numerical simulations and regional or global ocean circulation models.
@@
 A new parameterization of ice-shelf melting that accounts for the dynamics of IOBL turbulence is needed to achieve a more physically based, accurate coupling of ice sheets and oceans in climate models \citep{dinniman_modeling_2016, edwards_projected_2021, gwyther_cold_2020, naughten_future_2018}.
+Supercooling of the IOBL and frazil ice accretion to the ice-shelf base are also regionally important processes for cold cavities, but are not the focus of this work \citep{galton-fenzi_modeling_2012, jordan_conditional_2015}.
 
 % Overview of IOBL turbulence lit
-IOBLs present unique conditions in the global ocean, involving a stabilizing flux from phase change (ice-melting) and a boundary layer that is positively buoyant against a sloping boundary.
+IOBLs present unique conditions in the global ocean, involving a stabilizing buoyancy flux from melting ice and a boundary layer that is positively buoyant against a sloping boundary.
 There is a rich literature on stably-stratified boundary layers (typically under constant stabilizing flux boundary conditions), but the dependence of heat, salt and momentum fluxes on stratification remains a difficult problem, especially for strongly stratified regimes \citep{zonta_stably_2018}.
-The IOBL has most frequently been explored at small scales through laboratory experiments and direct numerical simulations, with some recent numerical studies addressing intermediate scales \citep{middleton_numerical_2021, mondal_ablation_2019, vreugdenhil_stratification_2019}.
+IOBL turbulence has been explored through laboratory experiments, direct numerical simulations, and large-eddy simulations \citep{middleton_numerical_2021, mondal_ablation_2019, vreugdenhil_stratification_2019, mcconnochie_dissolution_2018, rosevear_role_2021}.
 However, this body of work has not yet matured to setting a new standard for ice-shelf melt parameterization in ocean models.
@@
         \frac{\partial u_i}{\partial t} &= 
-        -\frac{\partial u_i u_j}{\partial x_i}
+        -\frac{\partial u_i u_j}{\partial x_j}
         -\varepsilon_{ijk} f_j u_k 
@@
         -\frac{\partial u_j \theta}{\partial x_j} 
-        - \frac{\partial}{\partial x_j}\left(\overline{u''_i \theta''}\right) 
+        - \frac{\partial}{\partial x_j}\left(\overline{u''_j \theta''}\right) 
         + \Phi_{\theta}\label{eq:ptprog}\\
@@
         -\frac{\partial u_j S}{\partial x_j} 
-        - \frac{\partial}{\partial x_j}\left(\overline{u''_i S''}\right) 
+        - \frac{\partial}{\partial x_j}\left(\overline{u''_j S''}\right) 
         + \Phi_{S}\label{eq:saprog}
@@
 
-The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow, buoyancy forcing, a correction for divergence in the flow using the pressure perturbation $\pi^*$ (imposing incompressibility), and sub-grid scale momentum flux.
+The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow with a geostrophic velocity $u_g$, buoyancy forcing, a correction for divergence in the flow using the pressure perturbation $\pi^*$ (imposing incompressibility), and sub-grid scale momentum flux.
 All prognostic variables are considered filtered at the grid scale.
@@
 \end{align}
-where $g_z$ is the magnitude of gravitational acceleration in the geopotential z-direction, $\beta$ is the angle the up-slope direction makes with north, and $\alpha$ is the slope angle from horizontal.
+where $g_z$ is the magnitude of gravitational acceleration in the geopotential z-direction, $\beta$ is the angle the up-slope direction makes with north, and $\alpha$ is the slope angle from horizontal or equivalently the angle between the z-axis and $\vec{g}$.
 For the rotated Coriolis vector $\vec{f}$, $\Omega$ is the rotation rate and $\phi$ is the latitude.
@@
 The buoyancy term in Equation~\ref{eq:uprog} combines the contributions of along-slope pressure gradient due to the slope of the ice shelf in hydrostatic equilibrium and buoyancy due to changes in density relative to the ambient density of the water column $\rho_a$.
+We use the nonlinear equation of state from \citet{jackett_algorithms_2006} to compute densities.
 $\rho_a$ varies along slope and with depth from the ice interface as a function of the hydrostatic pressure:
@@
 
-\subsection{Turbulence closure}\label{meth:tcm}
+We employ PALM's implementation of the \citet{piacsek_conservation_1970} second-order advection scheme for momentum and scalars and a third-order Runge-Kutta timestepping scheme.
+We also use the \citet{temperton_generalized_1992} Fast-Fourier Transform algorithm for the pressure solver.
 
 The turbulence closure scheme is Anisotropic Minimum Dissipation \cite[AMD;][]{rozema_minimum-dissipation_2015} employing the extension to scalars introduced by \citet{abkar_minimum-dissipation_2016}.
-We validated our implementation against the stable atmospheric boundary layer test case published in \citet{abkar_large-eddy_2017}.
+We validated our implementation against the stable atmospheric boundary layer test case published in \citet{abkar_large-eddy_2017} and \citet{stoll_large-eddy_2008}.
+We follow \citet[]['s]{abkar_large-eddy_2017}'s model set-up exactly and chose their moderate resolution with 72 x 72 x 72 grid points.
+Our results are in good agreement with \citet[]['s]{abkar_large-eddy_2017} solution employing another LES model with AMD (boundary layer height differs by <10\%) and other LES models with different turbulence closures (Fig.
+S1, their Fig.
+1 and references therein).
 Typical sub-grid scale momentum and scalar diffusivities in our sub-ice-shelf simulations of stratified turbulence range from $10^{-5}$ to $10^{-4}$\,\unit{m^2\,s^{-1}} in the upper two-thirds of the domain where damping is not applied (the damping methodology is discussed in Section \ref{meth:setup}).
+
+\subsection{Boundary conditions for ice-shelf melting}\label{meth:tcm}
 
@@
 %
-where the exchange coefficients are defined following \citet{mcphee_dynamics_1987}:
+where the exchange coefficients are defined with two terms, one representing turbulent transfer within the turbulent surface layer and one representing molecular transfer within the viscous sublayer following \citet{mcphee_dynamics_1987} (their Equation 11):
 \begin{equation} \label{eq:gamma}
-    \Gamma_{\theta}^{-1} = \left(\Gamma_{\theta,turb} + \Gamma_{\theta,mol}\right)^{-1},\:
-    \Gamma_S^{-1} = \left(\Gamma_{S,turb} + \Gamma_{S,mol}\right)^{-1}
+    \Gamma_{\theta} = \left(\Gamma_{\theta,turb} + \Gamma_{\theta,mol}\right),\:
+    \Gamma_S = \left(\Gamma_{S,turb} + \Gamma_{S,mol}\right)
 \end{equation}
@@
     \left[\Gamma_{\theta} - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(\theta_b-\theta_{\frac{1}{2}}\right) \label{eq:vflux_heat}\\
-    \overline{w'S'}_{b} =& -u_*
+    \overline{w''S''}_{b} =& -u_*
     \left[\Gamma_S - \Gamma_S \frac{S_b - S_{\frac{1}{2}}}{S_b}\right]\left(S_b-S_{\frac{1}{2}}\right) \label{eq:vflux_salt}
@@
 \begin{align}
-    \rho c_p \overline{w''\theta''}_{b,v} &= -\rho_w m L \label{eq:melt_1}\\
-    \rho \overline{w''S''}_{b,v} &= −\rho_w m S_b \label{eq:melt_2}\\
+    \rho c_p \overline{w''\theta''}_{b} &= -\rho_w m L \label{eq:melt_1}\\
+    \rho \overline{w''S''}_{b} &= −\rho_w m S_b \label{eq:melt_2}\\
     \theta_b &= \theta_f(p,S_b) \label{eq:melt_3}
@@
 It is noted by the PALM developers that this error was found to be small, but we have not confirmed this for the sub-ice case.
-This error would be small if the first $\sim$10\,\unit{cm} were largely a constant flux layer, as hypothesized by \citet{mcphee_turbulent_1983}.
+This error would be small if the first $\sim$10\,\unit{cm} were nearly a constant flux layer; \citet{mcphee_analytic_1981} hypothesized that the sub-ice surface layer would be nearly but not exactly a constant flux layer.
 
@@
 
+A schematic of the simulation domain is shown in Figure \ref{fig:schematic}.
+A list of parameter choices relevant to our simulations can be found in Table~S1.
 The domain is a 64 m$^3$ cube with horizontal resolution of 0.5\,\unit{m} and vertical resolution of 0.25\,\unit{m}.
@@
 
+\begin{figure*}[t]
+\includegraphics[width=6cm]{fig1_schematic.pdf}
+\caption{Schematic of the simulated ocean domain with background pressure gradient $\text{dp/dy}$.
+Purple arrow is oriented north and green arrow is aligned with gravitational acceleration.
+*The bottom boundary condition is Dirichlet, but there is also no flux as a result of damping.
+}
+\label{fig:schematic}
+\end{figure*}
+
 %\paragraph{Initial and boundary conditions}
-Boundary conditions for velocity, temperature and salinity are periodic at the side boundaries, Dirichlet at the bottom boundary, and von Neumann at the top boundary.
+We set von Neumann boundary conditions at the top boundary corresponding to the dynamic sub-grid momentum and scalar fluxes (Equations~\ref{eq:tau}, \ref{eq:vflux_heat}, and \ref{eq:vflux_salt}), as resolved fluxes go to zero at a no-penetration boundary.
+The roughness length ($z_0$ in Equations~\ref{eq:tau} and \ref{eq:gamma_turb}) is chosen such that the equivalent drag coefficient assuming quadratic drag is 0.003, an intermediate value for sea ice and ice shelf bottoms, though poorly constrained \citep{holland_modeling_1999, holland_effects_2006, macayeal_numerical_1984, nicholls_measurements_2006}.
+Boundary conditions are Dirichlet at the bottom boundary, set to the far-field temperature, salinity, and geostrophic velocity.
 The bottom third of the domain is a sponge layer (Rayleigh damping) within which velocity, temperature, and salinity are relaxed toward their assigned values at the bottom of the domain \citep{klemp_numerical_1978, maronga_parallelized_2015}.
 The sponge layer results in negligible vertical fluxes of heat, salt, or momentum across the bottom boundary because scalar and velocity gradients go to 0.
-The von Neumann boundary conditions at the top of the domain correspond to the sub-grid fluxes of heat, salt and momentum (Equations~\ref{eq:tau}, \ref{eq:vflux_heat}, and \ref{eq:vflux_salt}), as resolved fluxes go to zero at a no-penetration boundary.
-The roughness length ($z_0$ in Equations~\ref{eq:tau} and \ref{eq:gamma_turb}) is chosen such that the equivalent drag coefficient assuming quadratic drag is 0.003, an intermediate value for sea ice and ice shelf bottoms, though poorly constrained \citep{holland_modeling_1999, holland_effects_2006, macayeal_numerical_1984, nicholls_measurements_2006}.
-A list of parameter choices can be found in Table~S1.
+The flow is periodic along the x and y dimensions.
 
 We present two sets of simulations which have a base case in common.
-The base case has low far-field thermal driving of 0.15\unit{^{\circ}C} and a relatively high slope for Antarctic ice shelves of 1\unit{^{\circ}} and vigorous far-field inertial oscillations of 20\,\unit{cm\,s^{-1}} generated by a 0.03\,\unit{Pa\,m^{-1}} pressure gradient.
+The base case has low far-field thermal driving of 0.15\unit{^{\circ}C} and a slope of 1\unit{^{\circ}} and vigorous far-field inertial oscillations of 20\,\unit{cm\,s^{-1}} generated by a 0.03\,\unit{Pa\,m^{-1}} pressure gradient.
 These conditions were chosen to favor an energetic regime, for reasons discussed in Section~\ref{disc:dyn}.
@@
 
+We initiate turbulence over first 50\,min of the simulation with perturbations to the horizontal velocity components on the order of 0.01\,\unit{m s^{-1}}.
 The simulation duration is 50\,\unit{h}, corresponding to $\sim$4 inertial periods of 13\,\unit{h}.
+PALM employs adaptive timestepping; timesteps for the simulations presented here range from 0.5\,s to 2.75\,s after 2\,\unit{h}.
 By the end of our simulations, the time-mean kinetic energy of the flow has reached steady-state.
@@
 
+\subsection{Overview of the mean simulated state}
 % Description of time evolution
@@
 \begin{figure*}[t]
-\includegraphics[width=12cm]{fig1.pdf}
+\includegraphics[width=12cm]{fig1_rev1.pdf}
 \caption{Time evolution of (a,d) domain-averaged, resolved turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
@@
 
+\subsection{Turbulent kinetic energy budget}
+
 % TKE budget, shear
@@
 Since we evaluate resolved TKE ($e$), dissipation here represents the transfer of energy to the sub-grid scales; there is no flow of energy from sub-grid to resolved scales in the turbulence closure scheme.
-In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$\,\unit{m^2\,s^{-3}} as seen in Figure \ref{fig:timeseries}a,c.
+In these simulations TKE is not in steady-state, with an average  dissipation rate over the course of a simulation of $\mathcal{O}(10^{-11})$\,\unit{m^2\,s^{-3}} as seen in Figure \ref{fig:timeseries}a,d.
 Dissipation in the IOBL is on the same order as shear production ($10^{-9}$\,\unit{m^2\,s^{-3}}), as all other terms in the TKE budget are small.
@@
 
+\subsection{Boundary layer turbulence}
 % discuss turbulent structures
@@
 
+\subsection{Melting and its relation to thermal driving and slope}
 % Melt rate relationship with inertial period
+Average melt rates over the last inertial period range from 0.3--2.5\unit\,{m} (Fig.
+\ref{fig:timeseries}c,f) and average Monin-Obukhov lengthscales are 3--5\,\unit{m} (not shown).
 The dominant temporal frequency in melt rate is the inertial frequency, and the melt response to those oscillations is highly nonlinear.
 Maximum melt rates occur when the mean flow is oriented between the up-slope direction and the Coriolis-favored direction, and minimum melt rates roughly 180\unit{^{\circ}} opposed to that.
-These melt rate fluctuations correspond to fluctuations in TKE which are reflected in the friction velocity shown in Figure \ref{fig:timeseries}b.
+These melt rate fluctuations correspond to fluctuations in TKE which are reflected in the friction velocity shown in Figure \ref{fig:timeseries}b,e.
 The dominant contribution to turbulence is shear production of TKE, which changes its distribution with depth as the mean flow profile evolves.
@@
 
+\subsection{Vertical structure of turbulent fluxes}
+
 Vertical heat fluxes are shown in Figure \ref{fig:flux_profiles}b,e.
@@
 The linear scaling of melt rate with thermal driving suggests a linear scaling of heat flux profiles with thermal driving.
-We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (pink curves in Figures \ref{fig:timeseries}c, \ref{fig:flux_profiles}c).
+We find that this scaling largely collapses the four thermal driving profiles, with notable deviation from this shape for the run that experiences temporal gaps in shear stress during the analysis period (pink curves in Figures \ref{fig:timeseries}a, \ref{fig:flux_profiles}c).
 The shape of these profiles can be reasonably approximated by a linear decrease in the scaled heat flux with scaled depth over the boundary layer (Figure \ref{fig:flux_profiles}c).
@@
 The flux Richardson number, $\text{Ri}_f$, the ratio of buoyancy flux to shear-driven TKE production, provides a measure of mixing efficiency.
-The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.25$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \citep{armenio_investigation_2002, peltier_mixing_2003}.
+The simulated $\text{Ri}_f$ values of 0.05 -- 0.1 are well below the critical $\text{Ri}_f$ of $\sim\!0.25$, indicating that we are in the regime in which mixing efficiency ($\text{Ri}_f$) decreases with increasing stratification ($\text{Ri}_g$) \citep{miles_stability_1961, howard_note_1961, armenio_investigation_2002, peltier_mixing_2003}.
 This is consistent with our finding that the derived, 2\,\unit{m}-depth thermal exchange coefficient decreases for the high thermal driving cases which also achieve stronger IOBL stratification.
@@
 One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure~S7).
-On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}e,f).
+On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}d-f).
 Nonetheless we are able to find relationships between the vertical heat flux profiles and ocean temperature and slope that suggest predictability of the mean effects of turbulence despite the transience of these simulations.
@@
 In contrast, in sea-ice settings this sensitivity of melt rates to local thermal driving was found to be significantly smaller with an exponent of 0.38 \citep{ramudu_large_2018}.
-It's worth noting that our simulations do not capture the large scale increase in overturning circulation that accompanies a distant increase in thermal driving (i.e., changes to the water masses entering the ice-shelf cavity).
-The relationship between melt rate and distant thermal driving is a function of both the relationship between the local thermal driving and melt rate and the relationship between distant thermal driving and friction velocity \citep{holland_response_2008}.
-The former relationship is addressed by this study; the latter is only partially captured by the increase in IOBL velocity due to an increase in buoyancy while the far-field velocity remains constant.
-We note that the often cited quadratic relationship between thermal driving and melting pertains to this distant thermal driving  \citep{holland_response_2008}; studies generally find this exponent to be between 1.5 and 2 \citep{favier_assessment_2019, jourdain_ocean_2017, little_how_2009}.
+The relationship between average ice-shelf melt rates and the thermal driving for the cavity as a whole can be conceptualized in two components.
+The first is the relationship between the local thermal driving and melt rate, determined primarily by the local ocean turbulence.
+The second is the relationship between distant thermal driving (i.e., the water masses entering the ice-shelf cavity) and the strength of sub-ice-shelf circulation \citep{holland_response_2008}.
+Only the former is addressed by this study.
+Our simulations do not capture the large-scale increase in overturning circulation that accompanies an increase in distant thermal driving.
+Our simulations partially capture the increase in IOBL velocity due to an increase in thermal driving but the far-field velocity is unaffected.
+We note that the often cited quadratic relationship between distant thermal driving and melt rate involves both local turbulent processes and large-scale processes \citep{holland_response_2008}; studies generally find this exponent on distant thermal driving to be between 1.5 and 2 \citep{favier_assessment_2019, jourdain_ocean_2017, little_how_2009}.
 
@@
 
-\codeavailability{The modified version of PALM used for this study is currently under review at Los Alamos National Laboratory for open access release.}
+\codeavailability{The modified version of PALM used for this study is LANL Contributions to PALM, v1.0.0, available at https://github.com/lanl/palm_lanl.}
 
@@
 \begin{acknowledgements}
-This research was supported by the Los Alamos National
-Laboratory (LANL) through its Center for Space and Earth Science
-(CSES). CSES is funded by LANL’s Laboratory Directed Research
-and Development (LDRD) program under project number
-20210528CR.
+This research was supported by the Los Alamos National Laboratory (LANL) through its Center for Space and Earth Science (CSES).
+CSES is funded by LANL’s Laboratory Directed Research and Development (LDRD) program under project number 20210528CR.
 This research was also supported by the LDRD program of LANL under project numbers 20210289ER and 20180549ECR.

### 2021-10-06 Response_reviewers_rev1.tex

--- 2021-10-06 Response_reviewers_rev1.tex
@@
 It would be interesting to see how friction length changes over slope, assuming eddy viscousity is estimated as a product of friction velocity and mixing length.\\
-%XX
+\textit{Unfortunately, we have not output the 2-d friction velocity and momentum flux fields at the ice boundary necessary to compute a friction length as you define it.
+Furthermore, since the momentum fluxes at the boundary is defined by our subgrid near-wall scheme (Equation \ref{eq:tau}), you could express the friction length as
+$\frac{\kappa}{\Delta z}(\textrm{ln}\left(z_{\frac{1}{2}}/z_0\right)-\Psi_m\left(\zeta_{\frac{1}{2}}\right))^{-1}$.
+Thus, the friction length is chiefly a function of the Monin-Obukhov length.
+We can show how the Monin-Obukhov length varies with slope, as well as the ratio of resolved TKE 2m from the boundary to the friction velocity used by the near-wall scheme (figure below).
+However, we believe that this discussion is }
+\begin{figure}
+    \centering
+    \includegraphics[width=4in]{Figures/ol_eres_dslope_t43h_tav13h_fit.png}
+    \caption{Caption}
+    \label{fig:R1}
+\end{figure}
 

### 2021-10-06 SI_rev1.tex

\documentclass[tc, manuscript]{copernicus}

\setcounter{figure}{0}
\makeatletter 
\renewcommand{\thefigure}{S\arabic{figure}}

\begin{document}

\title{Supporting Information for ``Ice-shelf ocean boundary layer dynamics from large-eddy simulations"}

\runningtitle{IOBL dynamics}

\runningauthor{Begeman et al.}

\correspondence{Carolyn Begeman (cbegeman@lanl.gov)}

\Author[1]{Carolyn Branecky}{Begeman}
\Author[1]{Xylar}{Asay-Davis}
\Author[1]{Luke}{Van Roekel}

\affil[1]{Los Alamos National Laboratory, P.O. Box 1663, Los Alamos, New Mexico, USA 87545}

\firstpage{1}

\maketitle

\noindent\textbf{Contents of this file}

\noindent
Table S1. Parameter choices for simulations.\\
Figure S1. Results of the atmospheric stable boundary layer test case.
Figure S1. Vertical profiles of resolved and sub-grid vertical heat fluxes.\\
Figure S2. Vertical profiles of TKE budget terms for thermal driving simulations.\\
Figure S3. Vertical profiles of the ratio of vertical to horizontal variance.\\
Figure S4. Vertical profiles of sub-grid vertical diffusivities.\\
Figure S5. Vertical profiles of the total vertical salt flux.\\
Figure S6. Vertical profiles of the vertical eddy viscosity.\\
Figure S7. Relationship between thermal driving and melt rate over multiple inertial periods.

\clearpage

\begin{table*}[t]
\caption{Parameters relevant to the configuration of referenced simulations. Asterisks denote variables whose values were varied between simulations.}
\label{table:var}
\begin{tabular}{column = lcr}
\tophline
Variable & Description & Value\\
\middlehline
$c_d$       & drag coefficient          & 0.003 \\
$c_p$       & heat capacity of water    & 4218\\   
$dP/dx,dP/dy$   & horizontal pressure gradient & $0.0,0.03$ Pa m$^{-1}$\\
$dS/dz$     & far-field vertical salinity gradient & 0.5 PSU km$^{-1}$\\
$d\theta/dz$& far-field vertical temperature gradient & 0.1 $^{\circ}$C km$^{-1}$\\
$h_x,h_y$   & domain width              & 64 m\\
$h_z$       & domain height             & 64 m\\ 
$L_f$       & latent heat of fusion     & $3.3 \times 10^5$ J kg\textsuperscript{-1}\\
$P_0$       & domain top pressure       & 800 dbar\\
$Pr$        & Prandtl number            & 13.8\\
$rdf$       & Rayleigh damping coefficient & 0.0001\\
$S_{\infty}$& far-field salinity        & $35$ PSU \\
$Sc$        & Schmidt number            & 2432\\
$\alpha$    & *ice shelf slope          &$0.01$ to $1.0^{\circ}$ \\
$\beta$     & angle between vector oriented up-slope and North & 90$^{\circ}$\\
$\beta_m$   & Businger coefficient for momentum & $-4.8$ \\
$\beta_{\theta}$& Businger coefficient for temperature & $-5.6$ \\
$\beta_S$   & Businger coefficient for salinity & $-5.6$\\
$\Delta_x,\Delta_y$& horizontal resolution  & 0.5 m\\
$\Delta_z$  & vertical resolution       & 0.25 m\\
$\Gamma_{\theta,mol}$& thermal molecular exchange coefficient  & $12.5 \textrm{Pr}^{2/3} - 6$\\
$\Gamma_{S,mol}$& salt molecular exchange coefficient  & $12.5 \textrm{Sc}^{2/3} - 6$\\
$\Gamma_f$  & destabilizing transfer coefficient & $5.7 \times 10^{-3}$\\
$\phi$      & latitude                  & $-70^{\circ}$S \\
$\theta_{\infty}$& *far-field temperature& $-2.4$ to $-1.9^{\circ}$C \\
\bottomhline
\end{tabular}
\end{table*}

\begin{figure*}[t]
\includegraphics[width=15cm]{figA1.pdf}
\caption{Results of the atmospheric stable boundary layer test case presented in Abkar and Moin (2017) using PALM with the Anisotropic Minimum Dissipation (AMD) turbulence closure. Compare with their Figure 1.} 
\label{fig:validation}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width=12cm]{figS1.pdf}
\caption{Vertical heat flux depth-profiles averaged over one inertial period for (a,c) thermal driving simulations and (b,d) variable slope simulations. Profiles shown in (a,b) are averaged over the first inertial period after a 2\,\unit{h} spin-up, (b,d) over the last inertial period. Solid lines
represent the total flux, dashed resolved flux and dotted subgrid flux. Colors correspond to those shown in Figure 1.}
\label{fig:res_sgs_flux}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width=12cm]{figS2.pdf}
\caption{(a) Simulated turbulent kinetic energy for variable thermal driving simulations averaged over the last inertial period and (b-d) turbulent kinetic energy production terms over the same period. (b) Shear production. (c) Buoyancy production. The total buoyancy production is shown with solid lines, vertical component dashed, and upslope component dotted. (d) TKE transport. Positive denotes production, negative destruction. Note that the x-axis scales differ between panels.}
\label{fig:tke_budget_1}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width=12cm]{figS3.pdf}
\caption{Ratio of vertical to horizontal velocity variance for (a) thermal driving simulations and (b) variable slope simulations averaged over the last inertial period.}
\label{fig:vel_var_ratio}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width=12cm]{figS4.pdf}
\caption{Sub-grid vertical diffusivities for momentum (solid), heat (dashed) and salt (dotted) for (a) thermal driving simulations and (b) variable slope simulations. Heat and salt diffusivities curves are visually indistinguishable.}
\label{fig:k_all}
\end{figure*}

\begin{figure*}[t]
\includegraphics[width=12cm]{figS5.pdf}
\caption{Total vertical salt flux depth-profiles averaged over one inertial period for (a) thermal driving simulations and (b) variable slope simulations.}
\label{fig:saltflux}
\end{figure*}%

\begin{figure*}[t]
\includegraphics[width=12cm]{figS6.pdf}
\caption{Vertical eddy viscosity from (a) thermal driving simulations and (b) slope-varying simulations over the last inertial period. Depths below -20 m are not shown as the eddy viscosity is only used to compute the Ekman depth within the IOBL. }
\label{fig:km}
\end{figure*}

\begin{figure}[t]
\includegraphics[width=6cm]{figS7.pdf}
\caption{Relationship between far-field thermal driving and melt rate. This figure is the same as Figure 7a but values are averaged over each inertial cycle. The largest points correspond to the fourth and last inertial cycle with progressively smaller points for previous inertial cycles. }
\label{fig:melt_sensitivity_cycles}
\end{figure}

\end{document}

### 2021-10-06 vis_scripts/dT_sensitivity_fig.py
Add linefitting option to cross-plot

@@ -20,7 +20,9 @@ palm.plot_tseries_cross(diri, run, runlabel,
                         data_type = ['parameter','ts'],
                         tav=tav_ts, teval=[tprofile,tprofile],
                         plot_legend=False, legtitle = legtitle,
-                        figsize = figsize2, plot_cycles=True, 
+                        figsize = figsize2, 
+                        #plot_cycles=True, 
+                        fit_power_law = True,
                         col = colorVal, overwrite=True)
 #palm.plot_tseries_cross(diri, run, runlabel, 
 #                        plotvar = ['thermal_driving_infty','gamma_T_2m'], 

### 2021-10-06 vis_scripts/extract_var_palm.py
Changes to cross plotting routine to support ratio and depth choice

@@ -68,7 +68,7 @@ def extract_var(data,var_name,data_type='pr',ops=[],
                 yval=[9999.,9999.],zval=[9999.,9999.],
                 tunits = 'hr', tav = 0., 
                 varaxes = ['t'], p0 = 10., data_dir=''):
-    #print('extract_var',var_name,data_type,slice_obj)
+    print('extract_var',var_name,data_type,slice_obj)
     if data_type == 'pr':
         tav_native = 1.
     else:
@@ -89,13 +89,13 @@ def extract_var(data,var_name,data_type='pr',ops=[],
         var_name,data_type = grid_var(var_name,data_type=data_type,grid=grid)
     if (var_name == 'zE'):
         grid = 'z'#vartype[varlist.index(var_name)] 
-    if slice_obj == [] and data_type != 'parameter': 
-        #print('____slice_var called in extract_var for ',var_name)
+    if slice_obj == [] and data_type != 'parameter':
+        print('____slice_var called in extract_var for ',var_name)
         slice_obj,varaxes = slice_var(data,source_var[varlist.index(var_name)],data_type=data_type,
                                       tval = tval,
                                       xval=xval, yval=yval, zval=zval, grid=grid)
     if var_name in dervar:
-        #print('____derived_var called in extract_var for ',var_name)
+        print('____derived_var called in extract_var for ',var_name)
         slice_obj_der,_ = slice_var(data,source_var[varlist.index(var_name)],data_type=data_type)
         var1 = derived_var(data,var_name,
                            slice_obj_der,
@@ -109,6 +109,7 @@ def extract_var(data,var_name,data_type='pr',ops=[],
         var1 = data.variables[var_name][:]
     
     if tav > 0. and 't' in varaxes:
+        print('____time average in extract_var')
         #slice_obj_tav,_ = slice_var(data,source_var[varlist.index(var_name)],data_type=data_type,
         #                              tval = [tval[0] - tav/2., tval[1] + tav/2.],
         #                              xval=xval, yval=yval, zval=zval, grid=grid)
@@ -120,11 +121,12 @@ def extract_var(data,var_name,data_type='pr',ops=[],
         var1_shape = np.shape(var1)
         var1 = var1.data
         if len(var1_shape) == 2:#data_type == 'pr':
-            #print('shape tmask',np.shape(tmask))
-            #print('shape var1 tav',np.shape(var1))
-            #print('tmask',t[tmask])
[…]

### 2021-10-06 vis_scripts/plot_palm_mod.py

@@ -549,9 +549,11 @@ def plot_tseries(filedir, runname, plotvar,
 def plot_tseries_cross(filedir, runname, runlabel,
                        plotvar = ['us','melt'], data_type = ['ts','ts'],
                        teval = [-9999.,-9999.], tunits='hr', tav=0.,
+                       zeval = [9999.,9999.],
                        figsize = (6.4,4.8), plot_cycles=False,
                        plot_jenkins=False, fit_power_law=False,
                        plot_legend = True, legtitle='',
+                       x_ratio = False,
                        color_by_time = False, col = col, 
                        overwrite=False, outputdir = '', printformat = 'png'):
         
@@ -587,17 +589,26 @@ def plot_tseries_cross(filedir, runname, runlabel,
         y_var,y_axis_label = extract_var(y_data,plotvar[1],
                                          slice_obj=slice_obj_input,
                                          data_type=data_type[1],data_dir=diri,
-                                         tval=teval,tav=tav)
+                                         tval=teval,tav=tav,zval=zeval)
+        x_var_2,_ = extract_var(y_data,'u*',
+                                slice_obj=slice_obj_input,
+                                data_type=data_type[1],data_dir=diri,
+                                tval=teval,tav=tav,zval=zeval)
         x_data = load_data(diri,data_type=data_type[0])
         if data_type[0] != 'parameter':
-            slice_obj_x,varaxes = slice_var(x_data,'time',data_type=data_type[0],
-                                                tunits=tunits,tval=teval)
+            slice_obj_x,varaxes = slice_var(x_data,'e*',data_type=data_type[0],
+                                            tunits=tunits,tval=teval,zval=zeval)
+            #slice_obj_x,varaxes = slice_var(x_data,'time',data_type=data_type[0],
+            #                                tunits=tunits,tval=teval,zval=zeval)
         else:
             slice_obj_x = []
         x_var,x_axis_label = extract_var(x_data,plotvar[0],
                                          slice_obj=slice_obj_x,
                                          data_type=data_type[0],data_dir=diri,
-                                         tval=teval,tav=tav)
+                                         tval=teval,tav=tav,zval=zeval)
+        if x_ratio:
+            x_var = np.divide(x_var,x_var_2)
+            x_axis_label = r'$\textrm{TKE}_{-2m}/u_*$'
         data_all[0,i] = x_var[0]
         data_all[1,i] = y_var[0]
         if color_by_time:
[…]

### 2021-10-06 vis_scripts/var_param_palm.py

@@ -144,9 +144,9 @@ varlabel[varlist.index('drho_gswdz')]   = r'd\rho/dz'
 varlabel[varlist.index('dprho_gswdz')]  = r'd\sigma/dz'
 varlabel[varlist.index('dt')]           = r'\delta t'
 varlabel[varlist.index('e')]            = r'TKE\:SGS'
-#varlabel[varlist.index('e*')]           = r'TKE\:\textrm{resolved}'
 varlabel[varlist.index('E*')]           = r'\textrm{TKE}'
 varlabel[varlist.index('e*')]           = r'\textrm{TKE}'
+#varlabel[varlist.index('e*')]           = r'TKE\:\textrm{resolved}' Technically is the resolved TKE since AMD scheme does not measure sub-grid TKE
 varlabel[varlist.index('gamma_T_2m')]   = r'\Gamma_{T,der}'
 varlabel[varlist.index('gamma_T')]      = r'\Gamma_{T}'
 varlabel[varlist.index('gammaT')]       = r'\gamma_{T}'

### 2021-10-12 Response_reviewers_rev1.tex
Updates from Overleaf

@@
 
-\title{Response to reviewers for ``Ice-shelf ocean boundary layer dynamics from large-eddy simulations"}
+\title{Response to reviewers for ``Ice-shelf ocean boundary layer dynamics from large-eddy simulations''}
 
@@
 
-Abstract:
+Abstract:\vspace{12pt}
 
-Line 2: “Yet these small scale processes, which regulate heat transfer between….”\\
-Should be heat and salt transfer.\\
-\textit{The suggested change has been made.}
+Line 2: “Yet these small scale processes, which regulate heat transfer between….” Should be heat and salt transfer.\\
+\textit{The suggested change has been made.}\vspace{12pt}
 
-Introduction:
+Introduction:\vspace{12pt}
 
-Line 27: “….an overturning circulation known as “ice pump” “
-Could talk about the refreezing process.\\
+Line 27: “….an overturning circulation known as “ice pump” Could talk about the refreezing process.\\
 \textit{We have added the following sentence to this paragraph:}
+\begin{quote}
 ``Supercooling of the IOBL and frazil ice accretion to the ice-shelf base are also regionally important processes for cold cavities, but are not the focus of this work \citep{galton-fenzi_modeling_2012, jordan_conditional_2015}.''
+\end{quote}\vspace{12pt}
 
 Line 31: “ IOBLs present unique conditions in the global ocean, involving a stabilizing flux from phase change” The stabilizing flux mostly comes from the freshening of the boundary layer not from ‘phase-change’.\\
-\textit{We intended to specifically refer to the stabilizing buoyancy flux at the boundary associated with ice-shelf melting. We hope this revision is more clear:}\\
+\textit{We intended to specifically refer to the stabilizing buoyancy flux at the boundary associated with ice-shelf melting. We hope this revision is more clear:}
+\begin{quote}
 ``IOBLs present unique conditions in the global ocean, involving a stabilizing buoyancy flux from melting ice and a boundary layer that is positively buoyant against a sloping boundary.''    
+\end{quote}\vspace{12pt}
 
@@
 Please define ‘Intermediate scale’. Also to my knowledge Mondal et al., 2019 was a DNS study that resolved the Kolmogorov scale.\\
-\textit{We have avoided this vague term in our revision. The revised sentence reads:}\\
+\textit{We have avoided this vague term in our revision. The revised sentence reads:}
+\begin{quote}
 ``IOBL turbulence has been explored through laboratory experiments, direct numerical simulations, and large-eddy simulations \citep{middleton_numerical_2021, mondal_ablation_2019, vreugdenhil_stratification_2019, mcconnochie_dissolution_2018}.''
+\end{quote}\vspace{12pt}
 
@@
 \textit{This comment wasn't entirely clear to us.
-If the reviewer is referring to this study, it isn't the case that the Lewis number=1 either in the melt parameterization or the AMD turbulence closure model.}
+If the reviewer is referring to this study, it isn't the case that the Lewis number=1 either in the melt parameterization or the AMD turbulence closure model.}\vspace{12pt}
 
@@
 We can show how the Monin-Obukhov length varies with slope, as well as the ratio of resolved TKE 2m from the boundary to the friction velocity used by the near-wall scheme (figure below).
-However, we believe that this discussion is }
-\begin{figure}
+However, we interpret these relationships to be primarily driven by the relationships between slope, mean velocity (and TKE) of IOBL, and melt rate already discussed in the manuscript.}\vspace{12pt}
+\begin{figure}[h!]
     \centering
     \includegraphics[width=4in]{Figures/ol_eres_dslope_t43h_tav13h_fit.png}
-    \caption{Caption}
+    \caption{Relationship between Monin-Obukov length and the ratio of TKE at 2m below the boundary to the friction velocity evaluated at the boundary.
+All quantities are horizontally-averaged and time-averaged over the last inertial period.}
     \label{fig:R1}
@@
 
-Methods:
+Methods:\vspace{12pt}
 
 General Comment: I would love a schematic of the model set up.\\
-\textit{We have added a schematic figure, now labeled Figure 1.}
+\textit{We have added a schematic figure, now labeled Figure 1.}\vspace{12pt}
 
 Overview of the LES model: It would help the readers if you clearly mention whether you have used a linear or non-linear equation of state.\\
-\textit{Thanks for catching the omission. We have added the following text:}\\
+\textit{Thanks for catching the omission. We have added the following text:}
+\begin{quote}
 ``We use the nonlinear equation of state from  \citet{jackett_algorithms_2006} to compute densities.''
+\end{quote}\vspace{12pt}
 
-Simulation set-up:
+Simulation set-up:\vspace{12pt}
 
-Line 150: What about the time step?
+Line 150: What about the time step?\\
 \textit{We have added the following text:}
+\begin{quote}
 ``PALM employs adaptive timestepping; timesteps for the simulations presented here range from 0.5 s to 2.75 s after 2 h.''
+\end{quote}
 \textit{We also realized that the following information might be useful to the reader:}
+\begin{quote}
 ``We initiate turbulence over first 50 min of the simulation with perturbations to the horizontal velocity components on the order of 0.01 m/s.''
+\end{quote}\vspace{12pt}
 
-Line 167: I don’t think 1 degree is a relatively high slope for Antarctic ice-shelves.
+Line 167: I don’t think 1 degree is a relatively high slope for Antarctic ice-shelves.\\
 \textit{That's fair. We have deleted the judgment so that it now reads:}
+\begin{quote}
     ``and a slope of 1\unit{^{\circ}}''
+\end{quote}\vspace{12pt}
 
-Result:
+Result:\vspace{12pt}
 
-A plot with temporal evolution of melt rate, obukhov lengthscales could help the reader.
+A plot with temporal evolution of melt rate, obukhov lengthscales could help the reader.\\
 \textit{We have included a plot with the temporal evolution of melt rates, Figure 1 c,f.
@@
 However, we added the following text to provide some context for the reader:}
+\begin{quote}
     ``Average melt rates over the last inertial period range from 0.3--2.5\unit\,{m} (Fig. \ref{fig:timeseries}a,d) and average Monin-Obukhov lengthscales are 3--5\,\unit{m} (not shown).''
+\end{quote}\vspace{12pt}
 
-Discussion :
+Discussion:\vspace{12pt}
 
@@
 \textit{To make our point clear, we have rewritten the latter portion of this paragraph:}
+\begin{quote}
 ``The relationship between average ice-shelf melt rates and the thermal driving for the cavity as a whole can be conceptualized in two components.
@@
 We note that the often cited quadratic relationship between distant thermal driving and melt rate involves both local turbulent processes and large-scale processes \citep{holland_response_2008}; studies generally find this exponent on distant thermal driving to be between 1.5 and 2 \citep{favier_assessment_2019, jourdain_ocean_2017, little_how_2009}.''
+\end{quote}\vspace{12pt}
 
@@
 Although the method chosen in the paper (LES using relatively low resolution) gives the results of limited applicability, which is admitted by the authors, it provides some important insights.
-The manuscript can be published if the authors address the following points
+The manuscript can be published if the authors address the following points\vspace{12pt}
 
-Major points:
+Major points:\vspace{12pt}
 
-Section 2.3: Please add the figure illustrating simulation setup for your base case. Add more detail in this figure: currently even the sizes of the domain are not written anywhere.
-
+Section 2.3: Please add the figure illustrating simulation setup for your base case. Add more detail in this figure: currently even the sizes of the domain are not written anywhere.\\
 \textit{We have added a schematic figure (Figure 1).
 This text specifying the domain size was included in the original manuscript, but it would be easy to miss.
-With the new figure, it should be more visible}\\
+With the new figure, it should be more visible}
+\begin{quote}
 ``The domain is a 64 m$^3$ cube''
+\end{quote}\vspace{12pt}
 
@@
 It would be useful to have an idea how the chosen model works compared to other model (which one?
-Was it DNS or measurements or another LES model?).
-
+Was it DNS or measurements or another LES model?).\\
 \textit{We have added a figure to the supplemental materials (Figure S1) and the following text to the manuscript.
-We don't feel that too much information is needed about model set-up because we follow Abkar and Moin (2017) exactly.}\\
+We don't feel that too much information is needed about model set-up because we follow Abkar and Moin (2017) exactly.}
+\begin{quote}
 ``We validated our implementation against the stable atmospheric boundary layer test case published in \citet{abkar_large-eddy_2017} and \citet{stoll_large-eddy_2008}.
@@
 1 and references therein).''
+\end{quote}\vspace{12pt}
 
 L 150: How does the resolution influence the results? Why this particular resolution was chosen?
+\vspace{12pt}
 
-L 157-158: It would be helpful to write the boundary conditions explicitly, not just Dirichlet/von Neumann. 
+L 157-158: It would be helpful to write the boundary conditions explicitly, not just Dirichlet/von Neumann. \\
 \textit{We have modified this paragraph to explicitly state the boundary conditions, and rearrange some of the text accordingly. The relevant sentences are:}
+\begin{quote}
 ``We set von Neumann boundary conditions at the top boundary corresponding to the dynamic sub-grid momentum and scalar fluxes (Equations~\ref{eq:tau}, \ref{eq:vflux_heat}, and \ref{eq:vflux_salt}), as resolved fluxes go to zero at a no-penetration boundary.
@@
 The flow is periodic along the x and y dimensions.''
-If there is a flow developing along the ice face due to buoyancy, how justified is the use of the periodic boundary conditions?
+\end{quote}\vspace{12pt}
+
+If there is a flow developing along the ice face due to buoyancy, how justified is the use of the periodic boundary conditions?\\
 \textit{In the literature, periodic boundary conditions in the context of simulations of the IOBL have been employed either to represent the domain moving with the IOBL in a Lagrangian sense (Chen et al.
 2021.
-The Cryosphere Discussions.) or the domain remaining fixed in space and the periodic boundary conditions providing the opportunity for the development of turbulence and of equilibrium conditions (Vreugdenhil and Taylor, 2019; Rosevear et al.
-2021).
-We take the latter view, with the intent to bring the flow to equilibrium with the forcing by the end of the simulations.
+The Cryosphere Discussions.) or the domain remaining fixed in space with periodic boundary conditions that provide the opportunity for the development of turbulence and of equilibrium conditions (Vreugdenhil and Taylor, 2019; Rosevear et al., 2021).
+We take the latter approach, with the intent to bring the flow to equilibrium with the forcing by the end of the simulations.
 As discussed in Section 4.1, equilibrium was not achieved.
-}
+}\vspace{12pt}
 
-The whole Sec. 2.2, called ‘Turbulence closure’, is about boundary conditions at the ice-ocean interface.
+The whole Sec. 2.2, called ‘Turbulence closure’, is about boundary conditions at the ice-ocean interface.\\
 \textit{We agree that this may not be the clearest descriptor of this section.
-We move the first paragraph to the previous section and rename this section ``Boundary conditions for ice-shelf melting.''}
+We move the first paragraph to the previous section and rename this section ``Boundary conditions for ice-shelf melting.''}\vspace{12pt}
 
-Section Results should be split into smaller subsections with separate titles to make it more reader-friendly.
+Section Results should be split into smaller subsections with separate titles to make it more reader-friendly.\\
 \textit{Good suggestion.
-We have added the following subsections: Overview of the mean simulated state, Turbulent kinetic energy budget, Boundary layer turbulence, Melting and its relation to thermal driving and slope, Vertical structure of turbulent fluxes.}
+We have added the following subsections: Overview of the mean simulated state, Turbulent kinetic energy budget, Boundary layer turbulence, Melting and its relation to thermal driving and slope, Vertical structure of turbulent fluxes.}\vspace{12pt}
 
-Minor points:
+Minor points:\vspace{12pt}
 
-Please check the equations. Several equations have misprints:
-\textit{Thank you for reviewing the equations so carefully. We have made the changes you requested}
+Please check the equations. Several equations have misprints:\\
+\textit{Thank you for reviewing the equations so carefully. We have made the changes you requested}\vspace{12pt}
 
-Eq (1), rhs: 1st term: should be $x_j$ and not $x_i$; 3rd term: what does index g in $u_g$ mean?
+Eq (1), rhs: 1st term: should be $x_j$ and not $x_i$; 3rd term: what does index g in $u_g$ mean?\\
 \textit{We have added the following text to define $u_g$:}
+\begin{quote}
 ``The momentum terms on the right hand side of Equation \ref{eq:uprog} are, in order: advection, Coriolis forcing, imposed geostrophic flow with a geostrophic velocity $u_g$, ...''
+\end{quote}\vspace{12pt}
 
-Eq (3),(4): 2nd terms in the rhs: should be $u_j$ not $u_i$;
-\textit{Change has been made.}
+Eq (3),(4): 2nd terms in the rhs: should be $u_j$ not $u_i$;\\
+\textit{Change has been made.}\vspace{12pt}
 
-Eq (11): not clear, does this mean that gamma is the sum of the molecular and turbulent coefficients? 
+Eq (11): not clear, does this mean that gamma is the sum of the molecular and turbulent coefficients? \\
 \textit{The text has been modified to make this equation more clear:}
+\begin{quote}
 ``where the exchange coefficients are defined with two terms, one representing turbulent transfer within the turbulent surface layer and one representing molecular transfer within the viscous sublayer following \citet{mcphee_dynamics_1987} (their Equation 11):.''
-Why the form with power ‘-1’ is chosen if that power can be removed from this equation. In addition, I have not found this or similar expression in McPhee et al (1987), please clarify.
+\end{quote}\vspace{12pt}
+
+Why the form with power ‘-1’ is chosen if that power can be removed from this equation. In addition, I have not found this or similar expression in McPhee et al (1987), please clarify.\\
 \textit{The power of -1 was not necessary in these equations an has been removed.
 This form (without the -1 power) can be found in Equation 11 of McPhee et al.
-(1987) where the second term is the molecular contribution.}
+(1987) where the second term is the molecular contribution.}\vspace{12pt}
 
-Eq (14) $c_p$ should be removed, it makes the expression dimensionally inconsistent.
-\textit{Change has been made.}
+Eq (14) $c_p$ should be removed, it makes the expression dimensionally inconsistent.\\
+\textit{Change has been made.}\vspace{12pt}
 
-L 146: ‘It is noted by the PALM developers that this error was found to be small’ –please provide a reference here.
+L 146: ‘It is noted by the PALM developers that this error was found to be small’ –please provide a reference here.\\
 \textit{This note is embedded in the code itself.}
-\url{https://github.com/lanl/palm_lanl/blob/7f1444073b20ae81b451d4ab469d13e66b5358b7/trunk/SOURCE/surface_layer_fluxes_mod.f90#L2513-L2519}
+\url{https://github.com/lanl/palm_lanl/blob/7f1444073b20ae81b451d4ab469d13e66b5358b7/trunk/SOURCE/surface_layer_fluxes_mod.f90#L2513-L2519}\vspace{12pt}
 
-L 168: far field thermal driving is 0.15C, but in the figures elsewhere, there is no such case, only 0.1C. I believe one of those is a misprint.
+L 168: far field thermal driving is 0.15C, but in the figures elsewhere, there is no such case, only 0.1C. I believe one of those is a misprint.\vspace{12pt}
 
@@
 Clearly, if 10 cm were a constant flux layer, then the mentioned fluxes would be equal.
-What was hypothesized by McPhee?
+What was hypothesized by McPhee?\\
 \textit{We have edited the text to be a bit more specific about what we mean.
 We hoped to convey that the surface layer is thought to deviate only slightly from a constant flux layer.
-We also changed the citation to McPhee (1981), which contains this argument in more detail (though the 1983 paper provides the extension to scalar fluxes).}``This error would be small if the first $\sim$10\,\unit{cm} were nearly a constant flux layer; \citet{mcphee_analytic_1981} hypothesized that the sub-ice surface layer would be nearly but not exactly a constant flux layer.''
+We also changed the citation to McPhee (1981), which contains this argument in more detail (though the 1983 paper provides the extension to scalar fluxes).}
+\begin{quote}
+``This error would be small if the first $\sim$10\,\unit{cm} were nearly a constant flux layer; \citet{mcphee_analytic_1981} hypothesized that the sub-ice surface layer would be nearly but not exactly a constant flux layer.''
+\end{quote}\vspace{12pt}
 
 L 205: ‘thermal driving increases from 0.5 to 0.6C ’: there is no 0.5C case in the figure.
-XX
+XX\vspace{12pt}
 
-Fig. 1: the caption does not match the figure: (a) is not TKE but friction velocity etc.
-\textit{We have replaced figure 1 with the version with TKE in panels a,d.}
+Fig. 1: the caption does not match the figure: (a) is not TKE but friction velocity etc.\\
+\textit{We have replaced figure 1 with the version with TKE in panels a,d.}\vspace{12pt}
 
-L 347: critical gradient Richardson number for development of hydrodynamic instabilities, and further transition to turbulence, $Ri_g$=0.25, has been first obtained by Miles and Howard in 1961.
-\textit{Thanks for the tip. This reference has been added.}
+L 347: critical gradient Richardson number for development of hydrodynamic instabilities, and further transition to turbulence, $Ri_g$=0.25, has been first obtained by Miles and Howard in 1961.\\
+\textit{Thanks for the tip. This reference has been added.}\vspace{12pt}
 
 \section{Community comments}
-I believe sections 1 and 2 would benefit greatly from a figure showing a sketch of the simulated flow, and some relevant physical quantities and conditions, e.g. the angles alpha and beta, etc.
+I believe sections 1 and 2 would benefit greatly from a figure showing a sketch of the simulated flow, and some relevant physical quantities and conditions, e.g. the angles alpha and beta, etc.\\
+\textit{We have added a schematic figure, now labeled Figure 1.}\vspace{12pt}
 
-\textit{We have added a schematic figure, now labeled Figure 1.}
-
-Also, if I'm not mistaking, the numerical methods used by the LES solver are not discussed. They should at least be mentioned briefly.
+Also, if I'm not mistaking, the numerical methods used by the LES solver are not discussed. They should at least be mentioned briefly.\\
 \textit{This is a good suggestion, particularly as PALM has several methods available for advection, timestepping, and pressure. We have added the following text:}
+\begin{quote}
 ``We employ PALM's implementation of the \citet{piacsek_conservation_1970} second-order advection scheme for momentum and scalars and a third-order Runge-Kutta timestepping scheme.
 We also use the \citet{temperton_generalized_1992} Fast-Fourier Transform algorithm for the pressure solver.''
+\end{quote}\vspace{12pt}
 
 \subsection{Unsolicited changes}
-\textit{We have also added the following citations:}
+
+\textit{We have also added the following citations:}\\
 Rosevear XX

### 2021-10-12 main_rev1.tex
Updates from Overleaf

@@
 These mean buoyancy effects increase flow velocities on the order of a few \unit{cm\,s^{-1}} as slope varies from 0.01\unit{^{\circ}} to 1\unit{^{\circ}}.
-Flow velocities near the boundary increase on the order of 10\,\unit{cm\,s^{-1}} as far-field thermal driving increases from 0.5 to 0.6\unit{^{\circ}C} at 1\unit{^{\circ}} slope (Figure \ref{fig:dT_profiles}c).
+Flow velocities near the boundary increase on the order of 10\,\unit{cm\,s^{-1}} as far-field thermal driving increases from 0.4 to 0.6\unit{^{\circ}C} at 1\unit{^{\circ}} slope (Figure \ref{fig:dT_profiles}c).
 This velocity increase is attributed to changes in the magnitude of buoyancy forcing near the boundary, related to differences in melt rates.

### 2021-10-19 vis_scripts/cmp_res_basecase.py
Revise resolution figs

@@ -1,0 +1,75 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+import sys
+import numpy as np
+import matplotlib as pltlib
+import matplotlib.pyplot as plt
+import matplotlib.colors as colors
+import matplotlib.cm as cmx
+from math import log10
+from run_table_mod import value_from_namelist
+from var_param_palm import K0
+import cmocean as cmo
+import run_table_mod as table
+from var_param_palm import *
+from plot_param_palm import *
+import plot_palm_mod as palm
+from gsw import t_freezing, pt0_from_t
+
+pltlib.rc_file('rcparams.txt', use_default_template=True)
+sens_var = 'pt'
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+base_dir = ['/turquoise/usr/projects/climate/cbegeman/palm/jobs/',
+            '/lustre/scratch3/turquoise/cbegeman/palm/jobs/']
+filedir = ['test_ocean_melt_batch_dpdy_021','test_ocean_melt_batch_dpdy_021_hires']
+rundir='/RUN_ifort.grizzly_hdf5_mpirun_test_oceanml/'
+diri = [base_dir[i]+filedir[i]+rundir for i in range(2)]
+legtitle=r'Resolution (m)'
+linestyle = ['-']
+
+runlabel = [r'\Delta x,y=0.5, \Delta z=0.25',
+            r'\Delta x,y=0.25, \Delta z=0.125']
+run = ['dz1, dz0.5']
+tend = np.zeros((len(filedir),))
+for idx,i in enumerate(diri):
+    runfile = i + 'RUN_CONTROL'
+    tend[idx] = palm.end_time(runfile)/3600.
+
+tplot = np.min(tend)
+tcross = np.min(tend)
+
+tmin = 2.
+if tplot <2:
+   tmin = 0.
+tunits = 'hr'
+tmax = 50
+tav_pr = 13
+tav_ts = 13.
+tprofile = tplot-tav_pr/2
+
+xmid = 64.
+ymid = 64.
+zlim = [-5,1.]
+zmax = -2*64/3
+z_cfl = -2
+
+#plot_tseries  = False
+plot_cross    = False
+#plot_profiles = False
+plot_slices   = False
+plot_hovmoller = False
+
+plot_tseries   = True
+#plot_cross     = True
+plot_profiles  = True
[…]

### 2021-10-19 vis_scripts/figs_res_sensitivity.py

@@ -1,0 +1,35 @@
+# -*- coding: utf-8 -*-
+"""
+Spyder Editor
+
+This is a temporary script file.
+"""
+
+from extract_var_palm import load_data,extract_var
+import sys
+import plot_palm_mod as palm
+import numpy as np
+from cmp_res_basecase import *
+
+sys.path.append('/Users/cbegeman/Software_files/my_python_code/')
+
+plotvar_t = ['melt']
+plotvar_pr = ['sa','velocity','heatflux_z']
+norm_pr = ['' for i in plotvar_pr]
+if plot_tseries:
+    palm.plot_tseries(diri, run, plotvar_t, 
+                      runlabel=runlabel, tlim=[tmin,tplot], 
+                      linestyle=['None'], linewidth=0.,
+                      marker='.',
+                      figsize=figsize2)
+if plot_profiles:
+    palm.plot_pr(diri, run, ['pt'],
+                 runlabel=runlabel,  
+                 teval = [tprofile,tprofile], 
+                 ops=norm_pr, tav = tav_pr, 
+                 figsize=figsize3, zlim=[zmax,0], legtitle=legtitle)
+    palm.plot_pr(diri, run, plotvar_pr,
+                 runlabel=runlabel,  
+                 teval = [tprofile,tprofile], 
+                 ops=norm_pr, tav = tav_pr, 
+                 figsize=figsize3, zlim=[zmax,0], plot_legend=False)

### 2021-10-19 vis_scripts/plot_palm_mod.py

@@ -436,14 +436,15 @@ def plot_TS(filedir,runname,teval = [-9999.], tunits = 'hr',
 #   printformat plot file extension (optional). Defaults to png.
 #------------------------------------------------------------------------------
 def plot_tseries(filedir, runname, plotvar, 
-                 tlim = [9999.,9999.],tav=0.,tunits='hr',tshade = [9999,9999],
-                 ylim = [-9999,-9999], runlabel=[''], 
-                 leglocation = 'best', legtitle = '',legvar = '', plot_legend=True,
-                 col=col, linestyle = ['-'], marker = mk, figsize=(6.4,4.8),
-                 outputdir = [], overwrite=True, printformat = 'png'):
+                 tlim=[9999.,9999.],tav=0.,tunits='hr',tshade=[9999,9999],
+                 ylim=[-9999,-9999], runlabel=[''], 
+                 leglocation='best', legtitle='',legvar='', plot_legend=True,
+                 col=col, linestyle=['-'], linewidth=pv.lw1, marker=mk, figsize=(6.4,4.8),
+                 outputdir=[], overwrite=True, printformat='png'):
     
     if runlabel[0] == '':
         runlabel = runname
+    print(runlabel)
     if len(linestyle) < len(filedir):
         linestyle = [linestyle[0] for i in filedir]
 
@@ -511,8 +512,8 @@ def plot_tseries(filedir, runname, plotvar,
 
                ax.plot(t,var,label = ln_label,
                        marker = marker,markersize = 0.5,
-                       linestyle=linestyle[idx],
-                       linewidth=lw,color = col[idx])
+                       linestyle=linestyle[idx],linewidth=lw,
+                       color = col[idx])
 
         if plot_legend:
             ax.legend(loc=leglocation, bbox_to_anchor = (1,1), title=legtitle)

### 2021-10-19 SI_rev1.tex
Revisions for review round 1

@@
 
+\begin{figure}[t]
+\includegraphics[width=12cm]{figS8.pdf}
+\caption{Sensitivity of simulated mean state and turbulent fluxes to resolution.
+The vertical resolution is double the horizontal resolution ($\Delta x, \Delta y$).
+Results are averaged over the first inertial period after a 2\unit{h} spin-up.
+(a) Temperature.
+(b) Salinity.
+(c) Total vertical heat flux (solid), resolved vertical heat flux (dashed), and sub-grid vertical heat flux (dotted).
+(d) Velocity, u-component (solid) and v-component (dashed).}
+\label{fig:res_sensitivity}
+\end{figure}
+
 \begin{figure*}[t]
@@
 This figure is the same as Figure 7a but values are averaged over each inertial cycle.
-The largest points correspond to the fourth and last inertial cycle with progressively smaller points for previous inertial cycles.
-}
+The largest points correspond to the fourth and last inertial cycle with progressively smaller points for previous inertial cycles.}
 \label{fig:melt_sensitivity_cycles}

### 2021-10-19 main_rev1.tex
Revisions for review round 1

@@
 We follow \citet[]['s]{abkar_large-eddy_2017}'s model set-up exactly and chose their moderate resolution with 72 x 72 x 72 grid points.
-Our results are in good agreement with \citet[]['s]{abkar_large-eddy_2017} solution employing another LES model with AMD (boundary layer height differs by <10\%) and other LES models with different turbulence closures (Fig.
-S1, their Fig.
+Our results are in good agreement with \citet[]['s]{abkar_large-eddy_2017} solution employing another LES model with AMD (boundary layer height differs by <10\%) and other LES models with different turbulence closures (Figure~S1, their Fig.
 1 and references therein).
@@
 We do not continue our simulations beyond 4 inertial periods in the hope of reaching steady-state conditions because the increase in stratification reduces the turbulent length scales and necessitates higher model resolution than we could computationally afford.
-Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes by at least a factor of two, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure~S1).
-Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE has been lost ($\leq\!0.1$\unit{^{\circ}C} slopes, Figure~S1d).
+Our simulations generally show resolved turbulent fluxes exceeding subgrid turbulent fluxes by at least a factor of two, but subgrid turbulent fluxes dominate within several meters of the ice base where the stratification is strongest (Figure~S2).
+Resolved turbulent fluxes are also comparable to subgrid turbulent fluxes late in the simulation of low slope cases after significant TKE has been lost ($\leq\!0.1$\unit{^{\circ}C} slopes, Figure~S2d).
+We evaluated the effects of doubling both horizontal and vertical resolution in a separate simulation with an otherwise identical set-up to the base case, run for one inertial period after spin-up.
+While a greater portion of the vertical heat fluxes was resolved as expected, the melt rate averaged over one inertial period only increased by 7\% and differences in the mean state were sufficiently small to justify the use of our standard resolution (Figure~S3).
 
 \begin{figure*}[t]
-\includegraphics[width=12cm]{fig1_rev1.pdf}
+\includegraphics[width=12cm]{fig1.pdf}
 \caption{Time evolution of (a,d) domain-averaged, resolved turbulence kinetic energy (TKE), (b,e) melt rate and (c,f) friction velocity for (a-c) thermal driving simulations and (d-f) variable slope simulations.
@@
 Here, we characterize the evolution of resolved TKE and primes designate resolved fluctuations.
-Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure~S2 and shows similar patterns.
+Figure \ref{fig:tke_budget}b-d shows the source terms in this budget for the variable slope simulations; the analogous figure for the thermal driving simulations is Figure~S4 and shows similar patterns.
 Shear production ($F_{shear}$) ranges from $\sim 10^{-9} \textrm{--} 10^{-8}$\,\unit{m^2\,s^{-3}} with a maximum at the ice-ocean interface and local maxima in the upslope flow within 5\,\unit{m} of the boundary (Figure \ref{fig:tke_budget}a).
@@
 The structures become increasingly filamentous (i.e., near-wall streaks, e.g., \citet{del_alamo_spectra_2003, hoyas_scaling_2006}) and coherent as slope and thus the velocity of the buoyancy-driven current increase.
-Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases; velocity fluctuations are less confined to the slope-parallel direction (Figure~S3).
+Since the stratification decreases with increasing slope, the ratio of vertical to horizontal velocity variance also increases; velocity fluctuations are less confined to the slope-parallel direction (Figure~S5).
 
@@
 \includegraphics[width=12cm]{fig6.pdf}
-\caption{Horizontally-averaged turbulence characteristics for (a) 0.1\unit{^{\circ}C} thermal driving, 0.01\unit{^{\circ}} slope case and (b) 0.6\unit{^{\circ}C} thermal driving, 1\unit{^{\circ}} slope case.
+\caption{Horizontally-averaged turbulence characteristics for (a) 0.15\unit{^{\circ}C} thermal driving, 0.01\unit{^{\circ}} slope case and (b) 0.6\unit{^{\circ}C} thermal driving, 1\unit{^{\circ}} slope case.
 Turbulence is considered intermittent when the dissipation contour of $10^{-9}$\,\unit{m^2\,s^{-3}} (dashed line) reaches the boundary.
@@
 The vertical heat flux has a maximum at the ice-ocean interface and decreases throughout the IOBL, with small values below the pycnocline.
-Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure~S4).
-The vertical salt flux profiles are shown in Figure~S5 and have a very similar shape to the vertical heat flux profiles.
+Since the IOBL is fully turbulent (with the exception of some intermittency discussed below), the sub-grid diffusivities of momentum, heat and salt closely resemble one another (Figure~S6).
+The vertical salt flux profiles are shown in Figure~S7 and have a very similar shape to the vertical heat flux profiles.
 
@@
 \end{equation}
-$K_e$ profiles are shown in Figure~S6.
+$K_e$ profiles are shown in Figure~S8.
 
@@
 However, we believe that our transient solutions do provide some indications of how melt rates and boundary layer properties depend on ocean temperature and ice-shelf slopes.
-One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure~S7).
+One justification for this belief is that the simulated sensitivity of melt rate to ocean temperature remains consistently linear through all inertial periods simulated (Figure~S9).
 On the other hand, the differently sloped simulations continue to diverge at the end of the simulation as the IOBL accelerates (Figure \ref{fig:timeseries}d-f).
@@
 This enhanced turbulent efficiency is due to enhanced shear instabilities, and is reflected in turbulent diffusivities parameterized by the AMD scheme.
-Much greater variability in sub-grid turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure~S4).
+Much greater variability in sub-grid turbulent diffusivities is seen over the variation in slope than the variation in thermal driving tested here (Figure~S6).
 

### 2021-10-19 Response_reviewers_rev1.tex

@@
 L 150: How does the resolution influence the results? Why this particular resolution was chosen?
+\textit{We chose this resolution as the highest we could afford for this parameter study while achieving similar behavior to higher resolution simulations.
+We conducted one simulation at twice the resolution and compared the results, now described in the following text and a supplemental figure.}
+\begin{quote}
+``We evaluated the effects of doubling both horizontal and vertical resolution in a separate simulation with an otherwise identical set-up to the base case, run for one inertial period after spin-up.
+While a greater portion of the vertical heat fluxes was resolved as expected, the melt rate averaged over one inertial period only increased by 7\% and differences in the mean state were sufficiently small to justify the use of our standard resolution (Figure~S2).''
+\end{quote}
 \vspace{12pt}
@@
 
-L 168: far field thermal driving is 0.15C, but in the figures elsewhere, there is no such case, only 0.1C. I believe one of those is a misprint.\vspace{12pt}
+L 168: far field thermal driving is 0.15C, but in the figures elsewhere, there is no such case, only 0.1C. I believe one of those is a misprint.
+It was actually the legend of these figures that was not shown with sufficient precision. We have increased the precision such that the 0.15C case is labeled appropriately in all figures.
+\vspace{12pt}
 
@@
 L 205: ‘thermal driving increases from 0.5 to 0.6C ’: there is no 0.5C case in the figure.
-XX\vspace{12pt}
+\textit{We have corrected this typo to refer to the 0.4C thermal driving case.}
+\vspace{12pt}
 
